### 2023-02-06 demog-analysis.tex
Initial Overleaf Import

 \subsection{Doing Old Things with Micro-Genres}
 The link clustering procedure yields a ``new'' data set out of the old. Instead, of 2263 people choosing 20 vague macro-genre labels, we now have the same 2263 people, but their choices have been distilled and focused on 111 micro-genres. Since this is still a plain old survey data set, with people in the rows and micro-genres in the columns, we can perform some of the same old tricks (Factor Analysis, Latent Class Analysis, Multiple Correspondence Analysis) as before. But this time, the results will be more revealing, because we have honed in a bit closer upon the actual object that people made a taste judgment on and engage in their everyday musical listening practices. In addition, applying old techniques in this new data is likely to yield insights (e.g., combinations and classifications of micro-genres) that will not simply reproduce the standard findings of the past (e.g., clumping of vague macro-genre labels into even vaguer ``discourses'' like highbrow, pop, folk, and the like).

 To show this, Figure~\ref{fig:mca-micro} displays what happens when we subject the new $2263 \times 111$ matrix to Multiple Correspondence Analysis. Because now we have 111 points (positive ``yes'' modalities) to worry about, I used hierarchical clustering on the MCA dimensions to clump the micro-genre points in the MCA space. Labels rendered in the same color are in the same cluster, suggesting that people tend to choose them together.

 Note that the resulting picture (compared to Figure~\ref{fig:mca}) is now richer and more complex. Micro-genres trade focus for ``legibility'' at least when it comes to vague macro-genre clumps. However, this does not mean that there no interpretable results. On the contrary, it just means that there are \textit{more} interpretable results. For instance, take the clump of genres that dominates the first (horizontal) dimension of the MCA space micro-genre classification. Here, we see all the macro-genre labels represented in close proximity (indicating people tend to choose all these micro-genres in tandem. The micro-genres in this region of the space (as given by their low number designation) tend to have the largest audiences of their kind (with signal exceptions such as Rap, Country, and Jazz). This, therefore indicates micro-genres that go together due to a rather indiscriminate mixing of styles, indicative of a \textit{type} (but not the only type) of ``omnivorousness.''

  \begin{figure}[ht!]
 \centering
 \includegraphics[width=0.9\textwidth]{Figs/Link Clust/micro-genre-mca.png}
 \caption{Multiple Correspondence Analysis of Micro-Genre Data. Upper panel shows the Euclidean space formed by the first two dimensions, and the lower panel shows the space corresponding to the third and fourth dimensions. Micro-genres are hierarchically clustered (using Ward's criterion) into 17 clusters (see inset) based on their proximity in the four-dimensional MCA space. Micro-genre labels in the plot belonging to the same cluster are rendered in the same color.}
  \label{fig:mca-micro}
 \end{figure}

 Other regions display more focused clumpings of micro-genre styles, but ones that are not easily interpretable using the usual macro-categories. Toward the top of the upper panel, we see a combination of genres usual classified as ``contemporary'' or ``youth'' but also containing Classic Rock. Immediately below this clump, we see a three-micro genre cluster featuring both Classic and contemporary rock styles. In the lower panel of the figure, showing the space formed by the third and fourth dimensions, we see other interesting micro-genre mixtures. Toward the top, a micro-genre cluster composed of traditional ``high status'' genres like Classical music, but also featuring two country micro-genres and classic rock. As we will see below, this Classical micro-genre (``Classical\_3''), tends to feature individuals who do not mind making many choices.

\section{Demographic Profiles of Micro-genre Communities}
We could continue trying to derive novel ``discourses'' of taste by looking at micro-genre clumps in the MCA space. Suffice to say that these are probably not going to look like the ones that have usually been noted in the literature (although some might). However, as noted, the core feature of the link clustering algorithm for discovering genre communities is that takes somewhat fuzzy and vaguely defined macro-genre labels (e.g., ``Classical,'' ``Classic Rocks/Oldies,'' ``Country,'' or ``Pop'') and decomposes them into more focused micro-genre communities. The remaining question is whether these micro-genres are valid, in terms of attracting systematically different types of people. To show this, I follow the venerable principle of audience segmentation to verify the validity of the procedure to discover interpretable micro-genres \citep{peterson92}.

\subsection{Classical}

 \begin{figure}[ht!]
 \centering
 \includegraphics[width=1.0\textwidth]{figs/demog-plots/Classical.png}
 \caption{}
  \label{fig:classical}
 \end{figure}

Figure~\ref{fig:classical} shows the demographic profiles for the eight ``Classical'' micro-genres discovered by the link clustering procedure. Demographic profiles are depicted as the predicted probabilities (and associated confidence intervals around these estimates) obtained from a logistic regression of the relevant sociodemographic characteristic (in this case, education (red), age (mustard), ethnoracial identification (green), subjective class identification (teal), gender (blue), and region of residence (purple), along with a categorical breakdown of the total number of genres chosen (pink)) against the log odds of having chosen that particular micro-genre \citep{king_etal00}.

 \begin{figure}[ht!]
 \centering
 \includegraphics[width=1.0\textwidth]{figs/demog-plots/Opera.png}
 \caption{}
  \label{fig:opera}
 \end{figure}

The first Classical micro-genre ($N=127$), picks up a micro-genre that appeals to the Classical music ``univore.'' This person is likely to be old, likely to be a man living in a New England state; some of us have perhaps met this person and can imagine what version of Classical music this is (likely to be the most stereotyped around the established canon \citep{kremp10}). The second Classical micro-genre ($N = 116$,) seems like what is seen as the prototypical consumer of Classical music \citep{lizardo_skiles16}. This person is likely to be older, hold and advanced degree, be white and identify as middle class. Interestingly, other micro-genre variations of Classical picked by the analysis (3, 5, 7, and 8) capture variations of Classical music that also appeal to older, highly educated people; interestingly, these other Classical musics differ from the last variant with respect to the other markers of social position. The third Classical micro-genre (($N = 100$) is characterized by extreme omnivorousness by volume; the fifth micro-genre ($N = 75$) is distinguished by the fact that the people who choose it are men who are also likely to identify as ``Upper Class'' (a rare designation in the U.S. case). The seventh micro-genre ($N = 51$) is inordinately likely to be consumed by Asian respondents, while the eighth, and smallest, micro-genre ($N = 32$) is more likely to attract nonwhite respondents. The link clustering approach can thus recover micro-genre communities that appeal to ethnoracial minorities even in the case of a stereotypically ``white'' macro-genre label such as Classical \citep{lizardo_skiles16}. The remaining Classical micro-genres have demographic profiles that deviate from the stereotypical Classical music consumer. People attracted to the fourth Classical micro-genre ($N = 96$) are young omnivores, while those choosing the sixth variation ($N = 72$) are middle-aged New Englanders who are either white or multiracial.

\subsection{Opera}

Not all macro-genre labels are decomposed into a multiplicity of micro-genres. Take the case of Opera, shown in Figure~\ref{fig:opera}. The link clustering procedure discovers only two micro-genre variations in this case. A version chosen by omnivorous respondents who choose a multiplicity of other genres (and who are also younger, identify as upper class and are likely to be multiracial)and a micro-genre that looks a look like the stereotype; older, highly educated, upper/middle-class person. This suggests that, save for the version chosen by omnivores, the macro-genre label ``Opera'' already gets at a relationally focused micro-genre. A situation very different from ``Classical.'' This puts into question the common strategy of treating these two macro-genre labels as equivalent indicators of an overall ``highbrow'' dispositions. As we have seen, while some versions of Classical do fit that bill in terms of their sociodemographic profile, others certainly do not.

 \begin{figure}[ht!]
 \centering
 \includegraphics[width=1.0\textwidth]{figs/demog-plots/Jazz.png}
 \caption{}
  \label{fig:jazz}
 \end{figure}

 \subsection{Jazz}

The case of Jazz is an instructive one for the link clustering procedure, given the complex historical trajectory of the genre. It began as an ``artistic'' (expert performer-driven and focused) genre in the Black art world in the early 20th century, diffusing into both Black middle and working-class consumer communities and white aesthetic (both performer and consumer-driven) circles by mid-century, and then legitimized as a high art form in conservatories later on \citep[see][]{lopes02}. Accordingly, ``Jazz'' has always been suspected of being the ultimate multivocal macro-genre labels, condensing complex dynamics of ethnoracial, social class, and generational status. Whatever it may be, ``Jazz'' is simply not a single kind of thing and thus represents one of the linchpins of the macro-genre label critique.

The link clustering analysis shown in Figure~\ref{fig:jazz}, agrees; but with a caveat. Split into relationally structured micro-genres, Jazz is not a single thing, but neither is it an unruly multiplicity of unrelated things. Instead, it seems to be a small collection, summarizing in the synchrony of respondent choices in 2012, the complex history alluded to. In that respect, the micro-genre approach can tell the difference between the Jazz variant appealing to mainly white, older, highly educated New Englanders (version 5, $N = 59$), perhaps the aestheticized and institutionalized conservatory version, and the one whose primary marker is appeal to middle-aged Black respondents who mainly reside in the American south, but otherwise lacking a strong education gradient (version 6, $N = 37$). Interestingly, there is also a version of Jazz (version 3, $N = 104$) that has a strong education gradient and a relatively weak relationship with age, that primarily appeals to non-white audiences. This version is also the most gendered, and univorous being more likely to be engaged in by men who do not choose a wide variety of other genres. Finally, in addition to two omnivorous versions (versions 3, 4) we discover one ultimate ``middlebrow'' version of Jazz, largest of micro-genre communities identified (version 1,$N = 144$); this genre appeals to middle-aged respondents with equally middling education levels who identify as middle class; Jazz as ``cultural goodwill'' \citep{bourdieu84}.

 \begin{figure}[ht!]
 \centering
 \includegraphics[width=1.0\textwidth]{figs/demog-plots/Rap_Hip_Hop.png}
 \caption{}
  \label{fig:rap}
 \end{figure}

\subsection{Rap/Hip Hop}
While not having as long a career as Jazz or the Blues, Rap/Hip Hop has also endured vicissitudes as its sociological genre bases have been transformed from its inception as a ``scene'' genre in the late 1970s, followed by a slow proliferation into geographically segmented scenes in the 1980s and 1990s, its slow and hesitant uptake by industry during the same period, and its emergence as a full-fledged industry-backed ``pop'' genre in the 21st century. Throughout, however, the strong association of Rap with young, Black, male performers and associated audiences (a situation that is in the process of being undone in the last decade or so with the emergence of powerful, iconic women rap performers with a strong foothold in industry) is one that is hard to shake \citep{lizardo_skiles16}.

The micro-genre analysis, shown in Figure~\ref{fig:rap} discovers six variations, producing results that both support and contravene those expectations. Regarding the latter, none of the micro-variations of rap are strongly gendered, suggesting that this is not a powerful principle of audience segmentation here. On other hand, age/generation is such a powerful principle with rap audiences across all six micro-genres all of which are more likely to appeal to young people. The only difference is the {\em strength} of the age effect, being strongest for variations 1, 2, and 3 ($N=164$, $N=84$, and $N=78$, respectively), and weaker for 4, 5, and 6 ($N=70$, $N=63$, and $N=57$, respectively). Variation 1, featuring the largest audience size, also features the least ethnoracial differentiation (save for the ``most omnivorous'' variation 4), and a penchant to combine with other genres; this suggests that this variation picks up the ``industry'' version of Hip Hop that presents itself today as radio-friendly pop music. This seems to stand opposed to variation 6; this is the smallest rap micro-genre, it has the strongest tilt toward Black, young audiences, and features the lowest propensity to be combined with other genres. Variation 5 is just like this last one, except that it features a strong tilt toward audiences without a college degree and a higher propensity to mix with other genres.

One issue, in the wake of the emergence of Rap and Hip Hop as general pop culture genres, is the extent to which some micro-variations appeal to non-Black audiences. The link clustering procedure can tell the difference, producing a micro-genre variation (2) that is much less likely to appeal to Black audiences and more likely to appeal to those who identify as ``Hispanic'' or ``multiracial'' (perhaps picking up ethnolinguistic variants of Hip Hop). In the same way, Neither variation 3 or 4 (along with 1 as already discussed) exhibit as strong a tilt toward Black audiences as 2, 5, and 6. Suggesting that audience segmentation along ethnoracial identity is strong within Rap/Hip Hop micro-genres despite the relatively weaker levels of segmentation along education or generational lines.

\subsection{Gospel/Religious}
The macro-genre fuzzy label ``Gospel/Religious'' is a lot like Jazz, in the sense that analysts know that it mixes micro-genre variations with distinct racialized audiences. As shown in Figure~\ref{fig:gospel}, the link clustering approach breaks this confounding, discovering three variations of Gospel primarily engaged in by Black people (1, 3 and 5) and one that primarily appeal to white people (4, $N = 86$), all of whom are likely to live the American South. Two of the Black gospel communities are mainly differentiated by age, with version 3 to working-class adults, and version 4 mainly appealing to middle class older people; both Black and white Gospel/Religious micro-genres are more likely to be engaged in by women. Version 1 is a Black Gospel univore community, and version 5 $N = 103$ is the omnivore micro-genre variation (which exists for all genres).

 \begin{figure}[ht!]
 \centering
 \includegraphics[width=1.0\textwidth]{figs/demog-plots/Gospel.png}
 \caption{}
  \label{fig:gospel}
 \end{figure}

\subsection{Latin/Spanish/Salsa}
Even when macro-genre labels point to styles with some level of presumed audience homogeneity around specific markers (e.g., ethnoracial status), the link micro-genre community approach can discover variations that differ in terms of other social markers. The (already hybrid) macro-genre label ``Latin/Spanish/Salsa'' is a good case in point (see Figure~\ref{fig:latin}). This macro-genre splits into five variations; all are overwhelmingly more likely to be engaged by people who identify as Hispanic (except for 3 which also attract people who identify as multiracial or ``other''). Yet, they differ on key characteristics that cut across ethnic identification. Versions 1, 3, and 4 are more likely to attract young people of middling education, but those who prefer 1 and 3 more likely to combine this engagement with engagement of other genres. The second Latin micro-genre variation, on the other hand, appeals to middle-age people (mainly women) who have more education and identify as middle class.

 \begin{figure}[ht!]
 \centering
 \includegraphics[width=1.0\textwidth]{figs/demog-plots/Latin.png}
 \caption{}
  \label{fig:latin}
 \end{figure}

 \subsection{Heavy Metal}
Previous studies in the sociology of taste show that no genre is more polarizing than Heavy Metal. Even the most ``tolerant'' of omnivores have no problem expressing dislike of it. Mass stereotypes of the genre \citep{lizardo_skiles16}, show it to be associated with less educated, ``lower'' or working-class young white men, which accounts for its persistent role as a resource for symbolic boundary drawing, as encoded in the title of Bryson's \citeyearpar{bryson96} classic paper. But in (liking or rejecting) Metal, are Americans affiliating or disaffiliating from a single monolithic thing? As shown in Figure~\ref{fig:metal}, the micro-genre analysis discovers four variations of the ``heavy metal'' micro-genre. These results show support for the idea of ``Heavy Metal'' being one of the most socio-demographically consistent genres, but also show important \textit{generational} variations in its micro-instantiations. On the consistency side, the sociodemographic reality of engagement seems to conform to stereotypical perceptions. Heavy Metal is gendered, racialized, and classed.

  \begin{figure}[ht!]
     \centering
     \includegraphics[width=1.0\textwidth]{figs/demog-plots/Heavy_Metal.png}
     \caption{}
  \label{fig:metal}
 \end{figure}

Men are more likely to engage all micro-genre variants more than women, consistent with previous work pointing to the strong gendering of the genre \citep{miller2016gender}. The only difference, among the four micro-genres uncovered is the size of the men-to-women disparity. For instance, ``Heavy\_Metal 3" ($N = 75$) is the most tilted toward men, while variations 1 ($N=89$) and 4 ($N=70$) are less so. White respondents are more likely to engage all four micro-genre variations, but so are those who classify themselves as ``multiracial or other," especially for the Metal micro-variation that mixes well with other genres (although the relatively small number of these respondents does not lead to very precise estimates). Surprisingly, for three of the four variations (excepting 4), respondents how identify as Hispanic are statistically more likely to engage the genre than Black respondents. In the same way, for three of the four variations, Metal fans are less likely to have a college degree, although variant 2 ($N = 88$) shows a tilt toward middling (e.g., ``some college'') levels of education. Interestingly, this is also the micro-genre that has the highest concentration of middle-aged adult respondents (e.g., people in their 40s and 50s). The subjective class identification of Metal fans does controvert that projected to them by others; while it is true that some micro-variations are likely to feature people who identify as either lower or working class, they are likely to contain statistically indistinguishable proportions of people who identify as middle class.

\subsection{Classic Rock/Oldies}
Perhaps the test case for the misleading nature of the macro-genre label approach are composite or vague labels like ``Classic Rock/Oldies.'' The suspicion is that such a vague designation hides a wide variety of more focused and perhaps stylistically and demographically disjoint micro-genres. The link-community approach produces results consistent with this claim. This macro-genre label (the most ``popular'' in terms of audience size in the original data) is also the one that splits into the largest number (thirteen) of micro-genres, shown in Figures~\ref{fig:Class-Rock1}, and~\ref{fig:Class-Rock2}. These vary substantially in terms of all the sociodemographic indicators considered.

\begin{figure}[ht!]
    \centering
     \begin{subfigure}[b]{0.8\textwidth}
        \includegraphics[width=1.0\textwidth]{figs/demog-plots/Classic_Rock1.png}
        \caption{}
        \label{fig:Class-Rock1}
    \end{subfigure} 
     \begin{subfigure}[b]{0.8\textwidth}
        \includegraphics[width=1.0\textwidth]{figs/demog-plots/Classic_Rock2.png}
        \caption{}
        \label{fig:Class-Rock2}
    \end{subfigure}
     \caption{}
  \label{fig:Class-Rock}
 \end{figure}

The largest community (version 1, $N = 149$) depicts the Classic Rock univore; a middle-aged white person who resides in the Midwest, Southwest or Mountain West with less than a high-school education. The second-largest Classic Rock micro-genre ($N = 139$ is a lot like the first, except that the tilt to older respondents is much stronger as is concentration among respondents who either finished high school or received some college education. But perhaps the prototypical Classic Rock micro-genre is version 6 ($N = 76$), appealing to older respondents very much likely to identify as both white and working class, with relatively low education, who reside in the Mountain and Southwest region.

Some of the smaller micro-genre communities controvert the usual expectations as to who is the typical Classic Rock/Oldies fan \citep{lizardo_skiles16}. For instance, people who engage variation 9 ($N = 60$) are of low education (which is expected), but they are also likely to be very young, working or middle class-identified Hispanics with less than a high school education and live in the Southwest. Version 10 ($N = 55$ is a lot like this last one, but concentrates among respondents with some college attainment; yet another variant of this micro-genre (version 13, $N = 31$) tilts toward middle-aged Hispanic-identified women who live on either coast.\footnote{Perhaps these last set of respondents understand ``Classic Rock'' to include such long existing American genres as ``Tex-Mex.''} There is even a version of Classic Rock that contravenes socioeconomic, gender, and regional expectations, appealing to middle-class, highly educated women who identify as white and live in New England (version 8, $N = 32$).

\subsection{Pop/Top 40}
As shown in Figure~\ref{fig:Pop}, landscape of the very vague macro-genre label ``Pop/Top 40,'' presents as variegated a landscape as that presented by Classic Rock, with ten micro-genre versions. There are consistent (and expected) patterns. In terms of age distribution, Pop micro-genres communities tilt toward the very young (3, 5, and 10, $N=104$, $N=95$, and $N=17$, respectively) or toward young adults (1, 2, $N=143$ and $N=126$). The rest are either age-neutral (7, 8, 9, $N=64$, $N=43$, and $N=30$, respectively) and only two  (4, 6, $N=102$, $N=71$) tilt toward or are preferred by people in their 40s and 50s. None concentrate among older respondents. The very young pop micro-genres communities are differentiated by class: Version 3 is low education, working class, while version 5 is college-educated and middle class. Version 10 is differentiated by gender and race, attracting mainly young nonwhite women. Versions 3, 7, and 8 are pop micro-genres that combine well with others at the level of people's repertoire (their audience tend to be omnivorous), while version 1 reveals a classic pop univore.

  \begin{figure}[ht!]
      \centering
     \begin{subfigure}[b]{0.8\textwidth}
        \includegraphics[width=1.0\textwidth]{figs/demog-plots/Pop1.png}
        \caption{}
        \label{fig:Pop1}
    \end{subfigure} 
     \begin{subfigure}[b]{0.8\textwidth}
        \includegraphics[width=1.0\textwidth]{figs/demog-plots/Pop2.png}
        \caption{}
        \label{fig:Pop2}
    \end{subfigure}
     \caption{}
  \label{fig:Pop}
 \end{figure}

\subsection{Country}
The macro-genre label of ``country music'' has always been one suspected of hiding untold levels of micro-genre heterogeneity. This is not only the case style, but also sociodemographics, generations and even politics \citep{rossman2004elites}. As shown in Figure~\ref{fig:Country}, the micro-genres discovered by the cluster analysis agree with this take. First, the analysis reveals ten distinct macro-genres within the larger vague label. Within these, there is strong generational differentiation across different versions of ``country." Five appeal mainly to older audiences (1, 2, 4, 6, 8, $N=123$, $N=115$, $N=87$, $N=70$, and $N=58$, respectively), two tilting toward younger fans (3 and 7, $N=110$ and $N=61$), and two engaging middle-aged people (5 and 10, $N=70$ and $N=49$). Micro-genre 1 recovers the prototypical ``country univore." Fans of these micro-genre are largely white, shun the upper-class label, do not have a college degree, and engage only this micro-genre to the exclusion of others. Version 3, by way of contrast, is the obligatory micro-genre that mixes indiscriminately with other genres. Country micro-genres attracting older respondents exhibit class differentiation, with versions 1, 2, and 6 attracting respondents with less than a college education, and versions 4 and 8 reversing this pattern; the great bulk of fans of country version 4 identify as middle class making this micro-genre distinctive in that respect.

  \begin{figure}[ht!]
    \centering
     \begin{subfigure}[b]{0.8\textwidth}
        \includegraphics[width=1.0\textwidth]{figs/demog-plots/Country1.png}
        \caption{}
        \label{fig:Country1}
    \end{subfigure} 
     \begin{subfigure}[b]{0.8\textwidth}
        \includegraphics[width=1.0\textwidth]{figs/demog-plots/Country2.png}
        \caption{}
        \label{fig:Country2}
    \end{subfigure}
     \caption{}
  \label{fig:Country}
 \end{figure}

### 2023-02-06 main.tex
Initial Overleaf Import

\documentclass[a4paper,12pt]{extarticle}
\usepackage[utf8]{inputenc}
\usepackage{graphicx}
\usepackage{natbib}
\usepackage{amsmath}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{geometry}
    \geometry{a4paper}
\bibliographystyle{plainnat}

\title{Discovering Focused Microgenre Communities}

\begin{document}
\maketitle
\subsubsection*{Abstract} 
Recent work in the sociology of taste has begun to grapple directly with the relational properties of traditional survey-based data using techniques inspired by network analysis. Despite the generally salutary results from this endeavor, critics rightly question the face and ecological validity of the vague macrogenre labels included in standard arts participation surveys (e.g., Classical, Rock, Rap). To deal with this issue, in this paper, I propose a link-clustering approach for discovering focused microgenres from standard survey-based information on cultural tastes, one that exploits the underlying relational patterns realized by the indirect connectivity structure of genres (via persons) in a two-mode network. The link-clustering approach partially answers two of the challenges of macro-genre critics: The fact that actual genres are overlapping and not crisply bounded and the fact that there is hidden heterogeneity within the broad labels we usually focus on. To demonstrate the validity of the approach, I contrast the application of the usual techniques to the same data, conceived in the usual ``macro" way, and after discovering hidden microgenres. The results reveal an intuitive partition of traditional macrogenres into focused microgenres, capable of separating audiences along relevant sociodemographic markers, such as education, ethnoracial identity, subjective class identification, and age/generation. 
\newpage

\section{Persons and Cultural Choices}
Recent work in the sociology of taste has blurred the distinction, foundational for much early work, between ``relational'' network data (codifying the relationships between people) and survey data (codifying the relationship between people and ``variables''). The basic idea is that all data, whether collected purposefully as ``network'' data or collected as part of a social survey, is \textit{relational} data. The main difference is the types of entities that are related \citep{borgatti_everett97}. That is, any data source that can be stored in matrix form has ``modes'' (how many types of entities are related) and ``ways'' (the number of entities linked by a relation, usually two at a time). The standard network data set is ``one mode'' (we usually look at one type of entity at a time, like people, organizations, schools, countries, and the like) and two ``ways'' (people-by-people or organization-by-organization pairs). In the same way, the usual person-by-variables survey data has two modes and two ways. The relations are not people-by-people but people-by-variables. People are connected to the survey items they answer by relations of affinity, disagreement, choice, or even negatively (by not answering). Following, \citet{breiger74}, it is possible to recover person-by-person (one mode, two ways) matrices from the usual person-by-variables data matrices. People can be connected to others if they share the same values, opinions, tastes, practices, or demographics recorded as variables in the columns of the matrix.

When transplanted to the sociology of taste, for which survey data has been the workhorse source of insights and empirical generalizations \citep{peterson_kern96, bryson96, vaneijck01,savage_gayo11}, this blurring of the boundaries between the two main sources of relational data in the social sciences can be revelatory. This goes beyond the fact, to be exploited below, that once we treat survey data as network data, then the entire methodological panoply developed by social network analysts (and increasingly ``network scientists'' working across many disciplines) for the last fifty or so years becomes part of the analytic toolbox. In addition to this, the entire \textit{conceptual} arsenal of social network theory \citep{borgatti11} also becomes available. As \citet[244]{borgatti_everett97} note, once we convert ``2-mode data sets into 1-mode matrices{\dots}we can then apply the techniques (if not the theories) of network analysis.''

Accordingly, a spate of recent work has begun the job of theoretical translation, enriching the first-generation of work in the sociology of taste with network-flavored concepts. Accordingly, \citet{pachucki2010cultural} extend Ronald Burt's theory of structural holes for understanding how people can bridge gaps not just in one-mode person-to-person networks but in two-mode person-to-culture networks. Following this lead, \citet{lizardo14} provides a metric based on Burt's conception of network efficiency that is meant to characterize the slippery concept of ``omnivorousness" concerning genres and cultural forms that people engage in. This approach goes beyond just summing or counting people's cultural engagements to consider the audience overlap between the genres themselves. Thus, the true omnivore is a person who consumes genres with low audience overlap. Other work in this same vein extends ideas related to positional equivalence in networks \citet{breiger1976social} to uncover ``blocks'' of respondents that tend to dislike the same set of genres that others like \citep{okada2017structure}. A similar approach, based on ideas of positional equivalence in networks, can be extended beyond the study of beliefs and social attitudes more generally to identify respondents who share cultural schemas \citep{goldberg2011mapping}. \citet{lizardo18} adapts techniques first developed for the study of economic complexity in two-mode networks of geographic sites and products/technologies for the characterization of genres (e.g., popular versus niche) and audience (e.g., omnivore versus ``univore'') characteristics in survey data on cultural tastes.

\section{The Problem of Genre in the Sociology of Taste}
In this paper, I continue to ride this wave of adapting network approaches to survey data on cultural tastes to tackle a fundamental problem (both substantive and measurement-wise) in the sociology of taste, namely, the problem of \textit{genre}. In a foundational paper, \citet{dimaggio1987classification} provided a prescient conceptualization of the core constructs of the sociology of taste in a way that exploited the network imagery that has become a routine reality of late. In the paper, \citet[244]{dimaggio1987classification} asked us to

\begin{quote}
   {\dots}imagine a matrix defined by persons on the vertical axis and artworks on the horizontal axis, with{\dots}signifying relationships (knowledge about, like for, dislike of) between person and artworks, genres consist of those sets of works which bear similar relations to the same set of persons. The logic behind this imagery will be familiar to students of network analysis as one of ``structural equivalence.''
\end{quote}

Thus, for DiMaggio, genres are dual entities precisely in Breiger's sense defined above. Genre categories are composed of the audiences that engage them (are subsets of the larger set of people). People, on the other hand, are related to one another (e.g., via relations of similarity, opposition, or non-overlap) by the genres they choose, and genres related to one another via overlaps (intersections) in the sets of people who choose them \citet{lizardo18}.

This conceptualization, like a lot of network theorizing, is elegant but gets messy in the application. As \citet[149]{lena2015relational} has noted, ``[n]o ordering principle is as fundamental to culture as genre'' yet, none is also as vexed. One issue Lena raises is that sociologists have relational intuitions about genres but tend to default to musicological definitions for convenience's sake. Thus, when it comes to considering which genres to include in a survey on cultural tastes, the tendency is simply to pick off the shelf from the menu of genre categories. The problem with these folk genre classifications is that they tend to miss the fuzzy, overlapping ways that real-world genres are organized. This leads us to treat what are, in fact, contested boundaries as if they were natural, crisp boundaries (e.g., assigning respondents who like ``Rap" to a different taste community than those who like ``Opera."). This is the problem of \textit{overlapping boundaries among genre categories}.

The other issue has to do with the level of aggregation. For convenience’s sake, survey data must settle on a ``middle'' level of categorization so as not to tax respondents' patience (or knowledge). Thus, the standard ``lists'' of cultural genres, such as ``Pop Art,'' ``Romantic Comedy," or ``Blues.'' However, as recent work points out, people, venues, fandoms, scenes, subcultures, communities, organizations, critics, gatekeepers, and even states and other powerful institutions, make sociologically relevant distinctions within macro-genres categories \citep{hesmondhalgh2005subcultures, Holt2007, Van_Poecke2018}. Genres may also develop and accumulate subvariations as they ``travel'' across production, dissemination, and consumption sites in their historical trajectory \citep{Lena2012}. These ``micro-genres'' are embedded within larger macro-genres in complex ways that the standard survey approach misses.

\section{What to do about the problem of genre}
One solution to the problem posed by vague macro-genre labels, suggested by \citet{vlegels2015music, vlegels2017music} concerning musical genres, is to ``change the mode'' and ``drop the label'' by asking respondents not just for their levels of engagement or liking of broad macro-genre labels but for performers within those labels. This work shows that once these ``micro-genre'' distinctions based on performers are made, some core empirical generalizations in the sociology of taste (e.g., highly educated people like classical music) are controverted or at least heavily qualified. This \textit{micro-genre heterogeneity} critique thus asserts that the standard genre labels studied by social scientist hide as much as they reveal because micro-genre communities can be internally diverse and even contain mutually opposed groups in the social space \citep{flemmen_etal18}. For people, the unit of selection and judgment is the {\em micro-genre}, not the broad genre classification, so it is unclear what to do (and how to interpret) the usual data collected by sociologists who study taste using surveys.

But what happens when all the data we have (as it is with the long-standing surveys such as the Survey for Public Participation in the Arts or the General Social Survey) is at the macro-genre label? Both overlapping boundary and micro-genre heterogeneity critics of traditional genre labels would say to simply ignore these data and collect new data that does not rely on misleading macro-genre labels. Here I propose another solution: {\em Exploit the inherent relationality embedded in survey data responses} \citep{goldberg2011mapping, boutyline2017belief, lizardo18}.

More specifically, my point will be that by exploiting the inherent relationality already contained in the usual survey data (when treated as two-mode network data), old data can reveal insights that pertain to the very features sociological critics of the macro-genre label concept say is missing. In particular, it is possible to use embedded sets of relations between people and genres to discover the very heterogeneous micro-genre communities critics say are hidden by the macro-genre label (thus my point is that these are hidden but not necessarily absent). This approach is thus ideal for making new use of old data.

\subsection{Precursors of the Proposed Approach}
The approach proposed here builds on the core ideas of ``duality'' and ``relationality'' that have  become foundational for formal approaches to measuring culture in the sociology of taste \citep{mutzel2020duality, mohr2015formal}. In this sense, I followed a path already trailed by others. For instance, Goldberg's \citeyearpar{goldberg2011mapping} {\em Relational Class Analysis} (RCA) ``classifies the people'' (in the terms developed below when reviewing standard data-analytic approaches in the sociology of taste) included a survey by partitioning a person-by-person matrix built from higher order similarities (sums of differences of differences) between each pair of person's corresponding response vector coding their stances (e.g., like, dislike, neutral) toward a set of cultural objects (e.g., genres, attitude items). Boutyline's 
\citeyearpar{boutyline2017improving} {\em Correlational Class Analysis} (CCA) also classifies the people but this time by using the absolute value of the correlation distance between response vectors to build the person-by-person similarity matrix. Boutyline and Vaisey's {\em Belief Network Analysis} (BNA) classifies the objects people connect to (in their case, beliefs, but could also be genres) by creating a weighted object network, where the weight of the tie between two objects (attitude toward government spending and attitude toward immigration) is given by the magnitude of their correlation coefficient in the survey.

As we will see, I propose an approach thoroughly complementary to and synergistic with these previous efforts. More to the point, the relational identification of microgenres should be able to improve the applicability of techniques like RCA, CCA, and BNA (and related techniques), because, just like standard statistical approaches (like Factor Analysis, Principal Component Analysis, Latent Class Analysis and so forth), and even techniques (like Multiple Correspondence Analysis that are sometimes opposed to the traditional statistical ones, these newfangled relational techniques are also dragged down by the macrogenre curse. Thus, RCA and CCA are bound to compute relationality and correlation distances within people but have to rely on vague macrogenre labels. The resulting evaluation logics are thus interpreted using a macrogenre lens---e.g., ``Anything but Heavy Metal'' or ``Highbrow versus Lowbrow" \citep[e.g.,][]{goldberg2011mapping, willekens2022cultural}. But what if what one group means by "Heavy Metal" differs from what another group means by the same vague label? Are we sure that certain {\em all} types of classical music are ``opposed'' to or divergent from engagement with Country or Hip Hop? Some versions of Indie/Alt Rock are considered today as ``highbrow'' as Classical music (used to be) \citep{Van_Poecke2018}; or there may exist types of Country music that appeal to highly educated audiences and, thus, to people who might also listen to musicals? Overall, all quantitative techniques used by researchers in the sociology of taste must work with the (broad) genre categories included in the survey they are powerless to deal with these (reasonable) objections.

Importantly, this implies that the clumping of vague macrogenre labels into even vaguer meta-macrogenres (discourses, styles, logics, schemas) like ``highbrow'' could be a spurious by-product of the vague labeling (as micro-genres critics have long suspected). This matters because such macrogenre clumping does much conceptual (and technical) work in our data reduction, data interpretation, and substantive theorizing efforts. The result is that it is likely that people are classified as following the same cultural logic of genre valuation and evaluation when they, in fact, follow distinct logics. In fact, a key implication of the approach to be described below is that regardless of the particular technique used, sociologists of taste are likely to underestimate population heterogeneity in the logics of classification and evaluation people use to navigate the cultural space \citep{lahire2008individual}. This heterogeneity has to be {\em revealed} before constructing belief or attitude networks, classifying people into schematic classes, embedding genres into a dimensional space, or putting people into latent classes.

\subsection{Data to be Used in the Study}
The empirical part of the study uses data on the musical tastes of American collected with Sara Skiles in the summer of 2012 \citep{lizardo_skiles15, lizardo_skiles16}. The survey was (partially) designed to replicate the General Social Survey (GSS) 1993 Culture Module. This is now a canonical data set providing the empirical basis for a variety of analyses (and reanalyses) in the sociology of taste \citep[e.g.,][]{bryson96, goldberg2011mapping, schultz2010strength, han2003unraveling, tampubolon2008revisiting, okada2017structure}.  The data were collected by an organization then called Survey Sample International (SSI), a private firm specializing in sampling, data collection, and analysis. SSI managed recruitment and participation invitation tasks to generate a panel of adults from which our working sample was drawn. Survey respondents were selected from the panel for participation based on age, gender, race, education, and geographic region to approximate a sample representative of the U.S. population ($n = 2,263$). Like GSS 1993, SSI 2012 included items assessing respondents’ likes and dislikes (as well as a middle category of ``mixed feelings'') for 20 categories of musical style: classical/ symphony and chamber, opera/operetta, jazz, Broadway musicals/show tunes, mood/easy listening, big band/swing, classic rock/oldies, country, bluegrass, folk, hymns/gospel, Latin/Spanish/salsa, rap/hip hop, blues/R\&B, reggae, top 40/pop music, contemporary rock, indie/alternative rock, dance/club/electronic, and hard rock/heavy metal. In addition to providing a taste judgment for each item, respondents were also asked if they regularly listened to each macro-genre. The following analyses are based on a data frame in which people are coded as engaging the macro-genre if they report both liking and listening to it. The two-mode network we will be working with is thus of dimensions and has $2263$ people and $20$ genres. This defines an affiliation matrix $A_{PG}$ of the same dimensions, with entries equal to 1 if person $P$ likes \textit{and} listens to macro-genre label $G$ and zero otherwise.

\subsection{The Link Clustering Approach}
I propose that exploiting {\em relationality} hidden in the usual survey data collecting information on people and genres can help us make headway on the micro-genre critique outlined in the preceding. As noted at the outset, this requires that we stop looking at the usual survey data that forms the bulk of empirical material in the quantitative study of taste as ``survey data'' (e.g., data collected on the characteristics of individuals in the form of ``variables''). This is a presumption that is baked into traditional techniques (like Factor Analysis or Latent Class Analysis) that fit statistical models to such data. It is also embedded in ``relational'' techniques like Multiple Correspondence Analysis which, while not steeped in the preoccupations of standard statistical inference (although it could be), divert our attention to the indirect relations between macro-genres (or between people), usually conceptualized as distances in a social space. This kind of indirect relationality is fine and dandy but as already noted in the case of RCA, CCA, and BNA, all the relationality built into MCA is powerless, if what is fed {\em into} the process is the same old, limited, overextended macro-genre categories.

I address the micro-genre issue using a technique for overlapping community detection called link clustering \citep{ahn_etal10}. The basic idea is simple and is illustrated in the toy example shown in Figure~\ref{fig:link-toy1}. Breaking with approaches that attempt to cluster people and genres by focusing on the people or the genres, we take the person-to-genre {\em link} as the unit of analysis and focus our classification energies on those. Classifying the links gives (by definition) a classification of the entities at the end of each link (people and genres) for free. Not only that, because most people choose multiple genres, and all genres ``choose'' multiple people, this classification guarantees that genres get assigned to multiple \textit{overlapping} clusters, at the same time splitting up the macro-genres into more relationally focused clumps. This allows us to make headway on both horns of the micro-genre critique---namely, overlapping categories and internal differentiation---at once.

\begin{figure}[ht!]
     \centering
     \begin{subfigure}[b]{0.6\textwidth}
        \includegraphics[width=1.0\textwidth]{Figs/Toy/link-clust-toy1.png}
        \caption{Two person-genre edges sharing the same genre.}
        \label{fig:link-toy1}
    \end{subfigure} 
     \begin{subfigure}[b]{0.3\textwidth}
        \includegraphics[width=1.0\textwidth]{Figs/Toy/link-clust-toy2.png}
        \caption{Similarity between person-genre edges depends on the other genres people are linked to.}
        \label{fig:link-toy2}
    \end{subfigure}
     \begin{subfigure}[b]{0.45\textwidth}
        \includegraphics[width=1.0\textwidth]{Figs/Toy/link-clust-toy3.png}
        \caption{Edge similarity matrix from toy example.}
        \label{fig:link-toy3}
    \end{subfigure}
     \begin{subfigure}[b]{0.45\textwidth}
        \includegraphics[width=1.0\textwidth]{Figs/Toy/link-clust-toy4.png}
        \caption{Edge distance matrix from toy example.}
        \label{fig:link-toy4}
    \end{subfigure}
     \begin{subfigure}[b]{0.6\textwidth}
        \includegraphics[width=1.0\textwidth]{Figs/Toy/link-clust-toy5.png}
        \caption{Dendrogram from Ward clustering of toy example edge distance matrix cut at four clusters.}
        \label{fig:link-toy5}
    \end{subfigure}
    \caption{Toy illustration of how the link clustering approach works.}
    \label{fig:link-toy}
 \end{figure}

How does this work? As Figure~\ref{fig:link-toy1} shows, once we string out the original two-mode person-by-network in our toy example into an edge list (now containing eleven person-genre edges), where the cases are the person to genre pairs that are marked by a ``1'' in the original matrix, it is possible to ask: ``How similar is one edge to another?'' We can answer that question as follows. The similarity of one person-to-genre edge to another, when both edges point to the same genre \citep{ahn_etal10}, should be proportional to the overlap between the ``cultural ego networks'' of the two people at the tail end of the edges. As \citet{lizardo14} defines it, for any respondent $i$, in a survey on cultural taste, the cultural ego network is simply the set of genres $\{G_1, G_2,\dots G_k\}$ chosen by the person.

Going back to our running toy example, we are tasked with computing the similarities between $\frac{11 \times (11-1)}{2} = 55$ person to genre pairs. Suppose we wanted to calculate the similarity between the $P_1-G_2$ and $P_3-G_2$ person-to-genre edges in the two-mode network. In Figure~\ref{fig:link-toy1}, these two links are highlighted in yellow the ``strung out'' edgelist and are shown in red in the corresponding bipartite subgraph shown in Figure~\ref{fig:link-toy2}. The similarity ($S$) between the two links is then given by:

\begin{equation}
    S(P_1G_2, P_3G_2) = \frac{n_+(P_1) \cap n_+(P_3)}{n_+(P_1) \cup n_+(P_3)}
\end{equation}

Where $n_+(P_1)$ is the cultural ego network of Person 1 and $n_+(P_3)$ is the cultural ego network of Person 3. The formula says that the similarity between two person-to-genre links sharing a genre, in this case, the similarity between the $P_1-G_2$ edge and the $P_3-G_2$ edge, is given by the intersection of Person 1's and Person 3's cultural ego network divided by their union (also known as Jaccard's coefficient). When the cultural ego networks of two people are the same then $S=1$, when they are completely disjoint (share no genres, meaning the intersection is the empty set), then $S = 0$. All other cases of person-to-genre edges sharing the same genre return a number between zero and one ($0 > S < 1$).\footnote{Note that the only substantive similarities we care about are between person-to-genre edges that shared the same genre but have different people attached to them at the other end. All other person-to-genre edges, featuring people connected to different genres are set to zero.} In the toy example case, $P_1$ and $P_3$ consume two genres out of the four possible ones they could consume in common, resulting in an edge similarity score of $\frac{2}{4} = 0.50$.

If we do that for all pairs of person-to-culture genres sharing one genre node in common, we end up with the two-way, one-mode (now the only mode is edges) $11 \times 11$ similarity matrix shown in Figure~\ref{fig:link-toy3}. Note two features of the similarity matrix. First, by definition two person-to-genre links that go from different genres to the same person are maximally similar (as the overlap is 1.0). This means that only links that go from different people to the same genre exhibit overlap variation, and this is driven (``reflectively'' \citep{lizardo18}) by the overlap between the neighborhoods of the other mode (people). Next, we transform the similarity matrix into a {\em dissimilarity} matrix by subtracting one from each entry (shown in  Figure~\ref{fig:link-toy4}). We then subject this matrix to hierarchical clustering using Ward's \citeyearpar{ward63} method.

The resulting dendrogram from the cluster analysis is shown in Figure~\ref{fig:link-toy5}. Note that moving from the top down, the dendrogram splits person-to-genre links according to the macro-genre label. That is macro-genre information is preserved in the clustering, and can be recovered by splitting the dendrogram at a height where the number of clusters is equal to the original number of macro-genres (in this case, four as shown in Figure~\ref{fig:link-toy5}). Moving from the bottom up, the hierarchical clustering of the dissimilarity matrix yields {\em link communities} \citep{ahn_etal10}, in which both people nodes, but, most crucially, genres nodes are assigned to different clumps. In the limiting case (the bottom-most ``leafs'' of the dendrogram, each person-to-genre links are assigned to their cluster. The more interesting thing is that as we move up to a point below macro-genres clusters and above the leafs, we see a partition of {\em varieties} of macro-genres. For instance, macro-genre $G4$ is split into two focused micro-genre varieties. The first is attached to persons $P2$ and $P4$ and the second attached to persons $P3$ and $P5$ respectively. The idea then, is that the macro-genre nodes (e.g., ``Classical,'') assigned to different clumps represent micro-variations of the macro-genre label that differ primarily in a relational or structural way; different ``types'' of ``Classical'' are different because their audiences make distinct choices {\em with respect} to the other genres in the survey.

\begin{figure}[ht!]
     \begin{subfigure}[b]{0.5\textwidth}
        \centering
        \includegraphics[width=1.0\textwidth]{Figs/Dend/all-branches-macro.png}
        \caption{c = 8, k = 20}
        \label{fig:dend-macro}
    \end{subfigure} 
     \begin{subfigure}[b]{0.5\textwidth}
        \centering
        \includegraphics[width=1.0\textwidth]{Figs/Dend/all-branches-macro-labels.png}
        \caption{c = 8, k = 20}
        \label{fig:dend-macro-labels}
    \end{subfigure} 
     \begin{subfigure}[b]{0.5\textwidth}
        \centering
        \includegraphics[width=1.0\textwidth]{Figs/Dend/all-branches-micro.png}
        \caption{c = 3, k = 102}
        \label{fig:dend-micro}
    \end{subfigure} 
     \begin{subfigure}[b]{0.5\textwidth}
        \centering
        \includegraphics[width=1.0\textwidth]{Figs/Dend/all-branches-micro-labels.png}
        \caption{c = 3, k = 102}
        \label{fig:dend-micro-labels}
    \end{subfigure}
     \begin{subfigure}[b]{0.32\textwidth}
        \centering
        \includegraphics[width=1.0\textwidth]{Figs/Dend/classic-rock-branches.png}
        \caption{c = 3, k = 12}
        \label{fig:dend-micro-classic-rock}
    \end{subfigure} 
     \begin{subfigure}[b]{0.32\textwidth}
        \centering
        \includegraphics[width=1.0\textwidth]{Figs/Dend/blues-branches.png}
        \caption{c = 3, k = 5}
        \label{fig:dend-micro-blues}
    \end{subfigure}
     \begin{subfigure}[b]{0.32\textwidth}
        \centering
        \includegraphics[width=1.0\textwidth]{Figs/Dend/opera-branches.png}
        \caption{c = 3, k = 2}
        \label{fig:dend-micro-opera}
    \end{subfigure}
    \caption{}
    \label{fig:dend}
 \end{figure}

The resulting partition has two interesting (and desirable) properties. First, the number of genre communities that \textit{people} belong to is deterministic, and it is given by the number of macro-genre labels they initially chose. Thus, link clustering preserves the cultural ego network degrees (omnivorousness by volume) of the people mode \citep{lizardo14}. Second, the number of micro-genres into which the macro-genres are split is {\em not} deterministic. Instead, it is data-driven (discovered or learned) and cannot be pre-specified in advance. It is a function of relational information implicit in the overlap structure of the cultural ego networks of people in the data. Thus, link community detection of the person-to-genre network allows us to go from  a situation starting with a person-to-genre network featuring a relatively small number of macro-genres and end up with an enlarged two-mode network with the same number of nodes in one mode (the people) but many more nodes in the other mode (the micro-genres). How many micro-genres ($N_m$) emerge is up to the analyst as it depends on where we ``cut'' the resulting clustering dendrogram. This will be somewhere in between $N_g \geq N_m \leq N_l$, where $N_g$ is the number of original (macro) genres and $N_l$ is the number of person-to-genre links.

\section{Analysis and Results}
\subsection{Discovering Micro-genre Communities in Real Data}
Let us see how this process works in real data. We will see that link clustering can uncover valid micro-genres. Recall that the data feature 2,263 people choosing up to 20 macro-genre labels. When strung out as an edgelist, this results in 9,216 person-to-genre connections in the data, the resulting $9216 \times 9,216$ matrix, containing Jaccard similarities among person-to-genre links sharing a node in either of the two modes, is then the input to an agglomerative hierarchical clustering algorithm using Ward's \citep{ward63} method. The hierarchical clustering process proceeds as follows. Initially  each person-to-genre link is initially assigned to its own community. Then, in the second time step, the pairs of links with the largest Jaccard similarities are put in the same clump. This continues at each time step, where pairs of links with the largest similarity are chosen, and their respective communities are merged. This process is repeated until all links belong to a single cluster. The history of the clustering process is then stored in a dendrogram, which encodes all the information on the hierarchical organization of the genre communities. The height of the dendrogram provides information about the strength of the genre communities. As we have seen, the highest levels reproduce the original macro-genres, while the lower levels uncover more focused micro-genres embedded within them. This is shown in Figure~\ref{fig:dend}.

Figure~\ref{fig:dend-macro} shows that when we cut the dendrogram at a high level (e.g., $C = 8$), we reproduce the original twenty macro-genres we began with as the ``discovered'' link communities. Note that, as Figure~\ref{fig:dend-macro-labels} shows, the agglomerative link clustering procedure arranges the macro-genre levels roughly by their original popularity (number of person-to-genre links). From left to right, these are Classic Rock/Oldies, Pop/Top 40, Country, Classical, Easy Listening, Blues/R\&B, Contemporary Rock, Rap/Hip Hop, Jazz, Gospel, Dance/Club, Indie Alternative, Latin, Broadway/Musicals, Heavy Metal/Hard Rock, Reggae, Big Band, Folk, Bluegrass, and Opera. As shown in Figure~\ref{fig:dend-micro}, micro-genre communities are produced by cutting the link clustering dendrogram at a lower level. When we choose a cutoff value of $c = 3$ results in $k = 102$ micro-genre communities extracted from the original twenty macro-genre labels. Data scientists wring their hands when performing cluster analysis about choosing a cut value. One advantage of the link clustering approach is that we always know what we are doing because micro-genres are strictly nested within the original macro-genres. On the other hand, choosing a smaller cut value produces finer-grained micro-genres (perhaps at the expense of analytic tractability and interoperability), and selecting a higher value returns us to broader genre communities closer to the original macro-genre labels we began with (with the limiting case as shown in Figure~\ref{fig:dend-macro} being the original macro genre labels themselves). As Figure~\ref{fig:dend-micro-labels} shows, at any cut value $C$, the more popular macro-genres produce more micro-genre communities, while the less popular ones produce a smaller number. For instance, as shown in Figure~\ref{fig:dend-micro-classic-rock}, at $c = 3$, the macro-genre ``Classic Rock/Oldies'' (the leftmost set of branches in the dendrogram in Figure~\ref{fig:dend-macro}) is split (at the point at which the branches intersect the red dashed cut line) into $k_{(CR)} = 12$ distinct micro-variations, while, as Figure~\ref{fig:dend-micro-opera} shows, the macro-genre ``Opera" (the rightmost set of branches in the dendrogram in Figure~\ref{fig:dend-macro}) is split into only $k_{(Op)} = 2$  micro-genre communities. Figure~\ref{fig:dend-micro-blues} shows that ``Blues/R\&B'' falls somewhere in between, with $k_{(BRB)} = 5$  micro-genre communities uncovered.

Each cut point in the dendrogram will have a micro-genre size distribution $N$ associated with it. Lower cut points return a micro-genre size distribution dominated by many micro-genres with tiny ($N_{mg} < 10$) or trivial $N_{mg} = 2$ audiences. In this respect, although I have been using the labels ``macro'' and ``micro'' as if they referred to substantive or objective partitions, they are best interpreted as {\em relative} to a given classification level. Thus, micro-genres are ``micro'' relative to the usual (perhaps ``basic'' in Rosch's \citeyearpar{Rosch1978-ue} sense) level of vague macro-genre labels that populate most arts participation surveys. But these may be micro, as we will see, relative to the (logics, discourses, schemas) meta-groupings that we generate when applying the usual suite of statistical and data reduction techniques (e.g., such as ``highbrow'' or ``Folk"). Further, at any given classification level, further micro-genres will be nested within any given micro-partition. In this way, micro-genre communities reflect a substantively valid way in which people partition the cultural world, whereby there is always the possibility of making finer-grained distinctions within fine-grained distinctions (e.g., ``old school rap," ``1980s old school rap,", ``early 1980s old school rap," and the like).

Ultimately, there is no magical ``right'' answer here, but for analytic purposes $c = 3, k = 102, max(N_{mg}) = X, min(N_{mg}) = Y$ is sufficiently fine-grained to showcase the analytic advantages of the micro-genre approach. The resulting size distribution is shown in Figure~\ref{fig:size-dist}. The main panel shows the micro-genre communities chosen by 75 or more people, and the inset shows the entire size distribution. micro-genre communities are named according to the original macro-genre label, followed by a number. As the figure shows, the largest micro-genre communities in the data pertain to micro-variants of Indie/Alternative Rock, Contemporary Rock, Reggae, Classic Rock, Blues/R\&B, and Gospel.

 \begin{figure}[ht!]
 \centering
 \includegraphics[width=0.7\textwidth]{Figs/Link Clust/micro-genre-size-dist.png}
 \caption{}
  \label{fig:size-dist}
 \end{figure}

\subsection{What Micro-Genre Communities Reveal}
\subsubsection{Hidden Dimensionality}
So what do we learn about people's tastes and about the micro-genres themselves after subjecting our data to link clustering? Comparing the answers we get from applying a standard, relatively undemanding (in terms of statistical assumptions foisted upon the data), namely, Principal Components Analysis, to the original and link-clustered cultural network data (hereafter OD, and LCD, respectively) can be illuminating in this respect. Particularly in terms of showing what is revealed by the link clustering in exposing the hidden relationality in the data and in what ways relying on vague macro-genre levels leads us astray both substantively and theoretically.

\begin{figure}[ht!]
    \includegraphics[width=1.0\textwidth]{Figs/Link Clust/macro-v-micro-pca-eig.png}
    \caption{}
    \label{fig:eig}
 \end{figure}

The first---perhaps already evident---thing we learn is that macrogenre labels hide underlying multidimensionality in cultural taste data, which the link clustering reveals. To show this, Figure \ref{fig:eig} shows the scree plot of the PCA analysis of the OD and the LCD. In the figure, the size of the eigenvalue is shown on the y-axis; the order (first, second, third, and so forth) of the corresponding eigenvalue is shown on the x-axis. The vertical red line going across the plot corresponds to the value on the y-axis where $\lambda = 1$. The black vertical line separates the eigenvalues for which $\lambda >= 1$ (on the left side of the plot) from those for which $\lambda < 1$ (on the right side of the plot). Using the rule of thumb that the number of eigenvalues for which $\lambda > 1$ point to significant dimensions of variation in the data, the PCA on the OD suggests the relevance of perhaps four dimensions that we may want to consider (usually, most analysts stick to the first two). The corresponding scree plot for the LCD reveals upwards of {\em twenty-five} dimensions that could be relevant.

The first lesson we learn is that {\em macro-genre labels hide relevant dimensions of genre-level (and thus potential person-level) of differentiation in the data}. As we will see next, the artificial lower-dimensionality of the data considered by relying on macro-genre levels leads to substantively misleading answers to our questions.

\subsubsection{Misleading Answers to Substantive Questions}
 What does the dimension-reduction analysis reveal substantively? Figures \ref{fig:macro-pca} and \ref{fig:micro-pca} show the result of ``classifying'' the genres using the first four dimensions of the PCA on the OD and the first twenty-five dimensions of the PCA on the LCD. In the figures, genres are classified using a ``hybrid'' (hierarchical/k-means) clustering of the (Euclidean) genre distance matrix in four-dimensional space (for the OD) and twenty-five-dimensional space (for the LCD). The number of clusters corresponds to the number of dimensions in the space; four macro-genre clusters ($k_{MG}$) and twenty-five micro-genre clusters ($k_{mg}$). After clustering, macro and micro-genres are re-embedded into two-dimensional space using their respective scores along the first two Principal Coordinates.

\begin{figure}[ht!]
     \begin{subfigure}[b]{1.0\textwidth}
        \centering
        \includegraphics[width=0.6\textwidth]{Figs/Link Clust/macro-pca-clust.png}
        \caption{}
        \label{fig:macro-pca}
    \end{subfigure} 
     \begin{subfigure}[b]{1.0\textwidth}
        \centering
        \includegraphics[width=0.6\textwidth]{Figs/Link Clust/micro-pca-clust.png}
        \caption{}
        \label{fig:micro-pca}
    \end{subfigure} 
    \caption{}
    \label{fig:macro-v-micro-pca}
 \end{figure}

 Figure~\ref{fig:macro-pca} suggests that a two-dimensional space does a good job of representing distinctions between macro-genres (accounting for about 65\% of the variance). Moreover, the macro-genre clusters correspond to the usual logics or discourses that populate many studies in the sociology of taste. On the upper-left, we have a variety of ``folk'' genres, including Country, Gospel, Bluegrass, and the eponymous Folk (with ``Easy'' as a boundary macrogenre). On the lower-left, we have the usual set of ``highbrow'' genres (with Jazz as a boundary macrogenre). On the right, we have the standard set of ``Pop/Industry'' macrogenres, perhaps partitioned, in the four-cluster solution, into ``Rock/Pop" (the varieties of Rock and Roll, with ``Classic Rock/Oldies as a boundary macrogenre) and ``Afro/Pop" (Rap, Reggae, Blues) variants (with ``Latin/Spanish" as a boundary macrogenre).

 Suppose we follow the now well-established ``structuralist'' approach to interpreting these types of embeddings of cultural objects as a space governed by binary oppositions popularized by Bourdieu \citeyearpar{bourdieu84}. In that case, we might say that the first dimension separates or opposes Highbrow and Folk discourses to Pop/Industry logics. The second dimension opposes the (perhaps high-status) highbrow discourse to the perhaps lower-status folk discourse. The fact that Pop/Industry genres are less differentiated on this second, seemingly status-focused dimension might indicate less relevance of status distinctions among these macro-genres. This is all consistent with the usual story of the persistence of these broad meta-macro-genre distinctions and oppositions over time (e.g., in the case of the U.S.) or across national settings.

\begin{figure}[ht!]
    \includegraphics[width=1.0\textwidth]{Figs/Link Clust/macro-v-micro-clust.png}
    \caption{}
    \label{fig:macro-v-micro-cluster}
 \end{figure}

 Two contrasts are evident in the corresponding PCA-cluster plot (Figure~\ref{fig:micro-pca} for the LCD. First, the two-dimensional embedding represents the data poorly (covering less than 10\% of the variance). This makes sense since the LCD is a higher-dimensional entity, to begin with. Of more substantive importance, note that the cluster solution now presents a more complicated picture that is harder to fit into the stylized story of opposition and differentiation between broad discourses or logics. In Figure~\ref{fig:micro-pca}, micro-genres that belong to opposed or differentiated macro-discourses in Figure~\ref{fig:macro-pca} mingle freely into ``micro-discourses'' or ``micro-logics'' (e.g., combining variants of Country, Classic Rock, Classic, Gospel, and Pop) that would be harder to characterize except as varieties of ``omnivorousness.'' The problem with this approach, however, is that we will end up with more varieties of omnivorousness that we will know what to do with.

 Figure~\ref{fig:macro-v-micro-pca} makes this point evident. In the figure, the twenty-five micro-genre clusters shown in Figure~\ref{fig:micro-pca} are plotted along the y-axis. The x-axis consists of the unordered four-category variable formed by the (labeled) clusters in Figure~\ref{fig:macro-pca}. Thus, micro-genres in the same horizontal ``row'' belong to the same micro-genre cluster; reading down the columns assigns each micro-genre to a macro-genre discourse based on their macro-genre ``parent'' label. The point of Figure~\ref{fig:macro-v-micro-pca} is evident; {\em micro-genres combine with one another in ways that typically violate the system of oppositions and differentiation posed by macro-genre discourses}. In that respect, it is clear that the way people combine micro-genres does not follow the rule book suggested by the usual dimension-reduction analyses that rely on macro-genre labels like those shown in Figure~\ref{fig:macro-pca}. Such an approach could not make sense of the micro-genre cluster combining Classical, Opera, Gospel, Country, and Classic Rock ($k_{mg}=11)$ or the set of micro-genre clusters on the bottom left of the figure combining various (presumed) ``highbrow'' and ``Folk'' micro-genres.

 Of course, the standard approach cannot explain these micro-genre combination patterns. Some micro-genre clusters (e.g., $12 >=k_{mg}<=16$) stay within designated macro-genre discourse boundaries, consisting mainly of Rock/Pop and Afro/Pop combinations. Towards the top right, we see that the (very) vague macro-genre ``Classic Rock'' splits into micro-genre variants with the affinity to combine with various ``Country/Folk'' and "Highbrow'' micro-genres. The point of the micro-genre critique, however, is precisely that it is very likely that the {\em type} of Classic Rock that plays well with Rap is different, both stylistically and in terms of underlying audience, from the one that plays well with Country. In the same way, the type of Rap listened to by people who also like Classic Rock is likely to differ in consequential ways from the type of Rap listened to by people who also like to listen to Country.

 Overall, we learn our second lesson: Audiences combine micro-genres in ways that do not respect the traditional boundaries suggested by standard data-reduction techniques applied to macro-genre labels. As such, some substantive conclusions, such as those regarding the existence of logics or discourses that explain affinities and oppositions between macro-genre categories prevalent in previous work, are likely to have been overstated and, in most cases, misleading. The principles of vision, division, and classification people use to combine and divide micro-genre categories seem to be keyed to distinctions that cut across macro-genre categories.

 \subsubsection{Audience Segmentation and Microgenre Heterogeneity}
 A key task in the sociology of taste is linking audience engagement with particular cultural objects and genre categories to specific sociodemographic markers, primarily of class position, education, and socio-economic status, but also of such identity categories as gender, age (or generation), region of residence, and the like. This approach is crucial in getting a sense of the location of genres in social space and in making inferences about the ``status'' of genre categories themselves.

\begin{figure}[ht!]
    \centering
    \includegraphics[width=0.8\textwidth]{Figs/Link Clust/classic-rock-macro-demog.png}
    \caption{}
    \label{fig:classic-rock-main}
\end{figure}

For instance, we can ascertain whether a given cluster of genres is indeed ``highbrow'' if such high-status markers of social position like higher education diplomas, high income, managerial/professional occupational status, and the like are correlated with their consumption (and the same for ``lower status'' genre categories \citep{bryson96}. The microgenre critique suggests that this crucial task will be controverted if macrogenre labels do not correspond to phenomenologically valid objects from the perspective of personal choices. That is, the conclusions that we may reach about the ``status'' of particular genre categories will be misleading if the macrogenre labels hide substantively important and relevant audience heterogeneity at the microgenre level.

\begin{figure}[ht!]
    \centering
    \includegraphics[width=1.0\textwidth]{Figs/Link Clust/classic-rock-fav.png}
    \caption{}
    \label{fig:fav}
\end{figure}

Let us take the case of the (very) vague (and hybrid) macrogenre label ``Classic Rock/Oldies'' as a case study (a similar exercise could be done with each of the twenty macrogenre labels). This is an instructive example since the link clustering approach divides this very broad macrogenre into the most microgenres (twelve). As shown in Figure~\ref{fig:macro-v-micro-cluster}, these micro-genres combine with most of the other micro-genres, indicative of substantial levels of stylistic diversity (and cultural meaning) within the category. If we were to follow the traditional approach, an inquiry as to the audience segmentation pattern of the vague macrogenre label ``Classic Rock,'' by, for instance, specifying a logistic regression with a binary indicator that equals one if the person reports both liking and listening to the genre and a variety of socio-demographic predictors on the right-hand side, we would end up with the results shown in Figure ~\ref{fig:classic-rock-main}.

\begin{figure}[ht!]
    \centering
    \includegraphics[width=1.0\textwidth]{Figs/Link Clust/classic-rock-age.png}
    \caption{}
    \label{fig:age}
\end{figure}

In the Figure, different socio-demographic characteristics are on the y-axis, and the probability of selecting the macrogenre is on the x-axis. The points represented the predicted probability, obtained from the logistic regression model that a person with that characteristic reports both listening to and liking ``Classic Rock''; the horizontal line around the point represents the 90\% confidence interval around the prediction. The red vertical line sits at the point on the x-axis, indicating the base-probability (sample average) of engaging ``Classic Rock''; points to the right of the red line indicating socio-demographic segments that are overrepresented among Classic Rock engagers, and points to the left, represent social categories underrepresented among ``Classic Rock'' engagers.

\begin{figure}[ht!]
    \centering
    \includegraphics[width=1.0\textwidth]{Figs/Link Clust/classic-rock-educ.png}
    \caption{}
    \label{fig:educ}
\end{figure}

If we proceed in the usual fashion, we would draw various substantive conclusions regarding ``Classic Rock'' from these results. For instance, we would conclude, looking at the curvilinear---``inverted u-shape''---pattern for the effect of age, that ``Classic Rock'' is decidedly ``middle-aged'' genre, being engaged primarily by people in their 40s, 50s, and 60s--peaking for those in their late 50s---but being less likely to be engaged young adults (people younger than 40) or the old (people in their late seventies and eighties). We would also conclude that ``Classic Rock'' is a decidedly ``white'' genre, with white people being overrepresented among listeners, Black and Asian people being underrepresented, and Hispanic people being no more or less likely to engage it. We would also conclude that, beyond the higher likelihood of people without a college degree engaging ``Classic Rock," the genre does not have much class, regional, or gender differentiation (with men, women, people of class designations, and regions comparably likely to engage it). In other words, we would conclude that in the U.S. as of the early 2010s, ``Classic Rock'' is a generationally declining, raced (as white), partially classed (concerning education) musical genre that otherwise functions as a socio-demographically ``unmarked'' form of popular culture (it is the most chosen genre in the survey).

The corresponding analysis for the twelve microgenre variations, shown in Figures~\ref{fig:age} through~\ref{fig:race} shows that pretty much every single one of these conclusions is either wrong, misleading, or both. Each figure presents the twelve ``Classic Rock'' variations in a separate panel, with the corresponding predictor categories on the y-axis and the (scaled) predicted probability on the x-axis. To facilitate comparison, the shape of the effect (for age, education, and class) for all variations is presented in light gray, and the corresponding effect for that ``Classic Rock'' microgenre is highlighted. Figures~\ref{fig:gender} and \ref{fig:race} show a dot plot using the same data visualization strategy. Additionally, to get more insight regarding the ``Classic Rock'' taste communities revealed by the microgenre analysis, Figure~\ref{fig:fav} plots the probability (on the x-axis) that people who chose each of the ``Classic Rock'' microgenres (on separate plot panels) reports choosing one of the twenty original macrogenres as their favorite. To facilitate interpretation, only macrogenres that are one-half a standard deviation above the predicted value are highlighted, indicating the strongest macrogenre preferences.

\begin{figure}[ht!]
    \centering
    \includegraphics[width=1.0\textwidth]{Figs/Link Clust/classic-rock-class.png}
    \caption{}
    \label{fig:class}
\end{figure}

First, take the characterization of ``Classic Rock'' as a generationally ``middle-aged'' genre. As shown in Figure~\ref{fig:age}, the shape of the age effect varies consequentially across the different microgenre variations. As such, we could conclude that ``Classic Rock'' is relatively age-neutral (1), tilts young (2, 4), is preferred by people in their forties (3, 12), or tilts towards senior citizens (5 and 6). Even for those ``Classic Rock'' microgenres for which the peak of the inverted u-shaped effect for age is preserved for people in their fifties and sixties, the peak varies systematically. Accordingly, the characterization of ``middle-aged'' would range from people in their 50s (10, 11) or their sixties (7, 8, 9).

\begin{figure}[ht!]
    \centering
    \includegraphics[width=1.0\textwidth]{Figs/Link Clust/classic-rock-gender.png}
    \caption{}
    \label{fig:gender}
\end{figure}

Looking at Figures~\ref{fig:educ} and Figure~\ref{fig:class}, we would also have to revise our conclusions about the alleged class neutrality of ``Classic Rock'' as a form of popular culture. While, indeed, some variants are class-neutral, others variants are decidedly class-inflected. For instance, (1) repels people without educational qualifications but attracts high-income people; (3) on the other hand, repels high-income people but attracts the highly educated. Variation (8) has an extreme tilt toward the less educated, and repels upper middle class and high-income people; as Figure~\ref{fig:fav} shows, fans of this Classic Rock variation are likely to report considering Bluegrass and Country as their favorite macrogenres. Other microgenre variations of ``Classic Rock'' like (10) and (11), appeal primarily to a socio-economically upper-middle class and high-income audience. Note that as shown in Figure~\ref{fig:fav} this is a variant combining preferentially with microgenre variations of Folk, Easy, and Country. These people are likely to report considering ``Classic Rock'' and Easy Listening as their favorite macrogenres.

A similar story emerges for gender. While Figure~\ref{fig:classic-rock-main}, suggests that the macrogenre label ``Classic Rock'' is only weakly gendered, Figure~\ref{fig:gender} shows wide variation in the extent to which different microgenre variations appeal to men and women. Some like (3), (5), and (7) tilt toward women; others like (4), (11), and, particularly (12) tilt toward men. Note that fans of microgenre (12) are also disproportionately likely to report having Hard Rock/Heavy Metal as their favorite macrogenre, shedding light on its extreme tilt toward men.

\begin{figure}[ht!]
    \centering
    \includegraphics[width=1.0\textwidth]{Figs/Link Clust/classic-rock-race.png}
    \caption{}
    \label{fig:race}
\end{figure}

Looking at Figure~\ref{fig:race}, we can conclude that when it comes to ``Classic Rock'' having a racial tilt toward white people, the macrogenre analysis is not too misleading; most of the predicted probability estimates for this ethnoracial category are to the right of the expected mean. The same goes for its lack of appeal for people who racially identify as Black; most of the predicted probability estimates for this ethnoracial category are to the left of the expected mean for this socio-demographic category. However, the macrogenre analysis hides a lot of variation in the appeal of different variants of ``Classic Rock'' for both Hispanics and Asians. People whos self-identify as Hispanic are attracted to (1), (2), (3), and particularly (10) and (12). People who identify as Asian, on the other hand, are attracted to (5) and (6); note that as shown in Figure~\ref{fig:fav}, fans of these last two microgenre variations are also likely to report having such macrogenres as Classical, Broadway Showtunes, and Jazz as their favorites, as noted earlier these two variants also tend to have the oldest audiences.

\section{Discussion}
Let us take stock. We began our discussion with the network or ``relational'' revolution in the quantitative study of taste in sociology \citep{pachucki2010cultural}. We noted that many good things have come from considering survey data on taste using a relational lens, including a deeper specification of core concepts in the literature and even discovering new phenomena and empirical patterns. However, we also noted that survey data are as good as the labels chosen to collect the data. A resurgent line of critics questions whether the labels that appear in our most venerable survey-based studies are true ``genres'' in the sociological (or even stylistic) sense \citep{lena2015relational, vlegels2015music}. The labels are broad, likely to be interpreted by people in heterogeneous ways, and thus hide as much as they reveal. I noted recent attempts to just drop the idea of vague macro-genre labels and either study actual sociological genres on the ground (thus partially abandoning studies of audience segmentation or at least radically reconfigure them) or ``dropping the label'' \citep{sonnett2016ambivalence} by querying people about more focused objects of taste (e.g., performers within genres). These are all important and good developments, but we also noted that they may throw away a good thing. Upping the relationality by exploiting hidden patterns in the same old vague macro-genre-based data collected before can reveal focused micro-genres.

I proposed to do this using recent developments in the discovery of \textit{overlapping communities} in networks \citep{ahn_etal10}, which partially answers two of the challenges of macro-genre critics: The fact that actual genres are overlapping and not crisply bounded. The fact that there is hidden heterogeneity within the broad labels we usually focus on. Our analysis contrasted the application of the usual techniques to the same data, conceived in the usual ``macro" way, and \textit{after} upping the relationality and discovering the micro-genres hidden within. It is clear that focusing on micro-genres reveals variation and patterns of cultural choice (as well as audience segmentation) that we would not have noticed using the standard approach (in this, the critics are right). Still, we could do this without dropping the label or querying people about hundreds of micro-styles (most of which they'd be unfamiliar with). Instead, we exploited the venerable principle, etched into classical approaches to defining genres in network terms \citep{dimaggio1987classification}, noting that if genres are defined by the people that choose them, then they are also defined by the other choices that people make when they choose them; the country that combines with one version of Classical may not be the same country that combines with a version of the Blues (and neither is the same as the country that refuses to combine with any other style).

The approach here is general and can be applied to studying other genre complexes beyond musical taste (allowing for economic data collection) and to studying other processes beyond taste. This includes belief, opinion, and attitude data. Essentially allows us to move from ``vague'' responses to more focused responses by exploiting the hidden patterns in the inter-response network formed when people respond to other items. Overall, we also learned a general lesson concerning our usual people or item classification techniques: To the extent that these are applied to items that themselves are ``vaguely'' defined, they will also yield even vaguer (and perhaps less than useful) macro-classifications of those items (like ``popular'' and ``high status''). The same may be said for such macro-classifications of opinions such as ``liberal'' and ``conservative,'' which, while being the primary way we interpret how people split themselves into groups by the beliefs they choose to hold, is decreasingly apt today if they ever were.

\bibliography{refs.bib}
\end{document}

### 2023-02-06 three-variations.tex
Initial Overleaf Import

\section{Macro-genre Analysis Strategies: Three Variations}
There are three standard analytic approaches in the quantitative sociology of taste. All begin from the same starting point, however, a rectangular (two-way, two-mode) matrix ($A$) with (usually) people $\left(P1, P2, P3,\ldots P_N
\right)$ in the rows and cultural genres $\left(G1, G2, G3,\dots G_K\right)$ in the columns. As noted at the outset, the {\em ways} of the matrix are the number of dimensions, and the {\em modes} of the matrix are the number of entity types for which data have been collected \citep{borgatti_everett97}. In the usual case, we have two-way, two-mode (people and genres) data \citep{lizardo18}. The goal of the analysis is to learn some kind of \textit{classification} of either the people or the genres (or both) from the data. This setup is shown in figure~\ref{fig:reg_approaches}.

In this (toy) example, we have five people and four genres. Each cell in the $A_{PG}$ matrix equals one when person $P$ engages (e.g., likes, listens) genre $G$; otherwise, it equals zero. Reading across the rows, we find each person's pattern of cultural choices \citep{peterson83}. So we learn that person 1 engages genres 2 and 3, and person 3 engages all four genres; maybe they are an ``omnivore''. Reading down each column, we find the popularity of each genre or the number of people who engage in it. So we learn that genre 4 is engaged by four people (2, 3, 4, and 5), and genre 2 is only engaged by two people (3 and 4). Maybe genre 4 is a ``popular'' genre, and genre 2 is a ``niche'' genre \citep{lizardo18}.

Of course, researchers usually want to go beyond describing the cultural choice patterns of individual people or the audience distribution of each genre. Instead, researchers use specific data reduction techniques to classify either the genres, the people or both. Let us consider each of these possibilities in turn.

\begin{figure}[ht!]
 \centering
 \includegraphics[width=1.0\textwidth]{Figs/Regular/reg-approaches.png}
 \caption{Three approaches to classifying survey data on cultural tastes.}
 \label{fig:reg_approaches}
\end{figure}

\subsection{Classifying Genres: Factor Analysis (FA)}
One thing that we could do with the (real) data described earlier is to attempt to come up with a classification of musical genres. Recall that in these data, we have $2263$ people in the rows and $20$ (musical) genres in the columns. One well-established and long-pedigreed technique allowing us to come up with clumps of the variables in a person-by-variables table (with a long history in psychometrics) is Factor Analysis (FA). This method uses the genres as variables and relies on a factorization (hence the name) of the correlation or covariance matrix between these variables to extract a smaller number of dimensions. We can then classify each genre based on their loading (e.g., correlation with) each dimension extracted. The output of such an exploratory factor analysis of the SSI 2012 data, featuring a four-factor solution, is shown in figure~\ref{fig:efa}.

\begin{figure}[ht!]
 \centering
 \includegraphics[width=1.0\textwidth]{Figs/Regular/genre-efa-regular.png}
 \caption{\footnotesize Point and line plot of exploratory factor analysis results (four-factor solution) of the musical taste data. Positive loadings between each factor (circles) and each of the genres (squares) shown as green edges. Negative loadings shown as red edges. Edge width is proportional to magnitude. Node labels should be read as follows. Factor 1 (red Nodes): Ltn (Latin/Spanish), R\_H (Rap/Hip Hop), B\_R (Blues and R \& B), Rgg (Reggae), D\_C (Dance/Club); Factor 2 (green nodes): Cls = Classical, Opr = Opera, Jzz = Jazz, Brd = Broadway Musicals, Esy = Easy Listening, Bgb = Big Band, Factor 3 (teal nodes): Cl\_R = Classic Rock/Oldies, Pop = Pop/Top 40, Cn\_R = Contemporary Rock, I\_A = Indie/Alternative, H\_M = Hard Rock/Heavy Metal; Factor 4 (purple nodes): Cnt = Country, Blg = Bluegrass, Flk = Folk, Gsp = Gospel.}
   \label{fig:efa}
\end{figure}

How do we interpret these pattern of results? One approach, for instance followed by \citet{vaneijck01}, is to inspect the factor loadings as indicating a classification of genres according to a higher order principle (e.g., logics or discourses); namely, a set of ``meta-genres.'' The results of the factor analysis is broadly consistent with such a hypothesis. For instance, factor 3 groups all the ``rock and pop'' related genres, and factor 1 groups together a related set of ``Afro-pop'' genres such as Rap, Reggae, and R\&B. Together, they might constitute a discourse of ``fun.'' Factor 2 groups together all the usual ``highbrow'' genres, such as Classical, Opera, and Jazz, reflecting a more austere ``art'' discourse. Finally, the genres loading highly on factor 4 such as Country, Bluegrass, and Folk may reflect a more down to earth ``folk'' discourse linked to roots authenticity \cite{vaneijck01}.

\subsection{Classifying the People: Latent Class Analysis (LCA)}
Another approach relies not on classifying the genres, but classifying the people. The idea here is to rely on the fact that each person produces a ``response pattern'' (a ``pattern of cultural choice'' in Richard Peterson's \citeyear{peterson83} classic locution).The pattern corresponding to a person ($P_i$) is thus the vector of zeros and ones corresponding to their row in the matrix shown in Figure~\ref{fig:reg_approaches}. The idea is that we can then (probabilistically) clump people into classes based on how similar these patterns are. People with similar patterns end up in the same clump; people with dissimilar patterns end up in different clumps \citep{chan_goldthorpe07, tampubolon2008revisiting}. One well-established and equally long-pedigreed technique that allows us to group people into clumps in a person by (categorical) variables table (with a long history in sociology, marketing and related fields) is Latent Class Analysis (LCA).

\begin{figure}[ht!]
 \centering
 \includegraphics[width=1.0\textwidth]{Figs/Regular/genre-lca-regular.png}
 \caption{\footnotesize Stacked bar plot showing the proportion of people (shown in the x-axis) engaging ("yes" in dark blue) and not engaging ("no" in light blue) each genre (shown in the y-axis) by latent class assignment (plot panels).}
  \label{fig:lca}
 \end{figure}

The main output from an LCA is an $m$-dimensional vector (where $m$ is the number of latent classes requested) assigning each row $i$ of the data matrix (in this case the people) a probability of belonging to the $j^{th}$ latent class. Because memberships are mutually exclusive (each person can only belong to one latent class), these probabilities have to sum to $1.0$. This means that, if the solution fits the data well, one of the probabilities in the vector will be much larger than the others (e.g., $m_{ij} > 0.90$). We can then we can assign each person to the class they have the largest probability of belonging to. Once we have assigned each person to a class, we can go back to the data, and see how the clumps of people assigned to different classes differ in their cultural choice patterns. The output of such an exploratory latent class analysis applied to the same data as before, and featuring a six-class solution, is shown in figure~\ref{fig:lca}.

How do we interpret these pattern of results? The usual approach in the sociology of taste, exemplified by \citet{chan_goldthorpe07} and \citet{tampubolon2008revisiting}, is to use the conditional probabilities of engaging genre $G$ given that a person belongs to class $m$ (shown in the separate panels of figure~\ref{fig:lca}) to baptize the classes with a given name. Thus, information from the genres (whether given by previous research, theory, or intuition) can help us make sense of what each of the people clumps means. For instance, we may find that one class of people (in this case class 4) has relatively high probabilities of engaging {\em all} genres. Maybe they are ``omnivores'' \citep{peterson_kern96}. Others, only engage have a high probability of engaging a couple of genres like Country and Classic Rock/Oldies (Class 2); maybe they are ``univores'' \citep{peterson92}. Some univores (like Class 1) just engaging very fancy, traditionally high-status genres like Classical; others (like Class 5) specialize in ``Afro-Pop" genres like Rap/Hip Hop and R\&B, while others (like Class 6) gravitate toward Contemporary Rock, Pop, Indie and Alternative music.

We could further investigate the demographic composition of each class, by for instance, fitting a regression model for categorical response variables with multiple modalities (e.g., like the Multinomial Logit model) in the ``three-step'' approach \citep{bakk2013estimating}, or doing everything in one-step (letting the classes be affected by exogenous covariates, as with \citet{tampubolon2008revisiting}). We could then examine hypotheses about whether omnivores are young and educated, highbrow univores are old, Country/Oldies univores live mostly in the American South, Afro-Pop univores are more likely to be young and non-white and so forth (fancier approaches would do the class assignment and the regression model in a more efficient single step, but it is the same idea).

\subsection{Classifying the People and the Genres: Multiple Correspondence Analysis (MCA)}
Finally, we may be interested in a technique that allows for the simultaneous classification of the people and the genres. The go-to technique for this job is Multiple Correspondence Analysis (MCA). Correspondence Analysis and related techniques have as old and storied histories as FA and LCA, but for a long time remained a well-kept secret (for English speakers) ensconced in multi-volume French mathematical monographs written by Jean-Paul Benz\'{e}cri and collaborators.

Today the situation is different. MCA has now been fully introduced and extended in various anglophone monographs and collections \citep{leroux_rouanet04, greenacre_blasius06}, and algorithms implementing the basic mathematical ideas available in the standard statistical packages \citep{le_etal08}. Because of this, and very much ironically, while MCA (and not regression FA, or LCA) could be considered one of the {\em first} techniques that reinvigorated the modern empirical study of taste in sociology (figuring prominently in Pierre Bourdieu's \citeyearpar{bourdieu84} field-defining classic \emph{Distinction}), it has not been until recent that the method has begun to be used widely \citep[see][among many others]{flemmen_etal18, roose_etal12, savage_gayo11}.  
 \begin{figure}[ht!]
 \centering
 \includegraphics[width=1.0\textwidth]{Figs/Toy/mca-toy-ex.png}
 \caption{\footnotesize Transformation of original data matrix of people by genres, to an indicator matrix of people by genre-modality.}
  \label{fig:mca-toy}
 \end{figure}

 How does MCA work the magic of providing us with a simultaneous classification of people and genres? The trick, revealed in Figure~\ref{fig:mca-toy} using our running toy example, is to transform the original two-mode data matrix into an indicator matrix. In the indicator matrix, there is a column not for each variable (like in the original two-mode data) but for each {\em category of each variable} (these are usually called ``modalities'' in MCA-speak \citep{leroux_rouanet04}). Each variable has two categories in our toy case (and our real data). So we go from a 5 $\times$ 4 matrix to a 5 $\times$ 8 one (see Figure~\ref{fig:mca-toy}). Each genre $G$ column splits into two columns, $G_Y$ and $G_N$, and we put a one in the corresponding cell of the matrix under column $G_Y$ if the individual engages (e.g., likes, listens) to the genre. If the individual does not engage the genre, we put a one under the $G_N$.

 The singular value decomposition (a kind of ``factor analysis for matrices'') of a suitable transformed version (each cell entry weighted by the row and column marginal sum) of the indicator matrix yields scores for each row and each column (both the "yes" and "no" answers to engaging the genre in our toy example) along many ``dimensions'' (also called ``axes'' or ``principal components''). Like in FA, the dimensions are ordered so that the first captures the closest representation of the original matrix (in the least squares sense), the second captures the best representation of the stuff left over, and so forth. The scores on each dimension are orthogonal and thus can be plotted in Euclidean space (e.g., of two dimensions). This can be seen as a low-dimensional representation of the original multidimensional matrix object. The clumps of people and genres thus emerge as clusters of (same-kind) entities that end up close together in this low-dimensional space. The capacity to visualize both people and especially the genres ``social space'' is one of the main appeals of the method \citep{greenacre_blasius06}, as evident in Bourdieu's \citeyearpar{bourdieu84} classic work. These scores are the main thing that MCA learns from the data. The output of such a multiple correspondence analysis of the data, featuring a four-factor solution, is shown in figure~\ref{fig:mca}.

 \begin{figure}[ht!]
 \centering
 \includegraphics[width=1.0\textwidth]{Figs/Regular/genre-mca-regular.png}
    \caption{Multiple Correspondence Analysis (first four dimensions) of the musical taste data. Survey modalities (genre chosen: Yes/No) shown in blue text, ``cloud of individuals" shown as red points with shading proportional to the contribution. Inset plot (blue bars) show eigenvalues of first eight dimensions.}
    \label{fig:mca}
 \end{figure}

 How do we interpret these pattern of results? We can follow some of (many) recent papers that have used MCA to understand the link between people and genres \citep[e.g.,][]{roose_etal12}. As noted we can see the modalities that clump together along a given dimension as telling us something about what that dimension represents. So, looking at the horizontal (first) dimension of the left-hand side biplot (panel a), it is easy to see that all the "yes" modalities are to left of that horizontal dimension (indicating values greater than zero) and all the "no" modalities are to the right. So the main thing that the MCA picks up is a distinction between people who engage the genres and people who do not (actives versus abstainers). Note that the both people (the red dots forming the ``cloud of individuals'') and the genre modalities are distributed in a classic ``horseshoe'' pattern in this space, indicating that this first dimension is {\em ordinal}, separating people who engage many genres from those who engage none. This finding has been replicated repeatedly in many MCA analyses done on various cultural taste and participation data across dozens of countries.

 What does the second dimension tell us? Well, it seems like (looking at panel b) here, the usual distinction between fancy, high-status genres (with high positive scores at the top) and popular, industry, or just plain fun genres (with high negative scores at the bottom) reasserts itself. So ``net" of engagement, we find that engagers are partitioned across a highbrow/popular divide \citep{roose_etal12, flemmen_etal18}. Looking at genre clumps (really active engagement with genres clumps) in dimensions 3 and 4 reveals further insights. In fact, looking at how the genres and the people are distributed in this space, we can see that net of the quantitative distinction between engagers and non-engagers, and the broad binary genre distinction between ``traditional and popular'' what re-appears is the van Eijckian pattern differentiating of genres into four discourses or meta-genres: The same genre classification revealed by FA (see Figure~\ref{fig:efa}). Categories indicating engagement with (predominantly white-performer-dominated) rock genres clump together, engagement with Folk and Country genres clumps together, traditionally fancy genres clump together, and ``Afro-pop'' pop genres clump together. People are evenly distributed (in a nice circle) across all four quadrants of this space, indicating that these logics may be a powerful organizing principle of the ``musical taste field'' \citep{savage_gayo11} in the contemporary U.S.

More advanced applications of MCA would be beyond eyeballing the clumps and do some other things \citep{leroux_rouanet04}. For instance, since MCA produced scores along a multidimensional Euclidean space, this means that {\em distances} among each pair of elements of the same kind (people or genre engagement modalities) are defined. We can thus compute such distances and produce data (not eye) driven clumps using hierarchical clustering (with Ward's criterion) \citep{becue-bertaut_pages08}, an approach that was first developed by Benz\'{e}cri himself \citep{leroux_rouanet04}. We could also ``project'' categories (modalities) corresponding to people's demographic characteristics (e.g., by computing the average score in each dimension for people with e.g., a college degree, professional occupation, and so forth). We could even engage standard hypothesis testing, by for instance, figuring out if the mean score in Dimension 3 is statistically different for people who identify with different ethnoracial categories \citep{flemmen_etal18}.

\section{Getting out of the (Macro) Genre Bubble}
There is no question that the three approaches so far discussed, used to classify genres, classify people, or simultaneously classify people and genres, are the workhorses of the quantitative empirical study of taste today. All, by the same token, are vulnerable to the ``genre'' critique outlined in the introduction. For instance, both FA and MCA suggest that engagement with ``Opera'' or ``Classical'' is different from engagement with ``Rap'' or ``Country.'' These (macro) genres belong to different universes, discourses, or what have you \citep{vaneijck01}. But a critic of the genre concept can point to other types of qualitative and historical evidence collected on both people and genres, weakening our confidence in this conclusion \citep{lena2015relational}. All provide fodder for a version of the micro-genre or genre differentiation critique of traditional quantitative empirical work on the sociology of taste that does not collect sufficiently fine-grained information on cultural preferences.

Notably, {\em what} technique you use (FA, LCA, MCA) does not really matter; from the micro-genre critique perspective, it is garbage in and garbage out. MCA will produce an ``opposition'' between macro-genres and even results that are consistent with techniques (such as FA) that are usually posed as enemies of MCA. The problem is that poor MCA (or LCA or any other method) only has the macro-genre-based categories to work with. Tasked with finding patterns using these data, the algorithm delivers, but what it delivers is, from the micro-genre perspective, misleading or only partially true results.

### 2023-05-16 01_link-distance-matrix.qmd
This is a new commit for what I originally planned to be amended

---
    title: "Discovering Focused Microgenre Communities: Link Clustering"
    author: "Omar Lizardo"
    date: "`r Sys.Date()`"
    output:
        html_document: default
---

# Setup
```{r setup}
    knitr::opts_chunk$set(include=FALSE, echo = TRUE, warning = FALSE, message = FALSE)
    require("dendextend")
    require("fastcluster")
    require("here")   
    require("haven")
    require("tidyverse")
    source(here("Functions", "link.dist.R"))
```

# Data Wrangling
```{r Importing and creating two mode data frame of people by genres}
    taste.dat <- read_dta("C:/Users/Omar Lizardo/Google Drive/MISC DATA SOURCES/SSI-2012/SSI2012.dta")
    taste.dat <- taste.dat %>% 
      dplyr::select("id", ends_with(c("lis", "like")), -starts_with("none")) %>% 
      dplyr::select(c(1:41)) %>% 
      na.omit() %>% 
      mutate(Classical = classicallike * classicallis,
             Opera = operalike * operalis,
             Jazz = jazzlike * jazzlis,
             Broadway = bwaystlike * bwaystlis,
             Easy = moodezlike * moodezlis, 
             Bigband = bbandlike * bbandlis,
             Classic_Rock = croldlike * croldlis,
             Country = countrylike * countrylis,
             Bluegrass = blueglike * blueglis,
             Folk = folklike * folklis,
             Gospel = hymgoslike * hymgoslis,
             Latin = latlpsallike * latspsallis,
             Rap_Hip_Hop = raphiphoplike * raphiphoplis,
             Blues_RandB = blurblike * blurblis,
             Reggae = reggaelike * reggaelis,
             Pop = toppoplike * toppoplis,
             Contemp_Rock = controcklike * controcklis,
             Indie_Alt = indaltlike * indaltlis,
             Dance_Club = danclublike * danclublis,
             Heavy_Metal = hvymtllike * hvymtllis
             ) %>%  #people are linked to genres that the both like and listen to
      dplyr::select(id, Classical:Heavy_Metal)
      taste.mat <- as.matrix(taste.dat[, 2:ncol(taste.dat)])
```

```{r Importing demographic data}
        ed.labs <- c("< High School", "High School/GED", "Associate", "Some College", "Bachelor's", "Postgraduate")
        demog.dat <- read_dta("C:/Users/Omar Lizardo/Google Drive/MISC DATA SOURCES/SSI-2012/SSI2012.dta") %>% 
          dplyr::select(c("id", "age", "agemid", "female", "raceeth", 
                          "nodipdeg", "hsged", "somcol", "aadeg", "bach", "ma", 
                          "docprof", "incmid", "income", "percclass",
                          "region", "occ", "parented", "empstat", "favgen")) %>% 
          as_factor() %>% 
          mutate(educ = if_else(nodipdeg == "yes", 1, 
                                if_else(hsged == "yes", 2, 
                                        if_else(aadeg == "yes", 3, 
                                                if_else(somcol == "yes", 4,
                                                        if_else(bach == "yes", 5,
                                                                if_else(ma == "yes" | docprof == "yes", 6, 1)))))),
                 educ = factor(educ, labels = ed.labs),
                 percclass = fct_recode(percclass,
                                        "Lower Class I.D." = "lower class",
                                        "Workng Class I.D." = "working class",
                                        "Middle/Upper Class I.D." = "middle class",
                                        "Middle/Upper Class I.D." = "upper class"),
                 raceeth = fct_recode(raceeth,
                                      "Asian" = "Asian",
                                      "Black" = "Black",
                                      "Hisp." = "Hispanic",
                                      "White" = "White",
                                      "Mult./Other" = ">1 race",
                                      "Mult./Other" = "other"),
                 female = fct_recode(female, 
                                     "Men" = "male", 
                                             "Women" = "female"),
                 region = fct_recode(region,
                                     "New England" = "New Enlgnad",
                                     "South" = "East South",
                                     "South" = "South Atlantic",
                                     "Southwest" = "West South",
                                     "Midwest" = "Eastern Midwest",
                                     "Midwest" = "Western Midwest",
                                     "Mountain" = "Mountain West",
                                     "West Coast" = "Pacific West"),
                 parented = fct_recode(parented, 
                                       "Parent College? (No)" = "parent no college", 
                                       "Parent College? (Yes)" = "parent college"),
                 empstat_n = factor(as.numeric(empstat)),
                 objclass = case_when(incmid == "5000" | incmid == "15000" ~ 1,
                                      incmid == "25000" | incmid == "35000" ~ 2, 
                                      incmid == "45000" | incmid == "55000" | incmid == "65000" ~ 4,
                                      incmid == "75000" | incmid == "85000" | incmid == "95000" ~ 5,
                                      incmid == "105000" | incmid == "115000" | 
                                        incmid == "125000" | incmid == "135000" |
                                        incmid == "145000" | incmid == "150000" |
                                        incmid == "165000" | incmid == "175000" |
                                        incmid == "185000" | incmid == "195000" |
                                        incmid == "212500" | incmid == "237500" |
                                        incmid == "250,000 or more" ~ 6),
                 objclass = factor(objclass, labels = c("Poor", "Working Class", "Middle Class", "Upper Middle Class", "High Income")),
                 educ_n = as.numeric(educ),
                 college = if_else(educ_n > 4, 1, 0),
                 college = factor(college, labels = c("No Degree", "College")),
                 age_n = as.numeric(age),
                 objclass_n = as.numeric(objclass)
          ) %>% 
          dplyr::select(-c("nodipdeg", "hsged", "somcol", "aadeg", "bach", "ma", "docprof")) %>% 
            mutate(id = as.integer(id)) %>% 
            na.omit() 
```

# Link Clustering
```{r Performing link clustering and saving results}
    ldist.res <- link.dist(x = taste.mat, id = taste.dat$id) #computing link by link distance matrix
    lclust.res <- hclust(ldist.res$dist, method = "ward.D2") #link clustering of link by link distance matrix
    lclust.dend <- as.dendrogram(lclust.res) #transforming link clustering into dendrogram
```

```{r Creating objects for analysis}
    dend.macro <- cut(lclust.dend, h = 8) #cutting at macrogenre level
    a <- data.frame(g.size = sapply(dend.macro$lower, nleaves)) #macrogenres as ordered in dendrogram results
    b <- data.frame(g.size = colSums(taste.mat), g.names = names(colSums(taste.mat))) #original macrogenre sizes
    c <- right_join(a, b) #joining data frames by macrogenre sizes to get macrogenre labels ordered by dendrogram results
    names(dend.macro$lower) <- c$g.names #naming macrogenre dendrogram list
    n.micro <- sapply(dend.macro$lower, function(x) {length(table(cutree(x, h = 3)))}) #number of microgenres per macrogenre
    v <- sapply(sapply(n.micro, function(x) {1:x}), as.numeric)
    micro.g.names <- paste(c$g.names[1], v[[1]], sep = "_")
    for (i in 2:20) {
      micro.g.names <- c(micro.g.names, paste(c$g.names[i], v[[i]], sep = "_"))
        }
    bin.char <- function(x) { 
      if_else(is.na(x), 0, 1) #function to binarize data
        }
    dend.micro <- cut(lclust.dend, h = 3) #cutting at microgenre level
    edge.labs <- data.frame(id = ldist.res$edge.list[, 1],
                            macro.g = ldist.res$edge.list[, 2], 
                            edge.num = 1:nrow(ldist.res$edge.list)) #grabbing people and genre id labels
    micro.g.clust <- lapply(dend.micro$lower, labels) %>%
        lapply(data.frame) %>% 
        bind_rows() #transforming clustering cut results into data frame
    names(micro.g.clust) <- "edge.num" #adding column label
    micro.g.long <- data.frame(micro.g = rep(1:102, sapply(dend.micro$lower, nleaves)))
    micro.g.dat <- bind_cols(micro.g.clust, micro.g.long)
    micro.g.dat <- right_join(micro.g.dat, edge.labs) %>%
      mutate(micro.g.f = factor(micro.g, labels = micro.g.names),
             macro.g.f = factor(macro.g, labels = names(colSums(taste.mat))),
             micro.g.c = as.character(micro.g.f),
             macro.g.c = as.character(macro.g.f)) %>% 
      pivot_wider(id_cols = "id",
                  names_from = "micro.g.c",
                  values_from = "micro.g") %>% 
      mutate(across(is.integer, bin.char)) %>% 
      mutate(id = as.integer(id)) %>% 
      arrange(id)
```

# Saving Objects
```{r Remove garbage and keep important stuff}
    b <- ls()[! ls() %in% c("ldist.res", "lclust.res", "dend.macro", "dend.micro", "lclust.dend", "micro.g.names", "n.micro", "taste.dat", "demog.dat", "micro.g.dat")]
    rm(list = b)
    ls()
```

```{r Saving image}
    save.image(file= here("dat", "lclust-res.RData"))
```

### 2023-05-16 02_toy-ex.qmd
This is a new commit for what I originally planned to be amended

---
title: "Discovering Focused Microgenre Communities: Toy example"
author: "Omar Lizardo"
date: "`r Sys.Date()`"
---

# Setup
```{r setup}
    knitr::opts_chunk$set(include=FALSE, echo = TRUE, warning = FALSE, message = FALSE)
    library("fastcluster")
    library("factoextra")
    library("here")
    library("ggplot2")
    library("sjPlot")
    source(here("R", "Functions", "link.dist.R"))
```

# Link Clustering (Toy Example)
```{r Link Clustering toy example}
    x <- c(0, 1, 1, 0, 
           0, 0, 0, 1, 
           1, 1, 1, 1, 
           1, 0, 0, 1, 
           0, 0, 1, 1)
    x <- matrix(x, nrow = 5, ncol = 4,  byrow = TRUE) #toy data
    ldist.res <- link.dist(x = x, id = c(1:5)) #link distance matrix
    hc.res <- hclust(ldist.res$dist, method = "ward.D2") #link clustering
```

```{r Plotting toy example dendrogram}
    hc.res$labels <- c("P1-G2", "P1-G3", "P2-G4", "P3-G1", "P3-G2", "P3-G3", "P3-G4", "P4-G1", "P4-G4", "P5-G3", "P5-G4")
    p <- fviz_dend(hc.res, k = 4, k_colors = "uchicago", show_labels = TRUE, cex = 1.5, lwd = 2) 
    p <- p + geom_hline(yintercept = 0.75, linetype = "dashed", color = "red", size = 1.2)
    p <- p + labs(y = "", title = "") 
    p <- p + theme(axis.line.y = element_blank(), axis.text.y = element_blank())
    p
    save_plot(here("Plots", "Dend", "link-clust-toy5.png"), 
              width = 40, height = 25)
```

### 2023-05-16 03_real-dends.qmd
This is a new commit for what I originally planned to be amended

---
    title: "Discovering Focused Microgenre Communities: Dendrograms"
    author: "Omar Lizardo"
    date: "`r Sys.Date()`"
    output:
        html_document: default
---

# Setup
```{r setup}
    knitr::opts_chunk$set(include=FALSE, echo = TRUE, warning = FALSE, message = FALSE)
    require("dendextend")
    require("here")
    require("RColorBrewer")
```

```{r Loading link distance matrix and performing link clustering}
    load(file= here("dat", "lclust-res.RData"))
```

# Dendrogram Plots from Link Clustered Data
```{r Plotting macrogenre dendrograms (1)}
    k <- length(dend.macro$lower)
    png(here("Plots", "Dend", "all-branches-macro.png"), height = 900, width = 1600)
    d <- lclust.dend
    d %>% 
      set("labels", c(rep("", nleaves(d)))) %>% 
      set("branches_k_color", value = brewer.pal(k, "Dark2"), k = k) %>% 
      set("branches_lwd", value = 3) %>%
      plot(axes = FALSE) %>% 
      abline(h = 8, col="red", lty = 2, lwd = 3) 
```

```{r Plotting macrogenre dendrograms (2)}
    k <- length(dend.macro$lower)
    png(here("Plots", "Dend", "all-branches-macro-labels.png"), height = 900, width = 1600)
    d <- dend.macro$upper
    d %>% 
      set("labels", dend.macro$lower %>% names) %>% 
      set("branches_k_color", value = brewer.pal(k, "Dark2")) %>% 
      set("branches_lwd", value = 4) %>% 
      set("labels_color", value = brewer.pal(k, "Dark2")) %>% 
      set("labels_cex", value = 2.5) %>% 
      plot(axes = FALSE) 
    abline(h = 8, col="red", lty = 2, lwd = 3)
```

```{r Plotting microgenre dendrograms (1)}
    k <- length(dend.micro$lower)
    png(here("Plots", "Dend", "all-branches-micro.png"), height = 900, width = 1600)
    k <- length(dend.micro$lower)
    d <- lclust.dend
    d %>% 
      set("labels", c(rep("", nleaves(d)))) %>% 
      set("branches_k_color", value = brewer.pal(k, "Dark2"), k = k) %>% 
      set("branches_lwd", value = 3) %>%
      plot(axes = FALSE) %>% 
      abline(h = 3, col="red", lty = 2, lwd = 3) 
```

```{r Plotting microgenre dendrograms (2)}
    k <- length(dend.micro$lower)
    png(here("Plots", "Dend", "all-branches-micro-labels.png"), height = 900, width = 1600)
    d <- dend.micro$upper
    d %>% 
      set("labels", micro.g.names) %>% 
      set("branches_k_color", value = brewer.pal(k, "Dark2"), k = k) %>% 
      set("branches_lwd", value = 3) %>% 
      set("labels_color", value = brewer.pal(k, "Dark2")) %>% 
      set("labels_cex", value = 0.9) %>% 
      plot(axes = FALSE) 
    par(cex= 2.5)
    title(xlab="", ylab="", main="") %>% 
      abline(h = 3, col="red", lty = 2, lwd = 3)
```

```{r Plotting genre-specific dendrograms (1)}
    png(here("Plots", "Dend", "classic-rock-branches.png"), height = 900, width = 1600)
    k <- n.micro["Classic_Rock"]
    d <- dend.macro$lower$Classic_Rock
    d %>% 
      set("labels", c(rep("", nleaves(d)))) %>% 
      set("branches_k_color", value = brewer.pal(k, "Dark2"), k = k) %>% 
      set("branches_lwd", value = 3) %>% 
      plot(axes = FALSE) 
    par(cex = 5)
    title(xlab="", ylab="", main="Classic Rock") %>% 
      abline(h = 3, col="red", lty = 2, lwd = 3)
```

```{r Plotting genre-specific dendrograms (2)}
    png(here("Plots", "Dend", "blues-branches.png"), height = 900, width = 1600)
    k <- n.micro["Blues_RandB"]
    d <- dend.macro$lower$Blues_RandB
    d %>% 
      set("labels", c(rep("", nleaves(d)))) %>% 
      set("branches_k_color", value = brewer.pal(k, "Dark2"), k = k) %>% 
      set("branches_lwd", value = 3) %>%        
      plot(axes = FALSE) 
    par(cex = 5)
    title(xlab="", ylab="", main="Blues/R&B") %>% 
      abline(h = 3, col="red", lty = 2, lwd = 3)
```

```{r Plotting genre-specific dendrograms (3)}
    png(here("Plots", "Dend", "opera-branches.png"), height = 900, width = 1600)
    k <- n.micro["Opera"]
    d <- dend.macro$lower$Opera
    d %>% 
      set("labels", c(rep("", nleaves(d)))) %>% 
      set("branches_k_color", value = brewer.pal(k, "Dark2"), k = k) %>% 
      set("branches_lwd", value = 3) %>%
      plot(axes = FALSE) 
    par(cex = 5)
    title(xlab="", ylab="", main="Opera") %>% 
      abline(h = 3, col="red", lty = 2, lwd = 3)
```

### 2023-05-16 05_new-micro-analysis.qmd
This is a new commit for what I originally planned to be amended

---
  title: "Discovering Focused Microgenre Communities: Microgenre Analysis"
  author: "Omar Lizardo"
  date: "`r Sys.Date()`"
  output:
    html_document: default
---

# Setup
```{r setup}
    knitr::opts_chunk$set(include=FALSE, echo = TRUE, warning = FALSE, message = FALSE)
    library("car")
    library("conflicted")
    library("dendextend")
    library("FactoMineR")
    library("gghighlight")
    library("ggrepel")
    library("here")
    library("RColorBrewer")
    library("scales")
    library("sjPlot")
    library("splines")
    library("tidyverse")
    library("wesanderson")
```

```{r Loading required objects}
    load(file= here("dat", "lclust-res.RData"))
```

```{r Heavy Metal Microgenre Analysis}
    source(here("Functions", "micro.genre.dat.R"))
    heavy.dat <- micro.genre.dat(genre = "Heavy_Metal", k = 3) 
```

```{r}
    dat.ca <- heavy.dat$b %>% 
              right_join(demog.dat) %>% 
              dplyr::select(c(starts_with("Heavy"), "educ", "age", -"id"))
    res.ca <- MCA(dat.ca, graph = FALSE, quali.sup = c("educ", "age"))
```

```{r}
      d <- data.frame(res.ca$var$coord) %>% 
           bind_rows(data.frame(res.ca$quali.sup$coord)*20)
      plot.dat <- d %>% 
                  mutate(rowname = rownames(d)) %>% 
                  dplyr::filter(!str_detect(rowname, ".NA$")) %>% 
                  dplyr::filter(!str_detect(rowname, "_No$"))
     p <- ggplot(data = plot.dat, aes(x = Dim.2, y = Dim.3))
     p <- p + geom_hline(yintercept = 0, color = "lightgray") 
     p <- p + geom_vline(xintercept = 0, color = "lightgray")
     p <- p + geom_text_repel(aes(label = rownames(plot.dat)), 
                              max.overlaps = 100)
     p <- p + theme_sjplot()
     p <- p + theme(legend.position = "none",
                    axis.line.x = element_blank(),
                    axis.line.y = element_blank(),
                    axis.text = element_text(size = 12))
     p <- p + labs(x = "First Dimension", y = "Second Dimension")
     #p <- p + scale_color_brewer(palette = "Dark2")
     #p <- p + scale_x_continuous(limits = c(-2, 2.5))
     #p <- p + scale_y_continuous(limits = c(-1.1, 1.1))
     p
```

```{r}
    source(here("Functions", "pred.probs.R"))
    source(here("Functions", "mpred.probs.R"))
    bin.var <- function(x) {
      if_else(x == 2, 1, 0)
      }
    dat.pred <- heavy.dat$m %>% 
              mutate(across(starts_with("Heavy"), as.numeric)) %>% 
              mutate(across(starts_with("Heavy"), bin.var)) %>% 
              right_join(demog.dat) 
    pred.res <- mpred.probs("Heavy", dat.pred)
```

```{r}
    plot.dat <- pred.res$probs$Heavy_Metal_1
    p <- ggplot(data = dat,
                mapping = aes(x = cat.labs, y = prob, 
                              fill = var.type, color = var.type, group = var.type))
    p <- p + geom_hline(yintercept = b, color = "red", linewidth = 0.25)
    p <- p + geom_point(size = 2.5)
    p <- p + geom_line(data = con.x, linewidth = 0.75)
    p <- p + geom_segment(data = cat.x,
                          mapping = aes(y = lo, x = cat.labs, yend = hi, xend = cat.labs), 
                          alpha = 0.2, linewidth = 1.15)
    p <- p + geom_ribbon(data = con.x, 
                         mapping = aes(ymin = lo, ymax = hi), 
                         alpha = 0.15, linetype = 0)

```

### 2023-05-16 Functions/hl.plot.R

@@ -1,0 +1,35 @@
+hl.plot <- function(x, n.micro, dem.var, nr = 2) {
+   scal.x <- function(x) {
+      (x - mean(x)) / sd(x)
+      }
+   f.test <- function(x) {
+      linearHypothesis(x, 
+                       c("bs(educ_n, degree = 2)1 = 0", 
+                         "bs(educ_n, degree = 2)2 = 0"))
+   }
+   b <- lapply(x$mods, f.test)
+   plot.dat <- x$probs[1:n.micro] %>% 
+      bind_rows(.id = "micro.gen") %>% 
+      mutate(micro.gen = factor(micro.gen)) %>%
+      dplyr::filter(cat.labs %in% levels(dem.var)) %>% 
+      #mutate(across(c("prob", "hi", "lo"), scal.x)) %>% 
+      tibble() 
+   p <- ggplot(data = plot.dat, mapping = aes(y = prob, x = cat.labs, 
+                                              color = micro.gen, group =micro.gen))
+   p <- p + geom_hline(aes(yintercept = 0), linewidth = 1, color = "pink")
+   p <- p + geom_line()
+   p <- p + geom_point(size = 2)
+   #p <- p + geom_segment(aes(y = lo, x = cat.labs, yend = hi, xend = cat.labs),
+                         #alpha = 0.5, linewidth = 0.8)   
+   p <- p + gghighlight(use_direct_label = FALSE,
+                        label_key = micro.gen,
+                        unhighlighted_params = list(color = "grey90"))
+   p <- p + labs(x = "", y = "")
+   p <- p + theme_sjplot()
+   p <- p + facet_wrap(~ micro.gen, nrow = nr)
+   p <- p + theme(legend.position = "none",
+                  strip.background = element_blank(),
+                  strip.text = element_text(size = 10))
+   p <- p + coord_flip()
+   return(p)
+}

### 2023-05-16 Functions/link.dist.R

@@ -1,0 +1,40 @@
+link.dist <- function(x, id, null = 0) { #takes binary two mode person by genre data matrix as input
+    Jaccard <- function (a, b) { #function to compute Jaccard similarity between binary vectors
+        M.11 <- sum(a == 1 & b == 1)
+        M.10 <- sum(a == 1 & b == 0)
+        M.01 <- sum(a == 0 & b == 1)
+    return (M.11 / (M.11 + M.10 + M.01))
+    }
+    r <- length(id) #getting number of persons in data
+    c <- ncol(x) #getting number of genres in data
+    e <- matrix(0, nrow = 0, ncol = 2) #creating empty two mode edge list from affiliation matrix
+    for (i in 1:r) {
+        for (j in 1:c) {
+            if (x[i, j] == 1) {
+                e <- rbind(e, c(id[i], j)) #populating edge list with edges from two mode data
+                }
+            }
+        }
+    m <- nrow(e) #number of edges in two mode data
+    s <- matrix(null, nrow = m, ncol = m) #creating empty edge similarity matrix 
+    for (i in 1:m) {
+        for (j in 1:m) {
+            g1 <- e[i, 2] #genre node in first edge
+            g2 <- e[j, 2] #genre node in second edge
+            if (g1 == g2) { #condition: if the two edges share the same genre node
+                p1 <- e[i, 1] #person node in first edge
+                p2 <- e[j, 1] #person node in second edge
+                pos.1 <- which(id == p1)
+                pos.2 <- which(id == p2)
+                s[i, j] <- Jaccard(x[pos.1, ], x[pos.2, ]) #populating matrix with similarities between cultural ego networks of the two people
+            }
+        }
+    }
+    d <- 1 - s #transforming into dissimilarity matrix
+    d <- as.dist(d) #transforming into dist object for clustering
+    res <- list(s, d, e)
+    names(res) <- c("sim", "dist", "edge.list")
+return(res)
+}
+
+

### 2023-05-16 Functions/micro.genre.dat.R

@@ -1,0 +1,42 @@
+micro.genre.dat <- function(genre, k) {
+   bin <- function(x) { 
+      if_else(is.na(x), 0, 1) #function to binarize data
+      }
+   
+   id.list <- taste.dat$id
+   g <- names(dend.macro$lower)
+   g.pos <- which(g == genre)
+   g.dend <- dend.macro$lower[[g.pos]]
+   
+   edge.labs <- data.frame(id = ldist.res$edge.list[, 1],
+                           macro.g = ldist.res$edge.list[, 2], 
+                           edge.num = 1:nrow(ldist.res$edge.list)) %>% 
+      mutate(macro.g.f = factor(macro.g, labels = names(taste.dat[,2:21]))) %>% 
+      mutate(macro.g.c = as.character(macro.g.f))
+   
+   b <- cutree(g.dend, k = k) %>% 
+      data.frame() 
+   b <- b %>% 
+      rename(micro.genre = ".") %>% 
+      mutate(edge.num = as.integer(rownames(b))) %>% 
+      right_join(edge.labs) %>% 
+      mutate(micro.genre.c = paste(genre, micro.genre, sep = "_")) %>% 
+      dplyr::filter(macro.g.c == genre) %>% 
+      pivot_wider(id_cols = "id",
+               names_from = "micro.genre.c",
+               values_from = "micro.genre") %>% 
+      mutate(across(starts_with(genre), bin)) 
+   rest.samp <- id.list[! id.list %in% b$id]
+   m <- matrix(nrow = length(rest.samp), ncol = k, 0) %>% 
+     data.frame() %>% 
+      mutate(id = rest.samp)
+   names(m) <- c(paste(genre, 1:k, sep = "_"), "id") 
+   lab.micro <- function(x) {
+      factor(x, labels = c("No", "Yes"))
+      }
+   m <- bind_rows(b, m) %>% 
+      mutate(across(starts_with(genre), lab.micro))
+   b <- b %>% 
+      mutate(across(starts_with(genre), lab.micro))
+   return(list(b = b, m = m))
+}

### 2023-05-16 Functions/pred.probs.R

@@ -1,0 +1,42 @@
+pred.probs <- function(y, w) {
+    #run regression
+    mod <- "bs(educ_n, degree = 2) + bs(age_n, degree = 3) + objclass + 
+                parented + percclass + female + raceeth + region"
+    f <- as.formula(paste(y, mod, sep = "~"))
+    res <- lm(f, data = w)
+    #get predicted probabilities
+    educ <- data.frame(plot_model(res, type = "eff", 
+                                  terms = "educ_n")$data) %>% 
+                    mutate(x = factor(x), var.type = 1) 
+    paeduc <- data.frame(plot_model(res, type = "eff", 
+                                    terms = "parented")$data) %>% 
+                    mutate(x = factor(x), var.type = 2) 
+    objclass <- data.frame(plot_model(res, type = "eff", 
+                                      terms = "objclass")$data) %>% 
+                    mutate(x = factor(x), var.type = 3) 
+    subjclass <- data.frame(plot_model(res, type = "eff", 
+                                       terms = "percclass")$data) %>% 
+                    mutate(x = factor(x), var.type = 4) 
+    age <- data.frame(plot_model(res, type = "eff", 
+                                 terms = "age_n")$data) %>% 
+                    mutate(x = factor(x), var.type = 5) 
+    gender <- data.frame(plot_model(res, type = "eff", 
+                                    terms = "female")$data) %>% 
+                    mutate(x = factor(x), var.type = 6) 
+    race <- data.frame(plot_model(res, type = "eff", 
+                                  terms = "raceeth")$data) %>% 
+                    mutate(x = factor(x), var.type = 7) 
+    region <- data.frame(plot_model(res, type = "eff", 
+                                    terms = "region")$data) %>% 
+                    mutate(x = factor(x), var.type = 8) 
+    #put predicted probabilities into data frame#
+    pred.dat <- bind_rows(educ, paeduc, objclass, subjclass, 
+                          age, gender, race, region) %>% 
+        dplyr::select(c("x", "predicted", "conf.low", "conf.high", "var.type")) %>% 
+        dplyr::rename(cat.labs = 1,
+                      prob = 2,
+                      lo = 3,
+                      hi = 4) %>% 
+        mutate(var.type = factor(var.type))
+    return(list(mod = res, preds = pred.dat))
+  }

### 2023-05-17 02_toy-ex.qmd
Updated toy example and link clustering function

@@
     library("sjPlot")
-    source(here("R", "Functions", "link.dist.R"))
+    source(here("Functions", "link.dist.R"))
 ```
@@
     x <- matrix(x, nrow = 5, ncol = 4,  byrow = TRUE) #toy data
-    ldist.res <- link.dist(x = x, id = c(1:5)) #link distance matrix
+    ldist.res <- link.dist(x = x, id = c(1:5), null = 1) #link distance matrix
     hc.res <- hclust(ldist.res$dist, method = "ward.D2") #link clustering

### 2023-05-17 Functions/link.dist.R

@@ -1,4 +1,4 @@
-link.dist <- function(x, id, null = 0) { #takes binary two mode person by genre data matrix as input
+link.dist <- function(x, id, null = 1) { #takes binary two mode person by genre data matrix as input
     Jaccard <- function (a, b) { #function to compute Jaccard similarity between binary vectors
         M.11 <- sum(a == 1 & b == 1)
         M.10 <- sum(a == 1 & b == 0)

### 2023-07-31 01_link-distance-matrix.qmd
Updated linkdist function

@@
     knitr::opts_chunk$set(include=FALSE, echo = TRUE, warning = FALSE, message = FALSE)
-    require("dendextend")
-    require("fastcluster")
-    require("here")   
-    require("haven")
-    require("tidyverse")
-    source(here("Functions", "link.dist.R"))
+    library(conflicted)
+    library(dendextend)
+    library(fastcluster)
+    library(here)   
+    library(haven)
+    library(tidyverse)
 ```
@@
 
-```{r Importing demographic data}
-        ed.labs <- c("< High School", "High School/GED", "Associate", "Some College", "Bachelor's", "Postgraduate")
-        demog.dat <- read_dta("C:/Users/Omar Lizardo/Google Drive/MISC DATA SOURCES/SSI-2012/SSI2012.dta") %>% 
-          dplyr::select(c("id", "age", "agemid", "female", "raceeth", 
-                          "nodipdeg", "hsged", "somcol", "aadeg", "bach", "ma", 
-                          "docprof", "incmid", "income", "percclass",
-                          "region", "occ", "parented", "empstat", "favgen")) %>% 
-          as_factor() %>% 
-          mutate(educ = if_else(nodipdeg == "yes", 1, 
-                                if_else(hsged == "yes", 2, 
-                                        if_else(aadeg == "yes", 3, 
-                                                if_else(somcol == "yes", 4,
-                                                        if_else(bach == "yes", 5,
-                                                                if_else(ma == "yes" | docprof == "yes", 6, 1)))))),
-                 educ = factor(educ, labels = ed.labs),
-                 percclass = fct_recode(percclass,
-                                        "Lower Class I.D." = "lower class",
-                                        "Workng Class I.D." = "working class",
-                                        "Middle/Upper Class I.D." = "middle class",
-                                        "Middle/Upper Class I.D." = "upper class"),
-                 raceeth = fct_recode(raceeth,
-                                      "Asian" = "Asian",
-                                      "Black" = "Black",
-                                      "Hisp." = "Hispanic",
-                                      "White" = "White",
-                                      "Mult./Other" = ">1 race",
-                                      "Mult./Other" = "other"),
-                 female = fct_recode(female, 
-                                     "Men" = "male", 
-                                             "Women" = "female"),
-                 region = fct_recode(region,
-                                     "New England" = "New Enlgnad",
-                                     "South" = "East South",
-                                     "South" = "South Atlantic",
-                                     "Southwest" = "West South",
-                                     "Midwest" = "Eastern Midwest",
-                                     "Midwest" = "Western Midwest",
-                                     "Mountain" = "Mountain West",
-                                     "West Coast" = "Pacific West"),
-                 parented = fct_recode(parented, 
-                                       "Parent College? (No)" = "parent no college", 
-                                       "Parent College? (Yes)" = "parent college"),
-                 empstat_n = factor(as.numeric(empstat)),
-                 objclass = case_when(incmid == "5000" | incmid == "15000" ~ 1,
-                                      incmid == "25000" | incmid == "35000" ~ 2, 
-                                      incmid == "45000" | incmid == "55000" | incmid == "65000" ~ 4,
-                                      incmid == "75000" | incmid == "85000" | incmid == "95000" ~ 5,
-                                      incmid == "105000" | incmid == "115000" | 
-                                        incmid == "125000" | incmid == "135000" |
-                                        incmid == "145000" | incmid == "150000" |
-                                        incmid == "165000" | incmid == "175000" |
-                                        incmid == "185000" | incmid == "195000" |
-                                        incmid == "212500" | incmid == "237500" |
-                                        incmid == "250,000 or more" ~ 6),
-                 objclass = factor(objclass, labels = c("Poor", "Working Class", "Middle Class", "Upper Middle Class", "High Income")),
-                 educ_n = as.numeric(educ),
-                 college = if_else(educ_n > 4, 1, 0),
-                 college = factor(college, labels = c("No Degree", "College")),
-                 age_n = as.numeric(age),
-                 objclass_n = as.numeric(objclass)
-          ) %>% 
-          dplyr::select(-c("nodipdeg", "hsged", "somcol", "aadeg", "bach", "ma", "docprof")) %>% 
-            mutate(id = as.integer(id)) %>% 
-            na.omit() 
-```
-
 # Link Clustering
-```{r Performing link clustering and saving results}
-    ldist.res <- link.dist(x = taste.mat, id = taste.dat$id) #computing link by link distance matrix
-    lclust.res <- hclust(ldist.res$dist, method = "ward.D2") #link clustering of link by link distance matrix
-    lclust.dend <- as.dendrogram(lclust.res) #transforming link clustering into dendrogram
-```
-
-```{r Creating objects for analysis}
-    dend.macro <- cut(lclust.dend, h = 8) #cutting at macrogenre level
-    a <- data.frame(g.size = sapply(dend.macro$lower, nleaves)) #macrogenres as ordered in dendrogram results
-    b <- data.frame(g.size = colSums(taste.mat), g.names = names(colSums(taste.mat))) #original macrogenre sizes
-    c <- right_join(a, b) #joining data frames by macrogenre sizes to get macrogenre labels ordered by dendrogram results
-    names(dend.macro$lower) <- c$g.names #naming macrogenre dendrogram list
-    n.micro <- sapply(dend.macro$lower, function(x) {length(table(cutree(x, h = 3)))}) #number of microgenres per macrogenre
-    v <- sapply(sapply(n.micro, function(x) {1:x}), as.numeric)
-    micro.g.names <- paste(c$g.names[1], v[[1]], sep = "_")
-    for (i in 2:20) {
-      micro.g.names <- c(micro.g.names, paste(c$g.names[i], v[[i]], sep = "_"))
-        }
-    bin.char <- function(x) { 
-      if_else(is.na(x), 0, 1) #function to binarize data
-        }
-    dend.micro <- cut(lclust.dend, h = 3) #cutting at microgenre level
-    edge.labs <- data.frame(id = ldist.res$edge.list[, 1],
-                            macro.g = ldist.res$edge.list[, 2], 
-                            edge.num = 1:nrow(ldist.res$edge.list)) #grabbing people and genre id labels
-    micro.g.clust <- lapply(dend.micro$lower, labels) %>%
-        lapply(data.frame) %>% 
-        bind_rows() #transforming clustering cut results into data frame
-    names(micro.g.clust) <- "edge.num" #adding column label
-    micro.g.long <- data.frame(micro.g = rep(1:102, sapply(dend.micro$lower, nleaves)))
-    micro.g.dat <- bind_cols(micro.g.clust, micro.g.long)
-    micro.g.dat <- right_join(micro.g.dat, edge.labs) %>%
-      mutate(micro.g.f = factor(micro.g, labels = micro.g.names),
-             macro.g.f = factor(macro.g, labels = names(colSums(taste.mat))),
-             micro.g.c = as.character(micro.g.f),
-             macro.g.c = as.character(macro.g.f)) %>% 
-      pivot_wider(id_cols = "id",
-                  names_from = "micro.g.c",
-                  values_from = "micro.g") %>% 
-      mutate(across(is.integer, bin.char)) %>% 
-      mutate(id = as.integer(id)) %>% 
-      arrange(id)
-```
-
-# Saving Objects
-```{r Remove garbage and keep important stuff}
-    b <- ls()[! ls() %in% c("ldist.res", "lclust.res", "dend.macro", "dend.micro", "lclust.dend", "micro.g.names", "n.micro", "taste.dat", "demog.dat", "micro.g.dat")]
+```{r Creating link by link distance matrix and saving results}
+    source(here("Functions", "link.dist.R"))
+    ldist.res <- link.dist(x = taste.mat, id = taste.dat$id)
+    b <- ls()[! ls() %in% "ldist.res"]
     rm(list = b)
     ls()
-```
-
-```{r Saving image}
     save.image(file= here("dat", "lclust-res.RData"))

### 2023-07-31 02_toy-ex.qmd
Updated linkdist function

--- 2023-05-16 02_toy-ex.qmd
@@
     knitr::opts_chunk$set(include=FALSE, echo = TRUE, warning = FALSE, message = FALSE)
+    library("conflicted")
     library("fastcluster")
@@
     p <- fviz_dend(hc.res, k = 4, k_colors = "uchicago", show_labels = TRUE, cex = 1.5, lwd = 2) 
-    p <- p + geom_hline(yintercept = 0.75, linetype = "dashed", color = "red", size = 1.2)
+    p <- p + geom_hline(yintercept = 0.75, linetype = "dashed", color = "red", linewdith = 1.2)
     p <- p + labs(y = "", title = "") 

### 2023-07-31 07-new-micro-analysis-for-real.Rmd
Updated linkdist function

---
  title: "Discovering Focused Microgenre Communities: Microgenre Analysis"
  author: "Omar Lizardo"
  date: "`r Sys.Date()`"
  output:
    html_document: default
---

# Setup
```{r setup}
    knitr::opts_chunk$set(include=FALSE, echo = TRUE, warning = FALSE, message = FALSE)
    library(conflicted)
    library(dendextend)
    library(haven)
    library(here)
    library(sjPlot)
    library(tidyverse)
    load(file= here("dat", "lclust-res.RData"))
```

```{r Importing and creating two mode data frame of people by genres}
    taste.dat <- read_dta("C:/Users/Omar Lizardo/Google Drive/MISC DATA SOURCES/SSI-2012/SSI2012.dta")
    taste.dat <- taste.dat %>% 
      dplyr::select("id", ends_with(c("lis", "like")), -starts_with("none")) %>% 
      dplyr::select(c(1:41)) %>% 
      na.omit() %>% 
      mutate(Classical = classicallike * classicallis,
             Opera = operalike * operalis,
             Jazz = jazzlike * jazzlis,
             Broadway = bwaystlike * bwaystlis,
             Easy = moodezlike * moodezlis, 
             Bigband = bbandlike * bbandlis,
             Classic_Rock = croldlike * croldlis,
             Country = countrylike * countrylis,
             Bluegrass = blueglike * blueglis,
             Folk = folklike * folklis,
             Gospel = hymgoslike * hymgoslis,
             Latin = latlpsallike * latspsallis,
             Rap_Hip_Hop = raphiphoplike * raphiphoplis,
             Blues_RandB = blurblike * blurblis,
             Reggae = reggaelike * reggaelis,
             Pop = toppoplike * toppoplis,
             Contemp_Rock = controcklike * controcklis,
             Indie_Alt = indaltlike * indaltlis,
             Dance_Club = danclublike * danclublis,
             Heavy_Metal = hvymtllike * hvymtllis
             ) %>%  #people are linked to genres that the both like and listen to
      dplyr::select(id, Classical:Heavy_Metal)
```

```{r Performing Link Clustering}
    lclust.res <- hclust(ldist.res$dist, method = "ward.D2") #clustering of link by link distance matrixco
    lclust.dend <- as.dendrogram(lclust.res) #transforming link clustering into dendrogram
```

```{r}
    source(here("Functions", "micro.genre.dat.R"))
    source(here("Functions", "demog.dat.R"))
    source(here("Functions", "genre.reg.mods.R"))
    m <- genre.reg.mods("Country", k = 7,
                        xvars = c("educ", "race", "gender", "age.n",
                           "subjclass"))
    tab_model(m, digits = 3, show.ci = FALSE, 
              file = here("Tabs", "reg-tab-latin.html"))
```

```{r}
    source(here("Functions", "micro.genre.dat.R"))
    source(here("Functions", "demog.dat.R"))
    latin.micro <- micro.genre.dat("Latin", k = 6)$all %>% 
      left_join(demog.dat())
    head(latin.micro)
    mod1 <- lm(as.numeric(Latin_1) ~ educ + race + gender + age.n, 
               data = latin.micro)
    mod2 <- lm(as.numeric(Latin_2) ~ educ + race + gender + age.n, 
               data = latin.micro)
    mod3 <- lm(as.numeric(Latin_3) ~ educ + race + gender + age.n, 
               data = latin.micro)
    mod4 <- lm(as.numeric(Latin_4) ~ educ + race + gender + age.n, 
               data = latin.micro)
    mod5 <- lm(as.numeric(Latin_5) ~ educ + race + gender + age.n, 
               data = latin.micro)
    mod6 <- lm(as.numeric(Latin_6) ~ educ + race + gender + age.n, 
               data = latin.micro)
    tab_model(mod1, mod2, mod3, mod4, mod5, mod6,
                show.ci = FALSE, auto.label = FALSE, digits = 3,
                #dv.labels = c(),
                #rm.terms = c(), 
                #pred.labels = c(), 
                file = here("Tabs", "reg-tab-latin.html") 
              )
    #webshot(here("Tabs", "reg-tab-latin.html"), here("Tabs", "reg-latin-ASR.png"))
```

### 2023-07-31 Functions/link.dist.R

@@ -1,4 +1,4 @@
-link.dist <- function(x, id, null = 1) { #takes binary two mode person by genre data matrix as input
+link.dist <- function(x, id) { #takes binary two mode person by genre data matrix as input
     Jaccard <- function (a, b) { #function to compute Jaccard similarity between binary vectors
         M.11 <- sum(a == 1 & b == 1)
         M.10 <- sum(a == 1 & b == 0)
@@ -16,7 +16,7 @@ link.dist <- function(x, id, null = 1) { #takes binary two mode person by genre 
             }
         }
     m <- nrow(e) #number of edges in two mode data
-    s <- matrix(null, nrow = m, ncol = m) #creating empty edge similarity matrix 
+    s <- matrix(0, nrow = m, ncol = m) #creating empty edge similarity matrix 
     for (i in 1:m) {
         for (j in 1:m) {
             g1 <- e[i, 2] #genre node in first edge

### 2023-07-31 Functions/demog.dat.R
New cluster cutting and regression modeling functions

@@ -1,0 +1,56 @@
+demog.dat <- function() {
+   library(haven)
+   x <- read_dta("C:/Users/Omar Lizardo/Google Drive/MISC DATA SOURCES/SSI-2012/SSI2012.dta", col_select = c("id", "nodipdeg", "hsged", "somcol", "aadeg", 
+                                "bach", "ma", "docprof", "raceeth", 
+                                "female", "age", "percclass", "incmid",
+                                "region", "parented")) %>% 
+      mutate(educ = case_when(nodipdeg == 1 ~ 1,
+                              hsged == 1 ~ 2,
+                              aadeg == 1 ~ 3,
+                              somcol == 1 ~ 4,
+                              bach == 1 ~ 5,
+                              ma == 1 ~ 6,
+                              docprof == 1 ~ 6),
+             race = factor(raceeth, labels = c("Asian", 
+                                               "Black", 
+                                               "Hisp.", 
+                                               "White", 
+                                               "Mult.", 
+                                               "Other")),
+             age = factor(age, labels = c("18 – 19",
+                                          "20 – 24",
+                                          "25 – 29",
+                                          "30 – 34",
+                                          "35 – 39",
+                                          "40 – 44",
+                                          "45 – 49",
+                                          "50 – 54",
+                                          "55 – 59",
+                                          "60 – 64",
+                                          "65 – 69",
+                                          "70 – 74",
+                                          "75 – 79",
+                                          "80+"), ordered = TRUE),
+             subjclass = factor(percclass, labels = c("Lower",
+                                                    "Working",
+                                                    "Middle",
+                                                    "Upper")),
+             objclass = case_when(incmid == 5000 | incmid == 15000 ~ 1,
+                                  incmid == 25000 | incmid == 35000 ~ 2, 
+                                  incmid == 45000 | incmid == 55000 | 
+                                  incmid == 65000 ~ 3,
+                                  incmid == 75000 | incmid == 85000 | 
+                                  incmid == 95000 ~ 4,
+                                  incmid == 105000 | incmid == 115000 | 
+                                  incmid == 125000 | incmid == 135000 |
+                                  incmid == 145000 | incmid == 150000 |
+                                  incmid == 165000 | incmid == 175000 |
+                                  incmid == 185000 | incmid == 195000 |
[…]

### 2023-07-31 Functions/genre.reg.mods.R

@@ -1,0 +1,15 @@
+genre.reg.mods <- function(genre, xvars, k = 3) {
+   genre.micro <- micro.genre.dat(genre, k = k)$all %>% 
+      right_join(demog.dat()) %>% 
+      mutate(across(starts_with(substr(genre, 1, 4)), as.numeric))
+   # VECTOR OF COLUMN NAMES (NOT VALUES)
+   dep.vars <- c(paste(genre, 1:k, sep = "_"))
+   # USER-DEFINED METHOD TO PROCESS DIFFERENT DEP VAR
+   run_model <- function(dep.var) {
+      fml <- reformulate(xvars, dep.var)
+      lm(fml, data = genre.micro)
+      }
+   # NAMED LIST OF MODELS
+   mods <- sapply(dep.vars, run_model, simplify = FALSE)
+   return(mods)
+   }

### 2023-07-31 Functions/micro.genre.dat.R

@@ -1,9 +1,22 @@
-micro.genre.dat <- function(genre, k) {
+micro.genre.dat <- function(genre, k = 3) {
+   # Functions
    bin <- function(x) { 
       if_else(is.na(x), 0, 1) #function to binarize data
       }
    
+   lab.micro <- function(x) {
+      factor(x, labels = c("No", "Yes")) # function to label binary data
+      }
+   
    id.list <- taste.dat$id
+   dend.macro <- cut(lclust.dend, h = 8) #cutting at macrogenre level
+   
+   a <- data.frame(g.size = sapply(dend.macro$lower, nleaves)) #macrogenres as ordered in dendrogram results
+   b <- colSums(taste.dat[,2:21])
+   c <- data.frame(g.size = b, g.names = names(b)) #original macrogenre sizes
+   d <- right_join(a, c) #joining data frames by macrogenre sizes to get macrogenre labels ordered by dendrogram results
+   names(dend.macro$lower) <- d$g.names #naming macrogenre dendrogram list
+   
    g <- names(dend.macro$lower)
    g.pos <- which(g == genre)
    g.dend <- dend.macro$lower[[g.pos]]
@@ -15,7 +28,7 @@ micro.genre.dat <- function(genre, k) {
       mutate(macro.g.c = as.character(macro.g.f))
    
    b <- cutree(g.dend, k = k) %>% 
-      data.frame() 
+      data.frame()
    b <- b %>% 
       rename(micro.genre = ".") %>% 
       mutate(edge.num = as.integer(rownames(b))) %>% 
@@ -26,17 +39,15 @@ micro.genre.dat <- function(genre, k) {
                names_from = "micro.genre.c",
                values_from = "micro.genre") %>% 
       mutate(across(starts_with(genre), bin)) 
+   
    rest.samp <- id.list[! id.list %in% b$id]
    m <- matrix(nrow = length(rest.samp), ncol = k, 0) %>% 
      data.frame() %>% 
       mutate(id = rest.samp)
    names(m) <- c(paste(genre, 1:k, sep = "_"), "id") 
-   lab.micro <- function(x) {
-      factor(x, labels = c("No", "Yes"))
-      }
    m <- bind_rows(b, m) %>% 
       mutate(across(starts_with(genre), lab.micro))
    b <- b %>% 
-      mutate(across(starts_with(genre), lab.micro))
-   return(list(b = b, m = m))
+     mutate(across(starts_with(genre), lab.micro))
+   return(list(fans = b, all = m))
 }

### 2023-08-02 07-new-micro-analysis-for-real.Rmd
Updated and new functions

@@
     library(dendextend)
+    library(ggplot2)
     library(haven)
@@
     source(here("Functions", "genre.reg.mods.R"))
-    m <- genre.reg.mods("Country", k = 7,
-                        xvars = c("educ", "race", "gender", "age.n",
-                           "subjclass"))
-    tab_model(m, digits = 3, show.ci = FALSE, 
+    a <- demog.dat()
+    summary(a)
+    spec <- c("educ", "parcoll", "age.n", "blk", "his", "asn", "gender")
+    labs <- c("Intercept", "Education", "Parents College",
+                            "Age", "Race ID: Black", "Race ID: Hispanic",
+                            "Race ID: Asian", "Gender ID: Woman")
+
+    res.latin <- genre.reg.mods("Latin", k = 4, xvars = spec)
+    res.metal <- genre.reg.mods("Heavy_Metal", k = 4, xvars = spec)
+
+    tab_model(res.latin$mods, 
+              digits = 3, show.ci = FALSE, 
+              auto.label = FALSE, transform = NULL,
+              pred.labels = labs,
               file = here("Tabs", "reg-tab-latin.html"))
+    #webshot(here("Tabs", "reg-tab-latin.html"), here("Tabs", "reg-tab-latin.png"))
+    tab_model(res.metal$mods, 
+              digits = 3, show.ci = FALSE, 
+              auto.label = FALSE, transform = NULL,
+              pred.labels = labs,
+              file = here("Tabs", "reg-tab-metal.html"))
+    #webshot(here("Tabs", "reg-tab-metal.html"), here("Tabs", "reg-tab-metal.png"))
 ```
@@
 ```{r}
-    source(here("Functions", "micro.genre.dat.R"))
-    source(here("Functions", "demog.dat.R"))
-    latin.micro <- micro.genre.dat("Latin", k = 6)$all %>% 
-      left_join(demog.dat())
-    head(latin.micro)
-    mod1 <- lm(as.numeric(Latin_1) ~ educ + race + gender + age.n, 
-               data = latin.micro)
-    mod2 <- lm(as.numeric(Latin_2) ~ educ + race + gender + age.n, 
-               data = latin.micro)
-    mod3 <- lm(as.numeric(Latin_3) ~ educ + race + gender + age.n, 
-               data = latin.micro)
-    mod4 <- lm(as.numeric(Latin_4) ~ educ + race + gender + age.n, 
-               data = latin.micro)
-    mod5 <- lm(as.numeric(Latin_5) ~ educ + race + gender + age.n, 
-               data = latin.micro)
-    mod6 <- lm(as.numeric(Latin_6) ~ educ + race + gender + age.n, 
-               data = latin.micro)
-    tab_model(mod1, mod2, mod3, mod4, mod5, mod6,
-                show.ci = FALSE, auto.label = FALSE, digits = 3,
-                #dv.labels = c(),
-                #rm.terms = c(), 
-                #pred.labels = c(), 
-                file = here("Tabs", "reg-tab-latin.html") 
-              )
-    #webshot(here("Tabs", "reg-tab-latin.html"), here("Tabs", "reg-latin-ASR.png"))
+    source(here("Functions", "pred.probs.R"))
+    source(here("Functions", "plot.preds.R"))
+    age.preds <- pred.probs(x = "age.n", res.latin$mods)
+    p <- plot.preds(d = age.preds, 
+                    xb = c(3, 7, 11),
+                    xlabs = c("Young", "Mid. Aged", "Old"),
+                    yl = .1, 
+                    xm = 2, 
+                    xl = 12)
+    p
 ```
+`

### 2023-08-02 Functions/demog.dat.R

@@ -3,14 +3,24 @@ demog.dat <- function() {
    x <- read_dta("C:/Users/Omar Lizardo/Google Drive/MISC DATA SOURCES/SSI-2012/SSI2012.dta", col_select = c("id", "nodipdeg", "hsged", "somcol", "aadeg", 
                                 "bach", "ma", "docprof", "raceeth", 
                                 "female", "age", "percclass", "incmid",
-                                "region", "parented")) %>% 
-      mutate(educ = case_when(nodipdeg == 1 ~ 1,
-                              hsged == 1 ~ 2,
-                              aadeg == 1 ~ 3,
-                              somcol == 1 ~ 4,
-                              bach == 1 ~ 5,
-                              ma == 1 ~ 6,
+                                "region", "parented", "empstat")) %>% 
+      rename(parcoll = parented) %>% 
+      mutate(educ = case_when(nodipdeg == 1 ~ 0 ,                          
+                              hsged == 1 ~ 1,
+                              aadeg == 1 ~ 2,
+                              somcol == 1 ~ 3,
+                              bach == 1 ~ 4,
+                              ma == 1 ~ 5,
                               docprof == 1 ~ 6),
+             region = case_when(region == 1 ~ 1,
+                                region == 2 ~ 1,
+                                region == 3 ~ 2,
+                                region == 4 ~ 3,
+                                region == 5 ~ 4,
+                                region == 6 ~ 4,
+                                region == 7 ~ 4,
+                                region == 8 ~ 5,
+                                region == 9 ~ 6),
              race = factor(raceeth, labels = c("Asian", 
                                                "Black", 
                                                "Hisp.", 
@@ -48,9 +58,41 @@ demog.dat <- function() {
                                   incmid == 185000 | incmid == 195000 |
                                   incmid == 212500 | incmid == 237500 ~ 5),
              gender = factor(female, labels = c("Men", "Women"))) %>%
-      mutate(age.n = as.numeric(age), age.n2 = as.numeric(age)^2) %>% 
-      mutate(objclass = factor(objclass, labels = c("Poor", "Working", "Middle", "Upper Middle", "High Income"))) %>% 
-      dplyr::select(c("id", "educ", "race", "gender", 
-                      "age.n", "age.n2", "subjclass", "objclass"))
+      mutate(age.n = as.numeric(age), 
+             age.n2 = as.numeric(age)^2,
+             region.f = factor(region, labels = c("Northeast", 
+                                                  "Midwest", 
+                                                  "Plains", 
[…]

### 2023-08-02 Functions/genre.reg.mods.R

@@ -1,15 +1,24 @@
 genre.reg.mods <- function(genre, xvars, k = 3) {
+   library(estimatr)
+   rec.taste <- function(x) {
+      x = case_when(x == 1 ~ 0, x == 2 ~ 1)
+      }
    genre.micro <- micro.genre.dat(genre, k = k)$all %>% 
       right_join(demog.dat()) %>% 
-      mutate(across(starts_with(substr(genre, 1, 4)), as.numeric))
+      mutate(across(starts_with(substr(genre, 1, 4)), as.numeric)) %>%
+      mutate(across(starts_with(substr(genre, 1, 4)), rec.taste)) %>% 
+      right_join(taste.dat[c("id", genre)])
    # VECTOR OF COLUMN NAMES (NOT VALUES)
    dep.vars <- c(paste(genre, 1:k, sep = "_"))
+   dep.vars <- c(genre, dep.vars)
    # USER-DEFINED METHOD TO PROCESS DIFFERENT DEP VAR
    run_model <- function(dep.var) {
       fml <- reformulate(xvars, dep.var)
-      lm(fml, data = genre.micro)
+      glm(fml, data = genre.micro, family = "binomial")
+      #lm(fml, data = genre.micro)
+      #lm_robust(fml, data = genre.micro)
       }
    # NAMED LIST OF MODELS
    mods <- sapply(dep.vars, run_model, simplify = FALSE)
-   return(mods)
+   return(list(mods = mods, dat = genre.micro))
    }

### 2023-08-02 Functions/plot.preds.R

@@ -1,0 +1,18 @@
+plot.preds <- function(d, xb, xlabs, yl, r.alpha = .1, p.size = 3, xm, xl) {
+   p <- ggplot(data = d, 
+               mapping = aes(x = x, y = pr, fill = genre, color = genre, group = genre))
+   p <- p + geom_point(size = p.size)
+   p <- p + geom_line(linewidth = 0.75)
+   p <- p + geom_ribbon(mapping = aes(ymin = lo, ymax = hi), 
+                        alpha = r.alpha, linetype = 0)
+   p <- p + scale_y_continuous(limits = c(0, yl))
+   p <- p + scale_x_continuous(limits = c(xm, xl), 
+                               breaks = xb, labels = xlabs)
+   p <- p + theme_minimal()
+   p <- p + theme(legend.position = "top",
+                  legend.title = element_blank(),
+                  axis.title = element_blank(),
+                  axis.text = element_text(size = 12),
+                  legend.text = element_text(size = 12))
+   return(p)
+   }

### 2023-08-02 Functions/pred.probs.R

@@ -1,42 +1,13 @@
-pred.probs <- function(y, w) {
-    #run regression
-    mod <- "bs(educ_n, degree = 2) + bs(age_n, degree = 3) + objclass + 
-                parented + percclass + female + raceeth + region"
-    f <- as.formula(paste(y, mod, sep = "~"))
-    res <- lm(f, data = w)
-    #get predicted probabilities
-    educ <- data.frame(plot_model(res, type = "eff", 
-                                  terms = "educ_n")$data) %>% 
-                    mutate(x = factor(x), var.type = 1) 
-    paeduc <- data.frame(plot_model(res, type = "eff", 
-                                    terms = "parented")$data) %>% 
-                    mutate(x = factor(x), var.type = 2) 
-    objclass <- data.frame(plot_model(res, type = "eff", 
-                                      terms = "objclass")$data) %>% 
-                    mutate(x = factor(x), var.type = 3) 
-    subjclass <- data.frame(plot_model(res, type = "eff", 
-                                       terms = "percclass")$data) %>% 
-                    mutate(x = factor(x), var.type = 4) 
-    age <- data.frame(plot_model(res, type = "eff", 
-                                 terms = "age_n")$data) %>% 
-                    mutate(x = factor(x), var.type = 5) 
-    gender <- data.frame(plot_model(res, type = "eff", 
-                                    terms = "female")$data) %>% 
-                    mutate(x = factor(x), var.type = 6) 
-    race <- data.frame(plot_model(res, type = "eff", 
-                                  terms = "raceeth")$data) %>% 
-                    mutate(x = factor(x), var.type = 7) 
-    region <- data.frame(plot_model(res, type = "eff", 
-                                    terms = "region")$data) %>% 
-                    mutate(x = factor(x), var.type = 8) 
-    #put predicted probabilities into data frame#
-    pred.dat <- bind_rows(educ, paeduc, objclass, subjclass, 
-                          age, gender, race, region) %>% 
-        dplyr::select(c("x", "predicted", "conf.low", "conf.high", "var.type")) %>% 
-        dplyr::rename(cat.labs = 1,
-                      prob = 2,
-                      lo = 3,
-                      hi = 4) %>% 
-        mutate(var.type = factor(var.type))
-    return(list(mod = res, preds = pred.dat))
[…]

### 2023-08-02 07-new-micro-analysis-for-real.Rmd
deleted plots and new plots

@@
 
-```{r}
+```{r Custom Functions}
     source(here("Functions", "micro.genre.dat.R"))
@@
     source(here("Functions", "genre.reg.mods.R"))
+    source(here("Functions", "pred.probs.R"))
+    source(here("Functions", "plot.preds.R"))
+```
+
+```{r}
     a <- demog.dat()
@@
 ```{r}
-    source(here("Functions", "pred.probs.R"))
-    source(here("Functions", "plot.preds.R"))
+
     age.preds <- pred.probs(x = "age.n", res.latin$mods)

### 2023-08-03 main.tex

@@
     \geometry{a4paper}
-\bibliographystyle{plainnat}
+\bibliographystyle{apalike}
 
@@
 Despite the generally salutary results from this endeavor, critics rightly question the face and ecological validity of the vague macrogenre labels included in standard arts participation surveys (e.g., Classical, Rock, Rap).
-To deal with this issue, in this paper, I propose a link-clustering approach for discovering focused microgenres from standard survey-based information on cultural tastes, one that exploits the underlying relational patterns realized by the indirect connectivity structure of genres (via persons) in a two-mode network.
-The link-clustering approach partially answers two of the challenges of macro-genre critics: The fact that actual genres are overlapping and not crisply bounded and the fact that there is hidden heterogeneity within the broad labels we usually focus on.
+To deal with this issue, in this paper, I propose a link-clustering approach for discovering focused microgenres from standard survey-based information on cultural tastes, one that exploits the underlying relational patterns realized by the indirect connectivity structure of genres (via people) in a two-mode network.
+The link-clustering approach partially answers two of the challenges of macrogenre critics: The fact that actual genres are overlapping and not crisply bounded and the fact that there is hidden heterogeneity within the broad labels we usually focus on.
 To demonstrate the validity of the approach, I contrast the application of the usual techniques to the same data, conceived in the usual ``macro" way, and after discovering hidden microgenres.
@@
 
-\section{Persons and Cultural Choices}
+\section{People and Cultural Choices}
 Recent work in the sociology of taste has blurred the distinction, foundational for much early work, between ``relational'' network data (codifying the relationships between people) and survey data (codifying the relationship between people and ``variables'').
-The basic idea is that all data, whether collected purposefully as ``network'' data or collected as part of a social survey, is \textit{relational} data.
+The basic idea is that all data, whether collected purposefully as ``network'' data collected as part of a social survey, is \textit{relational} data.
 The main difference is the types of entities that are related \citep{borgatti_everett97}.
-That is, any data source that can be stored in matrix form has ``modes'' (how many types of entities are related) and ``ways'' (the number of entities linked by a relation, usually two at a time).
+Any data source that can be stored in matrix form has ``modes'' (how many types of entities are related) and ``ways'' (the number of entities linked by a relation, usually two at a time).
 The standard network data set is ``one mode'' (we usually look at one type of entity at a time, like people, organizations, schools, countries, and the like) and two ``ways'' (people-by-people or organization-by-organization pairs).
@@
 This goes beyond the fact, to be exploited below, that once we treat survey data as network data, then the entire methodological panoply developed by social network analysts (and increasingly ``network scientists'' working across many disciplines) for the last fifty or so years becomes part of the analytic toolbox.
-In addition to this, the entire \textit{conceptual} arsenal of social network theory \citep{borgatti11} also becomes available.
+In addition, the entire \textit{conceptual} arsenal of social network theory \citep{borgatti11} also becomes available.
 As \citet[244]{borgatti_everett97} note, once we convert ``2-mode data sets into 1-mode matrices{\dots}we can then apply the techniques (if not the theories) of network analysis.''
@@
 Accordingly, \citet{pachucki2010cultural} extend Ronald Burt's theory of structural holes for understanding how people can bridge gaps not just in one-mode person-to-person networks but in two-mode person-to-culture networks.
-Following this lead, \citet{lizardo14} provides a metric based on Burt's conception of network efficiency that is meant to characterize the slippery concept of ``omnivorousness" concerning genres and cultural forms that people engage in.
+Following this lead, \citet{lizardo14} provides a metric based on Burt's conception of network efficiency that is meant to characterize the slippery concept of ``omnivorousness" concerning genres and cultural forms people engage in.
 This approach goes beyond just summing or counting people's cultural engagements to consider the audience overlap between the genres themselves.
@@
 Other work in this same vein extends ideas related to positional equivalence in networks \citet{breiger1976social} to uncover ``blocks'' of respondents that tend to dislike the same set of genres that others like \citep{okada2017structure}.
-A similar approach, based on ideas of positional equivalence in networks, can be extended beyond the study of beliefs and social attitudes more generally to identify respondents who share cultural schemas \citep{goldberg2011mapping}.
+A similar approach, based on ideas of positional equivalence in networks, can be extended beyond the study of beliefs and social attitudes to identify respondents who share cultural schemas \citep{goldberg2011mapping}.
 \citet{lizardo18} adapts techniques first developed for the study of economic complexity in two-mode networks of geographic sites and products/technologies for the characterization of genres (e.g., popular versus niche) and audience (e.g., omnivore versus ``univore'') characteristics in survey data on cultural tastes.
@@
 
-This conceptualization, like a lot of network theorizing, is elegant but gets messy in the application.
+Like much network theorizing, this conceptualization is elegant but gets messy in the application.
 As \citet[149]{lena2015relational} has noted, ``[n]o ordering principle is as fundamental to culture as genre'' yet, none is also as vexed.
-One issue Lena raises is that sociologists have relational intuitions about genres but tend to default to musicological definitions for convenience's sake.
-Thus, when it comes to considering which genres to include in a survey on cultural tastes, the tendency is simply to pick off the shelf from the menu of genre categories.
-The problem with these folk genre classifications is that they tend to miss the fuzzy, overlapping ways that real-world genres are organized.
-This leads us to treat what are, in fact, contested boundaries as if they were natural, crisp boundaries (e.g., assigning respondents who like ``Rap" to a different taste community than those who like ``Opera.").
+Lena raises one issue: Sociologists have relational intuitions about genres but tend to default to musicological definitions for convenience.
+Thus, when it comes to considering which genres to include in a survey on cultural tastes, the tendency is to pick off-the-shelf from the menu of genre categories.
+The problem with these folk genre classifications is that they miss the fuzzy, overlapping ways real-world genres are organized.
+This leads us to treat what are, in fact, contested boundaries as if they were natural, crisp boundaries (e.g., assigning respondents who like ``Rap'' to a different taste community than those who like ``Opera.").
 This is the problem of \textit{overlapping boundaries among genre categories}.
@@
 For convenience’s sake, survey data must settle on a ``middle'' level of categorization so as not to tax respondents' patience (or knowledge).
-Thus, the standard ``lists'' of cultural genres, such as ``Pop Art,'' ``Romantic Comedy," or ``Blues.'' However, as recent work points out, people, venues, fandoms, scenes, subcultures, communities, organizations, critics, gatekeepers, and even states and other powerful institutions, make sociologically relevant distinctions within macro-genres categories \citep{hesmondhalgh2005subcultures, Holt2007, Van_Poecke2018}.
-Genres may also develop and accumulate subvariations as they ``travel'' across production, dissemination, and consumption sites in their historical trajectory \citep{Lena2012}.
-These ``micro-genres'' are embedded within larger macro-genres in complex ways that the standard survey approach misses.
+Thus, the standard ``lists'' of cultural genres, such as ``Pop Art,'' ``Romantic Comedy," or ``Blues.'' However, as recent work points out, people, venues, fandoms, scenes, subcultures, communities, organizations, critics, gatekeepers, and even states and other powerful institutions, make sociologically relevant distinctions within macrogenres categories \citep{hesmondhalgh2005subcultures, Holt2007, Van_Poecke2018, Hield2014-xe}.
+Genres may also develop and accumulate variations as they ``travel'' across production, dissemination, and consumption sites in their historical trajectory \citep{Lena2012}.
+These ``microgenres'' are embedded within larger macrogenres in complex ways that the standard survey approach misses.
+
+For instance, within the Sheffield ``musicworld,'' the broad genre category of ``Folk''---one usually included in the typical survey questionnaire like the one used in this paper---can refer to at least three existing microgenres: A ``traditionalist'' one---see \citep{Lena2012}---composed mainly of late nineteenth and early twentieth English ballads documenting working-class and mining-town life, a ``scene'' genre centered on 1960s political protest and pop songs (a la Dylan) or more contemporary ``avant-garde'' genre featuring reflexive, sometimes parodic takes on the previous two, and centered on blurring performer-audience boundaries.
+As Hield and Crossley \citeyearpar[197]{Hield2014-xe} note, ``[t]hese and other such distinctions are not registered in\ldots surveys.''
 
 \section{What to do about the problem of genre}
-One solution to the problem posed by vague macro-genre labels, suggested by \citet{vlegels2015music, vlegels2017music} concerning musical genres, is to ``change the mode'' and ``drop the label'' by asking respondents not just for their levels of engagement or liking of broad macro-genre labels but for performers within those labels.
-This work shows that once these ``micro-genre'' distinctions based on performers are made, some core empirical generalizations in the sociology of taste (e.g., highly educated people like classical music) are controverted or at least heavily qualified.
-This \textit{micro-genre heterogeneity} critique thus asserts that the standard genre labels studied by social scientist hide as much as they reveal because micro-genre communities can be internally diverse and even contain mutually opposed groups in the social space \citep{flemmen_etal18}.
-For people, the unit of selection and judgment is the {\em micro-genre}, not the broad genre classification, so it is unclear what to do (and how to interpret) the usual data collected by sociologists who study taste using surveys.
+One solution to the problem posed by vague macrogenre labels, suggested by \citet{vlegels2015music, vlegels2017music} concerning musical genres, is to ``change the mode'' and ``drop the label'' by asking respondents not just for their levels of engagement or liking of broad macrogenre labels but for performers within those labels.
+This work shows that once these ``microgenre'' distinctions based on performers are made, some core empirical generalizations in the sociology of taste (e.g., highly educated people like classical music) are controverted or at least heavily qualified.
+This \textit{microgenre heterogeneity} critique thus asserts that the standard genre labels studied by social scientists hide as much as they reveal because microgenre communities can be internally diverse and even contain mutually opposed groups in the social space \citep{flemmen_etal18}.
+For people, the unit of selection and judgment is the {\em microgenre}, not the broad genre classification.
+So, it is unclear what to do (and how to interpret) the usual data collected by sociologists who study taste using surveys.
 
-But what happens when all the data we have (as it is with the long-standing surveys such as the Survey for Public Participation in the Arts or the General Social Survey) is at the macro-genre label?
-Both overlapping boundary and micro-genre heterogeneity critics of traditional genre labels would say to simply ignore these data and collect new data that does not rely on misleading macro-genre labels.
-Here I propose another solution: {\em Exploit the inherent relationality embedded in survey data responses} \citep{goldberg2011mapping, boutyline2017belief, lizardo18}.
+But what happens when all the data we have (as with long-standing surveys such as the Survey for Public Participation in the Arts or the General Social Survey) is at the macrogenre label?
+Both overlapping boundary and microgenre heterogeneity critics of traditional genre labels would say to ignore these data and collect new data that does not rely on misleading macrogenre labels.
+I propose another solution: {\em Exploit the inherent relationality embedded in survey data responses} \citep{goldberg2011mapping, boutyline2017belief, lizardo18}.
 
-More specifically, my point will be that by exploiting the inherent relationality already contained in the usual survey data (when treated as two-mode network data), old data can reveal insights that pertain to the very features sociological critics of the macro-genre label concept say is missing.
-In particular, it is possible to use embedded sets of relations between people and genres to discover the very heterogeneous micro-genre communities critics say are hidden by the macro-genre label (thus my point is that these are hidden but not necessarily absent).
+More specifically, my point will be that by exploiting the inherent relationality already contained in the usual survey data (when treated as two-mode network data), old data can reveal insights that pertain to the very features sociological critics of the macrogenre label concept say are missing.
+In particular, it is possible to use embedded sets of relations between people and genres to discover the heterogeneous microgenre communities critics say are hidden by macrogenre labels (thus, my point is that these are hidden but not necessarily absent).
 This approach is thus ideal for making new use of old data.
@@
 
-As we will see, I propose an approach thoroughly complementary to and synergistic with these previous efforts.
-More to the point, the relational identification of microgenres should be able to improve the applicability of techniques like RCA, CCA, and BNA (and related techniques), because, just like standard statistical approaches (like Factor Analysis, Principal Component Analysis, Latent Class Analysis and so forth), and even techniques (like Multiple Correspondence Analysis that are sometimes opposed to the traditional statistical ones, these newfangled relational techniques are also dragged down by the macrogenre curse.
+As we will see, I propose a complementary and synergistic approach with these previous efforts.
+More to the point, the relational identification of microgenres should be able to improve the applicability of techniques like RCA, CCA, and BNA (and related techniques) because, just like standard statistical approaches (like Factor Analysis, Principal Component Analysis, Latent Class Analysis and so forth), and even techniques (like Multiple Correspondence Analysis that are sometimes opposed to the traditional statistical ones, these newfangled relational techniques are also dragged down by the macrogenre curse.
 Thus, RCA and CCA are bound to compute relationality and correlation distances within people but have to rely on vague macrogenre labels.
 The resulting evaluation logics are thus interpreted using a macrogenre lens---e.g., ``Anything but Heavy Metal'' or ``Highbrow versus Lowbrow" \citep[e.g.,][]{goldberg2011mapping, willekens2022cultural}.
-But what if what one group means by "Heavy Metal" differs from what another group means by the same vague label?
-Are we sure that certain {\em all} types of classical music are ``opposed'' to or divergent from engagement with Country or Hip Hop?
+But what if what one group means by ``Heavy Metal" differs from what another group means by the same vague label?
+Are we certain that certain {\em all} types of classical music are ``opposed'' to or divergent from engagement with Country or Hip Hop?
 Some versions of Indie/Alt Rock are considered today as ``highbrow'' as Classical music (used to be) \citep{Van_Poecke2018}; or there may exist types of Country music that appeal to highly educated audiences and, thus, to people who might also listen to musicals?
-Overall, all quantitative techniques used by researchers in the sociology of taste must work with the (broad) genre categories included in the survey they are powerless to deal with these (reasonable) objections.
+All quantitative techniques researchers use in the sociology of taste must work with the (broad) genre categories included in the survey.
+As such, they are powerless to deal with these (reasonable) objections.
 
-Importantly, this implies that the clumping of vague macrogenre labels into even vaguer meta-macrogenres (discourses, styles, logics, schemas) like ``highbrow'' could be a spurious by-product of the vague labeling (as micro-genres critics have long suspected).
-This matters because such macrogenre clumping does much conceptual (and technical) work in our data reduction, data interpretation, and substantive theorizing efforts.
+Importantly, this implies that the clumping of vague macrogenre labels into even vaguer meta-macrogenres (discourses, styles, logics, schemas) like ``highbrow'' ``Popular," or ``Folk," could be a spurious by-product of the vague labeling (as microgenres critics have long suspected).
+This matters because such macrogenre clumping does much conceptual (and technical) work in our data reduction, interpretation, and substantive theorizing efforts.
 The result is that it is likely that people are classified as following the same cultural logic of genre valuation and evaluation when they, in fact, follow distinct logics.
@@
 \subsection{Data to be Used in the Study}
-The empirical part of the study uses data on the musical tastes of American collected with Sara Skiles in the summer of 2012 \citep{lizardo_skiles15, lizardo_skiles16}.
+The empirical part of the study uses data on the musical tastes of Americans collected with Sara Skiles in the summer of 2012 \citep{lizardo_skiles15, lizardo_skiles16}.
 The survey was (partially) designed to replicate the General Social Survey (GSS) 1993 Culture Module.
@@
 Like GSS 1993, SSI 2012 included items assessing respondents’ likes and dislikes (as well as a middle category of ``mixed feelings'') for 20 categories of musical style: classical/ symphony and chamber, opera/operetta, jazz, Broadway musicals/show tunes, mood/easy listening, big band/swing, classic rock/oldies, country, bluegrass, folk, hymns/gospel, Latin/Spanish/salsa, rap/hip hop, blues/R\&B, reggae, top 40/pop music, contemporary rock, indie/alternative rock, dance/club/electronic, and hard rock/heavy metal.
-In addition to providing a taste judgment for each item, respondents were also asked if they regularly listened to each macro-genre.
-The following analyses are based on a data frame in which people are coded as engaging the macro-genre if they report both liking and listening to it.
+In addition to providing a taste judgment for each item, respondents were also asked if they regularly listened to each macrogenre.
+The following analyses are based on a data frame in which people are coded as engaging the macrogenre if they report both liking and listening to it.
 The two-mode network we will be working with is thus of dimensions and has $2263$ people and $20$ genres.
-This defines an affiliation matrix $A_{PG}$ of the same dimensions, with entries equal to 1 if person $P$ likes \textit{and} listens to macro-genre label $G$ and zero otherwise.
+This defines an affiliation matrix $A_{PG}$ of the same dimensions, with entries equal to 1 if person $P$ likes \textit{and} listens to macrogenre label $G$ and zero otherwise.
 
 \subsection{The Link Clustering Approach}
-I propose that exploiting {\em relationality} hidden in the usual survey data collecting information on people and genres can help us make headway on the micro-genre critique outlined in the preceding.
+I propose that exploiting {\em relationality} hidden in the usual survey data collecting information on people and genres can help us make headway on the microgenre critique outlined in the preceding.
 As noted at the outset, this requires that we stop looking at the usual survey data that forms the bulk of empirical material in the quantitative study of taste as ``survey data'' (e.g., data collected on the characteristics of individuals in the form of ``variables'').
 This is a presumption that is baked into traditional techniques (like Factor Analysis or Latent Class Analysis) that fit statistical models to such data.
-It is also embedded in ``relational'' techniques like Multiple Correspondence Analysis which, while not steeped in the preoccupations of standard statistical inference (although it could be), divert our attention to the indirect relations between macro-genres (or between people), usually conceptualized as distances in a social space.
-This kind of indirect relationality is fine and dandy but as already noted in the case of RCA, CCA, and BNA, all the relationality built into MCA is powerless, if what is fed {\em into} the process is the same old, limited, overextended macro-genre categories.
+It is also embedded in ``relational'' techniques like Multiple Correspondence Analysis which, while not steeped in the preoccupations of standard statistical inference (although it could be), divert our attention to the indirect relations between macrogenres (or between people), usually conceptualized as distances in a social space.
+This kind of indirect relationality is fine and dandy but as already noted in the case of RCA, CCA, and BNA, all the relationality built into MCA is powerless, if what is fed {\em into} the process is the same old, limited, overextended macrogenre categories.
 
-I address the micro-genre issue using a technique for overlapping community detection called link clustering \citep{ahn_etal10}.
+I address the microgenre issue using a technique for overlapping community detection called link clustering \citep{ahn_etal10}.
 The basic idea is simple and is illustrated in the toy example shown in Figure~\ref{fig:link-toy1}.
@@
 Classifying the links gives (by definition) a classification of the entities at the end of each link (people and genres) for free.
-Not only that, because most people choose multiple genres, and all genres ``choose'' multiple people, this classification guarantees that genres get assigned to multiple \textit{overlapping} clusters, at the same time splitting up the macro-genres into more relationally focused clumps.
-This allows us to make headway on both horns of the micro-genre critique---namely, overlapping categories and internal differentiation---at once.
+Not only that, because most people choose multiple genres, and all genres ``choose'' multiple people, this classification guarantees that genres get assigned to multiple \textit{overlapping} clusters, at the same time splitting up the macrogenres into more relationally focused clumps.
+This allows us to make headway on both horns of the microgenre critique---namely, overlapping categories and internal differentiation---at once.
 
@@
 
-If we do that for all pairs of person-to-culture genres sharing one genre node in common, we end up with the two-way, one-mode (now the only mode is edges) $11 \times 11$ similarity matrix shown in Figure~\ref{fig:link-toy3}.
+If we do that for all pairs of person-to-culture genres sharing one genre node in common, we end up with the two-way, one-mode (with the only mode being edges) $11 \times 11$ similarity matrix shown in Figure~\ref{fig:link-toy3}.
 Note two features of the similarity matrix.
-First, by definition two person-to-genre links that go from different genres to the same person are maximally similar (as the overlap is 1.0).
+First, by definition, two person-to-genre links that go from different genres to the same person are maximally similar (as the overlap is 1.0).
 This means that only links that go from different people to the same genre exhibit overlap variation, and this is driven (``reflectively'' \citep{lizardo18}) by the overlap between the neighborhoods of the other mode (people).
@@
 The resulting dendrogram from the cluster analysis is shown in Figure~\ref{fig:link-toy5}.
-Note that moving from the top down, the dendrogram splits person-to-genre links according to the macro-genre label.
-That is macro-genre information is preserved in the clustering, and can be recovered by splitting the dendrogram at a height where the number of clusters is equal to the original number of macro-genres (in this case, four as shown in Figure~\ref{fig:link-toy5}).
+Note that moving from the top down, the dendrogram splits person-to-genre links according to the macrogenre label.
+That is, macrogenre information is preserved in the clustering and can be recovered by splitting the dendrogram at a height where the number of clusters is equal to the original number of macrogenres (in this case, four as shown in Figure~\ref{fig:link-toy5}).
 Moving from the bottom up, the hierarchical clustering of the dissimilarity matrix yields {\em link communities} \citep{ahn_etal10}, in which both people nodes, but, most crucially, genres nodes are assigned to different clumps.
-In the limiting case (the bottom-most ``leafs'' of the dendrogram, each person-to-genre links are assigned to their cluster.
-The more interesting thing is that as we move up to a point below macro-genres clusters and above the leafs, we see a partition of {\em varieties} of macro-genres.
-For instance, macro-genre $G4$ is split into two focused micro-genre varieties.
-The first is attached to persons $P2$ and $P4$ and the second attached to persons $P3$ and $P5$ respectively.
-The idea then, is that the macro-genre nodes (e.g., ``Classical,'') assigned to different clumps represent micro-variations of the macro-genre label that differ primarily in a relational or structural way; different ``types'' of ``Classical'' are different because their audiences make distinct choices {\em with respect} to the other genres in the survey.
+In the limiting case (the dendrogram's bottom-most ``leafs''), each person-to-genre link is assigned to a cluster.
+The more interesting thing is that as we move up to a point below macrogenres clusters and above the leaves, we see a partition of {\em varieties} of macrogenres.
+For instance, macrogenre $G4$ is split into two focused microgenre varieties.
+The first is attached to persons $P2$ and $P4$, and the second attached to persons $P3$ and $P5$, respectively.
+The idea, is that the macrogenre nodes (e.g., ``Classical,'') assigned to different clumps represent micro-variations of the macrogenre label that differ primarily relationally or structurally; different ``types'' of ``Classical'' are different because their audiences make distinct choices {\em with respect} to the other genres in the survey.
 
@@
 The resulting partition has two interesting (and desirable) properties.
-First, the number of genre communities that \textit{people} belong to is deterministic, and it is given by the number of macro-genre labels they initially chose.
+First, the number of genre communities that \textit{people} belong to is deterministic, and it is given by the number of macrogenre labels they initially chose.
 Thus, link clustering preserves the cultural ego network degrees (omnivorousness by volume) of the people mode \citep{lizardo14}.
-Second, the number of micro-genres into which the macro-genres are split is {\em not} deterministic.
+Second, the number of microgenres into which the macrogenres are split is {\em not} deterministic.
 Instead, it is data-driven (discovered or learned) and cannot be pre-specified in advance.
 It is a function of relational information implicit in the overlap structure of the cultural ego networks of people in the data.
-Thus, link community detection of the person-to-genre network allows us to go from  a situation starting with a person-to-genre network featuring a relatively small number of macro-genres and end up with an enlarged two-mode network with the same number of nodes in one mode (the people) but many more nodes in the other mode (the micro-genres).
-How many micro-genres ($N_m$) emerge is up to the analyst as it depends on where we ``cut'' the resulting clustering dendrogram.
-This will be somewhere in between $N_g \geq N_m \leq N_l$, where $N_g$ is the number of original (macro) genres and $N_l$ is the number of person-to-genre links.
+Thus, link community detection of the person-to-genre network allows us to go from a situation starting with a person-to-genre network featuring a relatively small number of macrogenres and end up with an enlarged two-mode network with the same number of nodes in one mode (the people) but many more nodes in the other mode (the microgenres).
+How many microgenres ($N_m$) emerge is up to the analyst as it depends on where we ``cut'' the resulting clustering dendrogram.
+This will be somewhere between $N_g \geq N_m \leq N_l$, where $N_g$ is the number of original (macro) genres and $N_l$ is the number of person-to-genre links.
 
 \section{Analysis and Results}
-\subsection{Discovering Micro-genre Communities in Real Data}
+\subsection{Discovering microgenre Communities in Real Data}
 Let us see how this process works in real data.
-We will see that link clustering can uncover valid micro-genres.
-Recall that the data feature 2,263 people choosing up to 20 macro-genre labels.
+We will see that link clustering can uncover valid microgenres.
+Recall that the data features 2,263 people choosing up to 20 macrogenre labels.
 When strung out as an edgelist, this results in 9,216 person-to-genre connections in the data, the resulting $9216 \times 9,216$ matrix, containing Jaccard similarities among person-to-genre links sharing a node in either of the two modes, is then the input to an agglomerative hierarchical clustering algorithm using Ward's \citep{ward63} method.
 The hierarchical clustering process proceeds as follows.
-Initially  each person-to-genre link is initially assigned to its own community.
+
+Initially, each person-to-genre link is assigned to a singleton cluster.
 Then, in the second time step, the pairs of links with the largest Jaccard similarities are put in the same clump.
@@
 The height of the dendrogram provides information about the strength of the genre communities.
-As we have seen, the highest levels reproduce the original macro-genres, while the lower levels uncover more focused micro-genres embedded within them.
+As we have seen, the highest levels reproduce the original macrogenres, while the lower levels uncover more focused microgenres embedded within them.
 This is shown in Figure~\ref{fig:dend}.
 
-Figure~\ref{fig:dend-macro} shows that when we cut the dendrogram at a high level (e.g., $C = 8$), we reproduce the original twenty macro-genres we began with as the ``discovered'' link communities.
-Note that, as Figure~\ref{fig:dend-macro-labels} shows, the agglomerative link clustering procedure arranges the macro-genre levels roughly by their original popularity (number of person-to-genre links).
+Figure~\ref{fig:dend-macro} shows that when we cut the dendrogram at a high level (e.g., $C = 8$), we reproduce the original twenty macrogenres we began with as the ``discovered'' link communities.
+As Figure~\ref{fig:dend-macro-labels} shows, the agglomerative link clustering procedure roughly arranges the macrogenre levels by their original popularity (number of person-to-genre links).
 From left to right, these are Classic Rock/Oldies, Pop/Top 40, Country, Classical, Easy Listening, Blues/R\&B, Contemporary Rock, Rap/Hip Hop, Jazz, Gospel, Dance/Club, Indie Alternative, Latin, Broadway/Musicals, Heavy Metal/Hard Rock, Reggae, Big Band, Folk, Bluegrass, and Opera.
-As shown in Figure~\ref{fig:dend-micro}, micro-genre communities are produced by cutting the link clustering dendrogram at a lower level.
-When we choose a cutoff value of $c = 3$ results in $k = 102$ micro-genre communities extracted from the original twenty macro-genre labels.
-Data scientists wring their hands when performing cluster analysis about choosing a cut value.
-One advantage of the link clustering approach is that we always know what we are doing because micro-genres are strictly nested within the original macro-genres.
-On the other hand, choosing a smaller cut value produces finer-grained micro-genres (perhaps at the expense of analytic tractability and interoperability), and selecting a higher value returns us to broader genre communities closer to the original macro-genre labels we began with (with the limiting case as shown in Figure~\ref{fig:dend-macro} being the original macro genre labels themselves).
-As Figure~\ref{fig:dend-micro-labels} shows, at any cut value $C$, the more popular macro-genres produce more micro-genre communities, while the less popular ones produce a smaller number.
-For instance, as shown in Figure~\ref{fig:dend-micro-classic-rock}, at $c = 3$, the macro-genre ``Classic Rock/Oldies'' (the leftmost set of branches in the dendrogram in Figure~\ref{fig:dend-macro}) is split (at the point at which the branches intersect the red dashed cut line) into $k_{(CR)} = 12$ distinct micro-variations, while, as Figure~\ref{fig:dend-micro-opera} shows, the macro-genre ``Opera" (the rightmost set of branches in the dendrogram in Figure~\ref{fig:dend-macro}) is split into only $k_{(Op)} = 2$  micro-genre communities.
-Figure~\ref{fig:dend-micro-blues} shows that ``Blues/R\&B'' falls somewhere in between, with $k_{(BRB)} = 5$  micro-genre communities uncovered.
+As shown in Figure~\ref{fig:dend-micro}, microgenre communities are produced by cutting the link clustering dendrogram at a lower level.
+Choosing a cutoff value of $c = 3$ results in $k = 102$ microgenre communities extracted from the original twenty macrogenre labels.
+Data scientists wring their hands about choosing a cut value when performing cluster analysis.
+One advantage of the link clustering approach is that we always know what we are doing because microgenres are strictly nested within the original macrogenres.
+On the other hand, choosing a smaller cut value produces finer-grained microgenres (perhaps at the expense of analytic tractability and interoperability), and selecting a higher value returns us to broader genre communities closer to the original macrogenre labels we began with (with the limiting case as shown in Figure~\ref{fig:dend-macro} being the original macro genre labels themselves).
+As Figure~\ref{fig:dend-micro-labels} shows, at any cut value $C$, the more popular macrogenres produce more microgenre communities, while the less popular ones produce a smaller number.
+For instance, as shown in Figure~\ref{fig:dend-micro-classic-rock}, at $c = 3$, the macrogenre ``Classic Rock/Oldies'' (the leftmost set of branches in the dendrogram in Figure~\ref{fig:dend-macro}) is split (at the point at which the branches intersect the red dashed cut line) into $k_{(CR)} = 12$ distinct micro-variations, while, as Figure~\ref{fig:dend-micro-opera} shows, the macrogenre ``Opera" (the rightmost set of branches in the dendrogram in Figure~\ref{fig:dend-macro}) is split into only $k_{(Op)} = 2$  microgenre communities.
+Figure~\ref{fig:dend-micro-blues} shows that ``Blues/R\&B'' falls somewhere in between, with $k_{(BRB)} = 5$  microgenre communities uncovered.
 
-Each cut point in the dendrogram will have a micro-genre size distribution $N$ associated with it.
-Lower cut points return a micro-genre size distribution dominated by many micro-genres with tiny ($N_{mg} < 10$) or trivial $N_{mg} = 2$ audiences.
+Each cut point in the dendrogram will have a microgenre size distribution $N$ associated with it.
+Lower cut points return a microgenre size distribution dominated by many microgenres with tiny ($N_{mg} < 10$) or trivial $N_{mg} = 2$ audiences.
 In this respect, although I have been using the labels ``macro'' and ``micro'' as if they referred to substantive or objective partitions, they are best interpreted as {\em relative} to a given classification level.
-Thus, micro-genres are ``micro'' relative to the usual (perhaps ``basic'' in Rosch's \citeyearpar{Rosch1978-ue} sense) level of vague macro-genre labels that populate most arts participation surveys.
+Thus, microgenres are ``micro'' relative to the usual (perhaps ``basic'' in Rosch's \citeyearpar{Rosch1978-ue} sense) categorization level of vague macrogenre labels populating most arts participation surveys.
 But these may be micro, as we will see, relative to the (logics, discourses, schemas) meta-groupings that we generate when applying the usual suite of statistical and data reduction techniques (e.g., such as ``highbrow'' or ``Folk").
-Further, at any given classification level, further micro-genres will be nested within any given micro-partition.
-In this way, micro-genre communities reflect a substantively valid way in which people partition the cultural world, whereby there is always the possibility of making finer-grained distinctions within fine-grained distinctions (e.g., ``old school rap," ``1980s old school rap,", ``early 1980s old school rap," and the like).
+Further, at any given classification level, further microgenres will be nested within any given micro-partition.
+In this way, microgenre communities reflect a substantively valid way in which people partition the cultural world, whereby there is always the possibility of making finer-grained distinctions within fine-grained distinctions (e.g., ``old school rap," ``1980s old school rap,", ``early 1980s old school rap," and the like).
 
-Ultimately, there is no magical ``right'' answer here, but for analytic purposes $c = 3, k = 102, max(N_{mg}) = X, min(N_{mg}) = Y$ is sufficiently fine-grained to showcase the analytic advantages of the micro-genre approach.
-The resulting size distribution is shown in Figure~\ref{fig:size-dist}.
-The main panel shows the micro-genre communities chosen by 75 or more people, and the inset shows the entire size distribution.
-micro-genre communities are named according to the original macro-genre label, followed by a number.
-As the figure shows, the largest micro-genre communities in the data pertain to micro-variants of Indie/Alternative Rock, Contemporary Rock, Reggae, Classic Rock, Blues/R\&B, and Gospel.
+\subsection{Two Genre Case Studies}
+We have shown that we can perform a link clustering and that this clustering returns a nice set of microgenres nested within the usual macrogenres in the survey.
+But does this exercise result in any substantive gains?
+In this section, I show that the link clustering approach does allow you to extract new insights from old data.
+There are many ways we can proceed.
+I choose to present two ``case studies'' of macrogenre labels and the resulting microgenre variations returned by the link clustering procedure.
+My criteria were as follows: I selected a macrogenre label for which I could find some substantiated claim in the scholarly literature regarding possible microgenre variation.
+Naturally, general claims about microgenre variation apply to all macrogenre labels.
+Therefore, the ``substantiated in the scholarly literature" serves as a way to narrow the field.
+I settled on Heavy Metal and Latin/Spanish Music/Salsa using this criterion.
+I intended to identify macrogenre labels for which some sort of debate or uncertainty existed in the scholarly literature regarding their overall status and their variations.
+As we will see, Metal definitely fits this bill, as a lively debate already exists regarding its status.
+Latin/Spanish/Salsa represents a more ``minor'' case study in comparison but still serves to showcase the usefulness of the link clustering approach for resolving key issues.
 
- \begin{figure}[ht!]
- \centering
- \includegraphics[width=0.7\textwidth]{Figs/Link Clust/micro-genre-size-dist.png}
- \caption{}
-  \label{fig:size-dist}
- \end{figure}
+\subsection{Heavy Metal}
+Heavy Metal is one of the most storied macrogenre labels in the sociology of taste.
+It is featured in Bethany Bryson's \citeyearpar{bryson96} classic paper.
+Since then, it has been the subject of scholarly debate regarding its possibly changing status in the cultural stratification order.
+Heavy Metal was distinct in Bryson's study for several reasons.
+First, it was the most disliked genre in the 1993 General Social Survey culture module data---one of the most heavily analyzed data sources in the sociology of taste, hence its being featured in the title of Bryson's eponymous piece.
+Second, it was the prototypical genre that was relatively more favored by working-class audiences but absolutely hated by individuals with high education.
+Thus, it served as the linchpin of Bryson's symbolic exclusion argument; omnivores were omnivorous up to a point, except when it came to those genres most favored by those with low education.
 
-\subsection{What Micro-Genre Communities Reveal}
-\subsubsection{Hidden Dimensionality}
-So what do we learn about people's tastes and about the micro-genres themselves after subjecting our data to link clustering?
-Comparing the answers we get from applying a standard, relatively undemanding (in terms of statistical assumptions foisted upon the data), namely, Principal Components Analysis, to the original and link-clustered cultural network data (hereafter OD, and LCD, respectively) can be illuminating in this respect.
-Particularly in terms of showing what is revealed by the link clustering in exposing the hidden relationality in the data and in what ways relying on vague macro-genre levels leads us astray both substantively and theoretically.
+Regardless, the picture we got of Metal concerning audience segmentation was clear: It was a genre that primarily appealed to working-class, low-education white men and was rejected by pretty much everyone else.
+Lizardo and Skiles \citeyearpar[][6, table 2]{lizardo_skiles16} used the same data source as in this paper (data from 2012) and found that, nineteen years later, Metal was still the most disliked of the macrogenre labels; not only that, when asked who the typical fan of metal looked like, Americans agreed with the stereotype: Low education, ``lower'' and working-class white men \citep[][7, table 3]{lizardo_skiles16}.
 
-\begin{figure}[ht!]
-    \includegraphics[width=1.0\textwidth]{Figs/Link Clust/macro-v-micro-pca-eig.png}
-    \caption{}
-    \label{fig:eig}
- \end{figure}
+Yet, cracks began to appear in this picture as soon as it was hung.
+First, Tampubolon \citeyearpar{tampubolon2008revisiting} re-analyzed the Bryson data using a different methodological approach (latent-class analysis), making different inclusion decisions regarding the ``don't know'' responses.
+Tampubolon shows that including those ``don't know'' responses significantly changes things.
+Concerning Metal, it indicates that it is strongly disliked among low-education more than would have been surmised in Bryson's original study.
+For Tampubolon, this makes Metal ``quite exceptional'' since it is disliked across the board and even more by low-education people.
 
-The first---perhaps already evident---thing we learn is that macrogenre labels hide underlying multidimensionality in cultural taste data, which the link clustering reveals.
-To show this, Figure \ref{fig:eig} shows the scree plot of the PCA analysis of the OD and the LCD.
-In the figure, the size of the eigenvalue is shown on the y-axis; the order (first, second, third, and so forth) of the corresponding eigenvalue is shown on the x-axis.
-The vertical red line going across the plot corresponds to the value on the y-axis where $\lambda = 1$.
-The black vertical line separates the eigenvalues for which $\lambda >= 1$ (on the left side of the plot) from those for which $\lambda < 1$ (on the right side of the plot).
-Using the rule of thumb that the number of eigenvalues for which $\lambda > 1$ point to significant dimensions of variation in the data, the PCA on the OD suggests the relevance of perhaps four dimensions that we may want to consider (usually, most analysts stick to the first two).
-The corresponding scree plot for the LCD reveals upwards of {\em twenty-five} dimensions that could be relevant.
+So just because Metal's audience is composed of low-education people does not mean that the rest of the less-educated population loves it; in fact, they hate it passionately.
+Tampubolon's analysis of ``Like'' responses also shows that Metal, rather than being exclusively preferred by a univorous group of ``Metalheads'' (who only prefer metal and dislike everything else), also makes it into the taste profile of one of two omnivorous groups uncovered in his analysis.
+Thus, Metal ends up straddling omnivores and univores.
+Because of this, even in the 1993 GSS data, its association with markers of status was ambiguous, leading Tampubolon to conclude that ``[p]reference or dislike for heavy metal is, therefore, orthogonal to status as measured by education'' \citeyearpar[][257]{tampubolon2008revisiting}, and that ``heavy metal is definitely not a low culture in the sense of culture `strongly associated' or very much liked by those with low education.''
 
-The first lesson we learn is that {\em macro-genre labels hide relevant dimensions of genre-level (and thus potential person-level) of differentiation in the data}.
-As we will see next, the artificial lower-dimensionality of the data considered by relying on macro-genre levels leads to substantively misleading answers to our questions.
+Tampubolon's argument regarding Metal dovetail with those preferred by Lizardo and Skiles \citeyearpar{lizardo_skiles15}, using the same data source as in this paper.
+Yes, while Metal was still the most disliked genre in 2012, \textit{compared} to 1993, it was one of the macrogenre labels (Rap and Hip Hop being the other) that experienced the steepest \textit{declines} in being disliked in the intervening two decades, especially among younger audiences.
+This strongly suggests that enjoying some types of Metal music may be an ``emerging form'' of cultural capital \cite{prieur2013emerging} among certain segments of the young elite.
 
-\subsubsection{Misleading Answers to Substantive Questions}
- What does the dimension-reduction analysis reveal substantively?
-Figures \ref{fig:macro-pca} and \ref{fig:micro-pca} show the result of ``classifying'' the genres using the first four dimensions of the PCA on the OD and the first twenty-five dimensions of the PCA on the LCD.
-In the figures, genres are classified using a ``hybrid'' (hierarchical/k-means) clustering of the (Euclidean) genre distance matrix in four-dimensional space (for the OD) and twenty-five-dimensional space (for the LCD).
-The number of clusters corresponds to the number of dimensions in the space; four macro-genre clusters ($k_{MG}$) and twenty-five micro-genre clusters ($k_{mg}$).
-After clustering, macro and micro-genres are re-embedded into two-dimensional space using their respective scores along the first two Principal Coordinates.
+\subsubsection{Microgenre Analysis}
+So, will the real heavy metal please stand up?
+Is Metal a form of emerging cultural capital with an appeal to elites or a genre heavily favored by young white people with low education?
+Or is that an outdated picture of the American musical field?
+Is Metal even correlated with status markers like education at all, as Tampubolon suggested?
+Is speaking of Metal as a ``youth'' music accurate, or has its audience been aging along with the genre (going on more than four decades and counting)?
+Given prior work, a strong expectation is that, at the very least, we should observe a microgenre partition separating the ``prototypical'' Metal (appealing to low-education white men) and perhaps a less-prototypical one, appealing to younger audiences with high-level cultural capital with other micro-variations, perhaps track generational distinction \citep{lizardo_skiles15}.
 
-\begin{figure}[ht!]
-     \begin{subfigure}[b]{1.0\textwidth}
-        \centering
-        \includegraphics[width=0.6\textwidth]{Figs/Link Clust/macro-pca-clust.png}
-        \caption{}
-        \label{fig:macro-pca}
-    \end{subfigure} 
-     \begin{subfigure}[b]{1.0\textwidth}
-        \centering
-        \includegraphics[width=0.6\textwidth]{Figs/Link Clust/micro-pca-clust.png}
-        \caption{}
-        \label{fig:micro-pca}
-    \end{subfigure} 
-    \caption{}
-    \label{fig:macro-v-micro-pca}
- \end{figure}
-
- Figure~\ref{fig:macro-pca} suggests that a two-dimensional space does a good job of representing distinctions between macro-genres (accounting for about 65\% of the variance).
-Moreover, the macro-genre clusters correspond to the usual logics or discourses that populate many studies in the sociology of taste.
-On the upper-left, we have a variety of ``folk'' genres, including Country, Gospel, Bluegrass, and the eponymous Folk (with ``Easy'' as a boundary macrogenre).
-On the lower-left, we have the usual set of ``highbrow'' genres (with Jazz as a boundary macrogenre).
-On the right, we have the standard set of ``Pop/Industry'' macrogenres, perhaps partitioned, in the four-cluster solution, into ``Rock/Pop" (the varieties of Rock and Roll, with ``Classic Rock/Oldies as a boundary macrogenre) and ``Afro/Pop" (Rap, Reggae, Blues) variants (with ``Latin/Spanish" as a boundary macrogenre).
-
- Suppose we follow the now well-established ``structuralist'' approach to interpreting these types of embeddings of cultural objects as a space governed by binary oppositions popularized by Bourdieu \citeyearpar{bourdieu84}.
-In that case, we might say that the first dimension separates or opposes Highbrow and Folk discourses to Pop/Industry logics.
-The second dimension opposes the (perhaps high-status) highbrow discourse to the perhaps lower-status folk discourse.
-The fact that Pop/Industry genres are less differentiated on this second, seemingly status-focused dimension might indicate less relevance of status distinctions among these macro-genres.
-This is all consistent with the usual story of the persistence of these broad meta-macro-genre distinctions and oppositions over time (e.g., in the case of the U.S.) or across national settings.
-
-\begin{figure}[ht!]
-    \includegraphics[width=1.0\textwidth]{Figs/Link Clust/macro-v-micro-clust.png}
-    \caption{}
-    \label{fig:macro-v-micro-cluster}
- \end{figure}
-
- Two contrasts are evident in the corresponding PCA-cluster plot (Figure~\ref{fig:micro-pca} for the LCD.
-First, the two-dimensional embedding represents the data poorly (covering less than 10\% of the variance).
-This makes sense since the LCD is a higher-dimensional entity, to begin with.
-Of more substantive importance, note that the cluster solution now presents a more complicated picture that is harder to fit into the stylized story of opposition and differentiation between broad discourses or logics.
-In Figure~\ref{fig:micro-pca}, micro-genres that belong to opposed or differentiated macro-discourses in Figure~\ref{fig:macro-pca} mingle freely into ``micro-discourses'' or ``micro-logics'' (e.g., combining variants of Country, Classic Rock, Classic, Gospel, and Pop) that would be harder to characterize except as varieties of ``omnivorousness.'' The problem with this approach, however, is that we will end up with more varieties of omnivorousness that we will know what to do with.
-
- Figure~\ref{fig:macro-v-micro-pca} makes this point evident.
-In the figure, the twenty-five micro-genre clusters shown in Figure~\ref{fig:micro-pca} are plotted along the y-axis.
-The x-axis consists of the unordered four-category variable formed by the (labeled) clusters in Figure~\ref{fig:macro-pca}.
-Thus, micro-genres in the same horizontal ``row'' belong to the same micro-genre cluster; reading down the columns assigns each micro-genre to a macro-genre discourse based on their macro-genre ``parent'' label.
-The point of Figure~\ref{fig:macro-v-micro-pca} is evident; {\em micro-genres combine with one another in ways that typically violate the system of oppositions and differentiation posed by macro-genre discourses}.
-In that respect, it is clear that the way people combine micro-genres does not follow the rule book suggested by the usual dimension-reduction analyses that rely on macro-genre labels like those shown in Figure~\ref{fig:macro-pca}.
-Such an approach could not make sense of the micro-genre cluster combining Classical, Opera, Gospel, Country, and Classic Rock ($k_{mg}=11)$ or the set of micro-genre clusters on the bottom left of the figure combining various (presumed) ``highbrow'' and ``Folk'' micro-genres.
-
- Of course, the standard approach cannot explain these micro-genre combination patterns.
-Some micro-genre clusters (e.g., $12 >=k_{mg}<=16$) stay within designated macro-genre discourse boundaries, consisting mainly of Rock/Pop and Afro/Pop combinations.
-Towards the top right, we see that the (very) vague macro-genre ``Classic Rock'' splits into micro-genre variants with the affinity to combine with various ``Country/Folk'' and "Highbrow'' micro-genres.
-The point of the micro-genre critique, however, is precisely that it is very likely that the {\em type} of Classic Rock that plays well with Rap is different, both stylistically and in terms of underlying audience, from the one that plays well with Country.
-In the same way, the type of Rap listened to by people who also like Classic Rock is likely to differ in consequential ways from the type of Rap listened to by people who also like to listen to Country.
-
- Overall, we learn our second lesson: Audiences combine micro-genres in ways that do not respect the traditional boundaries suggested by standard data-reduction techniques applied to macro-genre labels.
-As such, some substantive conclusions, such as those regarding the existence of logics or discourses that explain affinities and oppositions between macro-genre categories prevalent in previous work, are likely to have been overstated and, in most cases, misleading.
-The principles of vision, division, and classification people use to combine and divide micro-genre categories seem to be keyed to distinctions that cut across macro-genre categories.
-
- \subsubsection{Audience Segmentation and Microgenre Heterogeneity}
- A key task in the sociology of taste is linking audience engagement with particular cultural objects and genre categories to specific sociodemographic markers, primarily of class position, education, and socio-economic status, but also of such identity categories as gender, age (or generation), region of residence, and the like.
-This approach is crucial in getting a sense of the location of genres in social space and in making inferences about the ``status'' of genre categories themselves.
-
-\begin{figure}[ht!]
-    \centering
-    \includegraphics[width=0.8\textwidth]{Figs/Link Clust/classic-rock-macro-demog.png}
-    \caption{}
-    \label{fig:classic-rock-main}
-\end{figure}
-
-For instance, we can ascertain whether a given cluster of genres is indeed ``highbrow'' if such high-status markers of social position like higher education diplomas, high income, managerial/professional occupational status, and the like are correlated with their consumption (and the same for ``lower status'' genre categories \citep{bryson96}.
-The microgenre critique suggests that this crucial task will be controverted if macrogenre labels do not correspond to phenomenologically valid objects from the perspective of personal choices.
-That is, the conclusions that we may reach about the ``status'' of particular genre categories will be misleading if the macrogenre labels hide substantively important and relevant audience heterogeneity at the microgenre level.
-
-\begin{figure}[ht!]
-    \centering
-    \includegraphics[width=1.0\textwidth]{Figs/Link Clust/classic-rock-fav.png}
-    \caption{}
-    \label{fig:fav}
-\end{figure}
-
-Let us take the case of the (very) vague (and hybrid) macrogenre label ``Classic Rock/Oldies'' as a case study (a similar exercise could be done with each of the twenty macrogenre labels).
-This is an instructive example since the link clustering approach divides this very broad macrogenre into the most microgenres (twelve).
-As shown in Figure~\ref{fig:macro-v-micro-cluster}, these micro-genres combine with most of the other micro-genres, indicative of substantial levels of stylistic diversity (and cultural meaning) within the category.
-If we were to follow the traditional approach, an inquiry as to the audience segmentation pattern of the vague macrogenre label ``Classic Rock,'' by, for instance, specifying a logistic regression with a binary indicator that equals one if the person reports both liking and listening to the genre and a variety of socio-demographic predictors on the right-hand side, we would end up with the results shown in Figure ~\ref{fig:classic-rock-main}.
-
-\begin{figure}[ht!]
-    \centering
-    \includegraphics[width=1.0\textwidth]{Figs/Link Clust/classic-rock-age.png}
-    \caption{}
-    \label{fig:age}
-\end{figure}
-
-In the Figure, different socio-demographic characteristics are on the y-axis, and the probability of selecting the macrogenre is on the x-axis.
-The points represented the predicted probability, obtained from the logistic regression model that a person with that characteristic reports both listening to and liking ``Classic Rock''; the horizontal line around the point represents the 90\% confidence interval around the prediction.
-The red vertical line sits at the point on the x-axis, indicating the base-probability (sample average) of engaging ``Classic Rock''; points to the right of the red line indicating socio-demographic segments that are overrepresented among Classic Rock engagers, and points to the left, represent social categories underrepresented among ``Classic Rock'' engagers.
-
-\begin{figure}[ht!]
-    \centering
-    \includegraphics[width=1.0\textwidth]{Figs/Link Clust/classic-rock-educ.png}
-    \caption{}
-    \label{fig:educ}
-\end{figure}
-
-If we proceed in the usual fashion, we would draw various substantive conclusions regarding ``Classic Rock'' from these results.
-For instance, we would conclude, looking at the curvilinear---``inverted u-shape''---pattern for the effect of age, that ``Classic Rock'' is decidedly ``middle-aged'' genre, being engaged primarily by people in their 40s, 50s, and 60s--peaking for those in their late 50s---but being less likely to be engaged young adults (people younger than 40) or the old (people in their late seventies and eighties).
-We would also conclude that ``Classic Rock'' is a decidedly ``white'' genre, with white people being overrepresented among listeners, Black and Asian people being underrepresented, and Hispanic people being no more or less likely to engage it.
-We would also conclude that, beyond the higher likelihood of people without a college degree engaging ``Classic Rock," the genre does not have much class, regional, or gender differentiation (with men, women, people of class designations, and regions comparably likely to engage it).
-In other words, we would conclude that in the U.S.
-as of the early 2010s, ``Classic Rock'' is a generationally declining, raced (as white), partially classed (concerning education) musical genre that otherwise functions as a socio-demographically ``unmarked'' form of popular culture (it is the most chosen genre in the survey).
-
-The corresponding analysis for the twelve microgenre variations, shown in Figures~\ref{fig:age} through~\ref{fig:race} shows that pretty much every single one of these conclusions is either wrong, misleading, or both.
-Each figure presents the twelve ``Classic Rock'' variations in a separate panel, with the corresponding predictor categories on the y-axis and the (scaled) predicted probability on the x-axis.
-To facilitate comparison, the shape of the effect (for age, education, and class) for all variations is presented in light gray, and the corresponding effect for that ``Classic Rock'' microgenre is highlighted.
-Figures~\ref{fig:gender} and \ref{fig:race} show a dot plot using the same data visualization strategy.
-Additionally, to get more insight regarding the ``Classic Rock'' taste communities revealed by the microgenre analysis, Figure~\ref{fig:fav} plots the probability (on the x-axis) that people who chose each of the ``Classic Rock'' microgenres (on separate plot panels) reports choosing one of the twenty original macrogenres as their favorite.
-To facilitate interpretation, only macrogenres that are one-half a standard deviation above the predicted value are highlighted, indicating the strongest macrogenre preferences.
-
-\begin{figure}[ht!]
-    \centering
-    \includegraphics[width=1.0\textwidth]{Figs/Link Clust/classic-rock-class.png}
-    \caption{}
-    \label{fig:class}
-\end{figure}
-
-First, take the characterization of ``Classic Rock'' as a generationally ``middle-aged'' genre.
-As shown in Figure~\ref{fig:age}, the shape of the age effect varies consequentially across the different microgenre variations.
-As such, we could conclude that ``Classic Rock'' is relatively age-neutral (1), tilts young (2, 4), is preferred by people in their forties (3, 12), or tilts towards senior citizens (5 and 6).
-Even for those ``Classic Rock'' microgenres for which the peak of the inverted u-shaped effect for age is preserved for people in their fifties and sixties, the peak varies systematically.
-Accordingly, the characterization of ``middle-aged'' would range from people in their 50s (10, 11) or their sixties (7, 8, 9).
-
-\begin{figure}[ht!]
-    \centering
-    \includegraphics[width=1.0\textwidth]{Figs/Link Clust/classic-rock-gender.png}
-    \caption{}
-    \label{fig:gender}
-\end{figure}
-
-Looking at Figures~\ref{fig:educ} and Figure~\ref{fig:class}, we would also have to revise our conclusions about the alleged class neutrality of ``Classic Rock'' as a form of popular culture.
-While, indeed, some variants are class-neutral, others variants are decidedly class-inflected.
-For instance, (1) repels people without educational qualifications but attracts high-income people; (3) on the other hand, repels high-income people but attracts the highly educated.
-Variation (8) has an extreme tilt toward the less educated, and repels upper middle class and high-income people; as Figure~\ref{fig:fav} shows, fans of this Classic Rock variation are likely to report considering Bluegrass and Country as their favorite macrogenres.
-Other microgenre variations of ``Classic Rock'' like (10) and (11), appeal primarily to a socio-economically upper-middle class and high-income audience.
-Note that as shown in Figure~\ref{fig:fav} this is a variant combining preferentially with microgenre variations of Folk, Easy, and Country.
-These people are likely to report considering ``Classic Rock'' and Easy Listening as their favorite macrogenres.
-
-A similar story emerges for gender.
-While Figure~\ref{fig:classic-rock-main}, suggests that the macrogenre label ``Classic Rock'' is only weakly gendered, Figure~\ref{fig:gender} shows wide variation in the extent to which different microgenre variations appeal to men and women.
-Some like (3), (5), and (7) tilt toward women; others like (4), (11), and, particularly (12) tilt toward men.
-Note that fans of microgenre (12) are also disproportionately likely to report having Hard Rock/Heavy Metal as their favorite macrogenre, shedding light on its extreme tilt toward men.
-
-\begin{figure}[ht!]
-    \centering
-    \includegraphics[width=1.0\textwidth]{Figs/Link Clust/classic-rock-race.png}
-    \caption{}
-    \label{fig:race}
-\end{figure}
-
-Looking at Figure~\ref{fig:race}, we can conclude that when it comes to ``Classic Rock'' having a racial tilt toward white people, the macrogenre analysis is not too misleading; most of the predicted probability estimates for this ethnoracial category are to the right of the expected mean.
-The same goes for its lack of appeal for people who racially identify as Black; most of the predicted probability estimates for this ethnoracial category are to the left of the expected mean for this socio-demographic category.
-However, the macrogenre analysis hides a lot of variation in the appeal of different variants of ``Classic Rock'' for both Hispanics and Asians.
-People whos self-identify as Hispanic are attracted to (1), (2), (3), and particularly (10) and (12).
-People who identify as Asian, on the other hand, are attracted to (5) and (6); note that as shown in Figure~\ref{fig:fav}, fans of these last two microgenre variations are also likely to report having such macrogenres as Classical, Broadway Showtunes, and Jazz as their favorites, as noted earlier these two variants also tend to have the oldest audiences.
+To examine these questions, I partitioned the Heavy-Metal branch of the dendrogram, at a height that resulted in four microgenre variations.
+To explore the issue of audience segmentation, I specify a logistic regression model with five binary outcomes: First, a binary variable indicating that a person chose (liked and listened to) the standard macrogenre label, and then four models with the microgenre variations as the outcome.
+The results are shown in Table~\ref{tab:metal}.
 
@@
 Let us take stock.
-We began our discussion with the network or ``relational'' revolution in the quantitative study of taste in sociology \citep{pachucki2010cultural}.
+We began by discussing the network or ``relational'' revolution in the quantitative study of taste in sociology \citep{pachucki2010cultural}.
 We noted that many good things have come from considering survey data on taste using a relational lens, including a deeper specification of core concepts in the literature and even discovering new phenomena and empirical patterns.
@@
 The labels are broad, likely to be interpreted by people in heterogeneous ways, and thus hide as much as they reveal.
-I noted recent attempts to just drop the idea of vague macro-genre labels and either study actual sociological genres on the ground (thus partially abandoning studies of audience segmentation or at least radically reconfigure them) or ``dropping the label'' \citep{sonnett2016ambivalence} by querying people about more focused objects of taste (e.g., performers within genres).
+I noted recent attempts to just drop the idea of vague macrogenre labels and either study actual sociological genres on the ground (thus partially abandoning studies of audience segmentation or at least radically reconfigure them) or ``dropping the label'' \citep{sonnett2016ambivalence} by querying people about more focused objects of taste (e.g., performers within genres).
 These are all important and good developments, but we also noted that they may throw away a good thing.
-Upping the relationality by exploiting hidden patterns in the same old vague macro-genre-based data collected before can reveal focused micro-genres.
+Upping the relationality by exploiting hidden patterns in the same old vague macrogenre-based data collected before can reveal focused microgenres.
 
-I proposed to do this using recent developments in the discovery of \textit{overlapping communities} in networks \citep{ahn_etal10}, which partially answers two of the challenges of macro-genre critics: The fact that actual genres are overlapping and not crisply bounded.
+I proposed to do this using recent developments in the discovery of \textit{overlapping communities} in networks \citep{ahn_etal10}, which partially answers two of the challenges of macrogenre critics: The fact that actual genres are overlapping and not crisply bounded.
 The fact that there is hidden heterogeneity within the broad labels we usually focus on.
-Our analysis contrasted the application of the usual techniques to the same data, conceived in the usual ``macro" way, and \textit{after} upping the relationality and discovering the micro-genres hidden within.
-It is clear that focusing on micro-genres reveals variation and patterns of cultural choice (as well as audience segmentation) that we would not have noticed using the standard approach (in this, the critics are right).
+Our analysis contrasted the application of the usual techniques to the same data, conceived in the usual ``macro" way, and \textit{after} upping the relationality and discovering the microgenres hidden within.
+It is clear that focusing on microgenres reveals variation and patterns of cultural choice (as well as audience segmentation) that we would not have noticed using the standard approach (in this, the critics are right).
 Still, we could do this without dropping the label or querying people about hundreds of micro-styles (most of which they'd be unfamiliar with).
-Instead, we exploited the venerable principle, etched into classical approaches to defining genres in network terms \citep{dimaggio1987classification}, noting that if genres are defined by the people that choose them, then they are also defined by the other choices that people make when they choose them; the country that combines with one version of Classical may not be the same country that combines with a version of the Blues (and neither is the same as the country that refuses to combine with any other style).
+Instead, we exploited the venerable principle, etched into classical approaches to defining genres in network terms \citep{dimaggio1987classification}, noting that if genres are defined by the people who choose them, then they are also defined by the other choices that people make when they choose them; the country that combines with one version of Classical may not be the same country that combines with a version of the Blues (and neither is the same as the country that refuses to combine with any other style).
 

### 2023-08-03 old-results.tex

Ultimately, there is no magical ``right'' answer here. Still, for analytic purposes, $c = 3, k = 102, max(N_{mg}) = X, min(N_{mg}) = Y$ is sufficiently fine-grained to showcase the analytic advantages of the micro-genre approach. The resulting size distribution is shown in Figure~\ref{fig:size-dist}. The main panel shows the micro-genre communities chosen by 75 or more people, and the inset shows the entire size distribution. micro-genre communities are named according to the original macro-genre label, followed by a number. As the figure shows, the largest micro-genre communities in the data pertain to micro-variants of Indie/Alternative Rock, Contemporary Rock, Reggae, Classic Rock, Blues/R\&B, and Gospel.

\subsubsection{Hidden Dimensionality}
So what do we learn about people's tastes and about the micro-genres themselves after subjecting our data to link clustering? Comparing the answers we get from applying a standard, relatively undemanding (in terms of statistical assumptions foisted upon the data), namely, Principal Components Analysis, to the original and link-clustered cultural network data (hereafter OD, and LCD, respectively) can be illuminating in this respect. Particularly in terms of showing what is revealed by the link clustering in exposing the hidden relationality in the data and in what ways relying on vague macro-genre levels leads us astray both substantively and theoretically.

\begin{figure}[ht!]
    \includegraphics[width=1.0\textwidth]{Figs/Link Clust/macro-v-micro-pca-eig.png}
    \caption{}
    \label{fig:eig}
 \end{figure}

The first---perhaps already evident---thing we learn is that macrogenre labels hide underlying multidimensionality in cultural taste data, which the link clustering reveals. To show this, Figure \ref{fig:eig} shows the scree plot of the PCA analysis of the OD and the LCD. In the figure, the size of the eigenvalue is shown on the y-axis; the order (first, second, third, and so forth) of the corresponding eigenvalue is shown on the x-axis. The vertical red line going across the plot corresponds to the value on the y-axis where $\lambda = 1$. The black vertical line separates the eigenvalues for which $\lambda >= 1$ (on the left side of the plot) from those for which $\lambda < 1$ (on the right side of the plot). Using the rule of thumb that the number of eigenvalues for which $\lambda > 1$ point to significant dimensions of variation in the data, the PCA on the OD suggests the relevance of perhaps four dimensions that we may want to consider (usually, most analysts stick to the first two). The corresponding scree plot for the LCD reveals upwards of {\em twenty-five} dimensions that could be relevant.

The first lesson we learn is that {\em macro-genre labels hide relevant dimensions of genre-level (and thus potential person-level) of differentiation in the data}. As we will see next, the artificial lower-dimensionality of the data considered by relying on macro-genre levels leads to substantively misleading answers to our questions.

\subsubsection{Misleading Answers to Substantive Questions}
 What does the dimension-reduction analysis reveal substantively? Figures \ref{fig:macro-pca} and \ref{fig:micro-pca} show the result of ``classifying'' the genres using the first four dimensions of the PCA on the OD and the first twenty-five dimensions of the PCA on the LCD. In the figures, genres are classified using a ``hybrid'' (hierarchical/k-means) clustering of the (Euclidean) genre distance matrix in four-dimensional space (for the OD) and twenty-five-dimensional space (for the LCD). The number of clusters corresponds to the number of dimensions in the space; four macro-genre clusters ($k_{MG}$) and twenty-five micro-genre clusters ($k_{mg}$). After clustering, macro and micro-genres are re-embedded into two-dimensional space using their respective scores along the first two Principal Coordinates.

\begin{figure}[ht!]
     \begin{subfigure}[b]{1.0\textwidth}
        \centering
        \includegraphics[width=0.6\textwidth]{Figs/Link Clust/macro-pca-clust.png}
        \caption{}
        \label{fig:macro-pca}
    \end{subfigure} 
     \begin{subfigure}[b]{1.0\textwidth}
        \centering
        \includegraphics[width=0.6\textwidth]{Figs/Link Clust/micro-pca-clust.png}
        \caption{}
        \label{fig:micro-pca}
    \end{subfigure} 
    \caption{}
    \label{fig:macro-v-micro-pca}
 \end{figure}

 Figure~\ref{fig:macro-pca} suggests that a two-dimensional space aptly represents distinctions between macro-genres (accounting for about 65\% of the variance). Moreover, the macro-genre clusters correspond to the usual logics or discourses that populate many studies in the sociology of taste. On the upper-left, we have a variety of ``folk'' genres, including Country, Gospel, Bluegrass, and the eponymous Folk (with ``Easy'' as a boundary macrogenre). On the lower-left, we have the usual set of ``highbrow'' genres (with Jazz as a boundary macrogenre). On the right, we have the standard set of ``Pop/Industry'' macrogenres, perhaps partitioned, in the four-cluster solution, into ``Rock/Pop" (the varieties of Rock and Roll, with ``Classic Rock/Oldies as a boundary macrogenre) and ``Afro/Pop" (Rap, Reggae, Blues) variants (with ``Latin/Spanish" as a boundary macrogenre).

 Suppose we follow the now well-established ``structuralist'' approach to interpreting these types of embeddings of cultural objects as a space governed by binary oppositions popularized by Bourdieu \citeyearpar{bourdieu84}. In that case, we might say that the first dimension separates or opposes Highbrow and Folk discourses to Pop/Industry logics. The second dimension opposes the (perhaps high-status) highbrow discourse to the perhaps lower-status folk discourse. The fact that Pop/Industry genres are less differentiated on this second, seemingly status-focused dimension might indicate less relevance of status distinctions among these macro-genres. This is all consistent with the usual story of the persistence of these broad meta-macro-genre distinctions and oppositions over time (e.g., in the case of the U.S.) or across national settings.

\begin{figure}[ht!]
    \includegraphics[width=1.0\textwidth]{Figs/Link Clust/macro-v-micro-clust.png}
    \caption{}
    \label{fig:macro-v-micro-cluster}
 \end{figure}

 Two contrasts are evident in the corresponding PCA-cluster plot (Figure~\ref{fig:micro-pca} for the LCD. First, the two-dimensional embedding represents the data poorly (covering less than 10\% of the variance). This makes sense since the LCD is a higher-dimensional entity to begin with. Of more substantive importance, note that the cluster solution presents a more complicated picture that is harder to fit into the stylized story of opposition and differentiation between broad discourses or logics. In Figure~\ref{fig:micro-pca}, micro-genres that belong to opposed or differentiated macro-discourses in Figure~\ref{fig:macro-pca} mingle freely into ``micro-discourses'' or ``micro-logics'' (e.g., combining variants of Country, Classic Rock, Classic, Gospel, and Pop) that would be harder to characterize except as varieties of ``omnivorousness.'' The problem with this approach, however, is that we will end up with more varieties of omnivorousness that we will know what to do with.

 Figure~\ref{fig:macro-v-micro-pca} makes this point evident. The twenty-five micro-genre clusters shown in Figure~\ref{fig:micro-pca} are plotted along the y-axis. The x-axis consists of the unordered four-category variable formed by the (labeled) clusters in Figure~\ref{fig:macro-pca}. Thus, micro-genres in the same horizontal ``row'' belong to the same micro-genre cluster; reading down the columns assigns each micro-genre to a macro-genre discourse based on their macro-genre ``parent'' label. The point of Figure~\ref{fig:macro-v-micro-pca} is evident; {\em micro-genres combine in ways that typically violate the system of oppositions and differentiation posed by macro-genre discourses}. In that respect, it is clear that the way people combine micro-genres does not follow the rule book suggested by the usual dimension-reduction analyses that rely on macro-genre labels like those shown in Figure~\ref{fig:macro-pca}. Such an approach could not make sense of the micro-genre cluster combining Classical, Opera, Gospel, Country, and Classic Rock ($k_{mg}=11)$ or the set of micro-genre clusters on the bottom left of the figure combining various (presumed) ``highbrow'' and ``Folk'' micro-genres.

 Of course, the standard approach cannot explain these micro-genre combination patterns. Some micro-genre clusters (e.g., $12 >=k_{mg}<=16$) stay within designated macro-genre discourse boundaries, consisting mainly of Rock/Pop and Afro/Pop combinations. Towards the top right, we see that the (very) vague macro-genre ``Classic Rock'' splits into micro-genre variants with the affinity to combine with various ``Country/Folk'' and "Highbrow'' micro-genres. The point of the micro-genre critique, however, is that it is very likely that the {\em type} of Classic Rock that plays well with Rap is different, stylistically and in terms of underlying audience, from the one that plays well with Country. In the same way, the type of Rap listened to by people who also like Classic Rock is likely to differ in consequential ways from the type of Rap listened to by people who also like to listen to Country.

 Overall, we learned our second lesson: Audiences combine micro-genres in ways that do not respect the traditional boundaries suggested by standard data-reduction techniques applied to macro-genre labels. As such, some substantive conclusions, such as those regarding the existence of logics or discourses that explain affinities and oppositions between macro-genre categories prevalent in previous work, are likely to have been overstated and, in most cases, misleading. The principles of vision, division, and classification people use to combine and divide micro-genre categories seem to be keyed to distinctions that cut across macro-genre categories.

 \subsubsection{Audience Segmentation and Microgenre Heterogeneity}
 A key task in the sociology of taste is linking audience engagement with particular cultural objects and genre categories to specific sociodemographic markers, primarily of class position, education, and socio-economic status, but also of such identity categories as gender, age (or generation), region of residence, and the like. This approach is crucial in getting a sense of the location of genres in social space and in making inferences about the ``status'' of genre categories themselves.

\begin{figure}[ht!]
    \centering
    \includegraphics[width=0.8\textwidth]{Figs/Link Clust/classic-rock-macro-demog.png}
    \caption{}
    \label{fig:classic-rock-main}
\end{figure}

For instance, we can ascertain whether a given cluster of genres is indeed ``highbrow'' if such high-status markers of social position like higher education diplomas, high income, managerial/professional occupational status, and the like are correlated with their consumption (and the same for ``lower status'' genre categories \citep{bryson96}. The microgenre critique suggests that this crucial task will be controverted if macrogenre labels do not correspond to phenomenologically valid objects from the perspective of personal choices. The conclusions we may reach about the ``status'' of particular genre categories will be misleading if the macrogenre labels hide substantively important and relevant audience heterogeneity at the microgenre level.

\begin{figure}[ht!]
    \centering
    \includegraphics[width=1.0\textwidth]{Figs/Link Clust/classic-rock-fav.png}
    \caption{}
    \label{fig:fav}
\end{figure}

Let us take the case of the (very) vague (and hybrid) macrogenre label ``Classic Rock/Oldies'' as a case study (a similar exercise could be done with each of the twenty macrogenre labels). This is an instructive example since the link clustering approach divides this very broad macrogenre into the most microgenres (twelve). As shown in Figure~\ref{fig:macro-v-micro-cluster}, these micro-genres combine with most of the other micro-genres, indicative of substantial levels of stylistic diversity (and cultural meaning) within the category. If we were to follow the traditional approach, an inquiry as to the audience segmentation pattern of the vague macrogenre label ``Classic Rock,'' by, for instance, specifying a logistic regression with a binary indicator that equals one if the person reports both liking and listening to the genre and a variety of socio-demographic predictors on the right-hand side, we would end up with the results shown in Figure ~\ref{fig:classic-rock-main}.

\begin{figure}[ht!]
    \centering
    \includegraphics[width=1.0\textwidth]{Figs/Link Clust/classic-rock-age.png}
    \caption{}
    \label{fig:age}
\end{figure}

In the Figure, different socio-demographic characteristics are on the y-axis, and the probability of selecting the macrogenre is on the x-axis. The points represented the predicted probability, obtained from the logistic regression model, that a person with that characteristic reports listening to and liking ``Classic Rock''; the horizontal line around the point represents the 90\% confidence interval around the prediction. The red vertical line sits at the point on the x-axis, indicating the base-probability (sample average) of engaging ``Classic Rock''; points to the right of the red line indicating socio-demographic segments that are overrepresented among Classic Rock engagers, and points to the left, represent social categories underrepresented among ``Classic Rock'' engagers.

\begin{figure}[ht!]
    \centering
    \includegraphics[width=1.0\textwidth]{Figs/Link Clust/classic-rock-educ.png}
    \caption{}
    \label{fig:educ}
\end{figure}

If we proceed in the usual fashion, we would draw various substantive conclusions regarding ``Classic Rock'' from these results. For instance, we would conclude, looking at the curvilinear---``inverted u-shape''---pattern for the effect of age, that ``Classic Rock'' is decidedly ``middle-aged'' genre, being engaged primarily by people in their 40s, 50s, and 60s--peaking for those in their late 50s---but being less likely to be engaged young adults (people younger than 40) or the old (people in their late seventies and eighties). We would also conclude that ``Classic Rock'' is a decidedly ``white'' genre, with white people being overrepresented among listeners, Black and Asian people being underrepresented, and Hispanic people being no more or less likely to engage it. We would also conclude that, beyond the higher likelihood of people without a college degree engaging ``Classic Rock," the genre does not have much class, regional, or gender differentiation (with men, women, people of class designations, and regions comparably likely to engage it). In other words, we would conclude that in the U.S. as of the early 2010s, ``Classic Rock'' is a generationally declining, raced (as white), partially classed (concerning education) musical genre that otherwise functions as a socio-demographically ``unmarked'' form of popular culture (it is the most chosen genre in the survey).

The corresponding analysis for the twelve microgenre variations, shown in Figures~\ref{fig:age} through~\ref{fig:race} shows that pretty much every single one of these conclusions is either wrong, misleading, or both. Each figure presents the twelve ``Classic Rock'' variations in a separate panel, with the corresponding predictor categories on the y-axis and the (scaled) predicted probability on the x-axis. To facilitate comparison, the shape of the effect (for age, education, and class) for all variations is presented in light gray, and the corresponding effect for that ``Classic Rock'' microgenre is highlighted. Figures~\ref{fig:gender} and \ref{fig:race} show a dot plot using the same data visualization strategy. Additionally, to get more insight regarding the ``Classic Rock'' taste communities revealed by the microgenre analysis, Figure~\ref{fig:fav} plots the probability (on the x-axis) that people who chose each of the ``Classic Rock'' microgenres (on separate plot panels) reports choosing one of the twenty original macrogenres as their favorite. To facilitate interpretation, only macrogenres that are one-half a standard deviation above the predicted value are highlighted, indicating the strongest macrogenre preferences.

\begin{figure}[ht!]
    \centering
    \includegraphics[width=1.0\textwidth]{Figs/Link Clust/classic-rock-class.png}
    \caption{}
    \label{fig:class}
\end{figure}

First, take the characterization of ``Classic Rock'' as a generationally ``middle-aged'' genre. As shown in Figure~\ref{fig:age}, the shape of the age effect varies consequentially across the different microgenre variations. As such, we could conclude that ``Classic Rock'' is relatively age-neutral (1), tilts young (2, 4), is preferred by people in their forties (3, 12), or tilts towards senior citizens (5 and 6). Even for those ``Classic Rock'' microgenres for which the peak of the inverted u-shaped effect for age is preserved for people in their fifties and sixties, the peak varies systematically. Accordingly, the characterization of ``middle-aged'' would range from people in their 50s (10, 11) or their sixties (7, 8, 9).

\begin{figure}[ht!]
    \centering
    \includegraphics[width=1.0\textwidth]{Figs/Link Clust/classic-rock-gender.png}
    \caption{}
    \label{fig:gender}
\end{figure}

Looking at Figures~\ref{fig:educ} and Figure~\ref{fig:class}, we would also have to revise our conclusions about the alleged class neutrality of ``Classic Rock'' as a form of popular culture. While, indeed, some variants are class-neutral, others variants are decidedly class-inflected. For instance, (1) repels people without educational qualifications but attracts high-income people; (3) on the other hand, repels high-income people but attracts the highly educated. Variation (8) has an extreme tilt toward the less educated, and repels upper middle class and high-income people; as Figure~\ref{fig:fav} shows, fans of this Classic Rock variation are likely to report considering Bluegrass and Country as their favorite macrogenres. Other microgenre variations of ``Classic Rock'' like (10) and (11), appeal primarily to a socio-economically upper-middle class and high-income audience. Note that as shown in Figure~\ref{fig:fav} this is a variant combining preferentially with microgenre variations of Folk, Easy, and Country. These people are likely to report considering ``Classic Rock'' and Easy Listening as their favorite macrogenres.

A similar story emerges for gender. While Figure~\ref{fig:classic-rock-main}, suggests that the macrogenre label ``Classic Rock'' is only weakly gendered, Figure~\ref{fig:gender} shows wide variation in the extent to which different microgenre variations appeal to men and women. Some like (3), (5), and (7) tilt toward women; others like (4), (11), and, particularly (12) tilt toward men. Note that fans of microgenre (12) are also disproportionately likely to report having Hard Rock/Heavy Metal as their favorite macrogenre, shedding light on its extreme tilt toward men.

\begin{figure}[ht!]
    \centering
    \includegraphics[width=1.0\textwidth]{Figs/Link Clust/classic-rock-race.png}
    \caption{}
    \label{fig:race}
\end{figure}

Looking at Figure~\ref{fig:race}, we can conclude that when it comes to ``Classic Rock'' having a racial tilt toward white people, the macrogenre analysis is not too misleading; most of the predicted probability estimates for this ethnoracial category are to the right of the expected mean. The same goes for its lack of appeal for people who racially identify as Black; most of the predicted probability estimates for this ethnoracial category are to the left of the expected mean for this socio-demographic category. However, the macrogenre analysis hides a lot of variation in the appeal of different variants of ``Classic Rock'' for both Hispanics and Asians. People whos self-identify as Hispanic are attracted to (1), (2), (3), and particularly (10) and (12). People who identify as Asian, on the other hand, are attracted to (5) and (6); note that as shown in Figure~\ref{fig:fav}, fans of these last two microgenre variations are also likely to report having such macrogenres as Classical, Broadway Showtunes, and Jazz as their favorites, as noted earlier these two variants also tend to have the oldest audiences.

### 2023-08-03 Functions/genre.reg.mods.R
New regression models

@@ -1,5 +1,4 @@
 genre.reg.mods <- function(genre, xvars, k = 3) {
-   library(estimatr)
    rec.taste <- function(x) {
       x = case_when(x == 1 ~ 0, x == 2 ~ 1)
       }
@@ -14,9 +13,8 @@ genre.reg.mods <- function(genre, xvars, k = 3) {
    # USER-DEFINED METHOD TO PROCESS DIFFERENT DEP VAR
    run_model <- function(dep.var) {
       fml <- reformulate(xvars, dep.var)
-      glm(fml, data = genre.micro, family = "binomial")
-      #lm(fml, data = genre.micro)
-      #lm_robust(fml, data = genre.micro)
+      #glm(fml, data = na.omit(genre.micro), family = "binomial")
+      lm(fml, data = na.omit(genre.micro))
       }
    # NAMED LIST OF MODELS
    mods <- sapply(dep.vars, run_model, simplify = FALSE)

### 2023-08-03 Functions/plot.preds.R
Fixed plot lower bound problem

@@ -1,11 +1,11 @@
-plot.preds <- function(d, xb, xlabs, yl, r.alpha = .1, p.size = 3, xm, xl) {
+plot.preds <- function(d, xb, xlabs, ym = 0, yl, r.alpha = .1, p.size = 3, xm, xl) {
    p <- ggplot(data = d, 
                mapping = aes(x = x, y = pr, fill = genre, color = genre, group = genre))
    p <- p + geom_point(size = p.size)
    p <- p + geom_line(linewidth = 0.75)
    p <- p + geom_ribbon(mapping = aes(ymin = lo, ymax = hi), 
                         alpha = r.alpha, linetype = 0)
-   p <- p + scale_y_continuous(limits = c(0, yl))
+   p <- p + scale_y_continuous(limits = c(ym, yl))
    p <- p + scale_x_continuous(limits = c(xm, xl), 
                                breaks = xb, labels = xlabs)
    p <- p + theme_minimal()

### 2023-08-03 main.tex
Updates from Overleaf

@@
 \subsection{Heavy Metal}
-Heavy Metal is one of the most storied macrogenre labels in the sociology of taste.
-It is featured in Bethany Bryson's \citeyearpar{bryson96} classic paper.
-Since then, it has been the subject of scholarly debate regarding its possibly changing status in the cultural stratification order.
-Heavy Metal was distinct in Bryson's study for several reasons.
-First, it was the most disliked genre in the 1993 General Social Survey culture module data---one of the most heavily analyzed data sources in the sociology of taste, hence its being featured in the title of Bryson's eponymous piece.
+Heavy Metal is one of the most storied macrogenre labels in the sociology of taste, as featured in the title of Bethany Bryson's \citeyearpar{bryson96} now classic paper.
+Since then, it has been the subject of scholarly debate regarding its possibly changing status in the cultural stratification order \citep{tampubolon2008revisiting, goldberg2011mapping, lizardo_skiles15}.
+Heavy Metal stood out in Bryson's study for several reasons.
+First, it was the most disliked genre in the 1993 General Social Survey culture module data---one of the most heavily analyzed data sources in the sociology of taste---hence the ``Anything But'' in the title of Bryson's eponymous piece.
 Second, it was the prototypical genre that was relatively more favored by working-class audiences but absolutely hated by individuals with high education.
@@
 Regardless, the picture we got of Metal concerning audience segmentation was clear: It was a genre that primarily appealed to working-class, low-education white men and was rejected by pretty much everyone else.
-Lizardo and Skiles \citeyearpar[][6, table 2]{lizardo_skiles16} used the same data source as in this paper (data from 2012) and found that, nineteen years later, Metal was still the most disliked of the macrogenre labels; not only that, when asked who the typical fan of metal looked like, Americans agreed with the stereotype: Low education, ``lower'' and working-class white men \citep[][7, table 3]{lizardo_skiles16}.
+Lizardo and Skiles \citeyearpar[][6, table 2]{lizardo_skiles16} used the same data source as in this paper (data from 2012) and found that, nineteen years later, Metal was still the most disliked of the macrogenre labels in a representative sample of Americans.
+Not only that, but when asked who the typical fan of metal looked like, Americans agreed with the stereotype: Low education, ``lower'' and working-class white men \citep[][7, table 3]{lizardo_skiles16}.
 
@@
 Tampubolon shows that including those ``don't know'' responses significantly changes things.
-Concerning Metal, it indicates that it is strongly disliked among low-education more than would have been surmised in Bryson's original study.
+Concerning Metal, it indicates that it is strongly disliked among low-education people more than would have been surmised in Bryson's original study, so it is not just a top-down symbolic exclusion story.
 For Tampubolon, this makes Metal ``quite exceptional'' since it is disliked across the board and even more by low-education people.
 
-So just because Metal's audience is composed of low-education people does not mean that the rest of the less-educated population loves it; in fact, they hate it passionately.
+Tampubolon's work indicates that just because Metal's audience is composed of low-education people does not mean that the rest of the less-educated population loves it; in fact, they hate it passionately.
 Tampubolon's analysis of ``Like'' responses also shows that Metal, rather than being exclusively preferred by a univorous group of ``Metalheads'' (who only prefer metal and dislike everything else), also makes it into the taste profile of one of two omnivorous groups uncovered in his analysis.
 Thus, Metal ends up straddling omnivores and univores.
-Because of this, even in the 1993 GSS data, its association with markers of status was ambiguous, leading Tampubolon to conclude that ``[p]reference or dislike for heavy metal is, therefore, orthogonal to status as measured by education'' \citeyearpar[][257]{tampubolon2008revisiting}, and that ``heavy metal is definitely not a low culture in the sense of culture `strongly associated' or very much liked by those with low education.''
+Because of this, even in the 1993 GSS data, its association with markers of status was ambiguous, leading Tampubolon to conclude that ``[p]reference or dislike for heavy metal is, therefore, orthogonal to status as measured by education'' \citeyearpar[][257]{tampubolon2008revisiting}, and that ``heavy metal is definitely not a low culture in the sense of culture `strongly associated' or very much liked by those with low education'' (\textit{ibid}).
 
@@
 Yes, while Metal was still the most disliked genre in 2012, \textit{compared} to 1993, it was one of the macrogenre labels (Rap and Hip Hop being the other) that experienced the steepest \textit{declines} in being disliked in the intervening two decades, especially among younger audiences.
-This strongly suggests that enjoying some types of Metal music may be an ``emerging form'' of cultural capital \cite{prieur2013emerging} among certain segments of the young elite.
+This led Lizardo and Skiles \citeyearpar[][18]{lizardo_skiles15} to conclude that ``The fact that young, highly educated Americans are now about as equally unlikely to dislike\ldots Heavy Metal as their same-age non-college educated peers constitutes a dramatic reversal of the pattern noted by Bryson\ldots [Metal] has experienced an improvement in standing among the college educated across almost all levels of age.'' This strongly suggests that enjoying some types of Metal music may be an ``emerging form'' of cultural capital \cite{prieur2013emerging} among certain segments of the young elite.
 
@@
 So, will the real heavy metal please stand up?
-Is Metal a form of emerging cultural capital with an appeal to elites or a genre heavily favored by young white people with low education?
+Is Metal a form of emerging cultural capital with potential appeal to young middle-class people or a genre heavily favored by white men with low education?
 Or is that an outdated picture of the American musical field?
@@
 
+\begin{figure}[ht!]
+    \centering    
+    \includegraphics[width=1.3\textwidth]{Tabs/reg-tab-metal.png}
+    \caption{}
+    \label{tab:reg-metal}
+\end{figure}
+
 To examine these questions, I partitioned the Heavy-Metal branch of the dendrogram, at a height that resulted in four microgenre variations.
-To explore the issue of audience segmentation, I specify a logistic regression model with five binary outcomes: First, a binary variable indicating that a person chose (liked and listened to) the standard macrogenre label, and then four models with the microgenre variations as the outcome.
-The results are shown in Table~\ref{tab:metal}.
+To explore the issue of audience segmentation, I specify a linear probability regression model with five outcomes: First, a binary variable indicating that a person chose (liked and listened to) the standard macrogenre label (Heavy Metal), and then four models with the microgenre variations as the outcome (Heavy Metal one through four).
+The results are shown in Table~\ref{tab:reg-metal}.
+The main predictors are the respondent's education, an indicator variable for whether at least one of the respondent's parents has a college degree, respondent's age, racial identification (in five categories), and gender identification (in two categories).
+Because the age effect is specified using a squared polynomial, it can be hard to interpret its substantive significance.
+To help with this, I show the predicted probabilities obtained for the model at different values of age for the four different microgenres in Figure~\ref{fig:age-metal}.
+
+\begin{figure}[ht!]
+    \centering    \includegraphics[width=1.0\textwidth]{Plots/Demog/micro-by-age-metal.png}
+    \caption{}
+    \label{fig:age-metal}
+\end{figure}
+
+As shown in the first model, the socio-demographic predictors of choosing the ``Heavy Metal'' macrogenre label are the ones we would expect from Bryson's original work and the stereotypical perception of the genre's audience held by Americans.
+Metal fans are less likely to have high levels of education, are less likely to be older, are more likely to be white (negative effects for all other racial identifications compared to the base category), and are more likely to be men ($p<0.01$).
+So much for the emerging cultural capital story?
+
+Not so fast.
+The results are different when looking at the predictors of the microgenre variation choices.
+Indeed, the predictors of choosing the first microgenre variation, shown in the second column of the table, are consistent with Tampubolon's story.
+For this microgenre, there is a flat education gradient ($p = 0.54$), and importantly, it is more likely to be consumed by people whose parents have a college degree ($p < 0.05$), indicating a link to cultural capital in the home environment.
+This microgenre is tilted towards younger audiences, as only the linear negative age term is statistically significant (see Figure~\ref{fig:age-metal}) and is also neutral with respect to race and gender.
+This version of Metal appeals mainly to young middle-class respondents and does not repel women or non-white audiences, a stark difference from what we would have concluded from observing the macrogenre label effects.
+
+Note that the other microgenre variations conform most closely to the audience segmentation we would expect from the version of Metal that would appeal to ``univore'' consumers, indicating that the link clustering can be discerned between these variants.
+Particularly, the second microgenre, whose predictors are shown in the third column, seems to be the ``uber-Metal,'' at least regarding the stereotype.
+It has a negative education gradient ($p = 0.06$), appeals to young-adult and middle-aged audiences (see Figure~\ref{fig:age-metal}), and repels Black and Hispanic people as well as women.
+The other Metal microgenres are variations on the same theme: The third microgenre, as shown in the fourth column in the table, is like the second but appeals mainly to young audiences, and the fourth Metal microgenre is also similar to the second but appeals to a comparatively older crowd.
+So the remaining microgenre partitions seem to indicate variations within the ``univore'' consumption profile, perhaps indicative of distinctive versions of Metal with an appeal to different generational niches \citep{koch2020evolutionary}.
+
+\subsection{Salsa}
+``it is plausible that increasing appreciation among high-status groups for a genre conventionally defined as ‘popular’ or ‘lowbrow’, will go hand in hand with its symbolic upgrading.
+And when a genre expands and spreads in terms of production, distribution and reception, it is likely to differentiate into distinct styles or subgenres.
+Under these conditions, it is to be expected that differential appreciations for different styles and forms within a given genre will develop, which may end up in a more or less clear hierarchy within this genre'' \citeyearpar[][62]{Bachmayer2014-pk}
+
+\begin{figure}[ht!]
+    \centering    
+    \includegraphics[width=1.3\textwidth]{Tabs/reg-tab-latin.png}
+    \caption{}
+    \label{tab:reg-metal}
+\end{figure}
+
+\begin{figure}[ht!]
+    \centering    \includegraphics[width=1.0\textwidth]{Plots/Demog/micro-by-age-latin.png}
+    \caption{}
+    \label{fig:age-salsa}
+\end{figure}
 

### 2023-08-03 main.tex
Updates from Overleaf

@@
     \centering    
-    \includegraphics[width=1.3\textwidth]{Tabs/reg-tab-metal.png}
+    \includegraphics[width=1.5\textwidth]{Tabs/reg-tab-metal.png}
     \caption{}
@@
 The results are shown in Table~\ref{tab:reg-metal}.
-The main predictors are the respondent's education, an indicator variable for whether at least one of the respondent's parents has a college degree, respondent's age, racial identification (in five categories), and gender identification (in two categories).
+The main predictors are the respondent's education, an indicator variable for whether at least one of the respondent's parents has a college degree, the respondent's age, racial identification (in five categories), and gender identification (in two categories).
 Because the age effect is specified using a squared polynomial, it can be hard to interpret its substantive significance.
-To help with this, I show the predicted probabilities obtained for the model at different values of age for the four different microgenres in Figure~\ref{fig:age-metal}.
+To help with this, I show the predicted probabilities obtained for the model at different age values for the four different microgenres in Figure~\ref{fig:age-metal}.
 
@@
 Not so fast.
-The results are different when looking at the predictors of the microgenre variation choices.
+The results differ when looking at the predictors of the microgenre variation choices.
 Indeed, the predictors of choosing the first microgenre variation, shown in the second column of the table, are consistent with Tampubolon's story.
@@
 
+``Taste in salsa music shows a strong internal, hierarchical order between ‘artistic’ versus ‘popular’ styles that is not only acknowledged and defined as such by experts and professionals within the field, but also structures the taste patterns of different social classes'' \citeyearpar[][62]{Bachmayer2014-pk}
+
 \begin{figure}[ht!]
     \centering    
-    \includegraphics[width=1.3\textwidth]{Tabs/reg-tab-latin.png}
+    \includegraphics[width=1.5\textwidth]{Tabs/reg-tab-latin.png}
     \caption{}

### 2023-08-03 old_Rmds/04_microgenre-analysis.qmd
A bunch of deleted and moved folders and updated toy example

---
  title: "Discovering Focused Microgenre Communities: Microgenre Analysis"
  author: "Omar Lizardo"
  date: "`r Sys.Date()`"
  output:
    html_document: default
---

# Setup
```{r setup}
    knitr::opts_chunk$set(include=FALSE, echo = TRUE, warning = FALSE, message = FALSE)
    require("factoextra")
    require("FactoMineR")
    require("gghighlight")
    require("ggplot2")
    require("ggrepel")
    require("here")
    require("patchwork")
    require("sjPlot")
    require("RColorBrewer")
    require("tidyverse")
    source(here("Functions", "pred.probs.R"))
    source(here("Functions", "mpred.probs.R"))
    source(here("Functions", "mfav.probs.R"))
    source(here("Functions", "fav.probs.R"))
```

```{r Creating new person by micro-genre two mode network data}
    load(file= here("dat", "lclust-res.RData"))
```

# Descriptive Plots
```{r histogram of cluster size distribution}
    micro.g.sizes <- colSums(micro.g.dat[, 2:ncol(micro.g.dat)])
    hist.small <- data.frame(size = micro.g.sizes, micro.g = names(micro.g.sizes)) 
    hist.big <- filter(hist.small, size >= 75)
    p <- ggplot(data = hist.big, #histogram of genre community size distribution for communities with 75 or more members
            mapping = aes(y = reorder(micro.g, size), x = size, fill = micro.g))
    p <- p + geom_bar(stat = "identity")
    p <- p + labs(x = "", y = "") 
    p <- p + theme_sjplot2()
    p.big <- p + theme(axis.text.y = element_text(size = 16), 
                       axis.text.x = element_text(size = 16),
                       legend.position = "none"
    )

    p <- ggplot(data = hist.small, #full histogram of genre community size distribution
                mapping = aes(y = reorder(micro.g, size), x = size))
    p <- p + geom_bar(stat = "identity", color = "red", fill = "red")
    p <- p + labs(x = "", y = "") 
    p <- p + theme_minimal()
    p.small <- p + theme(axis.text.y = element_blank(),
                         plot.background = 
                           element_rect(colour = "black", size = 0.45)
    )
    p <- p.big + inset_element(p.small, 0.7, 0.01, 1, 0.35) #inset plot using patchwork
    p
    save_plot(here("Plots", "Link Clust", "micro-genre-size-dist.png"), 
              width = 35, height = 45)
```

# PCA Analysis 
```{r PCA eigenvalue comparison of regular and link clustered data}
    pca.macro <- PCA(taste.dat[, 2:ncol(taste.dat)], 
                     ncp = 10, graph = FALSE)
    eig.macro <- get_eig(pca.macro)[, 1]
    pca.micro <- PCA(micro.g.dat[, 2:ncol(micro.g.dat)], 
                     ncp = 50, graph = FALSE)
    eig.micro <- get_eig(pca.micro)[, 1]
    p <- fviz_eig(pca.macro, ncp = 10, choice = "eigenvalue") 
    p <- p + geom_hline(yintercept = 1, color = "red")
    p <- p + geom_vline(xintercept = length(eig.macro[eig.macro >= 1]))
    p <- p + scale_y_continuous(breaks = seq(0, 8 , 1), limits = c(0,8))
    p <- p + ggtitle("Macrogenres")
    p <- p + theme(axis.text = element_text(size = 12))
    p1 <- p + scale_x_discrete(breaks = seq(1, 10, by = 1))

    p <- fviz_eig(pca.micro, ncp = 50, choice = "eigenvalue") 
    p <- p + geom_hline(yintercept = 1, color = "red")
    p <- p + geom_vline(xintercept = length(eig.micro[eig.micro >= 1]))
    p <- p + scale_y_continuous(breaks = seq(0, 8 , 1), limits = c(0,8))
    p <- p + ggtitle("Microgenres")
    p <- p + theme(axis.text = element_text(size = 12))
    p2 <- p + scale_x_discrete(breaks = seq(0, 50, by = 5))
    p1 + p2 + plot_annotation(title = "Scree Plot")
    save_plot(here("Plots", "Link Clust", "macro-v-micro-pca-eig.png"), 
              width = 25, height = 25)
```

```{r Clustering macrogenres on the main principal coordinates}
    k.macro <- 4
    clus.macro.dat <- data.frame(pca.macro$var$coord)[1:k.macro]
    hc.macro <- eclust(clus.macro.dat, "hclust", 
                       method = "ward.D2",
                       k = k.macro, graph = FALSE)
    clus.macro <- cbind(data.frame(cluster = hc.macro$cluster), 
                        clus.macro.dat) 
    clus.macro.centers <-  clus.macro %>% 
      group_by(cluster) %>% 
      summarize(across(starts_with("Dim"), mean)) %>% 
      dplyr::select(-1)
    clus.macro.centers
    km.macro <- eclust(clus.macro.dat, 
                       "kmeans", k = clus.macro.centers, graph = FALSE)
    p <- fviz_cluster(km.macro, 
                      ellipse = FALSE, 
                      repel = TRUE,
                      geom = "text",
                      labelsize = 16)
    p <- p + theme_sjplot()
    p <- p + theme(legend.position = "none",
                   axis.title = element_text(size = 14),
                   axis.text = element_text(size = 14),
                   axis.line = element_line(color = "white"))
    p <- p + ggtitle("")
    p <- p + geom_hline(yintercept = 0, color = "gray60")
    p <- p + geom_vline(xintercept = 0, color = "gray60")
    p 
    save_plot(here("Plots", "Link Clust", "macro-pca-clust.png"), width = 25, height = 25)

```

```{r Clustering microgenres on the main principal coordinates}
    k.micro <- 25
    clus.micro.dat <- data.frame(pca.micro$var$coord)[1:k.micro]
    hc.micro <- eclust(clus.micro.dat, "hclust", 
                       method = "ward.D2",
                       k = k.micro, graph = FALSE)
    clus.micro <- cbind(data.frame(cluster = hc.micro$cluster), 
                        clus.micro.dat) 
    clus.micro.centers <-  clus.micro %>% 
      group_by(cluster) %>% 
      summarize(across(starts_with("Dim"), mean)) %>% 
      dplyr::select(-1)
    clus.micro.centers
    km.micro <- eclust(clus.micro.dat, 
                       "kmeans", k = clus.micro.centers, graph = FALSE)
    p <- fviz_cluster(km.micro, 
                      ellipse = FALSE, 
                      repel = TRUE,
                      geom = "text")
    p <- p + theme_sjplot()
    p <- p + theme(legend.position = "none",
                   axis.title = element_text(size = 14),
                   axis.text = element_text(size = 14),
                   axis.line = element_line(color = "white"))
    p <- p + ggtitle("")
    p <- p + geom_hline(yintercept = 0, color = "gray60")
    p <- p + geom_vline(xintercept = 0, color = "gray60")
    p 
    save_plot(here("Plots", "Link Clust", "micro-pca-clust.png"), 
              width = 25, height = 25)
```

```{r Combining macro and micro-genre clusters into a single plot}
    km.macro.dat <- data.frame(macro.cluster =  km.macro$cluster) 
    km.macro.dat <- cbind(genre = rownames(km.macro.dat), km.macro.dat)
    km.micro.dat <- data.frame(micro.cluster =  km.micro$cluster)
    km.micro.dat <- cbind(genre = rownames(km.micro.dat), km.micro.dat)
    km.micro.dat$genre <- gsub('[0-9.]', '', km.micro.dat$genre)
    km.micro.dat$genre <- gsub('.{1}$', '', km.micro.dat$genre)
    km.cluster.dat <- km.micro.dat %>% 
      left_join(km.macro.dat) %>% 
      mutate(micro.g = rownames(km.micro.dat))
    km.cluster.dat
    km.cluster.dat$macro.cluster <- factor(km.cluster.dat$macro.cluster, labels = c("Highbrow", "Country/Folk", "Afro/Pop", "Rock/Pop"))
    km.cluster.dat$micro.cluster <- as.factor(km.cluster.dat$micro.cluster)
    p <- ggplot(data = km.cluster.dat, 
                mapping = aes(y = micro.cluster, x = macro.cluster))
    p <- p + geom_text_repel(aes(label = micro.g, color = micro.cluster), size = 2)
    p <- p + theme_minimal()
    p <- p + theme(legend.position = "none")
    p <- p + labs(x = "", y = "Microgenre Clusters")
    p <- p + scale_y_discrete(limits=rev)
    p <- p + scale_x_discrete(position = "top")
    p

    save_plot(here("Plots", "Link Clust", "macro-v-micro-clust.png"), 
              width = 15, height = 20)
```

# Classic Rock Case Study
```{r Merging and analyzing data}
    taste.demog.dat <- right_join(demog.dat, micro.g.dat) %>% 
        right_join(taste.dat) %>% 
        na.omit()
    res <- mpred.probs("Classic_Rock", taste.demog.dat)
```

```{r Main Classic Rock demographic plot}
    dat <- res$probs$Classic_Rock
    b <- lm(Classic_Rock ~ 1, data = taste.demog.dat)$coefficients
    con.x <- filter(dat, var.type == 1 | var.type == 3 | var.type == 4 | var.type == 5)
    cat.x <- filter(dat, var.type == 2 | var.type == 6 | var.type == 7 | var.type == 8)
    p <- ggplot(data = dat,
                mapping = aes(x = cat.labs, y = prob, 
                              fill = var.type, color = var.type, group = var.type))
    p <- p + geom_hline(yintercept = b, color = "red", linewidth = 0.25)
    p <- p + geom_point(size = 2.5)
    p <- p + geom_line(data = con.x, linewidth = 0.75)
    p <- p + geom_segment(data = cat.x,
                          mapping = aes(y = lo, x = cat.labs, yend = hi, xend = cat.labs), 
                          alpha = 0.2, linewidth = 1.15)
    p <- p + geom_ribbon(data = con.x, 
                         mapping = aes(ymin = lo, ymax = hi), 
                         alpha = 0.15, linetype = 0)
    p <- p + theme_sjplot()
    p <- p + ggtitle("Classic Rock")
    p <- p + theme(axis.title = element_blank(),
                   legend.position = "none",
                   title = element_text(size = 16))
    p <- p + scale_x_discrete(limits=rev)
    p <- p + expand_limits(y = c(0, NA))
    p <- p + scale_color_brewer(palette = "Dark2")
    p <- p + scale_fill_brewer(palette = "Dark2")
    p <- p + coord_flip()
    p
    save_plot(here("Plots", "Link Clust", "classic-rock-macro-demog.png"), 
              width = 15, height = 20)
```

```{r Classic Rock favorites plot}
    classic.rock.favs <- mfav.probs(names(taste.dat[,2:ncol(taste.dat)]),
                                              "Classic_Rock", taste.demog.dat)
    wrap_plots(classic.rock.favs$plots[1:12], ncol = 3)
    save_plot(here("Plots", "Link Clust", "classic-rock-fav.png"), 
                  width = 30, height = 30)
```

```{r Classic Rock Age plot}
    dat <- lapply(res$probs[1:12], transform, sc.prob = scale(prob))
    dat <- bind_rows(dat, .id = "micro.gen") %>% 
        mutate(micro.gen = factor(micro.gen)) %>%
        filter(cat.labs %in% levels(demog.dat$age)) %>% 
        as.tibble() %>% 
        mutate(micro.gen = factor(micro.gen, levels = micro.g.names[1:12]))
    p <- ggplot(data = dat, 
                mapping = aes(y = sc.prob, x = cat.labs, 
                              color = micro.gen, group =micro.gen))
    p <- p + geom_hline(aes(yintercept = 0), linewidth = 1, color = "pink")
    p <- p + geom_line(linewidth = 1.75)
    p <- p + gghighlight(use_direct_label = FALSE,
                         label_key = micro.gen,
                         unhighlighted_params = list(color = "grey90", linewidth = 0.75))
    p <- p + labs(x = "", y = "")
    p <- p + theme_minimal()
    p <- p + facet_wrap(~ micro.gen, nrow = 4)
    p <- p + theme(legend.position = "none",
                   strip.background = element_blank(),
                   strip.text = element_text(size = 14))
    p <- p + coord_flip()
    p
    sjPlot::save_plot(here("Plots", "Link Clust", "classic-rock-age.png"), 
                      width = 25, height = 28)
```

```{r Classic Rock Class plot}
    dat <- lapply(res$probs[1:12], transform, sc.prob = scale(prob))
    dat <- bind_rows(dat, .id = "micro.gen") %>% 
        mutate(micro.gen = factor(micro.gen)) %>%
        filter(cat.labs %in% levels(demog.dat$objclass)) %>% 
        as.tibble() %>% 
        mutate(micro.gen = factor(micro.gen, levels = micro.g.names[1:12]))
    p <- ggplot(data = dat, 
                mapping = aes(y = sc.prob, x = cat.labs, 
                              color = micro.gen, group =micro.gen))
    p <- p + geom_hline(aes(yintercept = 0), linewidth = 1, color = "pink")
    p <- p + geom_line(linewidth = 2)
    p <- p + gghighlight(use_direct_label = FALSE,
                         label_key = micro.gen,
                         unhighlighted_params = list(color = "grey88", linewidth = 0.75))
    p <- p + labs(x = "", y = "")
    p <- p + theme_minimal()
    p <- p + facet_wrap(~ micro.gen, nrow = 4)
    p <- p + theme(legend.position = "none",
                   strip.background = element_blank(),
                   strip.text = element_text(size = 10))
    p <- p + coord_flip()
    p
    sjPlot::save_plot(here("Plots", "Link Clust", "classic-rock-class.png"), 
                      width = 25, height = 15)
```

```{r Classic Rock Education plot}
    dat <- lapply(res$probs[1:12], transform, sc.prob = scale(prob))
    dat <- bind_rows(dat, .id = "micro.gen") %>% 
        mutate(micro.gen = factor(micro.gen)) %>%
        filter(cat.labs %in% levels(demog.dat$educ)) %>% 
        as.tibble() %>% 
        mutate(micro.gen = factor(micro.gen, levels = micro.g.names[1:12]))
    p <- ggplot(data = dat, 
                mapping = aes(y = sc.prob, x = cat.labs, 
                              color = micro.gen, group =micro.gen))
    p <- p + geom_hline(aes(yintercept = 0), linewidth = 1, color = "pink")
    p <- p + geom_line(linewidth = 2)
    p <- p + gghighlight(use_direct_label = FALSE,
                         label_key = micro.gen,
                         unhighlighted_params = list(color = "grey88", linewidth = 0.75))
    p <- p + labs(x = "", y = "")
    p <- p + theme_minimal()
    p <- p + facet_wrap(~ micro.gen, nrow = 4)
    p <- p + theme(legend.position = "none",
                   strip.background = element_blank(),
                   strip.text = element_text(size = 10))
    p <- p + coord_flip()
    p
    sjPlot::save_plot(here("Plots", "Link Clust", "classic-rock-educ.png"), 
                      width = 25, height = 15)
```

```{r Classic Rock Gender plot}
    dat <- lapply(res$probs[1:12], transform, sc.prob = scale(prob))
    dat <- bind_rows(dat, .id = "micro.gen") %>% 
        mutate(micro.gen = factor(micro.gen)) %>%
        filter(cat.labs %in% levels(demog.dat$female)) %>% 
        as.tibble() %>% 
        mutate(micro.gen = factor(micro.gen, levels = micro.g.names[1:12]))
    p <- ggplot(data = dat, 
                mapping = aes(y = sc.prob, x = cat.labs, 
                              color = micro.gen, group =micro.gen))
    p <- p + geom_hline(aes(yintercept = 0), linewidth = 1, color = "pink")
    p <- p + geom_point(size = 3)
    p <- p + gghighlight(use_direct_label = FALSE,
                         label_key = micro.gen,
                         unhighlighted_params = list(color = "grey90", linewidth = 0.75))
    p <- p + labs(x = "", y = "")
    p <- p + theme_minimal()
    p <- p + facet_wrap(~ micro.gen, nrow = 6)
    p <- p + theme(legend.position = "none",
                   strip.background = element_blank(),
                   strip.text = element_text(size = 10))
    p <- p + coord_flip()
    p
    sjPlot::save_plot(here("Plots", "Link Clust", "classic-rock-gender.png"), 
                      width = 20, height = 15)
```

```{r Classic Rock Race plot}
    dat <- lapply(res$probs[1:12], transform, sc.prob = scale(prob))
    dat <- bind_rows(dat, .id = "micro.gen") %>% 
        mutate(micro.gen = factor(micro.gen)) %>%
        filter(cat.labs %in% levels(demog.dat$raceeth)) %>% 
        filter(cat.labs != "Mult./Other") %>% 
        as.tibble() %>% 
        mutate(micro.gen = factor(micro.gen, levels = micro.g.names[1:12]))
    p <- ggplot(data = dat, 
                mapping = aes(y = sc.prob, x = cat.labs, 
                              color = micro.gen, group =micro.gen))
    p <- p + geom_hline(aes(yintercept = 0), linewidth = 1, color = "pink")
    p <- p + geom_point(size = 3)
    p <- p + gghighlight(use_direct_label = FALSE,
                         label_key = micro.gen,
                         unhighlighted_params = list(color = "grey90", linewidth = 0.75))
    p <- p + labs(x = "", y = "")
    p <- p + theme_minimal()
    p <- p + facet_wrap(~ micro.gen, nrow = 6)
    p <- p + theme(legend.position = "none",
                   strip.background = element_blank(),
                   strip.text = element_text(size = 10))
    p <- p + coord_flip()
    p
    sjPlot::save_plot(here("Plots", "Link Clust", "classic-rock-race.png"), 
                      width = 20, height = 18)
```

```{r Classic Rock Region plot}
    dat <- lapply(res$probs[1:12], transform, sc.prob = scale(prob))
    dat <- bind_rows(dat, .id = "micro.gen") %>% 
        mutate(micro.gen = factor(micro.gen)) %>%
        filter(cat.labs %in% levels(demog.dat$region)) %>% 
        as.tibble() %>% 
        mutate(micro.gen = factor(micro.gen, levels = micro.g.names[1:12]))
    p <- ggplot(data = dat, 
                mapping = aes(y = sc.prob, x = cat.labs, 
                              color = micro.gen, group =micro.gen))
    p <- p + geom_hline(aes(yintercept = 0), linewidth = 1, color = "pink")
    p <- p + geom_point(size = 3)
    p <- p + gghighlight(use_direct_label = FALSE,
                         label_key = micro.gen,
                         unhighlighted_params = list(color = "grey90", linewidth = 0.75))
    p <- p + labs(x = "", y = "")
    p <- p + theme_minimal()
    p <- p + facet_wrap(~ micro.gen, nrow = 6)
    p <- p + theme(legend.position = "none",
                   strip.background = element_blank(),
                   strip.text = element_text(size = 10))
    p <- p + coord_flip()
    p
    sjPlot::save_plot(here("Plots", "Link Clust", "classic-rock-region.png"), 
                      width = 20, height = 22)
```

### 2023-08-03 old_Rmds/05_new-micro-analysis.qmd
A bunch of deleted and moved folders and updated toy example

--- 2023-05-16 05_new-micro-analysis.qmd
@@
     pred.res <- mpred.probs("Heavy", dat.pred)
+
 ```
@@
     p <- p + geom_line(data = con.x, linewidth = 0.75)
-    p <- p + geom_segment(data = cat.x,
-                          mapping = aes(y = lo, x = cat.labs, yend = hi, xend = cat.labs), 
-                          alpha = 0.2, linewidth = 1.15)
+
     p <- p + geom_ribbon(data = con.x, 

### 2023-08-03 old_Rmds/07-new-micro-analysis-for-real.Rmd
A bunch of deleted and moved folders and updated toy example

--- 2023-08-02 07-new-micro-analysis-for-real.Rmd
@@
     library(tidyverse)
+    library(webshot)
     load(file= here("dat", "lclust-res.RData"))
@@
 
-```{r Custom Functions}
+```{r Loading Custom Functions}
     source(here("Functions", "micro.genre.dat.R"))
@@
 
-```{r}
-    a <- demog.dat()
-    summary(a)
-    spec <- c("educ", "parcoll", "age.n", "blk", "his", "asn", "gender")
+```{r Microgenre Regression Moldes}
+    spec <- c("educ", "parcoll", "poly(age.n, 2)", 
+              "blk", "his", "asn", "gender")
     labs <- c("Intercept", "Education", "Parents College",
-                            "Age", "Race ID: Black", "Race ID: Hispanic",
+                            "Age", "Age-Squared", 
+                            "Race ID: Black", "Race ID: Hispanic",
                             "Race ID: Asian", "Gender ID: Woman")
 
-    res.latin <- genre.reg.mods("Latin", k = 4, xvars = spec)
-    res.metal <- genre.reg.mods("Heavy_Metal", k = 4, xvars = spec)
+    res.metal <- genre.reg.mods("Heavy_Metal", k = 3, xvars = spec)
+    res.latin <- genre.reg.mods("Latin", k = 3, xvars = spec)
+
+    tab_model(res.metal$mods, 
+              digits = 3, show.ci = FALSE, 
+              auto.label = FALSE, transform = NULL,
+              pred.labels = labs,
+              file = here("Tabs", "reg-tab-metal.html"))
+    webshot(here("Tabs", "reg-tab-metal.html"), here("Tabs", "reg-tab-metal.png"))
 
@@
               file = here("Tabs", "reg-tab-latin.html"))
-    #webshot(here("Tabs", "reg-tab-latin.html"), here("Tabs", "reg-tab-latin.png"))
-    tab_model(res.metal$mods, 
-              digits = 3, show.ci = FALSE, 
-              auto.label = FALSE, transform = NULL,
-              pred.labels = labs,
-              file = here("Tabs", "reg-tab-metal.html"))
-    #webshot(here("Tabs", "reg-tab-metal.html"), here("Tabs", "reg-tab-metal.png"))
+    webshot(here("Tabs", "reg-tab-latin.html"), here("Tabs", "reg-tab-latin.png"))
+
 ```
 
-```{r}
+```{r Microgenre Regression Plots (Age)}
+    age.preds <- pred.probs(x = "age.n", res.metal$mods)
+    p <- plot.preds(d = age.preds, 
+                    xb = c(3, 7, 11),
+                    xlabs = c("Young", "Mid. Aged", "Old"),
+                    ym = -.02,
+                    yl = .2, 
+                    xm = 2, 
+                    xl = 12)
+    save_plot(filename = here("Plots", "Demog", "micro-by-age-metal.png"), 
+              fig = p,
+              height = 25, width = 20)
 
@@
                     xlabs = c("Young", "Mid. Aged", "Old"),
-                    yl = .1, 
+                    ym = -.02,
+                    yl = .16, 
                     xm = 2, 
                     xl = 12)
-    p
+    save_plot(filename = here("Plots", "Demog", "micro-by-age-latin.png"), 
+              fig = p,
+              height = 25, width = 20)
+
 ```
-`
+
+```{r}
+    res <- genre.reg.mods("Heavy_Metal", k = 3, xvars = spec)
+
+    tab_model(res$mods, 
+              digits = 3, show.ci = FALSE, 
+              auto.label = FALSE, transform = NULL,
+              pred.labels = labs,
+              file = here("Tabs", "reg-tab-genre.html"))
+    #webshot(here("Tabs", "reg-tab-latin.html"), here("Tabs", "reg-tab-latin.png"))
+    age.preds <- pred.probs(x = "age.n", res$mods)
+    p <- plot.preds(d = age.preds, 
+                    xb = c(3, 7, 11),
+                    xlabs = c("Young", "Mid. Aged", "Old"),
+                    yl = .2, 
+                    xm = 2, 
+                    xl = 12)
+    save_plot(filename = here("Plots", "Demog", "micro-by-age.png"), 
+              fig = p,
+              height = 25, width = 20)
+```

### 2023-08-03 qmd/01_link-distance-matrix.qmd
A bunch of deleted and moved folders and updated toy example

---
    title: "Discovering Focused Microgenre Communities: Link Clustering"
    author: "Omar Lizardo"
    date: "`r Sys.Date()`"
---

# Setup
```{r setup}
    knitr::opts_chunk$set(include=FALSE, echo = TRUE, warning = FALSE, message = FALSE)
    library(conflicted)
    library(dendextend)
    library(fastcluster)
    library(here)   
    library(haven)
    library(tidyverse)
```

# Data Wrangling
```{r Importing and creating two mode data frame of people by genres}
    taste.dat <- read_dta("C:/Users/Omar Lizardo/Google Drive/MISC DATA SOURCES/SSI-2012/SSI2012.dta")
    taste.dat <- taste.dat %>% 
      dplyr::select("id", ends_with(c("lis", "like")), -starts_with("none")) %>% 
      dplyr::select(c(1:41)) %>% 
      na.omit() %>% 
      mutate(Classical = classicallike * classicallis,
             Opera = operalike * operalis,
             Jazz = jazzlike * jazzlis,
             Broadway = bwaystlike * bwaystlis,
             Easy = moodezlike * moodezlis, 
             Bigband = bbandlike * bbandlis,
             Classic_Rock = croldlike * croldlis,
             Country = countrylike * countrylis,
             Bluegrass = blueglike * blueglis,
             Folk = folklike * folklis,
             Gospel = hymgoslike * hymgoslis,
             Salsa = latlpsallike * latspsallis,
             Rap_Hip_Hop = raphiphoplike * raphiphoplis,
             Blues_RandB = blurblike * blurblis,
             Reggae = reggaelike * reggaelis,
             Pop = toppoplike * toppoplis,
             Contemp_Rock = controcklike * controcklis,
             Indie_Alt = indaltlike * indaltlis,
             Dance_Club = danclublike * danclublis,
             Metal = hvymtllike * hvymtllis
             ) %>%  #people are linked to genres that the both like and listen to
      dplyr::select(id, Classical:Metal)
```

# Link Clustering
```{r Creating link by link distance matrix and saving results}
    source(here("Functions", "link.dist.R"))
    ldist.res <- link.dist(x = as.matrix(taste.dat[, 2:ncol(taste.dat)]), 
                           id = taste.dat$id)
    b <- ls()[! ls() %in% c("taste.dat", "ldist.res")]
    rm(list = b)
    save.image(file= here("dat", "lclust-res.RData"))
```

### 2023-08-03 qmd/02_toy-ex.qmd
A bunch of deleted and moved folders and updated toy example

---
title: "Discovering Focused Microgenre Communities: Toy example"
author: "Omar Lizardo"
date: "`r Sys.Date()`"
---

# Setup
```{r setup}
    knitr::opts_chunk$set(include=FALSE, echo = TRUE, warning = FALSE, message = FALSE)
    library("conflicted")
    library("factoextra")
    library("here")
    library("ggplot2")
    library("sjPlot")
    source(here("Functions", "link.dist.R"))
```

# Link Clustering (Toy Example)
```{r Link Clustering toy example}
    x <- c(0, 1, 1, 0, 
           0, 0, 0, 1, 
           1, 1, 1, 1, 
           1, 0, 0, 1, 
           0, 0, 1, 1)
    x <- matrix(x, nrow = 5, ncol = 4,  byrow = TRUE) #toy data
    ldist.res <- link.dist(x = x, id = c(1:5)) #link distance matrix
    hc.res <- hclust(ldist.res$dist, method = "ward.D2") #link clustering
```

```{r Plotting toy example dendrogram}
    hc.res$labels <- c("P1-G2", "P1-G3", "P2-G4", "P3-G1", "P3-G2", "P3-G3", "P3-G4", "P4-G1", "P4-G4", "P5-G3", "P5-G4")
    p <- fviz_dend(hc.res, k = 4, k_colors = "uchicago", show_labels = TRUE, cex = 1.5, lwd = 2) 
    p <- p + geom_hline(yintercept = 0.75, 
                        linetype = "dashed", 
                        color = "red", 
                        size = 1.2)
    p <- p + labs(y = "", title = "") 
    p <- p + theme(axis.line.y = element_blank(), axis.text.y = element_blank())
    p
    save_plot(here("Plots", "Toy", "link-clust-toy5.png"), 
              width = 40, height = 25)
```

### 2023-08-03 qmd/04_microgenre-analysis.qmd
A bunch of deleted and moved folders and updated toy example

--- 2023-08-03 old_Rmds/07-new-micro-analysis-for-real.Rmd
@@
 ```{r Microgenre Regression Moldes}
-    spec <- c("educ", "parcoll", "poly(age.n, 2)", 
+    spec <- c("poly(educ, 2)", "parcoll", "poly(age.n, 2)", 
               "blk", "his", "asn", "gender")
@@
 
-    res.metal <- genre.reg.mods("Heavy_Metal", k = 3, xvars = spec)
-    res.latin <- genre.reg.mods("Latin", k = 3, xvars = spec)
-
-    tab_model(res.metal$mods, 
-              digits = 3, show.ci = FALSE, 
-              auto.label = FALSE, transform = NULL,
-              pred.labels = labs,
-              file = here("Tabs", "reg-tab-metal.html"))
-    webshot(here("Tabs", "reg-tab-metal.html"), here("Tabs", "reg-tab-metal.png"))
+    res.latin <- genre.reg.mods("Latin", k = 4, xvars = spec)
+    res.metal <- genre.reg.mods("Heavy_Metal", k = 4, xvars = spec)
 
@@
 
+    tab_model(res.metal$mods, 
+              digits = 3, show.ci = FALSE, 
+              auto.label = FALSE, transform = NULL,
+              pred.labels = labs,
+              file = here("Tabs", "reg-tab-metal.html"))
+    webshot(here("Tabs", "reg-tab-metal.html"), here("Tabs", "reg-tab-metal.png"))
 ```
@@
 ```{r Microgenre Regression Plots (Age)}
-    age.preds <- pred.probs(x = "age.n", res.metal$mods)
-    p <- plot.preds(d = age.preds, 
-                    xb = c(3, 7, 11),
-                    xlabs = c("Young", "Mid. Aged", "Old"),
-                    ym = -.02,
-                    yl = .2, 
-                    xm = 2, 
-                    xl = 12)
-    save_plot(filename = here("Plots", "Demog", "micro-by-age-metal.png"), 
-              fig = p,
-              height = 25, width = 20)
-
     age.preds <- pred.probs(x = "age.n", res.latin$mods)
@@
                     xlabs = c("Young", "Mid. Aged", "Old"),
-                    ym = -.02,
-                    yl = .16, 
+                    yl = .1, 
                     xm = 2, 
@@
 
-```
-
-```{r}
-    res <- genre.reg.mods("Heavy_Metal", k = 3, xvars = spec)
-
-    tab_model(res$mods, 
-              digits = 3, show.ci = FALSE, 
-              auto.label = FALSE, transform = NULL,
-              pred.labels = labs,
-              file = here("Tabs", "reg-tab-genre.html"))
-    #webshot(here("Tabs", "reg-tab-latin.html"), here("Tabs", "reg-tab-latin.png"))
-    age.preds <- pred.probs(x = "age.n", res$mods)
+    age.preds <- pred.probs(x = "age.n", res.metal$mods)
     p <- plot.preds(d = age.preds, 
@@
                     xlabs = c("Young", "Mid. Aged", "Old"),
-                    yl = .2, 
+                    yl = .1, 
                     xm = 2, 
                     xl = 12)
-    save_plot(filename = here("Plots", "Demog", "micro-by-age.png"), 
+    save_plot(filename = here("Plots", "Demog", "micro-by-age-metal.png"), 
               fig = p,
@@
 ```
+`

### 2023-08-03 Functions/old-dend.stuff.R

@@ -1,0 +1,37 @@
+```{r Creating objects for analysis}
+dend.macro <- cut(lclust.dend, h = 8) #cutting at macrogenre level
+a <- data.frame(g.size = sapply(dend.macro$lower, nleaves)) #macrogenres as ordered in dendrogram results
+b <- data.frame(g.size = colSums(taste.mat), g.names = names(colSums(taste.mat))) #original macrogenre sizes
+c <- right_join(a, b) #joining data frames by macrogenre sizes to get macrogenre labels ordered by dendrogram results
+names(dend.macro$lower) <- c$g.names #naming macrogenre dendrogram list
+n.micro <- sapply(dend.macro$lower, function(x) {length(table(cutree(x, h = 3)))}) #number of microgenres per macrogenre
+v <- sapply(sapply(n.micro, function(x) {1:x}), as.numeric)
+micro.g.names <- paste(c$g.names[1], v[[1]], sep = "_")
+for (i in 2:20) {
+   micro.g.names <- c(micro.g.names, paste(c$g.names[i], v[[i]], sep = "_"))
+}
+bin.char <- function(x) { 
+   if_else(is.na(x), 0, 1) #function to binarize data
+}
+dend.micro <- cut(lclust.dend, h = 3) #cutting at microgenre level
+edge.labs <- data.frame(id = ldist.res$edge.list[, 1],
+                        macro.g = ldist.res$edge.list[, 2], 
+                        edge.num = 1:nrow(ldist.res$edge.list)) #grabbing people and genre id labels
+micro.g.clust <- lapply(dend.micro$lower, labels) %>%
+   lapply(data.frame) %>% 
+   bind_rows() #transforming clustering cut results into data frame
+names(micro.g.clust) <- "edge.num" #adding column label
+micro.g.long <- data.frame(micro.g = rep(1:102, sapply(dend.micro$lower, nleaves)))
+micro.g.dat <- bind_cols(micro.g.clust, micro.g.long)
+micro.g.dat <- right_join(micro.g.dat, edge.labs) %>%
+   mutate(micro.g.f = factor(micro.g, labels = micro.g.names),
+          macro.g.f = factor(macro.g, labels = names(colSums(taste.mat))),
+          micro.g.c = as.character(micro.g.f),
+          macro.g.c = as.character(macro.g.f)) %>% 
+   pivot_wider(id_cols = "id",
+               names_from = "micro.g.c",
[…]

### 2023-08-03 old-dend.stuff.R

@@ -1,37 +1,0 @@
-```{r Creating objects for analysis}
-dend.macro <- cut(lclust.dend, h = 8) #cutting at macrogenre level
-a <- data.frame(g.size = sapply(dend.macro$lower, nleaves)) #macrogenres as ordered in dendrogram results
-b <- data.frame(g.size = colSums(taste.mat), g.names = names(colSums(taste.mat))) #original macrogenre sizes
-c <- right_join(a, b) #joining data frames by macrogenre sizes to get macrogenre labels ordered by dendrogram results
-names(dend.macro$lower) <- c$g.names #naming macrogenre dendrogram list
-n.micro <- sapply(dend.macro$lower, function(x) {length(table(cutree(x, h = 3)))}) #number of microgenres per macrogenre
-v <- sapply(sapply(n.micro, function(x) {1:x}), as.numeric)
-micro.g.names <- paste(c$g.names[1], v[[1]], sep = "_")
-for (i in 2:20) {
-   micro.g.names <- c(micro.g.names, paste(c$g.names[i], v[[i]], sep = "_"))
-}
-bin.char <- function(x) { 
-   if_else(is.na(x), 0, 1) #function to binarize data
-}
-dend.micro <- cut(lclust.dend, h = 3) #cutting at microgenre level
-edge.labs <- data.frame(id = ldist.res$edge.list[, 1],
-                        macro.g = ldist.res$edge.list[, 2], 
-                        edge.num = 1:nrow(ldist.res$edge.list)) #grabbing people and genre id labels
-micro.g.clust <- lapply(dend.micro$lower, labels) %>%
-   lapply(data.frame) %>% 
-   bind_rows() #transforming clustering cut results into data frame
-names(micro.g.clust) <- "edge.num" #adding column label
-micro.g.long <- data.frame(micro.g = rep(1:102, sapply(dend.micro$lower, nleaves)))
-micro.g.dat <- bind_cols(micro.g.clust, micro.g.long)
-micro.g.dat <- right_join(micro.g.dat, edge.labs) %>%
-   mutate(micro.g.f = factor(micro.g, labels = micro.g.names),
-          macro.g.f = factor(macro.g, labels = names(colSums(taste.mat))),
-          micro.g.c = as.character(micro.g.f),
-          macro.g.c = as.character(macro.g.f)) %>% 
-   pivot_wider(id_cols = "id",
-               names_from = "micro.g.c",
[…]

### 2023-08-03 main.tex
Updates from Overleaf

@@
 
-\subsection{Heavy Metal}
+\subsubsection{Heavy Metal}
 Heavy Metal is one of the most storied macrogenre labels in the sociology of taste, as featured in the title of Bethany Bryson's \citeyearpar{bryson96} now classic paper.
@@
 
-Tampubolon's work indicates that just because Metal's audience is composed of low-education people does not mean that the rest of the less-educated population loves it; in fact, they hate it passionately.
+Tampubolon's work indicates that just because Metal's audience is composed of low-education people does not mean that the rest of the less-educated population loves it; they hate it passionately.
 Tampubolon's analysis of ``Like'' responses also shows that Metal, rather than being exclusively preferred by a univorous group of ``Metalheads'' (who only prefer metal and dislike everything else), also makes it into the taste profile of one of two omnivorous groups uncovered in his analysis.
@@
 
-\subsubsection{Microgenre Analysis}
+\subsubsection{Metal Microgenre Analysis}
 So, will the real heavy metal please stand up?
@@
 
-\subsection{Salsa}
-``it is plausible that increasing appreciation among high-status groups for a genre conventionally defined as ‘popular’ or ‘lowbrow’, will go hand in hand with its symbolic upgrading.
-And when a genre expands and spreads in terms of production, distribution and reception, it is likely to differentiate into distinct styles or subgenres.
-Under these conditions, it is to be expected that differential appreciations for different styles and forms within a given genre will develop, which may end up in a more or less clear hierarchy within this genre'' \citeyearpar[][62]{Bachmayer2014-pk}
+\subsubsection{Salsa}
+The Salsa music genre has not had as storied a career in the sociology of taste as Metal.
+In fact, it has been under-researched and, for the most part, ignored.
+I include it in the following analysis due to a shining exception to this pattern, represented in a high-quality recent study by \citep{Bachmayer2014-pk} which strongly suggests internal microgenre differentiation within this broad macrogenre label relevant to the reception and consumption side.
+These differentiations are keyed to hierarchical distinctions across Salsa microgenres based on social status and the concomitant internalization of class-based aesthetic dispositions \citep{lizardo2012reconceptualizing}.
 
-``Taste in salsa music shows a strong internal, hierarchical order between ‘artistic’ versus ‘popular’ styles that is not only acknowledged and defined as such by experts and professionals within the field, but also structures the taste patterns of different social classes'' \citeyearpar[][62]{Bachmayer2014-pk}
+Bachmayer et al.
+elicited a list of performers by asking experts to freely name performers and bands and then classify the music typical of the named acts into an ordinal rank based on their judgments of aesthetic quality (``superior,'', ``middlebrow,'' ``inferior'').
+They then selected the eight artists who were mentioned by at least three of the four expert informants and who displayed a high degree of concordance across experts in terms of their aesthetic rank.
+The eight compositions the experts judged to be typical of each artist's output were selected for guided interviews with forty first-generation Latinx immigrants in the Netherlands and Switzerland (there were no relevant cross-country differences).
+The most highly regarded expert pieces belonged to the sub-genre ``classic salsa,''---essentially early salsa performers that set the standard in the 1960s, 1970s, and 1980s---the middlebrow pieces were mainly variants of ``romantic salsa.'' The less aesthetically worthy pieces generally belonged to more recent styles of ``pop salsa styles.'' Note that this establishes a strict alignment between microgenre aesthetic standing and the historical sequencing of microgenre emergence within the salsa musicworld.
+We should thus expect this to be reflected in the generational location of each microgenre audience.
 
@@
     \caption{}
-    \label{tab:reg-metal}
+    \label{tab:reg-latin}
 \end{figure}
+
+What did \citet{Bachmayer2014-pk} find?
+The short answer is that they found a microcosm of a Bourdieusian world---with some wrinkles.
+More educated respondents gravitated towards classic salsa and explicitly denigrated audiences that went for more popular styles---enacting a version of Ien Ang's \citeyearpar{ang2000dallas} ``ideology of mass culture'' in this field.
+High status respondents emphasized compositional and thematic complexity over ``fun'' aspects like rhythm and ``danceability,'' elements crucial in working-class Latinx immigrants' explanations for why they gravitated towards more romantic and pop styles (finding classic salsa sleepy and boring).
+Importantly, ``expert consumers'' (people who worked in the musical field in some capacity) demonstrated the same aestheticized appreciation for classic salsa and denigration of popular styles regardless of their class background.
+\citep[][62]{Bachmayer2014-pk} conclude that ``[t]aste in salsa music shows a strong internal, hierarchical order between `artistic' versus `popular' styles that \ldots structures the taste patterns of different social classes.''
+
+This means that, at a minimum, we should expect the Salsa microgenres elicited by the link clustering procedure to reflect this hierarchical divide, with a microgenre more likely to be preferred by high-status respondents, particularly the higher-educated---the status marker that was most crucial in Bachmayer et al.'s study.
+
+\subsubsection{Salsa Microgenre Analysis}
+Table~\ref{tab:reg-latin} shows the result of a regression analysis analogous to that I specified for the Metal microgenres.
+The first column shows a model predicting choosing the ``Latin/Spanish/Salsa" macrogenre label using the usual socio-demographic covariates.
+The next three columns show the predictors of choosing each microgenre variation extracted from cutting the macrogenre label branch of the dendrogram at the required height.
+Looking at the first column, we would have concluded that choosing Salsa is not predicted by either respondent's ($p = 0.26$) or parent's ($0.17$) education, suggesting that taste for this genre is orthogonal to cultural capital and status.
+Instead, Salsa is mainly a genre preferred by young respondents (negative linear effect of age) who identify as Hispanic (no surprise there) and as women ($p < 0.05$).
 
@@
 
+The microgenre analysis tells a different story.
+Looking at the third column of the table, predicting choice for the second of the induced microgenres, we find that, indeed, there is a micro-variation that is statistically more likely to be preferred by people of high education whose parents are also more likely to be highly educated ($p < 0.05$).
+Moreover, the age effect on the choice of this microgenre is \textit{reversed} compared to baseline expectations from the macrogenre regression.
+This microgenre is more likely to be preferred by older respondents (see Figure~\ref{fig:age-salsa}).
+In this way, this microgenre contrasts strongly with the first one extracted by the link clustering procedure, which is overwhelmingly more likely to be preferred by younger respondents.
+These results point to two conclusions: First, there is hierarchical differentiation among microgenres extracted from the ``Latin/Spanish/Salsa'' macrogenre, with one microgenre standing out by its exclusive appeal to high-cultural-capital respondents.
+Second, this hierarchical differentiation is keyed to age, consistent with the idea that the most prestigious Salsa microgenre is also the ``oldest'' and most traditional \citep{Bachmayer2014-pk}.
+
 \section{Discussion}
@@
 However, we also noted that survey data are as good as the labels chosen to collect the data.
-A resurgent line of critics questions whether the labels that appear in our most venerable survey-based studies are true ``genres'' in the sociological (or even stylistic) sense \citep{lena2015relational, vlegels2015music}.
+A resurgent line of critics question whether the labels that appear in our most venerable survey-based studies are true ``genres'' in the sociological (or even stylistic) sense \citep{lena2015relational, vlegels2015music}.
 The labels are broad, likely to be interpreted by people in heterogeneous ways, and thus hide as much as they reveal.
-I noted recent attempts to just drop the idea of vague macrogenre labels and either study actual sociological genres on the ground (thus partially abandoning studies of audience segmentation or at least radically reconfigure them) or ``dropping the label'' \citep{sonnett2016ambivalence} by querying people about more focused objects of taste (e.g., performers within genres).
+I noted recent attempts to drop the idea of vague macrogenre labels and either study actual sociological genres on the ground (thus partially abandoning studies of audience segmentation or at least radically reconfigure them) or ``dropping the label'' \citep{sonnett2016ambivalence} by querying people about more focused objects of taste (e.g., performers within genres).
 These are all important and good developments, but we also noted that they may throw away a good thing.
-Upping the relationality by exploiting hidden patterns in the same old vague macrogenre-based data collected before can reveal focused microgenres.
+Upping the relationality by exploiting hidden patterns in the same old vague macrogenre data collected before can reveal focused microgenres.
 
@@
 Our analysis contrasted the application of the usual techniques to the same data, conceived in the usual ``macro" way, and \textit{after} upping the relationality and discovering the microgenres hidden within.
-It is clear that focusing on microgenres reveals variation and patterns of cultural choice (as well as audience segmentation) that we would not have noticed using the standard approach (in this, the critics are right).
+Focusing on microgenres reveals variations and patterns of cultural choice (as well as audience segmentation) that we would not have noticed using the standard approach (in this, the critics are right).
 Still, we could do this without dropping the label or querying people about hundreds of micro-styles (most of which they'd be unfamiliar with).

### 2023-08-03 main.tex

@@
      \begin{subfigure}[b]{0.6\textwidth}
-        \includegraphics[width=1.0\textwidth]{Figs/Toy/link-clust-toy1.png}
+        \includegraphics[width=1.0\textwidth]{Toy/link-clust-toy1.png}
         \caption{Two person-genre edges sharing the same genre.}
@@
      \begin{subfigure}[b]{0.3\textwidth}
-        \includegraphics[width=1.0\textwidth]{Figs/Toy/link-clust-toy2.png}
+        \includegraphics[width=1.0\textwidth]{Toy/link-clust-toy2.png}
         \caption{Similarity between person-genre edges depends on the other genres people are linked to.}
@@
     \end{subfigure}
-     \begin{subfigure}[b]{0.45\textwidth}
-        \includegraphics[width=1.0\textwidth]{Figs/Toy/link-clust-toy3.png}
+     \begin{subfigure}[b]{0.5\textwidth}
+        \includegraphics[width=1.0\textwidth]{Toy/toy-sim.png}
         \caption{Edge similarity matrix from toy example.}
-        \label{fig:link-toy3}
+        \label{fig:toy-sim}
     \end{subfigure}
-     \begin{subfigure}[b]{0.45\textwidth}
-        \includegraphics[width=1.0\textwidth]{Figs/Toy/link-clust-toy4.png}
+     \begin{subfigure}[b]{0.5\textwidth}
+        \includegraphics[width=1.0\textwidth]{Toy/toy-dis.png}
         \caption{Edge distance matrix from toy example.}
-        \label{fig:link-toy4}
+        \label{fig:toy-dis}
     \end{subfigure}
      \begin{subfigure}[b]{0.6\textwidth}
-        \includegraphics[width=1.0\textwidth]{Figs/Toy/link-clust-toy5.png}
+        \includegraphics[width=1.0\textwidth]{Toy/link-clust-toy.png}
         \caption{Dendrogram from Ward clustering of toy example edge distance matrix cut at four clusters.}
-        \label{fig:link-toy5}
+        \label{fig:link-toy}
     \end{subfigure}
     \caption{Toy illustration of how the link clustering approach works.}
-    \label{fig:link-toy}
+    \label{fig:link-toy-ex}
  \end{figure}
@@
         \centering
-        \includegraphics[width=1.0\textwidth]{Figs/Dend/all-branches-macro.png}
+        \includegraphics[width=1.0\textwidth]{Plots/Dend/all-branches-macro.png}
         \caption{c = 8, k = 20}
@@
         \centering
-        \includegraphics[width=1.0\textwidth]{Figs/Dend/all-branches-macro-labels.png}
+        \includegraphics[width=1.0\textwidth]{Plots/Dend/all-branches-macro-labels.png}
         \caption{c = 8, k = 20}
@@
     \end{subfigure} 
-     \begin{subfigure}[b]{0.5\textwidth}
-        \centering
-        \includegraphics[width=1.0\textwidth]{Figs/Dend/all-branches-micro.png}
-        \caption{c = 3, k = 102}
-        \label{fig:dend-micro}
-    \end{subfigure} 
-     \begin{subfigure}[b]{0.5\textwidth}
-        \centering
-        \includegraphics[width=1.0\textwidth]{Figs/Dend/all-branches-micro-labels.png}
-        \caption{c = 3, k = 102}
-        \label{fig:dend-micro-labels}
-    \end{subfigure}
      \begin{subfigure}[b]{0.32\textwidth}
         \centering
-        \includegraphics[width=1.0\textwidth]{Figs/Dend/classic-rock-branches.png}
+        \includegraphics[width=1.0\textwidth]{Plots/Dend/classic-rock-branches.png}
         \caption{c = 3, k = 12}
@@
         \centering
-        \includegraphics[width=1.0\textwidth]{Figs/Dend/blues-branches.png}
+        \includegraphics[width=1.0\textwidth]{Plots/Dend/blues-branches.png}
         \caption{c = 3, k = 5}
@@
         \centering
-        \includegraphics[width=1.0\textwidth]{Figs/Dend/opera-branches.png}
+        \includegraphics[width=1.0\textwidth]{Plots/Dend/opera-branches.png}
         \caption{c = 3, k = 2}

### 2023-08-04 qmd/02_toy-ex.qmd
Updated everything

@@
     knitr::opts_chunk$set(include=FALSE, echo = TRUE, warning = FALSE, message = FALSE)
-    library("conflicted")
-    library("factoextra")
-    library("here")
-    library("ggplot2")
-    library("sjPlot")
+    library(conflicted)
+    library(factoextra)
+    library(here)
+    library(kableExtra)
+    library(ggplot2)
+    library(sjPlot)
+    library(webshot)
     source(here("Functions", "link.dist.R"))
@@
 # Link Clustering (Toy Example)
-```{r Link Clustering toy example}
+```{r Link Clustering Toy Example}
     x <- c(0, 1, 1, 0, 
@@
 
+```{r Creating Similarity and Distance Matrices}
+    e.names <- c("P1-G2", "P1-G3", "P2-G4", "P3-G1", 
+                 "P3-G2", "P3-G3", "P3-G4", "P4-G1", 
+                 "P4-G4", "P5-G3", "P5-G4")
+
+    a <- round(ldist.res$sim, 2)
+    b <- round(as.matrix(ldist.res$dist), 2)
+    rownames(a) <- e.names
+    colnames(a) <- e.names
+    rownames(b) <- e.names
+    colnames(b) <- e.names
+
+    kbl(a, format = "html", padding = 2, align = "c") %>% 
+        column_spec(1, bold = TRUE) %>% 
+        save_kable(here("Toy", "toy-sim.png"))
+    #webshot(here("Toy", "toy-sim.html"), here("Toy", "toy-sim.png"))
+
+    kbl(b, format = "html", padding = 2, align = "c") %>% 
+        column_spec(1, bold = TRUE) %>% 
+        save_kable(here("Toy", "toy-dis.png"))
+    #webshot(here("Toy", "toy-dis.html"), here("Toy", "toy-dis.png"))
+```
+
 ```{r Plotting toy example dendrogram}
-    hc.res$labels <- c("P1-G2", "P1-G3", "P2-G4", "P3-G1", "P3-G2", "P3-G3", "P3-G4", "P4-G1", "P4-G4", "P5-G3", "P5-G4")
+    hc.res$labels <- e.names
     p <- fviz_dend(hc.res, k = 4, k_colors = "uchicago", show_labels = TRUE, cex = 1.5, lwd = 2) 
@@
     p
-    save_plot(here("Plots", "Toy", "link-clust-toy5.png"), 
+    save_plot(here("Toy", "link-clust-toy.png"), 
               width = 40, height = 25)

### 2023-08-04 qmd/04_microgenre-analysis.qmd
Updated everything

--- 2023-08-03 old_Rmds/07-new-micro-analysis-for-real.Rmd
@@
 
-```{r Importing and creating two mode data frame of people by genres}
-    taste.dat <- read_dta("C:/Users/Omar Lizardo/Google Drive/MISC DATA SOURCES/SSI-2012/SSI2012.dta")
-    taste.dat <- taste.dat %>% 
-      dplyr::select("id", ends_with(c("lis", "like")), -starts_with("none")) %>% 
-      dplyr::select(c(1:41)) %>% 
-      na.omit() %>% 
-      mutate(Classical = classicallike * classicallis,
-             Opera = operalike * operalis,
-             Jazz = jazzlike * jazzlis,
-             Broadway = bwaystlike * bwaystlis,
-             Easy = moodezlike * moodezlis, 
-             Bigband = bbandlike * bbandlis,
-             Classic_Rock = croldlike * croldlis,
-             Country = countrylike * countrylis,
-             Bluegrass = blueglike * blueglis,
-             Folk = folklike * folklis,
-             Gospel = hymgoslike * hymgoslis,
-             Latin = latlpsallike * latspsallis,
-             Rap_Hip_Hop = raphiphoplike * raphiphoplis,
-             Blues_RandB = blurblike * blurblis,
-             Reggae = reggaelike * reggaelis,
-             Pop = toppoplike * toppoplis,
-             Contemp_Rock = controcklike * controcklis,
-             Indie_Alt = indaltlike * indaltlis,
-             Dance_Club = danclublike * danclublis,
-             Heavy_Metal = hvymtllike * hvymtllis
-             ) %>%  #people are linked to genres that the both like and listen to
-      dplyr::select(id, Classical:Heavy_Metal)
-```
-
-```{r Performing Link Clustering}
-    lclust.res <- hclust(ldist.res$dist, method = "ward.D2") #clustering of link by link distance matrixco
-    lclust.dend <- as.dendrogram(lclust.res) #transforming link clustering into dendrogram
-```
-
 ```{r Loading Custom Functions}
@@
 
-```{r Microgenre Regression Moldes}
+```{r Performing Link Clustering}
+    lclust.res <- hclust(ldist.res$dist, method = "ward.D2") #clustering of link by link distance matrix
+    lclust.dend <- as.dendrogram(lclust.res) #transforming link clustering into dendrogram
+```
+
+```{r Microgenre Regression Models}
     spec <- c("educ", "parcoll", "poly(age.n, 2)", 
@@
 
-    res.metal <- genre.reg.mods("Heavy_Metal", k = 3, xvars = spec)
-    res.latin <- genre.reg.mods("Latin", k = 3, xvars = spec)
+    res.metal <- genre.reg.mods("Metal", k = 3, xvars = spec)
+    res.salsa <- genre.reg.mods("Salsa", k = 3, xvars = spec)
 
@@
 
-    tab_model(res.latin$mods, 
+    tab_model(res.salsa$mods, 
               digits = 3, show.ci = FALSE, 
@@
               pred.labels = labs,
-              file = here("Tabs", "reg-tab-latin.html"))
-    webshot(here("Tabs", "reg-tab-latin.html"), here("Tabs", "reg-tab-latin.png"))
+              file = here("Tabs", "reg-tab-salsa.html"))
+    webshot(here("Tabs", "reg-tab-salsa.html"), here("Tabs", "reg-tab-salsa.png"))
 
@@
                     xlabs = c("Young", "Mid. Aged", "Old"),
-                    ym = -.02,
+                    ym = -0.02,
                     yl = .2, 
@@
                     xl = 12)
-    save_plot(filename = here("Plots", "Demog", "micro-by-age-metal.png"), 
+    save_plot(filename = here("Plots", "Micro", "micro-by-age-metal.png"), 
               fig = p,
@@
 
-    age.preds <- pred.probs(x = "age.n", res.latin$mods)
+    age.preds <- pred.probs(x = "age.n", res.salsa$mods)
     p <- plot.preds(d = age.preds, 
@@
                     xlabs = c("Young", "Mid. Aged", "Old"),
-                    ym = -.02,
+                    ym = -0.02,
                     yl = .16, 
@@
                     xl = 12)
-    save_plot(filename = here("Plots", "Demog", "micro-by-age-latin.png"), 
-              fig = p,
-              height = 25, width = 20)
-
-```
-
-```{r}
-    res <- genre.reg.mods("Heavy_Metal", k = 3, xvars = spec)
-
-    tab_model(res$mods, 
-              digits = 3, show.ci = FALSE, 
-              auto.label = FALSE, transform = NULL,
-              pred.labels = labs,
-              file = here("Tabs", "reg-tab-genre.html"))
-    #webshot(here("Tabs", "reg-tab-latin.html"), here("Tabs", "reg-tab-latin.png"))
-    age.preds <- pred.probs(x = "age.n", res$mods)
-    p <- plot.preds(d = age.preds, 
-                    xb = c(3, 7, 11),
-                    xlabs = c("Young", "Mid. Aged", "Old"),
-                    yl = .2, 
-                    xm = 2, 
-                    xl = 12)
-    save_plot(filename = here("Plots", "Demog", "micro-by-age.png"), 
+    save_plot(filename = here("Plots", "Micro", "micro-by-age-salsa.png"), 
               fig = p,

### 2023-08-04 main.tex

@@
     \end{subfigure}
-     \begin{subfigure}[b]{0.5\textwidth}
+     \begin{subfigure}[b]{0.45\textwidth}
         \includegraphics[width=1.0\textwidth]{Toy/toy-sim.png}
@@
     \end{subfigure}
-     \begin{subfigure}[b]{0.5\textwidth}
+     \begin{subfigure}[b]{0.45\textwidth}
         \includegraphics[width=1.0\textwidth]{Toy/toy-dis.png}
@@
 \begin{figure}[ht!]
+     \begin{subfigure}[b]{1.0\textwidth}
         \centering    
-    \includegraphics[width=1.5\textwidth]{Tabs/reg-tab-metal.png}
+        \includegraphics[width=1.0\textwidth]{Tabs/reg-tab-metal.png}
         \caption{}
         \label{tab:reg-metal}
+    \end{subfigure} \\
+     \begin{subfigure}[b]{1.0\textwidth}
+        \centering    
+        \includegraphics[width=1.0\textwidth]{Tabs/reg-tab-latin.png}
+        \caption{}
+        \label{tab:reg-latin}
+    \end{subfigure}
 \end{figure}
@@
 \begin{figure}[ht!]
-    \centering    \includegraphics[width=1.0\textwidth]{Plots/Demog/micro-by-age-metal.png}
+     \begin{subfigure}[b]{0.45\textwidth}
+        \centering    
+        \includegraphics[width=1.0\textwidth]{Plots/Micro/micro-by-age-metal.png}
         \caption{}
         \label{fig:age-metal}
+    \end{subfigure}
+     \begin{subfigure}[b]{0.45\textwidth}
+        \centering    
+        \includegraphics[width=1.0\textwidth]{Plots/Micro/micro-by-age-latin.png}
+        \caption{}
+        \label{fig:age-latin}
+    \end{subfigure}
 \end{figure}
@@
 
-\begin{figure}[ht!]
-    \centering    
-    \includegraphics[width=1.5\textwidth]{Tabs/reg-tab-latin.png}
-    \caption{}
-    \label{tab:reg-latin}
-\end{figure}
-
 What did \citet{Bachmayer2014-pk} find?
@@
 Instead, Salsa is mainly a genre preferred by young respondents (negative linear effect of age) who identify as Hispanic (no surprise there) and as women ($p < 0.05$).
-
-\begin{figure}[ht!]
-    \centering    \includegraphics[width=1.0\textwidth]{Plots/Demog/micro-by-age-latin.png}
-    \caption{}
-    \label{fig:age-salsa}
-\end{figure}
 

### 2023-08-04 Functions/plot.preds.R
Updated plots

@@ -12,7 +12,7 @@ plot.preds <- function(d, xb, xlabs, ym = 0, yl, r.alpha = .1, p.size = 3, xm, x
    p <- p + theme(legend.position = "top",
                   legend.title = element_blank(),
                   axis.title = element_blank(),
-                  axis.text = element_text(size = 12),
-                  legend.text = element_text(size = 12))
+                  axis.text = element_text(size = 16),
+                  legend.text = element_text(size = 14))
    return(p)
    }

### 2023-08-04 main.tex
Updates from Overleaf

@@
 For instance, Goldberg's \citeyearpar{goldberg2011mapping} {\em Relational Class Analysis} (RCA) ``classifies the people'' (in the terms developed below when reviewing standard data-analytic approaches in the sociology of taste) included a survey by partitioning a person-by-person matrix built from higher order similarities (sums of differences of differences) between each pair of person's corresponding response vector coding their stances (e.g., like, dislike, neutral) toward a set of cultural objects (e.g., genres, attitude items).
+
 Boutyline's 
@@
 Thus, RCA and CCA are bound to compute relationality and correlation distances within people but have to rely on vague macrogenre labels.
+
 The resulting evaluation logics are thus interpreted using a macrogenre lens---e.g., ``Anything but Heavy Metal'' or ``Highbrow versus Lowbrow" \citep[e.g.,][]{goldberg2011mapping, willekens2022cultural}.
@@
 
+\section{Analytic Appproach}
 \subsection{Data to be Used in the Study}
@@
 population ($n = 2,263$).
+
 Like GSS 1993, SSI 2012 included items assessing respondents’ likes and dislikes (as well as a middle category of ``mixed feelings'') for 20 categories of musical style: classical/ symphony and chamber, opera/operetta, jazz, Broadway musicals/show tunes, mood/easy listening, big band/swing, classic rock/oldies, country, bluegrass, folk, hymns/gospel, Latin/Spanish/salsa, rap/hip hop, blues/R\&B, reggae, top 40/pop music, contemporary rock, indie/alternative rock, dance/club/electronic, and hard rock/heavy metal.
@@
 As noted at the outset, this requires that we stop looking at the usual survey data that forms the bulk of empirical material in the quantitative study of taste as ``survey data'' (e.g., data collected on the characteristics of individuals in the form of ``variables'').
-This is a presumption that is baked into traditional techniques (like Factor Analysis or Latent Class Analysis) that fit statistical models to such data.
+This presumption is baked into traditional techniques (like Factor Analysis or Latent Class Analysis) that fit statistical models to such data.
 It is also embedded in ``relational'' techniques like Multiple Correspondence Analysis which, while not steeped in the preoccupations of standard statistical inference (although it could be), divert our attention to the indirect relations between macrogenres (or between people), usually conceptualized as distances in a social space.
-This kind of indirect relationality is fine and dandy but as already noted in the case of RCA, CCA, and BNA, all the relationality built into MCA is powerless, if what is fed {\em into} the process is the same old, limited, overextended macrogenre categories.
+This kind of indirect relationality is fine and dandy.
+Still, as already noted in the case of RCA, CCA, and BNA, all the relationality built into MCA is powerless if what is fed {\em into} the process is the same old, limited, overextended macrogenre categories.
 
-I address the microgenre issue using a technique for overlapping community detection called link clustering \citep{ahn_etal10}.
-The basic idea is simple and is illustrated in the toy example shown in Figure~\ref{fig:link-toy1}.
+\subsubsection{A Toy Example}
+I address the microgenre issue using a technique for overlapping community detection called \textit{link clustering} \citep{ahn_etal10}.
+The basic idea is simple and illustrated in the toy example in Figure~\ref{fig:link-toy1}.
 Breaking with approaches that attempt to cluster people and genres by focusing on the people or the genres, we take the person-to-genre {\em link} as the unit of analysis and focus our classification energies on those.
 Classifying the links gives (by definition) a classification of the entities at the end of each link (people and genres) for free.
-Not only that, because most people choose multiple genres, and all genres ``choose'' multiple people, this classification guarantees that genres get assigned to multiple \textit{overlapping} clusters, at the same time splitting up the macrogenres into more relationally focused clumps.
+Moreover, because most people choose multiple genres, and all genres ``choose'' multiple people, this classification guarantees that genres get assigned to multiple \textit{overlapping} clusters while splitting up the macrogenres into more relationally focused clumps.
 This allows us to make headway on both horns of the microgenre critique---namely, overlapping categories and internal differentiation---at once.
 
-\begin{figure}[ht!]
+\begin{figure}[t!]
      \centering
@@
     \end{subfigure}
-     \begin{subfigure}[b]{0.45\textwidth}
+\end{figure}
+
+How does this work?
+As Figure~\ref{fig:link-toy1} shows, once we string out the original two-mode person-by-network in our toy example into an edge list (now containing eleven person-genre edges), where the cases are the person to genre pairs that are marked by a ``1'' in the original matrix, it is possible to ask: ``How similar is one edge to another?'' We can answer that question as follows.
+The similarity of one person-to-genre edge to another, when both edges point to the same genre \citep{ahn_etal10}, should be proportional to the overlap between the ``cultural ego networks'' of the two people at the tail end of the edges.
+As \citet{lizardo14} defines it, for any respondent $i$, in a survey on cultural taste, the cultural ego network is simply the set of genres $\{G_1, G_2,\dots G_k\}$ chosen by the person.
+
+Going back to our running toy example, we are tasked with computing the similarities between $\frac{11 \times (11-1)}{2} = 55$ person-to-genre pairs.
+Suppose we wanted to calculate the similarity between the $P_1-G_2$ and $P_3-G_2$ person-to-genre edges in the two-mode network.
+In Figure~\ref{fig:link-toy1}, these two links are highlighted in yellow by the ``strung out'' edgelist and are shown in red in the corresponding bipartite subgraph shown in Figure~\ref{fig:link-toy2}.
+The similarity ($S$) between the two links is then given by:
+
+\begin{equation}
+    S(P_1G_2, P_3G_2) = \frac{n_+(P_1) \cap n_+(P_3)}{n_+(P_1) \cup n_+(P_3)}
+\end{equation}
+
+Where $n_+(P_1)$ is the cultural ego network of Person 1 and $n_+(P_3)$ is the cultural ego network of Person 3.
+The formula says that the similarity between two person-to-genre links sharing a genre, in this case, the similarity between the $P_1-G_2$ edge and the $P_3-G_2$ edge, is given by the intersection of Person 1's and Person 3's cultural ego network divided by their union (also known as Jaccard's coefficient).
+When the cultural ego networks of two people are the same $S=1$, when they are completely disjoint, sharing no genres, meaning the intersection is the empty set,  $S = 0$.
+All other cases of person-to-genre edges sharing the same genre return a number between zero and one ($0 > S < 1$).\footnote{Note that the only substantive similarities we care about are between person-to-genre edges that share the same genre but have different people attached to them at the other end.
+All other person-to-genre edges featuring people connected to different genres are set to zero.} In the toy example case, $P_1$ and $P_3$ consume two genres out of the four possible ones they could consume in common, resulting in an edge similarity score of $\frac{2}{4} = 0.50$.
+
+\begin{figure}
+    \centering
+     \begin{subfigure}[b]{0.6\textwidth}
         \includegraphics[width=1.0\textwidth]{Toy/toy-sim.png}
         \caption{Edge similarity matrix from toy example.}
-        \label{fig:toy-sim}
+        \label{tab:toy-sim}
     \end{subfigure}
-     \begin{subfigure}[b]{0.45\textwidth}
+     \begin{subfigure}[b]{0.6\textwidth}
         \includegraphics[width=1.0\textwidth]{Toy/toy-dis.png}
         \caption{Edge distance matrix from toy example.}
-        \label{fig:toy-dis}
+        \label{tab:toy-dis}
     \end{subfigure}
@@
 
-How does this work?
-As Figure~\ref{fig:link-toy1} shows, once we string out the original two-mode person-by-network in our toy example into an edge list (now containing eleven person-genre edges), where the cases are the person to genre pairs that are marked by a ``1'' in the original matrix, it is possible to ask: ``How similar is one edge to another?'' We can answer that question as follows.
-The similarity of one person-to-genre edge to another, when both edges point to the same genre \citep{ahn_etal10}, should be proportional to the overlap between the ``cultural ego networks'' of the two people at the tail end of the edges.
-As \citet{lizardo14} defines it, for any respondent $i$, in a survey on cultural taste, the cultural ego network is simply the set of genres $\{G_1, G_2,\dots G_k\}$ chosen by the person.
-
-Going back to our running toy example, we are tasked with computing the similarities between $\frac{11 \times (11-1)}{2} = 55$ person to genre pairs.
-Suppose we wanted to calculate the similarity between the $P_1-G_2$ and $P_3-G_2$ person-to-genre edges in the two-mode network.
-In Figure~\ref{fig:link-toy1}, these two links are highlighted in yellow the ``strung out'' edgelist and are shown in red in the corresponding bipartite subgraph shown in Figure~\ref{fig:link-toy2}.
-The similarity ($S$) between the two links is then given by:
-
-\begin{equation}
-    S(P_1G_2, P_3G_2) = \frac{n_+(P_1) \cap n_+(P_3)}{n_+(P_1) \cup n_+(P_3)}
-\end{equation}
-
-Where $n_+(P_1)$ is the cultural ego network of Person 1 and $n_+(P_3)$ is the cultural ego network of Person 3.
-The formula says that the similarity between two person-to-genre links sharing a genre, in this case, the similarity between the $P_1-G_2$ edge and the $P_3-G_2$ edge, is given by the intersection of Person 1's and Person 3's cultural ego network divided by their union (also known as Jaccard's coefficient).
-When the cultural ego networks of two people are the same then $S=1$, when they are completely disjoint (share no genres, meaning the intersection is the empty set), then $S = 0$.
-All other cases of person-to-genre edges sharing the same genre return a number between zero and one ($0 > S < 1$).\footnote{Note that the only substantive similarities we care about are between person-to-genre edges that shared the same genre but have different people attached to them at the other end.
-All other person-to-genre edges, featuring people connected to different genres are set to zero.} In the toy example case, $P_1$ and $P_3$ consume two genres out of the four possible ones they could consume in common, resulting in an edge similarity score of $\frac{2}{4} = 0.50$.
-
-If we do that for all pairs of person-to-culture genres sharing one genre node in common, we end up with the two-way, one-mode (with the only mode being edges) $11 \times 11$ similarity matrix shown in Figure~\ref{fig:link-toy3}.
+If we do that for all pairs of person-to-culture genres sharing one genre node in common, we end up with the two-way, one-mode (with the only mode being the edges) $11 \times 11$ similarity matrix shown in Figure~\ref{tab:toy-sim}.
 Note two features of the similarity matrix.
@@
 This means that only links that go from different people to the same genre exhibit overlap variation, and this is driven (``reflectively'' \citep{lizardo18}) by the overlap between the neighborhoods of the other mode (people).
-Next, we transform the similarity matrix into a {\em dissimilarity} matrix by subtracting one from each entry (shown in  Figure~\ref{fig:link-toy4}).
+Next, we transform the similarity matrix into a {\em dissimilarity} matrix by subtracting one from each entry (shown in  Figure~\ref{tab:toy-dis}).
 We then subject this matrix to hierarchical clustering using Ward's \citeyearpar{ward63} method.
 
-The resulting dendrogram from the cluster analysis is shown in Figure~\ref{fig:link-toy5}.
+The resulting dendrogram from the cluster analysis is shown in Figure~\ref{fig:link-toy}.
 Note that moving from the top down, the dendrogram splits person-to-genre links according to the macrogenre label.
-That is, macrogenre information is preserved in the clustering and can be recovered by splitting the dendrogram at a height where the number of clusters is equal to the original number of macrogenres (in this case, four as shown in Figure~\ref{fig:link-toy5}).
+That is macrogenre information is preserved in the clustering and can be recovered by splitting the dendrogram at a height where the number of clusters is equal to the original number of macrogenres (in this toy case, four).
 Moving from the bottom up, the hierarchical clustering of the dissimilarity matrix yields {\em link communities} \citep{ahn_etal10}, in which both people nodes, but, most crucially, genres nodes are assigned to different clumps.
-In the limiting case (the dendrogram's bottom-most ``leafs''), each person-to-genre link is assigned to a cluster.
-The more interesting thing is that as we move up to a point below macrogenres clusters and above the leaves, we see a partition of {\em varieties} of macrogenres.
+In the limiting case, each person-to-genre link is assigned to a cluster, namely, the dendrogram's bottom-most ``leaves.'' The more interesting thing is that as we move up to a point below macrogenres clusters and above the leaves, we see a partition of {\em varieties} of macrogenres.
 For instance, macrogenre $G4$ is split into two focused microgenre varieties.
-The first is attached to persons $P2$ and $P4$, and the second attached to persons $P3$ and $P5$, respectively.
-The idea, is that the macrogenre nodes (e.g., ``Classical,'') assigned to different clumps represent micro-variations of the macrogenre label that differ primarily relationally or structurally; different ``types'' of ``Classical'' are different because their audiences make distinct choices {\em with respect} to the other genres in the survey.
+The first is attached to persons $P2$ and $P4$, and the second is attached to persons $P3$ and $P5$, respectively.
+The idea is that the macrogenre nodes (e.g., ``Classical'') assigned to different clumps represent micro-variations of the macrogenre label that differ primarily relationally or structurally; different ``types'' of ``Classical'' are different because their audiences make distinct choices {\em with respect} to the other genres in the survey.
 
-\begin{figure}[ht!]
+\begin{figure}[t!]
      \begin{subfigure}[b]{0.5\textwidth}
@@
 
-\section{Analysis and Results}
-\subsection{Discovering microgenre Communities in Real Data}
+\subsection{Discovering Microgenre Communities in Real Data}
 Let us see how this process works in real data.
-We will see that link clustering can uncover valid microgenres.
 Recall that the data features 2,263 people choosing up to 20 macrogenre labels.
@@
 The hierarchical clustering process proceeds as follows.
-
 Initially, each person-to-genre link is assigned to a singleton cluster.
@@
 From left to right, these are Classic Rock/Oldies, Pop/Top 40, Country, Classical, Easy Listening, Blues/R\&B, Contemporary Rock, Rap/Hip Hop, Jazz, Gospel, Dance/Club, Indie Alternative, Latin, Broadway/Musicals, Heavy Metal/Hard Rock, Reggae, Big Band, Folk, Bluegrass, and Opera.
-As shown in Figure~\ref{fig:dend-micro}, microgenre communities are produced by cutting the link clustering dendrogram at a lower level.
-Choosing a cutoff value of $c = 3$ results in $k = 102$ microgenre communities extracted from the original twenty macrogenre labels.
-Data scientists wring their hands about choosing a cut value when performing cluster analysis.
+As shown in Figures~\ref{fig:dend-micro-classic-rock}-\ref{fig:dend-micro-opera}, microgenre communities for specific genres are produced by cutting the link clustering dendrogram at a lower level; in the examples provided ($C = 3$).
+
+Data scientists worry constantly about choosing a cut value when performing cluster analysis.
 One advantage of the link clustering approach is that we always know what we are doing because microgenres are strictly nested within the original macrogenres.
-On the other hand, choosing a smaller cut value produces finer-grained microgenres (perhaps at the expense of analytic tractability and interoperability), and selecting a higher value returns us to broader genre communities closer to the original macrogenre labels we began with (with the limiting case as shown in Figure~\ref{fig:dend-macro} being the original macro genre labels themselves).
-As Figure~\ref{fig:dend-micro-labels} shows, at any cut value $C$, the more popular macrogenres produce more microgenre communities, while the less popular ones produce a smaller number.
-For instance, as shown in Figure~\ref{fig:dend-micro-classic-rock}, at $c = 3$, the macrogenre ``Classic Rock/Oldies'' (the leftmost set of branches in the dendrogram in Figure~\ref{fig:dend-macro}) is split (at the point at which the branches intersect the red dashed cut line) into $k_{(CR)} = 12$ distinct micro-variations, while, as Figure~\ref{fig:dend-micro-opera} shows, the macrogenre ``Opera" (the rightmost set of branches in the dendrogram in Figure~\ref{fig:dend-macro}) is split into only $k_{(Op)} = 2$  microgenre communities.
+Choosing a smaller cut value produces finer-grained microgenres (perhaps at the expense of analytic tractability and interoperability), and selecting a higher value returns us to broader genre communities closer to the original macrogenre labels we began with (with the limiting case as shown in Figure~\ref{fig:dend-macro} being the original macro genre labels themselves).
+At any cut value $C$, the more popular macrogenres produce more microgenre communities, while the less popular ones produce a smaller number.
+
+For instance, as shown in Figure~\ref{fig:dend-micro-classic-rock}, at $c = 3$, the macrogenre ``Classic Rock'' (the leftmost set of branches in the dendrogram in Figure~\ref{fig:dend-macro}) is split (at the point at which the branches intersect the red dashed cut line) into $k_{(CR)} = 12$ distinct micro-variations, while, as Figure~\ref{fig:dend-micro-opera} shows, the macrogenre ``Opera" (the rightmost set of branches in the dendrogram in Figure~\ref{fig:dend-macro}) is split into only $k_{(Op)} = 2$  microgenre communities.
 Figure~\ref{fig:dend-micro-blues} shows that ``Blues/R\&B'' falls somewhere in between, with $k_{(BRB)} = 5$  microgenre communities uncovered.
-
 Each cut point in the dendrogram will have a microgenre size distribution $N$ associated with it.
 Lower cut points return a microgenre size distribution dominated by many microgenres with tiny ($N_{mg} < 10$) or trivial $N_{mg} = 2$ audiences.
-In this respect, although I have been using the labels ``macro'' and ``micro'' as if they referred to substantive or objective partitions, they are best interpreted as {\em relative} to a given classification level.
+Another approach, and the one I will be using in the case studies that follow, is to pick a macrogenre label (a branch in the larger dendrogram), decide \textit{ex ante} how many microgenres it makes sense to analyze, and then cut that branch of the dendrogram at a value that returns the desired number of microgenres.
+
+Note, that although I have been using the labels ``macro'' and ``micro'' as if they referred to substantive or objective partitions, they are best interpreted as {\em relative} to a given classification level.
 Thus, microgenres are ``micro'' relative to the usual (perhaps ``basic'' in Rosch's \citeyearpar{Rosch1978-ue} sense) categorization level of vague macrogenre labels populating most arts participation surveys.
-But these may be micro, as we will see, relative to the (logics, discourses, schemas) meta-groupings that we generate when applying the usual suite of statistical and data reduction techniques (e.g., such as ``highbrow'' or ``Folk").
-Further, at any given classification level, further microgenres will be nested within any given micro-partition.
-In this way, microgenre communities reflect a substantively valid way in which people partition the cultural world, whereby there is always the possibility of making finer-grained distinctions within fine-grained distinctions (e.g., ``old school rap," ``1980s old school rap,", ``early 1980s old school rap," and the like).
+At any given classification level, further microgenres will be nested within any given micro-partition.
+In this way, microgenre communities should reflect a substantively valid way in which people partition the cultural world, whereby there is always the possibility of making finer-grained distinctions within fine-grained distinctions (e.g., ``old school rap," ``1980s old school rap," ``early 1980s old school rap," and the like).
 
-\subsection{Two Genre Case Studies}
+\section{Two Genre Case Studies}
 We have shown that we can perform a link clustering and that this clustering returns a nice set of microgenres nested within the usual macrogenres in the survey.
@@
 I choose to present two ``case studies'' of macrogenre labels and the resulting microgenre variations returned by the link clustering procedure.
-My criteria were as follows: I selected a macrogenre label for which I could find some substantiated claim in the scholarly literature regarding possible microgenre variation.
+My criteria were as follows: I selected two macrogenre labels for which I could find some substantiated claim in the scholarly literature regarding possible microgenre variation.
 Naturally, general claims about microgenre variation apply to all macrogenre labels.
 Therefore, the ``substantiated in the scholarly literature" serves as a way to narrow the field.
+I also intended to identify macrogenre labels for which some sort of debate or uncertainty existed in the scholarly literature regarding their overall status and their variations.
 I settled on Heavy Metal and Latin/Spanish Music/Salsa using this criterion.
-I intended to identify macrogenre labels for which some sort of debate or uncertainty existed in the scholarly literature regarding their overall status and their variations.
-As we will see, Metal definitely fits this bill, as a lively debate already exists regarding its status.
-Latin/Spanish/Salsa represents a more ``minor'' case study in comparison but still serves to showcase the usefulness of the link clustering approach for resolving key issues.
+As we will see, Metal definitely fits this bill, as a lively debate already exists regarding its status as non-elite or an elite cultural form \citep{tampubolon2008revisiting}.
+Latin/Spanish/Salsa represents a more ``minor'' case study, but one that has also been documented to exhibit the sort of microgenre variation we seek \citep{bakk2013estimating}.
+As such, Salsa also showcases the usefulness of the link clustering approach for resolving key issues in the literature and extracting new insights from existing data.
 
-\subsubsection{Heavy Metal}
+\subsection{Heavy Metal}
 Heavy Metal is one of the most storied macrogenre labels in the sociology of taste, as featured in the title of Bethany Bryson's \citeyearpar{bryson96} now classic paper.
@@
 Is speaking of Metal as a ``youth'' music accurate, or has its audience been aging along with the genre (going on more than four decades and counting)?
-Given prior work, a strong expectation is that, at the very least, we should observe a microgenre partition separating the ``prototypical'' Metal (appealing to low-education white men) and perhaps a less-prototypical one, appealing to younger audiences with high-level cultural capital with other micro-variations, perhaps track generational distinction \citep{lizardo_skiles15}.
+
+Given prior work, a strong expectation is that, at the very least, we should observe a microgenre partition separating the ``prototypical'' Metal (appealing to low-education white men) and perhaps a less-prototypical one, appealing to younger audiences with high-level cultural capital with other micro-variations, perhaps tracking generational distinction among members of the metal subculture \citep{lizardo_skiles15}.
 
 \begin{figure}[ht!]
-     \begin{subfigure}[b]{1.0\textwidth}
     \centering    
-        \includegraphics[width=1.0\textwidth]{Tabs/reg-tab-metal.png}
+     \begin{subfigure}[b]{0.9\textwidth}
+        \includegraphics[trim={0 10cm 7cm 0},clip, width=1.0\textwidth]{Tabs/reg-tab-metal.png}
+        % trim={<left> <lower> <right> <upper>}
+        %\includegraphics[width=1.0\textwidth]{}
         \caption{}
@@
     \end{subfigure} \\
-     \begin{subfigure}[b]{1.0\textwidth}
-        \centering    
-        \includegraphics[width=1.0\textwidth]{Tabs/reg-tab-latin.png}
+     \begin{subfigure}[b]{0.9\textwidth}
+        \includegraphics[trim={0 10cm 7cm 0},clip, width=1.0\textwidth]{Tabs/reg-tab-salsa.png}
         \caption{}
@@
 
-To examine these questions, I partitioned the Heavy-Metal branch of the dendrogram, at a height that resulted in four microgenre variations.
-To explore the issue of audience segmentation, I specify a linear probability regression model with five outcomes: First, a binary variable indicating that a person chose (liked and listened to) the standard macrogenre label (Heavy Metal), and then four models with the microgenre variations as the outcome (Heavy Metal one through four).
+To address these questions, I partitioned the Heavy-Metal branch of the dendrogram at a height yielding three microgenre variations.
+To examine the issue of audience segmentation, I specify a linear probability regression model with five outcomes: First, a binary variable indicating that a person chose (liked and listened to) the standard macrogenre label (Heavy Metal), and then four models with the microgenre variations as the outcome (Heavy Metal one through four).
 The results are shown in Table~\ref{tab:reg-metal}.
-The main predictors are the respondent's education, an indicator variable for whether at least one of the respondent's parents has a college degree, the respondent's age, racial identification (in five categories), and gender identification (in two categories).
+The main predictors are the respondent's education, an indicator variable for whether at least one of the respondent's parents has a college degree, the respondent's age, racial identification (in five categories with ``white'' as the reference), and gender identification (in two categories with ``man'' as the reference).
 Because the age effect is specified using a squared polynomial, it can be hard to interpret its substantive significance.
@@
 
-\begin{figure}[ht!]
+\begin{figure}[t!]
      \begin{subfigure}[b]{0.45\textwidth}
@@
         \centering    
-        \includegraphics[width=1.0\textwidth]{Plots/Micro/micro-by-age-latin.png}
+        \includegraphics[width=1.0\textwidth]{Plots/Micro/micro-by-age-salsa.png}
         \caption{}
@@
 
-As shown in the first model, the socio-demographic predictors of choosing the ``Heavy Metal'' macrogenre label are the ones we would expect from Bryson's original work and the stereotypical perception of the genre's audience held by Americans.
+As shown in the first model, the socio-demographic predictors of choosing the ``Metal'' macrogenre label are the ones we would expect from Bryson's original work and the stereotypical perception of the genre's audience held by Americans.
 Metal fans are less likely to have high levels of education, are less likely to be older, are more likely to be white (negative effects for all other racial identifications compared to the base category), and are more likely to be men ($p<0.01$).
@@
 For this microgenre, there is a flat education gradient ($p = 0.54$), and importantly, it is more likely to be consumed by people whose parents have a college degree ($p < 0.05$), indicating a link to cultural capital in the home environment.
-This microgenre is tilted towards younger audiences, as only the linear negative age term is statistically significant (see Figure~\ref{fig:age-metal}) and is also neutral with respect to race and gender.
-This version of Metal appeals mainly to young middle-class respondents and does not repel women or non-white audiences, a stark difference from what we would have concluded from observing the macrogenre label effects.
+This microgenre is tilted towards younger audiences, as only the linear negative age term is statistically significant (see Figure~\ref{fig:age-metal}) and is also neutral with respect to race and gender ($p > 0.05$).
+Given that this microgenre version of Metal appeals mainly to young middle-class respondents and does not repel women or non-white audiences, it starkly contrasts what we would have concluded from observing the macrogenre label effects.
 
-Note that the other microgenre variations conform most closely to the audience segmentation we would expect from the version of Metal that would appeal to ``univore'' consumers, indicating that the link clustering can be discerned between these variants.
-Particularly, the second microgenre, whose predictors are shown in the third column, seems to be the ``uber-Metal,'' at least regarding the stereotype.
-It has a negative education gradient ($p = 0.06$), appeals to young-adult and middle-aged audiences (see Figure~\ref{fig:age-metal}), and repels Black and Hispanic people as well as women.
-The other Metal microgenres are variations on the same theme: The third microgenre, as shown in the fourth column in the table, is like the second but appeals mainly to young audiences, and the fourth Metal microgenre is also similar to the second but appeals to a comparatively older crowd.
-So the remaining microgenre partitions seem to indicate variations within the ``univore'' consumption profile, perhaps indicative of distinctive versions of Metal with an appeal to different generational niches \citep{koch2020evolutionary}.
+Note that the other two microgenre variations, whose respective coefficient estimates are shown in the third and fourth columns of the table, conform most closely to the audience segmentation we would expect from the version of Metal.
+These two microgenres mainly appeal to white men of relatively low education.
+The main difference between these two microgenres is generational location, with the second microgenre appealing mainly to young adults and middle-aged men and the third variant attracting a younger crowd (see Figure~\ref{fig:age-metal}).
+This means that the two microgenre variations that most closely conform to the usual audience expectations represent partitions \textit{within} the ``univore'' consumption profile, indicative of distinctive versions of Metal with an appeal to different generational niches \citep{koch2020evolutionary}.
 
-\subsubsection{Salsa}
+\subsection{Salsa}
 The Salsa music genre has not had as storied a career in the sociology of taste as Metal.

### 2023-08-04 qmd/03_real-dends.qmd
New dends

---
    title: "Discovering Focused Microgenre Communities: Dendrograms"
    author: "Omar Lizardo"
    date: "`r Sys.Date()`"
---

# Setup
```{r setup}
    knitr::opts_chunk$set(include=FALSE, echo = TRUE, warning = FALSE, message = FALSE)
    require("dendextend")
    require("here")
    require("RColorBrewer")
```

```{r Loading link distance matrix and performing link clustering}
    load(file= here("dat", "lclust-res.RData"))
```

```{r Performing Link Clustering}
    lclust.res <- hclust(ldist.res$dist, method = "ward.D2") #clustering of link by link distance matrix
    lclust.dend <- as.dendrogram(lclust.res) #transforming link clustering into dendrogram
    dend.macro <- cut(lclust.dend, h = 8) #cutting at macrogenre level
```

# Dendrogram Plots from Link Clustered Data
```{r Creating macrogenre dendrograms}
    d1 <- lclust.dend %>% 
      set("labels", c(rep("", 20))) %>% 
      set("branches_k_color", value = brewer.pal(20, "Dark2"), k = 20) %>% 
      set("branches_lwd", value = 3)

    d2 <- dend.macro$upper %>% 
      set("labels", dend.macro$lower %>% names) %>% 
      set("branches_k_color", value = brewer.pal(20, "Dark2")) %>% 
      set("branches_lwd", value = 4) %>% 
      set("labels_color", value = brewer.pal(20, "Dark2")) %>% 
      set("labels_cex", value = 2.5)

```

```{r Plotting macrogenre dendrograms}
    dev.off()
    png(here("Plots", "Dend", "macro.png"), height = 900, width = 1600)
    plot(d1) %>% 
      abline(h = 8, col="red", lty = 2, lwd = 3)

    dev.off()
    png(here("Plots", "Dend", "macro-lab.png"), height = 900, width = 1600)
    plot(d2) 
```

```{r Creating microgenre dendrograms}
    d3 <- dend.macro$lower$Metal %>% 
      set("labels", c(rep("", nleaves(d3)))) %>% 
      set("branches_k_color", value = brewer.pal(3, "Dark2"), k = 3)

    d4 <- dend.macro$lower$Salsa %>% 
      set("labels", c(rep("", nleaves(d4)))) %>% 
      set("branches_k_color", value = brewer.pal(3, "Dark2"), k = 3)
```

```{r Plotting microgenre dendrograms}
    dev.off()
    png(here("Plots", "Dend", "metal-branches.png"), height = 900, width = 1600)
    plot(d3, axes = FALSE) %>% 
      par(cex = 5) %>% 
      title(xlab = "", ylab = "", main = "Metal")

    dev.off()
    png(here("Plots", "Dend", "salsa-branches.png"), height = 900, width = 1600)
    plot(d4, axes = FALSE) %>% 
      par(cex = 5) %>% 
      title(xlab = "", ylab = "", main = "Metal")

```

### 2023-08-04 qmd/04_microgenre-analysis.qmd
New dends

@@
     library(ggplot2)
-    library(haven)
     library(here)
@@
                     xb = c(3, 7, 11),
-                    xlabs = c("Young", "Mid. Aged", "Old"),
+                    xlabs = c("Young", "Middle Aged", "Old"),
                     ym = -0.02,

### 2023-08-04 Functions/old-dend.stuff.R

@@ -1,4 +1,3 @@
-```{r Creating objects for analysis}
 dend.macro <- cut(lclust.dend, h = 8) #cutting at macrogenre level
 a <- data.frame(g.size = sapply(dend.macro$lower, nleaves)) #macrogenres as ordered in dendrogram results
 b <- data.frame(g.size = colSums(taste.mat), g.names = names(colSums(taste.mat))) #original macrogenre sizes
@@ -34,4 +33,28 @@ micro.g.dat <- right_join(micro.g.dat, edge.labs) %>%
    mutate(across(is.integer, bin.char)) %>% 
    mutate(id = as.integer(id)) %>% 
    arrange(id)
-```
+
+k <- length(dend.micro$lower)
+png(here("Plots", "Dend", "all-branches-micro.png"), height = 900, width = 1600)
+k <- length(dend.micro$lower)
+d <- lclust.dend
+d %>% 
+   set("labels", c(rep("", nleaves(d)))) %>% 
+   set("branches_k_color", value = brewer.pal(k, "Dark2"), k = k) %>% 
+   set("branches_lwd", value = 3) %>%
+   plot(axes = FALSE) %>% 
+   abline(h = 3, col="red", lty = 2, lwd = 3) 
+
+k <- length(dend.micro$lower)
+png(here("Plots", "Dend", "all-branches-micro-labels.png"), height = 900, width = 1600)
+d <- dend.micro$upper
+d %>% 
+   set("labels", micro.g.names) %>% 
+   set("branches_k_color", value = brewer.pal(k, "Dark2"), k = k) %>% 
+   set("branches_lwd", value = 3) %>% 
+   set("labels_color", value = brewer.pal(k, "Dark2")) %>% 
+   set("labels_cex", value = 0.9) %>% 
+   plot(axes = FALSE) 
+par(cex= 2.5)
+title(xlab="", ylab="", main="") %>% 
+   abline(h = 3, col="red", lty = 2, lwd = 3)

### 2023-08-05 old_Rmds/Old/04_demog-analysis.Rmd
re-arranged folders and moved content from old folder

---
title: "Demographic Analysis of Microgenres Communities"
author: "Omar Lizardo"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
    knitr::opts_chunk$set(include = TRUE)
    knitr::opts_chunk$set(message = FALSE)
    knitr::opts_chunk$set(warning = FALSE)
    load(file = "C:/Users/Omar Lizardo/Google Drive/WORK/EARLY/CULTURE/lizardo-genre-communities/taste.comm.RData")
```

```{r loading required packages}
    library("tidyverse")
    library("haven")
    library("prediction")
    library("cowplot")
```

```{r import data and select demographic variables}
    #importing data
    demog.dat <- read_dta("C:/Users/Omar Lizardo/Google Drive/MISC DATA SOURCES/SSI-2012/SSI2012.dta")
     #replacing ids with character names
    demog.dat <- bind_cols(tibble(id_char = paste("id", sapply(demog.dat[, 1], as.character), sep = "_")), demog.dat)
    demog.dat <- select(demog.dat, c("id_char", "age","female", "raceeth", "nodipdeg", "hsged", "somcol", "aadeg", "bach", "ma", "docprof","income", "percclass", "region", "occ"))
    demog.dat <- demog.dat %>% 
        mutate(Degree = ifelse(nodipdeg == 1, 1, ifelse(hsged == 1, 2, ifelse(somcol == 1, 3, 
                               ifelse(aadeg == 1, 4, ifelse(bach == 1, 5, ifelse(ma == 1, 6, 
                               ifelse(docprof == 1, 7, 99)))))))) %>% #creating ordinal educ variable from dummies
        as_factor() %>% 
        na.omit() %>% 
        mutate(raceeth = fct_recode(raceeth,
                                    "Asian" = "Asian",
                                    "Black" = "Black",
                                    "Hisp." = "Hispanic",
                                    "White" = "White",
                                    "Mult./Other" = ">1 race",
                                    "Mult./Other" = "other"),
                female = fct_recode(female, 
                                   "Men" = "male", 
                                   "Women" = "female"),
                percclass = fct_recode(percclass, 
                                      "Lower Class" = "lower class", 
                                      "Working Class" = "working class", 
                                      "Middle Class" = "middle class", 
                                      "Upper Class" = "upper class"),
                region = fct_recode(region,
                                   "New England" = "New Enlgnad",
                                   "South" = "East South",
                                   "South" = "South Atlantic",
                                   "Southwest" = "West South",
                                   "Midwest" = "Eastern Midwest",
                                   "Midwest" = "Western Midwest",
                                   "Mountain" = "Mountain West",
                                   "West Coast" = "Pacific West")
                ) %>% 
        rename(Age = age, Gender = female, Race = raceeth, Class_ID = percclass, 
               Income = income, Region = region, Occupation = occ) %>% 
        select(-c("nodipdeg", "hsged", "somcol", "aadeg", "bach", "ma", "docprof"))  
        demog.dat$Degree <- factor(demog.dat$Degree, 
                               labels = c("< High School", "High School/GED", "Some College", 
                                          "Assoc. Deg.", "College", "M.A.", "PhD/Prof."))
```

```{r merging demographic and microgenre communities data}
    taste.demog.dat <- bind_cols(id_char = paste("id", sapply(taste.dat[, 1], as.character), sep = "_"), taste.comms.dat)
    taste.demog.dat$omnivore <- rowSums(taste.demog.dat[,c(2:ncol(taste.comms.dat) + 1)])
    taste.demog.dat <- taste.demog.dat %>% 
        left_join(demog.dat, by = "id_char") %>% 
        na.omit() %>% 
          mutate(omni_cat = case_when(
            omnivore %in% 0:1 ~ 1,
            omnivore %in% 2:3 ~ 2,
            omnivore %in% 4:6 ~ 3,
            omnivore %in% 7:9 ~ 4,
            omnivore %in% 10:20 ~ 5)
            )
    taste.demog.dat$omni_cat <- factor(taste.demog.dat$omni_cat, 
                                          labels = c("Zero-One", "Two-Three", "Four-Six", "Seven-Nine", "Ten+"))
    save.image(file = "C:/Users/Omar Lizardo/Google Drive/WORK/EARLY/CULTURE/lizardo-genre-communities/taste.comm.demog.RData")
```

```{r functions to generate predicted prob. plot}
    predProbs <- function(y, x, w, z = 1.96, p = 2, title = "", f = gaussian,  x.type = "") {
      if (title == "") {
        title <- deparse(substitute(y))
        }
      y <- eval(substitute(y), w)
      x <- eval(substitute(x), w)
      # regression
      if (x.type == "") {
        mymod <- glm(y ~ poly(as.numeric(x), p), data = w, family = deparse(substitute(f)))
        }
      if (x.type == "factor") {
        mymod <- glm(y ~ x, data = w, family = deparse(substitute(f)))
        }
      mypred <- prediction(mymod)
      mypred$lo <- mypred$fitted - (z*mypred$se.fitted)
      mypred$hi <- mypred$fitted + (z*mypred$se.fitted)
      m <- aggregate(mypred, by = list(x), "mean")
    return(m[, c("Group.1", "fitted", "se.fitted", "lo", "hi")])
    }

    plotPreds <- function(y, dat) {
      title <- deparse(substitute(y))
      y <- eval(substitute(y), dat)
      pred.res1 <- predProbs(y, Degree, dat, f = binomial)
      pred.res2 <- predProbs(y, Age, dat, f = binomial)
      pred.res3 <- predProbs(y, Income, dat, f = binomial)
      pred.res4 <- predProbs(y, Race, dat, f = binomial, x.type = "factor")
      pred.res5 <- predProbs(y, Class_ID, dat, f = binomial, x.type = "factor")
      pred.res6 <- predProbs(y, Gender, dat, f = binomial, x.type = "factor")
      pred.res7 <- predProbs(y, Region, dat, f = binomial, x.type = "factor")
      pred.res8 <- predProbs(y, omni_cat, dat, f = binomial, x.type = "factor")
      pred.res <- data.frame(rbind(pred.res1, pred.res2, pred.res3, 
                                   pred.res4, pred.res5, pred.res6,
                                   pred.res7, pred.res8))
      pred.res$var.type <- factor(c(rep(1, 7), rep(2, 14), rep(3, 23),
                                    rep(4, 5), rep(5, 4), rep(6, 2),rep(7, 7), rep(8, 5))) 
      return(pred.res)
    }

    plotDat <- function(x, line.size = 0.75, prob.size = 14, lab.size = 14, point.size = 4, title = "") {
      x1 <- x[c(which(x$var.type == 1), which(x$var.type == 2)), ]
      x2 <- x[c(which(x$var.type == 4), which(x$var.type == 5), which(x$var.type == 7)), ]
      x3 <- x[c(which(x$var.type == 6), which(x$var.type == 8)), ]
      x <- rbind(x1, x2, x3)
      p <- ggplot(mapping = aes(x = Group.1, group = var.type))
      p <- p + geom_point(data = x, mapping = aes(y = fitted, color = var.type), size = point.size)
      p <- p + geom_line(data = x1, mapping = aes(y = fitted, color = var.type), size = line.size)
      p <- p + geom_ribbon(data = x1, mapping = aes(ymin = lo, ymax = hi, fill = var.type, color = var.type), alpha = 0.15, linetype = 0)
      p <- p + geom_segment(data = x2, mapping = aes(y = lo, x = Group.1, yend = hi, xend = Group.1, color = var.type), alpha = 0.25, size = 1.25)
      p <- p + geom_segment(data = x3, mapping = aes(y = 0, x = Group.1, yend = fitted, xend = Group.1, color = var.type), size = 0.9)
      p <- p + geom_hline(yintercept = 0, color = "gray55")
      p <- p + coord_flip()
      p <- p + theme_minimal() + labs(x = "", y = "", title = "") + ggtitle(title)
      p <- p + theme(legend.position = "none", axis.text.y = element_text(size = lab.size), 
                     axis.text.x  = element_text(size = prob.size), 
                     plot.title = element_text(size = 16)) 
      p
      }
```

```{r demographic predictors of microgenre community membership (by cluster)}
      for (k in as.numeric(levels(mca.clust.dat$cluster))) {
        dat <- mca.clust.dat %>% filter(cluster == k)
        micro.g <- dat$id
        dat <- micro.genre.dat %>% filter(genre %in% micro.g)
        micro.g.sizes <- dat$size
        if (length(micro.g) > 8) {
            r <- 3 
            lab.s <- 8
            pt.s <- 2
          }
        if (length(micro.g) > 3 | length(micro.g) <= 8) {
            r <- 2
            lab.s <- 10
            pt.s <- 3
            }
        if (length(micro.g) <= 3) {
          r <- 1
          lab.s <- 14
          pt.s <- 4.5
          }
        g.plot.list <- list()
        for (i in 1:length(micro.g)) {
          p.title <- paste(micro.g[i], 
                           paste("(N = ", paste(micro.g.sizes[i], ")", sep = ""), sep = ""), sep = " ")
          g.plot.list[[i]] <- plotDat(plotPreds(y = eval(as.name(micro.g[i])), taste.demog.dat), 
                                      title = p.title, lab.size = lab.s, point.size = pt.s)
          }
        p <- plot_grid(plotlist = g.plot.list, align = "hv", nrow = r)
        g.save1 <- paste("cluster", k, sep = "_")
        g.save2 <- paste(g.save1, ".png", sep = "")
        ggsave(paste("C:/Users/Omar Lizardo/Google Drive/WORK/EARLY/CULTURE/lizardo-genre-communities/plots/demog-plots/cluster/", g.save2, sep = ""), scale = 0.85, height = 16, width = 22)
        }
```

```{r demographic predictors of microgenre community membership (Focused Genres)}
    macro.g <- names(taste.dat[, 2:length(taste.dat)])
    macro.g <- macro.g[!macro.g %in% c("Country", "Classic_Rock", "Pop")] #removing vague genres from vector
    for (k in 1:length(macro.g)) {
      micro.g <- names(taste.demog.dat[,grepl(macro.g[k], names(taste.demog.dat))])
      micro.g.sizes <- micro.genre.dat[grepl(macro.g[k], micro.genre.dat$genre), ]$size
      if (length(micro.g) > 8) {
          r <- 3 
          lab.s <- 8
          pt.s <- 2
        }
      if (length(micro.g) > 3 | length(micro.g) <= 8) {
          r <- 2
          lab.s <- 10
          pt.s <- 3
          }
      if (length(micro.g) <= 3) {
        r <- 1
        lab.s <- 14
        pt.s <- 4.5
        }
      g.plot.list <- list()
      for (i in 1:length(micro.g)) {
        p.title <- paste(micro.g[i], 
                         paste("(N = ", paste(micro.g.sizes[i], ")", sep = ""), sep = ""), sep = " ")
        g.plot.list[[i]] <- plotDat(plotPreds(y = eval(as.name(micro.g[i])), taste.demog.dat), 
                                    title = p.title, lab.size = lab.s, point.size = pt.s)
      }
      plot_grid(plotlist = g.plot.list, align = "hv", nrow = r)
      g.save <- paste(macro.g[k], ".png", sep = "")
      ggsave(paste("C:/Users/Omar Lizardo/Google Drive/WORK/EARLY/CULTURE/lizardo-genre-communities/plots/demog-plots/", g.save, sep = ""), scale = 0.85, height = 17, width = 22)
    }
```

```{r demographic predictors of microgenre community membership (Classic Rock)}
      micro.g <- names(taste.demog.dat[,grepl("Classic_Rock", names(taste.demog.dat))])
      micro.g.sizes <- micro.genre.dat[grepl("Classic_Rock", micro.genre.dat$genre), ]$size
      micro.g1 <- micro.g[1:8]
      micro.g2 <- micro.g[9:length(micro.g)]
      micro.g.sizes1 <- micro.g.sizes[1:8]
      micro.g.sizes2 <- micro.g.sizes[9:length(micro.g)]
      #First set of Classic Rock Microgenres
      g.plot.list <- list()
      for (i in 1:length(micro.g1)) {
        p.title <- paste(micro.g1[i], 
                         paste("(N = ", paste(micro.g.sizes1[i], ")", sep = ""), sep = ""), sep = " ")
        g.plot.list[[i]] <- plotDat(plotPreds(y = eval(as.name(micro.g1[i])), taste.demog.dat), 
                                    title = p.title, lab.size = 10, point.size = 3)
        }
      plot_grid(plotlist = g.plot.list, align = "hv", nrow = 2)
      g.save <- paste(macro.g[k], ".png", sep = "")
      ggsave("C:/Users/Omar Lizardo/Google Drive/WORK/EARLY/CULTURE/lizardo-genre-communities/plots/demog-plots/Classic_Rock1.png", scale = 0.85, height = 17, width = 22)
      #Second set of Classic Rock Microgenres
      g.plot.list <- list()
      for (i in 1:length(micro.g2)) {
        p.title <- paste(micro.g2[i], 
                         paste("(N = ", paste(micro.g.sizes2[i], ")", sep = ""), sep = ""), sep = " ")
        g.plot.list[[i]] <- plotDat(plotPreds(y = eval(as.name(micro.g2[i])), taste.demog.dat), 
                                    title = p.title, lab.size = 10, point.size = 3)
          }
      plot_grid(plotlist = g.plot.list, align = "hv", nrow = 2)
      g.save <- paste(macro.g[k], ".png", sep = "")
      ggsave("C:/Users/Omar Lizardo/Google Drive/WORK/EARLY/CULTURE/lizardo-genre-communities/plots/demog-plots/Classic_Rock2.png", scale = 0.85, height = 17, width = 22)
```

```{r demographic predictors of microgenre community membership (Country)}
      micro.g <- names(taste.demog.dat[,grepl("Country", names(taste.demog.dat))])
      micro.g.sizes <- micro.genre.dat[grepl("Country", micro.genre.dat$genre), ]$size
      micro.g1 <- micro.g[1:5]
      micro.g2 <- micro.g[6:length(micro.g)]
      micro.g.sizes1 <- micro.g.sizes[1:5]
      micro.g.sizes2 <- micro.g.sizes[6:length(micro.g)]
      #First set of Country Microgenres
      g.plot.list <- list()
      for (i in 1:length(micro.g1)) {
        p.title <- paste(micro.g1[i], 
                         paste("(N = ", paste(micro.g.sizes1[i], ")", sep = ""), sep = ""), sep = " ")
        g.plot.list[[i]] <- plotDat(plotPreds(y = eval(as.name(micro.g1[i])), taste.demog.dat), 
                                    title = p.title, lab.size = 10, point.size = 3)
        }
      plot_grid(plotlist = g.plot.list, align = "hv", nrow = 2)
      g.save <- paste(macro.g[k], ".png", sep = "")
      ggsave("C:/Users/Omar Lizardo/Google Drive/WORK/EARLY/CULTURE/lizardo-genre-communities/plots/demog-plots/Country1.png", scale = 0.85, height = 17, width = 22)
      #Second set of Country Microgenres
      g.plot.list <- list()
      for (i in 1:length(micro.g2)) {
        p.title <- paste(micro.g2[i], 
                         paste("(N = ", paste(micro.g.sizes2[i], ")", sep = ""), sep = ""), sep = " ")
        g.plot.list[[i]] <- plotDat(plotPreds(y = eval(as.name(micro.g2[i])), taste.demog.dat), 
                                    title = p.title, lab.size = 10, point.size = 3)
          }
      plot_grid(plotlist = g.plot.list, align = "hv", nrow = 2)
      g.save <- paste(macro.g[k], ".png", sep = "")
      ggsave("C:/Users/Omar Lizardo/Google Drive/WORK/EARLY/CULTURE/lizardo-genre-communities/plots/demog-plots/Country2.png", scale = 0.85, height = 17, width = 22)
```

```{r demographic predictors of microgenre community membership (Pop)}
      micro.g <- names(taste.demog.dat[,grepl("Pop", names(taste.demog.dat))])
      micro.g.sizes <- micro.genre.dat[grepl("Pop", micro.genre.dat$genre), ]$size
      micro.g1 <- micro.g[1:5]
      micro.g2 <- micro.g[6:length(micro.g)]
      micro.g.sizes1 <- micro.g.sizes[1:5]
      micro.g.sizes2 <- micro.g.sizes[6:length(micro.g)]
      #First set of Country Microgenres
      g.plot.list <- list()
      for (i in 1:length(micro.g1)) {
        p.title <- paste(micro.g1[i], 
                         paste("(N = ", paste(micro.g.sizes1[i], ")", sep = ""), sep = ""), sep = " ")
        g.plot.list[[i]] <- plotDat(plotPreds(y = eval(as.name(micro.g1[i])), taste.demog.dat), 
                                    title = p.title, lab.size = 10, point.size = 3)
        }
      plot_grid(plotlist = g.plot.list, align = "hv", nrow = 2)
      g.save <- paste(macro.g[k], ".png", sep = "")
      ggsave("C:/Users/Omar Lizardo/Google Drive/WORK/EARLY/CULTURE/lizardo-genre-communities/plots/demog-plots/Pop1.png", scale = 0.85, height = 17, width = 22)
      #Second set of Country Microgenres
      g.plot.list <- list()
      for (i in 1:length(micro.g2)) {
        p.title <- paste(micro.g2[i], 
                         paste("(N = ", paste(micro.g.sizes2[i], ")", sep = ""), sep = ""), sep = " ")
        g.plot.list[[i]] <- plotDat(plotPreds(y = eval(as.name(micro.g2[i])), taste.demog.dat), 
                                    title = p.title, lab.size = 10, point.size = 3)
          }
      plot_grid(plotlist = g.plot.list, align = "hv", nrow = 2)
      g.save <- paste(macro.g[k], ".png", sep = "")
      ggsave("C:/Users/Omar Lizardo/Google Drive/WORK/EARLY/CULTURE/lizardo-genre-communities/plots/demog-plots/Pop2.png", scale = 0.85, height = 17, width = 22)
```

### 2023-08-05 old_Rmds/Old/other-link-clustering-analyses.Rmd
re-arranged folders and moved content from old folder

```{r calculating micro-genre distance matrix from micro-genre overlap matrix}
    micro.overlaps <- t(as.matrix(lclust.dat[, 2:ncol(lclust.dat)])) %*% as.matrix(lclust.dat[, 2:ncol(lclust.dat)])
    micro.dist <- micro.overlaps 
    diag(micro.dist) <- 0
    micro.dist <- as.dist(1 - micro.dist/max(micro.dist))
    micro.clust.res <- hclust(micro.dist, method = "ward.D2") #link clustering of link by link distance matrix
    nc <- NbClust(diss = micro.dist, method = "ward.D2", 
                      index = "silhouette", distance = NULL)
```

```{r prepping data for mca plot of micro-genre communities}
    mca.dat <- lclust.dat[, 2:ncol(lclust.dat)]
    factor_commvars <- function(x) {
        factor(x, labels = c("No", "Yes"))
      }
    mca.dat <- mca.dat %>% 
        mutate(across(1:ncol(mca.dat), factor_commvars))
    mca.res <- MCA(mca.dat, ncp = 10, graph = FALSE,  method = "indicator") #peforming MCA of micro-genre communities
    mca.yes.mods <- mca.res$var$coord[seq(2, nrow(mca.res$var$coord), by = 2), ]
    mca.clust.dat <- as_tibble(mca.yes.mods)
    mca.hk.res <-hkmeans(mca.clust.dat[,1:4], k = 17, hc.method = "ward.D2") #clustering yes modalities on principal components
    mca.clust.dat <- bind_cols(
      tibble(id = gsub("_Yes", "", rownames(mca.yes.mods))),
      mca.clust.dat, 
      tibble(cluster = factor(mca.hk.res$cluster))
      )
```

```{r MCA biplot of micro-genre communities}
    p <- ggplot(data = mca.clust.dat, 
                mapping = aes(x = `Dim 1`, y = `Dim 2`, color = cluster))
    p <- p + theme_minimal()
    p <- p + geom_hline(yintercept = 0, colour = "gray75") 
    p <- p + geom_vline(xintercept = 0, colour = "gray75")
    p <- p + geom_text(aes(label = id), check_overlap = TRUE, size = 4)
    p <- p + stat_ellipse(linetype = 0, geom = "polygon", aes(fill = cluster), alpha = 0.02)
    p <- p + labs(x = "Dimension 1", y = "Dimension 2")
    p <- p + theme_sjplot()
    p.12 <- p + theme(
                    panel.grid.major.y = element_line(color = "grey90"),
                    panel.grid.major.x = element_line(color = "grey90"),
                    axis.title = element_text(size = 18), 
                    axis.text = element_text(size = 18),
                    axis.line.x = element_blank(),
                    axis.line.y = element_blank(),
                    legend.position = "none"
                    )
    p <- ggplot(data = mca.clust.dat, 
                mapping = aes(x = `Dim 3`, y = `Dim 4`, color = cluster))
    p <- p + theme_minimal()
    p <- p + geom_hline(yintercept = 0, colour = "gray75") 
    p <- p + geom_vline(xintercept = 0, colour = "gray75")
    p <- p + geom_text(aes(label = id), check_overlap = TRUE, size = 4)
    p <- p + stat_ellipse(linetype = 0, geom = "polygon", aes(fill = cluster), alpha = 0.02)
    p <- p + labs(x = "Dimension 3", y = "Dimension 4")
    p <- p + theme_sjplot()
    p.34 <- p + theme(
                    panel.grid.major.y = element_line(color = "grey90"),
                    panel.grid.major.x = element_line(color = "grey90"),
                    axis.title = element_text(size = 18), 
                    axis.text = element_text(size = 18),
                    axis.line.x = element_blank(),
                    axis.line.y = element_blank(),
                    legend.position = "none"
                    )
    p <- fviz_nbclust(mca.yes.mods, 
                      kmeans, method = "silhouette", 
                      k.max = 20, linecolor = "red")     
    p <- p + labs(y = "", x = "") 
    p.in <- p + theme(plot.background = 
                       element_rect(colour = "white", size = 0.25),
                   axis.text.x = element_text(size = 10))
    p <-  p.12 / p.34 #combining plots using patchwork
    p <- p + inset_element(p.in, 0.01, 0, 0.35, 0.35) #inset plot using patchwork
    save_plot(here("Plots", "Link Clust", "micro-genre-mca.png"), 
              width = 35, height = 45)

```

```{r Network plot of two mode micro-genre overlaps}
    linkcomm.net <- graph_from_adjacency_matrix(micro.overlaps, 
                                            mode = "undirected",
                                            diag = FALSE, weighted = TRUE)
    linkcomm.bb <- disparity(linkcomm.net, alpha = 0.05, narrative = TRUE)
    iso <- which(degree(linkcomm.bb)== 0)
    linkcomm.bb <- delete.vertices(linkcomm.bb, iso) 
    c <- cluster_louvain(linkcomm.bb)
    V(linkcomm.bb)$c <- c$membership   
    p <- ggraph(linkcomm.bb, layout = 'auto')
    p <- p + geom_node_text(aes(label = name, 
                                color = as.factor(c)), size = 6, check_overlap = TRUE)
    p <- p + geom_edge_link(color = "grey70", width = 0.5) 
    p <- p + theme_graph() + theme(legend.position = "none")
    p
    save_plot(here("Plots", "Link Clust", "micro-genre-net.png"), 
              width = 55, height = 45)
```

```{r Dendrogram representation of nested micro-genre communities}
    p <- fviz_dend(micro.clust.res, cex = 1.05, k = nc$Best.nc[1], 
                       type = "rectangle", repel = TRUE, k_colors = "uchicago",
                       color_labels_by_k = TRUE, rect = FALSE, lwd = 1.2) 
    p <- p + theme_minimal() 
    p <- p + labs(x = "", y = "")
    p.rect <- p + theme(
                axis.line=element_blank(),
                axis.text.x=element_blank(),
                axis.text.y=element_blank(),
                axis.ticks=element_blank(),
                axis.title.x=element_blank(),
                axis.title.y=element_blank()
                )
    p.rect
    save_plot(here("Plots", "Link Clust", "micro-genre-dend.png"), 
              width = 65, height = 45)
```

```{r Phylogenic representation of nested micro-genre communities}
    p <- fviz_dend(micro.clust.res, cex = 1.5, k = nc$Best.nc[1], 
                       type = "phylogenic", repel = TRUE, k_colors = "uchicago",
                       color_labels_by_k = TRUE) 
    p <- p + theme_minimal() 
    p <- p + labs(x = "", y = "")
    p.phylo <- p + theme(
                axis.line=element_blank(),
                axis.text.x=element_blank(),
                axis.text.y=element_blank(),
                axis.ticks=element_blank(),
                axis.title.x=element_blank(),
                axis.title.y=element_blank()
                )
    p.phylo
    save_plot(here("Plots", "Link Clust", "micro-genre-phylo.png"), 
              width = 55, height = 45)
```

### 2023-08-05 old_Rmds/Old/taste-comm-analysis.Rmd
re-arranged folders and moved content from old folder

---
title: "R Notebook"
output: html_notebook
---

```{r packages and loading user created functions, message=FALSE, warning=FALSE, paged.print=FALSE}
  library(ggrepel)
  library(ggplot2)
  library(ggpubr)
  library(FactoMineR)
  library(factoextra)
  library(qgraph)
  library(tidyverse)
  library(linkcomm)
```

```{r fancy dendrogram plot for all edges}
    windows(height = 15, width = 24)
    dend <- plot(taste.comm2, type = "dend")
    savePlot(filename = "C:/Users/Omar Lizardo/Google Drive/WORK/EARLY/CULTURE/lizardo-genre-communities/plots/edge-cluster-dendro.png", type = "png")
```

```{r regular dendrogram for genre communities}
    windows(height = 15, width = 24)
    fviz_dend(taste.hc, cex = 0.35, k = 12,  k_colors = "uchicago") +
    theme_minimal() + ylab("") + xlab("") +
    theme(axis.line=element_blank(),
          axis.text.x=element_blank(),
          axis.text.y=element_blank(),
          axis.ticks=element_blank(),
          axis.title.x=element_blank(),
          axis.title.y=element_blank())
    savePlot(filename = "C:/Users/Omar Lizardo/Google Drive/WORK/EARLY/CULTURE/lizardo-genre-communities/plots/genre-comm-dendro.png", type = "png")
    windows(height = 18, width = 10)
    fviz_dend(taste.hc, cex = .85, k = 12, ylim = c(-1,4), xlim = c(1, 24))
    savePlot(filename = "C:/Users/Omar Lizardo/Google Drive/WORK/EARLY/CULTURE/lizardo-genre-communities/plots/genre-comm-dendro-zoom.png", type = "png")
```

``

```{r mca biplot of micro-genre communities}
g <- c("Classical", "Opera", "Jazz", "Broadway", "Easy", "BigBand", "ClassicRock", "Country",
                 "Bluegrass", "Folk", "Gospel", "Latin", "Rap", "Blues", "Reggae", 
                 "Pop", "ContRock", "Alt", "Dance", "Metal")
     g <- c("Classical")
    i <- 1
    while(i <= length(g)) {
      p <- NiceInsetPlot(mca.res, sil = FALSE, yes.only = TRUE, cos.size = FALSE, 
                         v.size = log(comm.sizes[rownames(get.Yes.mca(mca.res$var$coord))])*.8, 
                         k = 16, xlims = c(-3,4), i.mag = 3, v.alpha = 0, e.alpha = 0.03)
      x <- get.Yes.mca(mca.res$var$coord)
      x <- x[grep(paste0("^", g[i]), rownames(x)), ]
      p <- p + geom_text_repel(data = x, 
                           mapping = aes(x = x[, 1], y = x[, 2], label = rownames(x), color = x$cluster), 
                           size = log(comm.sizes[rownames(x)])*.8, 
                           segment.alpha = 0) 
      windows(height = 18, width = 32)
      file <- paste0("genre-comm-hihglight-", g[i])
      file <- paste0(file, ".png")
      file <- paste0("C:/Users/Omar Lizardo/Google Drive/WORK/EARLY/CULTURE/lizardo-genre-communities/plots/", file)
      plot(p)
      savePlot(filename = file, type = "png")
      dev.off()
      i <- i + 1
    }

```

```{r mca plot genre communities cloud of individuals}
    i.dat <- mca.res$ind$coord[, 1:2]
    res.hclust <- eclust(i.dat, "hclust", k = 16, method = "ward.D", graph = FALSE) 
    clus <- res.hclust$cluster
    clus.centers <- aggregate(i.dat, list(clus), mean)
    clus.centers <- clus.centers[, -1]
    res.km <- eclust(i.dat, "kmeans", k = clus.centers, graph = FALSE)
    i.dat <- cbind(i.dat, as.data.frame(factor(res.km$cluster)))
    names(i.dat)[length(i.dat)] <- "cluster"

    windows(height = 18, width = 32)
    p <- ggplot(data = i.dat, mapping = aes(x = i.dat[, 1], y = i.dat[, 2], colour = cluster))
    p <- p + theme_classic() + guides(colour = FALSE, size = FALSE, alpha = FALSE)
    p <- p + geom_text(aes(label = comm.num$omni, size = comm.num$omni), position=position_jitter(width = 0.07,height = 0.07))
    p <- p + labs(x = "Dimension 1", y = "Dimension 2")
    p <- p + theme(axis.title = element_text(size = 18))
    p <- p + geom_hline(yintercept = 0, colour = "gray55") 
    p <- p + geom_vline(xintercept = 0, colour = "gray55") 
    p
    savePlot(filename = "C:/Users/Omar Lizardo/Google Drive/WORK/EARLY/CULTURE/lizardo-genre-communities/plots/genre-comm-mca-cloud.png",
             type = "png")

```

# Genre Demographic Profiles ##

```{r genre community demographic profiles (classical all), warning=FALSE}
    r1 <- plotPreds(y = Classical_134, data = comm.demog.num, plot.num = 1)
    r2 <- plotPreds(y = Classical_170, data = comm.demog.num, plot.num = 2)
    r3 <- plotPreds(y = Classical_184, data = comm.demog.num, plot.num = 3)
    r4 <- plotPreds(y = Classical_173, data = comm.demog.num, plot.num = 4)
    r5 <- plotPreds(y = Classical_153, data = comm.demog.num, plot.num = 5)
    r6 <- plotPreds(y = Classical_61, data = comm.demog.num, plot.num = 6)
    r7 <- plotPreds(y = Classical_144, data = comm.demog.num, plot.num = 7)
    r8 <- plotPreds(y = Classical_189, data = comm.demog.num, plot.num = 8)
    r9 <- plotPreds(y = Classical_240, data = comm.demog.num, plot.num = 9)
    r10 <- plotPreds(y = Classical_216, data = comm.demog.num, plot.num = 10)
    r11 <- plotPreds(y = Classical_171, data = comm.demog.num, plot.num = 11)
    r12 <- plotPreds(y = Classical_225, data = comm.demog.num, plot.num = 12)
    plot.dat <- rbind(r1, r2, r3, r4, r5, r6, r7, r8, r9, r10, r11, r12)
    p <- plotDat(plot.dat, n.row = 2)
    windows(height = 14, width = 24)
    p
    savePlot(filename = "C:/Users/Omar Lizardo/Google Drive/WORK/EARLY/CULTURE/lizardo-genre-communities/plots/genre-comm-classical-demog.png",
             type = "png")

```

```{r genre community demographic profiles (classical selected), warning=FALSE}
    r1 <- plotPreds(y = Classical_134, data = comm.demog.num, plot.num = 1)
    r2 <- plotPreds(y = Classical_170, data = comm.demog.num, plot.num = 2)
    r3 <- plotPreds(y = Classical_173, data = comm.demog.num, plot.num = 3)
    r4 <- plotPreds(y = Classical_61, data = comm.demog.num, plot.num = 4)
    r5 <- plotPreds(y = Classical_240, data = comm.demog.num, plot.num = 5)
    r6 <- plotPreds(y = Classical_216, data = comm.demog.num, plot.num = 6)
    r7 <- plotPreds(y = Classical_171, data = comm.demog.num, plot.num = 7)
    r8 <- plotPreds(y = Classical_144, data = comm.demog.num, plot.num = 8)
    plot.dat <- rbind(r1, r2, r3, r4, r5, r6, r7, r8)
    source("C:/Users/Omar Lizardo/Google Drive/WORK/EARLY/CULTURE/lizardo-genre-communities/R/plotDat.R")
    p <- plotDat(plot.dat, n.row = 2, ts = 12, ls = 10)
    windows(height = 18, width = 20)
    p
    savePlot(filename = "C:/Users/Omar Lizardo/Google Drive/WORK/EARLY/CULTURE/lizardo-genre-communities/plots/genre-comm-demog-classical.png",
             type = "png")
```

```{r genre community demographic profiles (Jazz selected), warning=FALSE}
    r1 <- plotPreds(y = Jazz_245, data = comm.demog.num, plot.num = 1)
    r2 <- plotPreds(y = Jazz_157, data = comm.demog.num, plot.num = 2)
    r3 <- plotPreds(y = Jazz_90, data = comm.demog.num, plot.num = 3)
    r4 <- plotPreds(y = Jazz_222, data = comm.demog.num, plot.num = 4)
    r5 <- plotPreds(y = Jazz_183, data = comm.demog.num, plot.num = 5)
    r6 <- plotPreds(y = Jazz_88, data = comm.demog.num, plot.num = 6)
    r7 <- plotPreds(y = Jazz_87, data = comm.demog.num, plot.num = 7)
    r8 <- plotPreds(y = Jazz_215, data = comm.demog.num, plot.num = 8)
    r9 <- plotPreds(y = Jazz_273, data = comm.demog.num, plot.num = 9)
    r10 <- plotPreds(y = Jazz_253, data = comm.demog.num, plot.num = 10)
    plot.dat <- rbind(r1, r2, r3, r4, r5, r6, r7, r8, r9, r10)
    source("C:/Users/Omar Lizardo/Google Drive/WORK/EARLY/CULTURE/lizardo-genre-communities/R/plotDat.R")
    p <- plotDat(plot.dat, n.row = 2, ts = 12, ls = 10)
    windows(height = 18, width = 20)
    p
    savePlot(filename = "C:/Users/Omar Lizardo/Google Drive/WORK/EARLY/CULTURE/lizardo-genre-communities/plots/genre-comm-demog-Jazz.png",
             type = "png")
```

```{r genre community demographic profiles (Blues selected), warning=FALSE}
    r1 <- plotPreds(y = Blues_179, data = comm.demog.num, plot.num = 1)
    r2 <- plotPreds(y = Blues_137, data = comm.demog.num, plot.num = 2)
    r3 <- plotPreds(y = Blues_55, data = comm.demog.num, plot.num = 3)
    r4 <- plotPreds(y = Blues_265, data = comm.demog.num, plot.num = 4)
    r5 <- plotPreds(y = Blues_234, data = comm.demog.num, plot.num = 5)
    r6 <- plotPreds(y = Blues_190, data = comm.demog.num, plot.num = 6)
    r7 <- plotPreds(y = Blues_152, data = comm.demog.num, plot.num = 7)
    r8 <- plotPreds(y = Blues_237, data = comm.demog.num, plot.num = 8)
    plot.dat <- rbind(r1, r2, r3, r4, r5, r6, r7, r8)
    source("C:/Users/Omar Lizardo/Google Drive/WORK/EARLY/CULTURE/lizardo-genre-communities/R/plotDat.R")
    p <- plotDat(plot.dat, n.row = 2, ts = 12, ls = 10)
    windows(height = 18, width = 20)
    p
    savePlot(filename = "C:/Users/Omar Lizardo/Google Drive/WORK/EARLY/CULTURE/lizardo-genre-communities/plots/genre-comm-demog-Blues.png",
             type = "png")
```

```{r genre community demographic profiles (ClassicRock), warning=FALSE}
    r1 <- plotPreds(y = ClassicRock_272, data = comm.demog.num, plot.num = 1)
    r2 <- plotPreds(y = ClassicRock_227, data = comm.demog.num, plot.num = 2)
    r3 <- plotPreds(y = ClassicRock_151, data = comm.demog.num, plot.num = 3)
    r4 <- plotPreds(y = ClassicRock_133, data = comm.demog.num, plot.num = 4)
    r5 <- plotPreds(y = ClassicRock_287, data = comm.demog.num, plot.num = 5)
    r6 <- plotPreds(y = ClassicRock_187, data = comm.demog.num, plot.num = 6)
    r5 <- plotPreds(y = ClassicRock_250, data = comm.demog.num, plot.num = 7)
    r6 <- plotPreds(y = ClassicRock_211, data = comm.demog.num, plot.num = 8)
    plot.dat <- rbind(r1, r2, r3, r4, r5, r6, r7, r8)
    p <- plotDat(plot.dat, n.row = 2, ts = 12, ls = 8)
    windows(height = 18, width = 18)
    p
    savePlot(filename = "C:/Users/Omar Lizardo/Google Drive/WORK/EARLY/CULTURE/lizardo-genre-communities/plots/genre-comm-demog-ClassicRock.png",
             type = "png")
```

```{r genre community demographic profiles (country), warning=FALSE}
    r1 <- plotPreds(y = Country_200, data = comm.demog.num, plot.num = 1)
    r2 <- plotPreds(y = Country_231, data = comm.demog.num, plot.num = 2)
    r3 <- plotPreds(y = Country_204, data = comm.demog.num, plot.num = 3)
    r4 <- plotPreds(y = Country_69, data = comm.demog.num, plot.num = 4)
    r5 <- plotPreds(y = Country_168, data = comm.demog.num, plot.num = 5)
    r6 <- plotPreds(y = Country_128, data = comm.demog.num, plot.num = 6)
    plot.dat <- rbind(r1, r2, r3, r4, r5, r6)
    p <- plotDat(plot.dat, n.row = 2, ts = 12, ls = 8)
    windows(height = 18, width = 18)
    p
    savePlot(filename = "C:/Users/Omar Lizardo/Google Drive/WORK/EARLY/CULTURE/lizardo-genre-communities/plots/genre-comm-demog-country.png",
             type = "png")
```

```{r genre community demographic profiles (broadway), warning=FALSE}
    r1 <- plotPreds(y = Broadway_114, data = comm.demog.num, plot.num = 1)
    r2 <- plotPreds(y = Broadway_214, data = comm.demog.num, plot.num = 2)
    r3 <- plotPreds(y = Broadway_244, data = comm.demog.num, plot.num = 3)
    r4 <- plotPreds(y = Broadway_122, data = comm.demog.num, plot.num = 4)
    plot.dat <- rbind(r1, r2, r3, r4)
    p <- plotDat(plot.dat, n.row = 1, ts = 18, ls = 16)
    windows(height = 12, width = 18)
    p
    savePlot(filename = "C:/Users/Omar Lizardo/Google Drive/WORK/EARLY/CULTURE/lizardo-genre-communities/plots/genre-comm-demog-broadway.png",
             type = "png")
```

```{r genre community demographic profiles (reggae), warning=FALSE}
    r1 <- plotPreds(y = Reggae_232, data = comm.demog.num, plot.num = 1)
    r2 <- plotPreds(y = Reggae_143, data = comm.demog.num, plot.num = 2)
    plot.dat <- rbind(r1, r2)
    p <- plotDat(plot.dat, n.row = 1, ts = 18)
    windows(height = 12, width = 14)
    p
    savePlot(filename = "C:/Users/Omar Lizardo/Google Drive/WORK/EARLY/CULTURE/lizardo-genre-communities/plots/genre-comm-demog-reggae.png",
             type = "png")
```

```{r genre community demographic profiles (alt), warning=FALSE}
    r1 <- plotPreds(y = Alt_160, data = comm.demog.num, plot.num = 1)
    r2 <- plotPreds(y = Alt_74, data = comm.demog.num, plot.num = 2)
    r3 <- plotPreds(y = Alt_223, data = comm.demog.num, plot.num = 3)
    plot.dat <- rbind(r1, r2, r3)
    p <- plotDat(plot.dat, n.row = 1, ts = 18)
    windows(height = 12, width = 18)
    p
    savePlot(filename = "C:/Users/Omar Lizardo/Google Drive/WORK/EARLY/CULTURE/lizardo-genre-communities/plots/genre-comm-demog-alt.png",
             type = "png")
```

```{r genre community demographic profiles (dance), warning=FALSE}
    r1 <- plotPreds(y = Dance_111, data = comm.demog.num, plot.num = 1)
    r2 <- plotPreds(y = Dance_154, data = comm.demog.num, plot.num = 2)
    r3 <- plotPreds(y = Dance_166, data = comm.demog.num, plot.num = 3)
    r4 <- plotPreds(y = Dance_124, data = comm.demog.num, plot.num = 4)
    plot.dat <- rbind(r1, r2, r3, r4)
    p <- plotDat(plot.dat, n.row = 1, ts = 20, ls = 16)
    windows(height = 10, width = 18)
    p
    savePlot(filename = "C:/Users/Omar Lizardo/Google Drive/WORK/EARLY/CULTURE/lizardo-genre-communities/plots/genre-comm-demog-dance.png",
             type = "png")
```

```{r genre community demographic profiles (metal), warning=FALSE}
    r1 <- plotPreds(y = Metal_242, data = comm.demog.num, plot.num = 1)
    r2 <- plotPreds(y = Metal_140, data = comm.demog.num, plot.num = 2)
    r3 <- plotPreds(y = Metal_257, data = comm.demog.num, plot.num = 3)
    r4 <- plotPreds(y = Metal_115, data = comm.demog.num, plot.num = 4)
    plot.dat <- rbind(r1, r2, r3, r4)
    p <- plotDat(plot.dat, n.row = 1, ts = 16, ls = 14)
    windows(height = 12, width = 18)
    p
    savePlot(filename = "C:/Users/Omar Lizardo/Google Drive/WORK/EARLY/CULTURE/lizardo-genre-communities/plots/genre-comm-demog-metal.png",
             type = "png")
```

```{r genre community demographic profiles (folk), warning=FALSE}
    r1 <- plotPreds(y = Folk_207, data = comm.demog.num, plot.num = 1)
    r2 <- plotPreds(y = Folk_283, data = comm.demog.num, plot.num = 2)
    plot.dat <- rbind(r1, r2)
    p <- plotDat(plot.dat, n.row = 1, ts = 18)
    windows(height = 12, width = 12)
    p
    savePlot(filename = "C:/Users/Omar Lizardo/Google Drive/WORK/EARLY/CULTURE/lizardo-genre-communities/plots/genre-comm-demog-folk.png",
             type = "png")
```

```{r genre community demographic profiles (opera), warning=FALSE}
    r1 <- plotPreds(y = Opera_282, data = comm.demog.num, plot.num = 1)
    r2 <- plotPreds(y = Opera_226, data = comm.demog.num, plot.num = 2)
    p <- plotDat(rbind(r1, r2), n.row = 1, ts = 18, ls = 16)
    windows(height = 12, width = 10)
    p
    savePlot(filename = "C:/Users/Omar Lizardo/Google Drive/WORK/EARLY/CULTURE/lizardo-genre-communities/plots/genre-comm-demog-opera.png",
             type = "png")
```

```{r genre community demographic profiles (gospel), warning=FALSE}
    r1 <- plotPreds(y = Gospel_264, data = comm.demog.num, plot.num = 1)
    r2 <- plotPreds(y = Gospel_284, data = comm.demog.num, plot.num = 2)
    r3 <- plotPreds(y = Gospel_220, data = comm.demog.num, plot.num = 3)
    r4 <- plotPreds(y = Gospel_270, data = comm.demog.num, plot.num = 4)
    plot.dat <- rbind(r1, r2, r3, r4)
    p <- plotDat(plot.dat, n.row = 1, ts = 20, ls = 16)
    windows(height = 10, width = 18)
    p
    savePlot(filename = "C:/Users/Omar Lizardo/Google Drive/WORK/EARLY/CULTURE/lizardo-genre-communities/plots/genre-comm-demog-gospel.png",
             type = "png")
```

```{r genre community demographic profiles (bluegrass), warning=FALSE}
    r1 <- plotPreds(y = Bluegrass_260, data = comm.demog.num, plot.num = 1)
    r2 <- plotPreds(y = Bluegrass_243, data = comm.demog.num, plot.num = 2)
    r3 <- plotPreds(y = Bluegrass_274, data = comm.demog.num, plot.num = 3)
    plot.dat <- rbind(r1, r2, r3)
    p <- plotDat(plot.dat, n.row = 1, ts = 18, ls = 18)
    windows(height = 14, width = 18)
    p
    savePlot(filename = "C:/Users/Omar Lizardo/Google Drive/WORK/EARLY/CULTURE/lizardo-genre-communities/plots/genre-comm-demog-bluegrass.png",
             type = "png")
```

```{r genre community demographic profiles (latin), warning=FALSE}
    r1 <- plotPreds(y = Latin_176, data = comm.demog.num, plot.num = 1)
    r2 <- plotPreds(y = Latin_89, data = comm.demog.num, plot.num = 2)
    r3 <- plotPreds(y = Latin_56, data = comm.demog.num, plot.num = 3)
    r4 <- plotPreds(y = Latin_178, data = comm.demog.num, plot.num = 4)
    r5 <- plotPreds(y = Latin_239, data = comm.demog.num, plot.num = 5)
    r6 <- plotPreds(y = Latin_86, data = comm.demog.num, plot.num = 6)
    plot.dat <- rbind(r1, r2, r3, r4, r5, r6)
    p <- plotDat(plot.dat, n.row = 2, ts = 12, ls = 9)
    windows(height = 18, width = 18)
    p
    savePlot(filename = "C:/Users/Omar Lizardo/Google Drive/WORK/EARLY/CULTURE/lizardo-genre-communities/plots/genre-comm-demog-latin.png",
             type = "png")
```

```{r genre community demographic profiles (rap), warning=FALSE}
    r1 <- plotPreds(y = Rap_191, data = comm.demog.num, plot.num = 1)
    r2 <- plotPreds(y = Rap_73, data = comm.demog.num, plot.num = 2)
    r3 <- plotPreds(y = Rap_218, data = comm.demog.num, plot.num = 3)
    r4 <- plotPreds(y = Rap_289, data = comm.demog.num, plot.num = 4)
    r5 <- plotPreds(y = Rap_156, data = comm.demog.num, plot.num = 5)
    r6 <- plotPreds(y = Rap_255, data = comm.demog.num, plot.num = 6)
    plot.dat <- rbind(r1, r2, r3, r4, r5, r6)
    p <- plotDat(plot.dat, n.row = 2, ts = 14, ls = 8)
    windows(height = 18, width = 18)
    p
    savePlot(filename = "C:/Users/Omar Lizardo/Google Drive/WORK/EARLY/CULTURE/lizardo-genre-communities/plots/genre-comm-demog-rap.png",
             type = "png")
```

```{r genre community demographic profiles (controck), warning=FALSE}
    r1 <- plotPreds(y = ContRock_278, data = comm.demog.num, plot.num = 1)
    r2 <- plotPreds(y = ContRock_177, data = comm.demog.num, plot.num = 2)
    r3 <- plotPreds(y = ContRock_149, data = comm.demog.num, plot.num = 3)
    r4 <- plotPreds(y = ContRock_288, data = comm.demog.num, plot.num = 4)
    r5 <- plotPreds(y = ContRock_161, data = comm.demog.num, plot.num = 5)
    r6 <- plotPreds(y = ContRock_254, data = comm.demog.num, plot.num = 6)
    plot.dat <- rbind(r1, r2, r3, r4, r5, r6)
    p <- plotDat(plot.dat, n.row = 2, ts = 12, ls = 8)
    windows(height = 18, width = 18)
    p
    savePlot(filename = "C:/Users/Omar Lizardo/Google Drive/WORK/EARLY/CULTURE/lizardo-genre-communities/plots/genre-comm-demog-controck.png",
             type = "png")
```

```{r genre community demogPophic profiles (pop), warning=FALSE}
    r1 <- plotPreds(y = Pop_228, data = comm.demog.num, plot.num = 1)
    r2 <- plotPreds(y = Pop_251, data = comm.demog.num, plot.num = 2)
    r3 <- plotPreds(y = Pop_249, data = comm.demog.num, plot.num = 3)
    r4 <- plotPreds(y = Pop_263, data = comm.demog.num, plot.num = 4)
    r5 <- plotPreds(y = Pop_181, data = comm.demog.num, plot.num = 5)
    r6 <- plotPreds(y = Pop_99, data = comm.demog.num, plot.num = 6)
    plot.dat <- rbind(r1, r2, r3, r4, r5, r6)
    p <- plotDat(plot.dat, n.row = 2, ts = 16, ls = 10)
    windows(height = 18, width = 18)
    p
    savePlot(filename = "C:/Users/Omar Lizardo/Google Drive/WORK/EARLY/CULTURE/lizardo-genre-communities/plots/genre-comm-demog-pop.png",
             type = "png")
```

### 2023-08-05 old_Rmds/Old/trad-analysis-latest.Rmd
re-arranged folders and moved content from old folder

---
title: "Discovering Focused Microgenre Communities"
author: "Omar Lizardo"
date: "`r Sys.Date()`"
output:
html_document: default
---

# Setup
```{r setup}
    knitr::opts_chunk$set(include=FALSE, echo = TRUE, warning = FALSE, message = FALSE)
    require("depmixS4")
    require("FactoMineR")
    require("factoextra")
    require("ggraph")
    require("ggplot2")
    require("haven")
    require("here")   
    require("patchwork")
    require("qgraph")
    require("sjPlot")
    require("tidyverse")
```

# Data Wrangling
```{r Importing and creating two mode data frame of people by genres}
    taste.dat <- read_dta("C:/Users/Omar Lizardo/Google Drive/MISC DATA SOURCES/SSI-2012/SSI2012.dta")
    taste.dat <- taste.dat %>% 
      dplyr::select("id", ends_with(c("lis", "like")), -starts_with("none")) %>% 
      dplyr::select(c(1:41)) %>% 
      na.omit() %>% 
      mutate(Classical = classicallike * classicallis,
             Opera = operalike * operalis,
             Jazz = jazzlike * jazzlis,
             Broadway = bwaystlike * bwaystlis,
             Easy = moodezlike * moodezlis, 
             Bigband = bbandlike * bbandlis,
             Classic_Rock = croldlike * croldlis,
             Country = countrylike * countrylis,
             Bluegrass = blueglike * blueglis,
             Folk = folklike * folklis,
             Gospel = hymgoslike * hymgoslis,
             Latin = latlpsallike * latspsallis,
             Rap_Hip_Hop = raphiphoplike * raphiphoplis,
             Blues_RandB = blurblike * blurblis,
             Reggae = reggaelike * reggaelis,
             Pop = toppoplike * toppoplis,
             Contemp_Rock = controcklike * controcklis,
             Indie_Alt = indaltlike * indaltlis,
             Dance_Club = danclublike * danclublis,
             Heavy_Metal = hvymtllike * hvymtllis
             ) %>%  #people are linked to genres that the both like and listen to
    dplyr::select(id, Classical:Heavy_Metal)
    g.names <- names(taste.dat[, 2:ncol(taste.dat)])

```

# Traditional Analytic Techniques
```{r Factor Analysis}
    f1 <- c(12, 13, 14, 15, 19)
    f2 <- c(1, 2, 3, 4, 5, 6)
    f3 <- c(7, 16, 17, 18, 20)
    f4 <- c(8, 9, 10, 11)
    gen.groups <- list(f1, f2, f3, f4)
    efa.res <- factanal(taste.dat[, g.names], 
                        factors = 4, rotation = "promax",
                        scores = "regression")
    png(here("Plots", "Regular", "genre-efa-regular.png"), 
        height = 3900, width = 6500)
    qgraph(efa.res$loadings, groups = gen.groups, borders = FALSE, 
          edge.labels = TRUE, minimum = 0.05, 
          edge.label.cex = 0.8, edge.width = 0.8)
```

```{r Latent Class Analysis}
    lca.dat <- taste.dat[, g.names]
    set.seed(25)
    mod1 <- mix(list(Classical~1, Opera~1, Jazz~1, Broadway~1, Easy~1, Bigband~1, Classic_Rock~1, Country~1, Bluegrass~1, Folk~1, Gospel~1, Latin~1, Rap_Hip_Hop~1, Blues_RandB~1, Reggae~1, Pop~1, Contemp_Rock~1, Indie_Alt~1, Dance_Club~1, Heavy_Metal~1), 
                data=lca.dat, # the dataset to use
                nstates = 6, # the number of latent classes
                family=list(multinomial("identity"), multinomial("identity"), 
                             multinomial("identity"), multinomial("identity"),
                             multinomial("identity"), multinomial("identity"), 
                             multinomial("identity"), multinomial("identity"),
                             multinomial("identity"), multinomial("identity"), 
                             multinomial("identity"), multinomial("identity"),
                             multinomial("identity"), multinomial("identity"), 
                             multinomial("identity"), multinomial("identity"),
                             multinomial("identity"), multinomial("identity"), 
                             multinomial("identity"), multinomial("identity")),
               respstart=runif(240))
    fmod1 <- fit(mod1, verbose=FALSE)
    lca.res <- as_tibble(posterior(fmod1)) #collecting latent class probabilities
```

```{r Data table for plotting latent classes}
    lc.plot.data <- bind_cols(lca.dat, lca.res) %>% 
        gather(key="measure", value="value", Classical:Heavy_Metal) %>% 
        mutate(state = factor(state, labels = c("Class 1", "Class 2", "Class 3", "Class 4", "Class 5", "Class 6"))) %>% 
        mutate(value = factor(value, labels = c("no", "yes")))
```

```{r Plotting latent classes}
    p <- ggplot(data = lc.plot.data, mapping = aes(x = measure, fill = value)) 
    p <- p + theme_sjplot()
    p <- p + geom_bar(position="fill")  
    p <- p + scale_fill_brewer(palette = "Paired")
    p <- p + facet_wrap(~ state, nrow = 2) + coord_flip() 
    p <- p + theme(
                axis.text = element_text(size = 12),
                legend.position = "bottom",
                strip.text = element_text(size = 18)
                )

    p.lca <- p + labs(x = "", y = "") + labs(fill="")
    p.lca
    save_plot(here("Plots", "Regular", "genre-lca-regular.png"), 
              width = 40, height = 25)
```

```{r Prepping data for MCA, performing MCA, and generating label size and individual alpha vectors}
    yesno.labs <- function(x) {
        factor(x, labels = c("No", "Yes"))
        }
    mca.dat <- taste.dat[, g.names] %>% 
        mutate(across(1:ncol(taste.dat)-1, yesno.labs))
    mca.res <- MCA(mca.dat, ncp = 10, graph = FALSE,  method = "indicator") #performing MCA
    mca.dim.vars <- as_tibble(mca.res$var$coord) #modality coordinates
    mca.dim.ind <- as_tibble(mca.res$ind$coord) #individual coordinates
    var.names <- rownames(mca.res$var$coord) #vector of label names
    text.size1 <- log(apply(mca.res$var$contrib[,c(1:2)], 1, sum))*3 #vector of sizes based on contributions
    text.size2 <- log(apply(mca.res$var$contrib[,c(3:4)], 1, sum))*3  #vector of sizes based on contributions
    ind.alpha1 <- apply(mca.res$ind$contrib[,c(1:2)], 1, mean)/ max(apply(mca.res$ind$contrib[,c(1:2)], 1, mean))  #vector of alphas based on contributions
    ind.alpha2<- apply(mca.res$ind$contrib[,c(3:4)], 1, mean)/ max(apply(mca.res$ind$contrib[,c(3:4)], 1, mean)) #vector of alphas based on contributions
```

```{r MCA biplots}
    p <- ggplot(data = mca.dim.vars, mapping = aes(x = `Dim 1`, y = `Dim 2`))
    p <- p + geom_text(aes(label = var.names), size = text.size1, color = "blue", check_overlap = TRUE) #cloud of modalities
    p <- p + geom_hline(yintercept = 0, colour = "gray45") 
    p <- p + geom_vline(xintercept = 0, colour = "gray45") 
    p <- p + labs(x = "Dimension 1", y = "Dimension 2") 
    p <- p + geom_point(data = mca.dim.ind, aes(x = `Dim 1`, y = `Dim 2`), color = "red", alpha = ind.alpha1) #cloud of individuals
    p <- p + theme_sjplot()
    p1 <- p + theme(
                    panel.grid.major.y = element_line(color = "grey90"),
                    panel.grid.major.x = element_line(color = "grey90"),
                    axis.title = element_text(size = 18), 
                    axis.text = element_text(size = 18),
                    axis.line.x = element_blank(),
                    axis.line.y = element_blank(),
                    legend.position = "none"
                    )
    p <- ggplot(data = mca.dim.vars, mapping = aes(x = `Dim 3`, y = `Dim 4`))
    p <- p + geom_text(aes(label = var.names), size = text.size1, color = "blue", check_overlap = TRUE) #cloud of modalities
    p <- p + geom_hline(yintercept = 0, colour = "gray45") 
    p <- p + geom_vline(xintercept = 0, colour = "gray45") 
    p <- p + labs(x = "Dimension 3", y = "Dimension 4") 
    p <- p + geom_point(data = mca.dim.ind, aes(x = `Dim 1`, y = `Dim 2`), color = "red", alpha = ind.alpha1) #cloud of individuals
    p <- p + xlim(-1.5, 2)
    p <- p + theme_sjplot()
    p2 <- p + theme(
                    panel.grid.major.y = element_line(color = "grey90"),
                    panel.grid.major.x = element_line(color = "grey90"),
                    axis.title = element_text(size = 18), 
                    axis.text = element_text(size = 18),
                    axis.line.x = element_blank(),
                    axis.line.y = element_blank(),
                    legend.position = "none"
                    )
    p.in <- fviz_eig(mca.res, ncp = 8, linecolor = "red")  #inset bar plot showing eigenvalue distribution
    p.in <- p.in + labs(y = "", x = "", title = "") 
    p.in <- p.in + theme_sjplot2()
    p.in <- p.in + theme(
                    plot.background = element_rect(colour = "grey60", size = 0.25),
                    panel.grid.major.y = element_blank(),
                    panel.grid.major.x = element_blank(),
                    )
    p3 <-  p1 / p2 #combining plots using patchwork
    p4 <- p3 + inset_element(p.in, 0.8, 0, 1, 0.5) #inset plot using patchwork
    p4
    save_plot(here("Plots", "Regular", "genre-mca-regular.png"), 
              width = 35, height = 40)
```

### 2023-08-05 Functions/fav.probs.R

@@ -1,0 +1,34 @@
+fav.probs <- function(y, w) {
+  f <- as.formula(paste(y, "favgen", sep = "~"))
+  res <- lm(f, data = w)
+  #get predicted probabilities#
+  fav.dat <- data.frame(plot_model(res, type = "pred", terms = "favgen")$data) %>% 
+    mutate(x = factor(x, labels = levels(w$favgen))) %>% 
+    dplyr::select(c("x", "predicted", "conf.low", "conf.high")) %>% 
+    dplyr::rename(cat.labs = 1,
+                  prob = 2,
+                  lo = 3,
+                  hi = 4) %>% 
+    mutate(fav.gen = factor(1:20),
+           sc.prob = scale(prob),
+           sc.lo = scale(lo),
+           sc.hi = scale(hi))
+  seg.dat <- filter(fav.dat, prob > 0.01)
+  p <- ggplot(data = fav.dat, 
+              mapping = aes(y = cat.labs, x = sc.prob, 
+                            color = fav.gen))
+  p <- p + geom_vline(aes(xintercept = 0), linewidth = 1, color = "pink")
+  p <- p + geom_point(size = 2.75)
+  #p <- p + geom_segment(data = seg.dat,
+                        #mapping = aes(x = sc.lo, u = cat.labs, 
+                                      #xend = sc.hi, yend = cat.labs), 
+                        #alpha = 0.2, linewidth = 1.15)
+  p <- p + gghighlight(sc.prob > 0.5)
+  p <- p + theme_minimal()
+  p <- p + ggtitle(gsub('_',' ', y))
+  p <- p + theme(axis.title = element_blank(),
+                 legend.position = "none",
+                 axis.text.y = element_blank(),
+                 title = element_text(size = 12)) 
+  return(list(prob = fav.dat, plot = p))
+  }

### 2023-08-05 Functions/mfav.probs.R

@@ -1,0 +1,8 @@
+mfav.probs <- function(g.names, x, w) {
+  g.names <- grep(x, names(w), value = TRUE)
+  res <- lapply(g.names, fav.probs, w = w)
+  names(res) <- g.names
+  probs.list <- lapply(res, "[[", 1)
+  plots.list <- lapply(res, "[[", 2)
+  return(list(probs = probs.list, plots = plots.list))        
+  }

### 2023-08-05 Functions/mpred (1).probs.R

@@ -1,0 +1,8 @@
+mpred.probs <- function(x, w) {
+  g.names <- grep(x, names(w), value = TRUE)
+  res <- lapply(g.names, pred.probs, w = w)
+  names(res) <- g.names
+  mods.list <- lapply(res, "[[", 1)
+  probs.list <- lapply(res, "[[", 2)
+  return(list(mods = mods.list, probs = probs.list))
+  }

### 2023-08-05 Functions/pred (1).probs.R

@@ -1,0 +1,42 @@
+pred.probs <- function(y, w) {
+    library(splines)
+    #run regression#
+    mod <- "bs(educ_n) + bs(age_n) + bs(objclass_n) + 
+                parented + percclass + female + raceeth + region"
+    f <- as.formula(paste(y, mod, sep = "~"))
+    res <- lm(f, data = w)
+    #get predicted probabilities#
+    educ <- data.frame(plot_model(res, type = "eff", terms = "educ_n")$data) %>% 
+                    mutate(x = factor(x, labels = levels(w$educ)),
+                           var.type = 1) 
+    paeduc <- data.frame(plot_model(res, type = "eff", terms = "parented")$data) %>% 
+                    mutate(x = factor(x, labels = levels(w$parented)),
+                           var.type = 2) 
+    objclass <- data.frame(plot_model(res, type = "eff", terms = "objclass_n")$data) %>% 
+                    mutate(x = factor(x, labels = levels(w$objclass)),
+                           var.type = 3) 
+    subjclass <- data.frame(plot_model(res, type = "eff", terms = "percclass")$data) %>% 
+                    mutate(x = factor(x, labels = levels(w$percclass)),
+                           var.type = 4) 
+    age <- data.frame(plot_model(res, type = "eff", terms = "age_n")$data) %>% 
+                    mutate(x = factor(x, labels = levels(w$age)),
+                           var.type = 5) 
+    gender <- data.frame(plot_model(res, type = "eff", terms = "female")$data) %>% 
+                    mutate(x = factor(x, labels = levels(w$female)),
+                           var.type = 6) 
+    race <- data.frame(plot_model(res, type = "eff", terms = "raceeth")$data) %>% 
+                    mutate(x = factor(x, labels = levels(w$raceeth)),
+                           var.type = 7) 
+    region <- data.frame(plot_model(res, type = "eff", terms = "region")$data) %>% 
+                    mutate(x = factor(x, labels = levels(w$region)),
+                           var.type = 8) 
+    #put predicted probabilities into data frame#
+    pred.dat <- bind_rows(educ, paeduc, objclass, subjclass, age, gender, race, region) %>% 
+        dplyr::select(c("x", "predicted", "conf.low", "conf.high", "var.type")) %>% 
+        dplyr::rename(cat.labs = 1,
+                      prob = 2,
+                      lo = 3,
+                      hi = 4) %>% 
+        mutate(var.type = factor(var.type))
+    return(list(mod = res, preds = pred.dat))
+  }

### 2023-08-05 old_Rmds/Old/plot.preds.R

@@ -1,0 +1,23 @@
+plot.preds <- function(x) {
+  cont.x <- filter(x, var.type == 2 | var.type == 3)
+  cat.x <- filter(x, var.type == 1 | var.type == 4 | var.type == 5 | var.type == 6)
+  p <- ggplot(mapping = aes(x = cat.labs, group = var.type))
+  p <- p + geom_point(data = x, 
+                      mapping = aes(y = prob, color = var.type), size = 2)
+  p <- p + geom_line(data = cont.x, 
+                     mapping = aes(x = prob, color = var.type), size = 0.8)
+  p <- p + geom_ribbon(data = cont.x, 
+                       mapping = aes(ymin = lo, ymax = hi, 
+                                     fill = var.type, color = var.type), 
+                       alpha = 0.15, linetype = 0)
+  p <- p + geom_segment(data = cat.x, 
+                        mapping = aes(y = lo, x = cat.labs, yend = hi, xend = cat.labs, 
+                                      color = var.type), alpha = 0.25, size = 1)
+  p <- p + theme_sjplot()
+  p <- p + coord_flip()
+  p <- p + ggtitle(t)
+  p <- p + theme(axis.title = element_blank(),
+                 legend.position = "none")
+  p <- p + geom_hline(yintercept = 0, color = "gray55")
+  return(p)
+  }

### 2023-08-05 old_Rmds/Old/pred.probs_old.R

@@ -1,0 +1,74 @@
+pred.probs <- function(y) {
+    #run regression#
+    mod <- "poly(as.numeric(educ), 2) + parented +
+                poly(as.numeric(age), 3) + 
+                objclass + percclass + female + raceeth + region"
+    f <- as.formula(paste(y, mod, sep = "~"))
+    res <- lm(f, data = demog.dat)
+    #get predicted probabilities#
+    c <- 0.8
+    educ.preds <- predictions(res, 
+                              newdata = datagrid(educ = levels(demog.dat$educ)),
+                              conf_level = c, objclass = "Middle Class", educ = "Some College", region = "New England")
+    paeduc.preds <- predictions(res, 
+                                newdata = datagrid(parented = levels(demog.dat$parented)),
+                                conf_level = c, objclass = "Middle Class", educ = "Some College", region = "New England")
+    objclass.preds <- predictions(res, 
+                                  newdata = datagrid(objclass = levels(demog.dat$objclass)),
+                                  conf_level = c, objclass = "Middle Class", educ = "Some College", region = "New England")
+    classid.preds <- predictions(res, 
+                                 newdata = datagrid(percclass = levels(demog.dat$percclass)),
+                                 conf_level = c, objclass = "Middle Class", educ = "Some College", region = "New England")
+    age.preds <- predictions(res, 
+                             newdata = datagrid(age = levels(demog.dat$age)),
+                             conf_level = c, objclass = "Middle Class", educ = "Some College", region = "New England")
+    gender.preds <- predictions(res, 
+                                newdata = datagrid(female = levels(demog.dat$female)),
+                                conf_level = c, objclass = "Middle Class", educ = "Some College", region = "New England")
+    race.preds <- predictions(res, 
+                              newdata = datagrid(raceeth = levels(demog.dat$raceeth)),
+                              conf_level = c, objclass = "Middle Class", educ = "Some College", region = "New England")
+    region.preds <- predictions(res, 
+                                  newdata = datagrid(region = levels(demog.dat$region)),
+                                  conf_level = c, FUN_factor = unique)
+    pred.list <- list(educ.preds, paeduc.preds, objclass.preds, classid.preds, age.preds, gender.preds, race.preds, region.preds)
+    k <- ncol(educ.preds)
[…]

### 2023-08-05 old_Rmds/Old/predProbs.R

@@ -1,0 +1,16 @@
+predProbs <- function(y, x, w, z = 1.96, p = 2, x.type = "num") {
+    y <- eval(substitute(as.name(y)), w)
+    x <- eval(substitute(as.name(x)), w)
+    if (x.type == "num") {
+        mymod <- glm(y ~ poly(as.numeric(x), p), family = "binomial", data = w)
+        }
+    if (x.type == "fac") {
+        mymod <- glm(y ~ x, family = "binomial", data = w)
+        }
+    mypred <- prediction(mymod)
+    mypred$lo <- mypred$fitted - (z*mypred$se.fitted)
+    mypred$hi <- mypred$fitted + (z*mypred$se.fitted)
+    m <- aggregate(mypred, by = list(x), "mean")
+    return(m[, c("Group.1", "fitted", "se.fitted", "lo", "hi")])
+    }
+

### 2023-08-05 old_Rmds/Old/taste-comm-analysis.R

@@ -1,0 +1,608 @@
+# load functions ####
+# local
+source("C:/Users/olizardo/Google Drive/WORK/EARLY/CULTURE/lizardo-genre-communities/niceMCAplot.R")
+source("C:/Users/olizardo/Google Drive/WORK/EARLY/CULTURE/lizardo-genre-communities/get.Yes.hc.R")
+source("C:/Users/olizardo/Google Drive/WORK/EARLY/CULTURE/lizardo-genre-communities/get.Yes.mca.R")
+source("C:/Users/olizardo/Google Drive/WORK/EARLY/CULTURE/lizardo-genre-communities/getEdges.R")
+source("C:/Users/olizardo/Google Drive/WORK/EARLY/CULTURE/lizardo-genre-communities/getCommDat.R")
+source("C:/Users/olizardo/Google Drive/WORK/EARLY/CULTURE/lizardo-genre-communities/genreGroups.R")
+# general 
+source("C:/Users/olizardo/Google Drive/R/Functions/cultnet.R") 
+source("C:/Users/olizardo/Google Drive/R/Functions/predPlot.R")
+
+# Importing and creating two mode data frame of people by genres ####
+library(foreign)
+taste.dat <- read.dta("C:/Users/olizardo/Google Drive/MISC DATA SOURCES/SSI-2012/SSI2012.dta")
+var.ind <- grep("*lis|like$", names(taste.dat), value = TRUE)
+var.ind <- var.ind[1:40]
+taste.dat <- subset(taste.dat, select = c("id", var.ind))
+taste.dat <- na.omit(taste.dat)
+for (i in 2:21) { 
+  j = i + 20
+  taste.dat[,i] <- taste.dat[,i] * taste.dat[,j] #people are linked to genres that the both like and listen to
+  }
+gen.labs <- c("Classical", "Opera", "Jazz", "Broadway", "Easy", "Big Band", "Oldies", "Country",
+                                  "Blueg", "Folk", "Gospel", "Latin", "Rap", "Blues", "Reggae", 
+                                  "Pop", "Rock", "Alt", "Dance", "Metal")
+names(taste.dat)[c(2:21)] <- gen.labs
+taste.dat <- taste.dat[c(1:21)]
+
+edge.dat <- getEdges(taste.dat) # Creating Edgelist Data 
+#Regular analyses
+# Factor Analysis ####
+f1 <- c(12, 13, 14, 15, 19)
+f2 <- c(1, 2, 3, 4, 5, 6)
[…]

### 2023-08-05 old_Rmds/blah.R

@@ -1,0 +1,76 @@
+predProbs <- function(y, x, z = 1.96) {
+    f <- as.formula(paste(y, x, sep = " ~ "))
+    res <- glm(f, data = demog.dat, family = "binomial")
+    pred <- prediction(res)
+    pred$lo <- pred$fitted - (z*pred$se.fitted)
+    pred$hi <- pred$fitted + (z*pred$se.fitted)
+    m <- pred %>% 
+        group_by(eval(as.name(x), pred)) %>% 
+        summarize(m.fitted = mean(fitted),
+                  m.se.fitted = mean(se.fitted),
+                  m.lo = mean(lo),
+                  m.hi = mean(hi))
+    names(m) <- c("Var", "Prob", "S.E", "Lo", "Hi")
+    return(m)
+}
+
+Pred.x <- function(y, x.list){
+    x.pred.list <- list()
+    for (i in 1:length(x.list)) {
+        x.pred.list[[i]] <- predProbs(y, x.list[i])
+        x.pred.list[[i]]$type <- i
+    }
+    names(x.pred.list) <- x.list
+    return(list.rbind(x.pred.list))
+}
+
+Pred.y <- function(y.list, x.list, pred.cols = 2) {
+    y.pred.list <- list()
+    for (i in 1:length(y.list)) {
+        Pred <- Pred.x(y.list[i], x.list)
+        y.pred.list[[i]] <- Pred[pred.cols]
+    }
+    res <- list.cbind(y.pred.list)
+    res <- cbind(Pred$Var, Pred$type, res)
+    names(res) <- c("Var", "Type", y.list)
+    return(res)
+}
+res <- Pred.y(y.list = micro.g.names, 
+              x.list = c("educ", "age", "female", "percclass", "raceeth"))
+res.long <- res %>% 
+    pivot_longer(
+        cols = c(micro.g.names),
+        names_to = "Genre",
+        values_to = "Prob"
+    )
+scale.res <- scale(res[,micro.g.names], center = TRUE)
+scale.res <- cbind(res[, c("Var", "Type")], scale.res)
+scale.res.long <- scale.res %>% 
+    pivot_longer(
+        cols = c(micro.g.names),
+        names_to = "Genre",
+        values_to = "Prob"
+    )
+
+plot.dat <- filter(scale.res.long, str_detect(Genre, "Classical"))
+p <- ggplot(data = plot.dat, 
+            aes(x = Prob, y = Var, group = Genre, color = Type)) 
+p <- p + geom_point(size = 2.8) 
[…]

### 2023-08-05 old_Rmds/ca.clust.R

@@ -1,0 +1,39 @@
+ca.clust <- function(x) {
+    require(expm)
+    require(stats)
+    r <- nrow(x)
+    c <- ncol(x)
+    D.r <- matrix(0, r, r)
+    D.c <- matrix(0, c, c)
+    diag(D.r) <- rowSums(x)
+    diag(D.c) <- colSums(x)
+    C.r <- svd(solve(D.r) %*% x %*% solve(D.c) %*% t(x))
+    C.c <- svd(solve(D.c) %*% t(x) %*% solve(D.r) %*% x)
+    e.Cr <- C.r$d
+    e.Cc <- C.c$d
+    ev.Cr <- C.r$u
+    ev.Cc <- C.c$u
+    eig.Cr <- data.frame(Pos = 1:nrow(x), Eig = e.Cr)
+    eig.Cc <- data.frame(Pos = 1:ncol(x), Eig = e.Cc)
+
+    S.r <- x%*% solve(D.c) %*% t(x)
+    S.c <- t(x)%*% solve(D.r) %*% x
+    L.r <- D.r - S.r
+    L.c <- D.c - S.c
+    Lr.svd <- svd(L.r)
+    Lc.svd <- svd(L.c)
+    e.Lr <- Lr.svd$d
+    e.Lc <- Lc.svd$d
+    ev.Lr <- Lr.svd$u
+    ev.Lc <- Lc.svd$u
+    eig.Lr <- data.frame(x = 1:nrow(x), y = e.Lr)
+    eig.Lc <- data.frame(x = 1:ncol(x), y = e.Lc)
+    res <- list(S.r = S.r, S.c = S.c,
+                L.r = L.r, L.c = L.c,
+                e.Cr = e.Cr, e.Cc = e.Cc,
+                ev.Cr = ev.Cr, ev.Cc = ev.Cc,
+                e.Lr = e.Lr, e.Lc = e.Lc,
+                ev.Lr = ev.Lr, ev.Lc = ev.Lc)
+    res <- lapply(res, round.list <- function(x) {round(x, 2)})
+    return(res)
+    }

### 2023-08-05 old_Rmds/demog.R

@@ -1,0 +1,37 @@
+ed.labs <- c("< High School", "High School/GED", "Associate", "Some College", "Bachelor's", "Postgraduate")
+demog.dat <- read_dta("C:/Users/Omar Lizardo/Google Drive/MISC DATA SOURCES/SSI-2012/SSI2012.dta") %>% 
+    dplyr::select(c("id", "age", "agemid", "female", "raceeth", 
+                    "nodipdeg", "hsged", "somcol", "aadeg", "bach", "ma", 
+                    "docprof", "incmid", "income", "percclass")) %>% 
+    as_factor() %>% 
+    mutate(educ = if_else(nodipdeg == "yes", 1, 
+                          if_else(hsged == "yes", 2, 
+                                  if_else(aadeg == "yes", 3, 
+                                          if_else(somcol == "yes", 4,
+                                                  if_else(bach == "yes", 5,
+                                                          if_else(ma == "yes" | docprof == "yes", 6, 1)))))),
+           educ = factor(educ, labels = ed.labs),
+           raceeth = fct_recode(raceeth,
+                                "Asian" = "Asian",
+                                "Black" = "Black",
+                                "Hisp." = "Hispanic",
+                                "White" = "White",
+                                "Mult./Other" = ">1 race",
+                                "Mult./Other" = "other"),
+           female = fct_recode(female, 
+                               "Men" = "male", 
+                               "Women" = "female")
+    ) %>% 
+    dplyr::select(-c("nodipdeg", "hsged", "somcol", "aadeg", "bach", "ma", "docprof")) %>% 
+    right_join(lclust.dat, by = "id") %>% 
+    mutate(id = as.integer(id),
+           omnivore = rowSums(across(where(is.double)))) %>% 
+    mutate(omnicat = case_when(omnivore %in% 1 ~ 1,
+                               omnivore %in% 2:3 ~ 1,
+                               omnivore %in% 4:6 ~ 2,
+                               omnivore %in% 7:9 ~ 3,
+                               omnivore %in% 10:20 ~ 4),
+           omnicat = factor(omnicat, 
+                            labels = c("One to Three", "Four to Six", "Seven to Nine", "Ten or More"))) %>%  
+    mutate(educ.n = as.numeric(educ)) %>% 
+    na.omit()

### 2023-08-05 old_Rmds/old_plot.R

@@ -1,0 +1,26 @@
+#plot predicted probabilities
+f <- as.formula(paste(y, 1, sep = "~"))
+b <- lm(f, data = demog.dat)$coefficients
+con.x <- filter(pred.dat, var.type == 1 | var.type == 3 | var.type == 4 | var.type == 5)
+cat.x <- filter(pred.dat, var.type == 2 | var.type == 6 | var.type == 7 | var.type == 8)
+p <- ggplot(data = pred.dat,
+            mapping = aes(x = cat.labs, y = prob, 
+                          fill = var.type, color = var.type, group = var.type))
+p <- p + geom_hline(yintercept = b, color = "red", size = 0.25)
+p <- p + geom_point(size = 2.5)
+p <- p + geom_line(data = con.x, size = 0.75)
+p <- p + geom_segment(data = cat.x,
+                      mapping = aes(y = lo, x = cat.labs, yend = hi, xend = cat.labs), 
+                      alpha = 0.2, size = 1.15)
+p <- p + geom_ribbon(data = con.x, 
+                     mapping = aes(ymin = lo, ymax = hi), 
+                     alpha = 0.15, linetype = 0)
+p <- p + theme_sjplot()
+p <- p + ggtitle(gsub('_',' ', y))
+p <- p + theme(axis.title = element_blank(),
+               legend.position = "none")
+p <- p + scale_x_discrete(limits=rev)
+p <- p + expand_limits(y = c(0, NA))
+p <- p + scale_color_brewer(palette = "Dark2")
+p <- p + scale_fill_brewer(palette = "Dark2")
+p <- p + coord_flip()

### 2023-08-05 old_Rmds/pred.dots.R

@@ -1,0 +1,20 @@
+pred.dots <- function(w, l, f = 0) {
+  dat <- w
+  dat <- lapply(dat, transform, sc.prob = scale(prob))
+  dat <- bind_rows(dat, .id = "micro.gen") %>% 
+    mutate(micro.gen = factor(micro.gen)) %>% 
+    filter(cat.labs %in% l)   
+  p <- ggplot(data = dat, 
+              mapping = aes(x = cat.labs, y = sc.prob, 
+                            color = micro.gen, group = micro.gen))
+  p <- p + geom_point(size = 4) 
+  p <- p + theme_minimal()
+  p <- p + labs(y = "Scaled Predicted Probability", x = "")
+  p <- p + theme(legend.position = "bottom", 
+                 legend.title = element_blank(),
+                 axis.text = element_text(size = 14))
+  if (f == 1) {
+    p <- p + coord_flip()
+    }
+  return(p)
+}

### 2023-08-05 old_Rmds/pred.lines.R

@@ -1,0 +1,17 @@
+pred.lines <- function(w, l, d.size = 2.75, xt.size = 12) {
+  dat <- w
+  dat <- lapply(dat, transform, sc.prob = scale(prob))
+  dat <- bind_rows(dat, .id = "micro.gen") %>% 
+    mutate(micro.gen = factor(micro.gen)) %>% 
+    filter(cat.labs %in% l)   
+  p <- ggplot(data = dat, 
+              mapping = aes(x = cat.labs, y = sc.prob, 
+                            color = micro.gen, group = micro.gen))
+  p <- p + geom_point(size = d.size) + geom_line()
+  p <- p + theme_minimal()
+  p <- p + labs(y = "Scaled Predicted Probability", x = "")
+  p <- p + theme(legend.position = "bottom", 
+                 legend.title = element_blank(),
+                 axis.text = element_text(size = xt.size))
+  return(p)
+  }

### 2023-08-05 old_Rmds/trash.R

@@ -1,0 +1,32 @@
+```{r MCA eigenvalue comparison of regular and link clustered data}
+    factor_commvars <- function(x) {
+        factor(x, labels = c("No", "Yes"))
+      }
+    taste.mca.dat <- taste.dat %>% 
+        mutate(across(2:ncol(taste.dat), factor_commvars))
+    mca.macro <- MCA(taste.mca.dat[,2:ncol(taste.mca.dat)], 
+                     ncp = 10, graph = FALSE)
+
+    taste.micro.mca.dat <- taste.micro.dat %>% 
+        mutate(across(2:ncol(taste.micro.dat), factor_commvars))
+    mca.macro <- MCA(taste.micro.mca.dat[,2:ncol(taste.micro.mca.dat)], 
+                     ncp = 50, graph = FALSE)
+    eig.macro <- get_eig(mca.macro)[, 1]
+    mca.micro <- MCA(taste.micro.mca.dat[, 2:ncol(taste.micro.mca.dat)], 
+                     ncp = 20, graph = FALSE)
+    eig.micro <- get_eig(mca.micro)[, 1]
+    p <- fviz_eig(mca.macro, ncp = 10, choice = "eigenvalue") 
+    p <- p + geom_hline(yintercept = 1, color = "red")
+    p <- p + geom_vline(xintercept = length(eig.macro[eig.macro >= 1]))
+    #p <- p + scale_y_continuous(breaks = seq(0, 8 , 1), limits = c(0,8))
+    p <- p + ggtitle("Macrogenres")
+    p1 <- p + scale_x_discrete(breaks = seq(1, 10, by = 1))
+
+    p <- fviz_eig(mca.micro, ncp = 50, choice = "eigenvalue") 
+    p <- p + geom_hline(yintercept = 1, color = "red")
+    p <- p + geom_vline(xintercept = length(eig.micro[eig.micro >= 1]))
+    #p <- p + scale_y_continuous(breaks = seq(0, 8 , 1), limits = c(0,8))
+    p <- p + ggtitle("Microgenres")
+    p2 <- p + scale_x_discrete(breaks = seq(0, 50, by = 5))
+    p1 + p2 + plot_annotation(title = "MCA Scree Plot")
+```

### 2023-08-05 main.tex

@@
         \caption{}
-        \label{fig:age-latin}
+        \label{fig:age-salsa}
     \end{subfigure}
@@
 In fact, it has been under-researched and, for the most part, ignored.
-I include it in the following analysis due to a shining exception to this pattern, represented in a high-quality recent study by \citep{Bachmayer2014-pk} which strongly suggests internal microgenre differentiation within this broad macrogenre label relevant to the reception and consumption side.
+I include it in the following analysis due to a shining exception to this pattern, represented by a qualitative study by \citet{Bachmayer2014-pk}, which strongly suggests internal microgenre differentiation within this broad macrogenre label relevant to the reception and consumption side.
 These differentiations are keyed to hierarchical distinctions across Salsa microgenres based on social status and the concomitant internalization of class-based aesthetic dispositions \citep{lizardo2012reconceptualizing}.
@@
 The next three columns show the predictors of choosing each microgenre variation extracted from cutting the macrogenre label branch of the dendrogram at the required height.
-Looking at the first column, we would have concluded that choosing Salsa is not predicted by either respondent's ($p = 0.26$) or parent's ($0.17$) education, suggesting that taste for this genre is orthogonal to cultural capital and status.
+Looking at the first column, we would have concluded that choosing Salsa is not predicted by either respondent's ($p = 0.26$) or parent's ($p = 0.17$) education, suggesting that taste for this genre is orthogonal to cultural capital and status.
 Instead, Salsa is mainly a genre preferred by young respondents (negative linear effect of age) who identify as Hispanic (no surprise there) and as women ($p < 0.05$).
@@
 
-I proposed to do this using recent developments in the discovery of \textit{overlapping communities} in networks \citep{ahn_etal10}, which partially answers two of the challenges of macrogenre critics: The fact that actual genres are overlapping and not crisply bounded.
-The fact that there is hidden heterogeneity within the broad labels we usually focus on.
+I proposed to do this using recent developments in the discovery of \textit{overlapping communities} in networks \citep{ahn_etal10}, which partially answers two of the challenges of macrogenre critics: The fact that actual genres are overlapping and not crisply bounded, and the fact that there is hidden heterogeneity within the broad labels we usually focus on.
 Our analysis contrasted the application of the usual techniques to the same data, conceived in the usual ``macro" way, and \textit{after} upping the relationality and discovering the microgenres hidden within.

### 2023-08-05 qmd/03_real-dends.qmd
Updated real dead qmd

@@
     knitr::opts_chunk$set(include=FALSE, echo = TRUE, warning = FALSE, message = FALSE)
-    require("dendextend")
-    require("here")
-    require("RColorBrewer")
+    library(dendextend)
+    library(here)
+    library(RColorBrewer)
+    library(tidyverse)
 ```
@@
     dend.macro <- cut(lclust.dend, h = 8) #cutting at macrogenre level
+    a <- data.frame(g.size = sapply(dend.macro$lower, nleaves)) #macrogenres as ordered in dendrogram results
+    b <- data.frame(g.size = colSums(taste.dat[, 2:21]), 
+                    g.names = names(colSums(taste.dat[, 2:21]))) #original macrogenre sizes
+    c <- right_join(a, b) #joining data frames by macrogenre sizes to get macrogenre labels ordered by dendrogram results
+    names(dend.macro$lower) <- c$g.names #naming macrogenre dendrogram list
 ```
@@
     d3 <- dend.macro$lower$Metal %>% 
-      set("labels", c(rep("", nleaves(d3)))) %>% 
+      set("labels", c(rep("", nleaves(dend.macro$lower$Metal)))) %>% 
+      set("branches_lwd", value = 4) %>% 
       set("branches_k_color", value = brewer.pal(3, "Dark2"), k = 3)
@@
     d4 <- dend.macro$lower$Salsa %>% 
-      set("labels", c(rep("", nleaves(d4)))) %>% 
+      set("labels", c(rep("", nleaves(dend.macro$lower$Salsa)))) %>% 
+      set("branches_lwd", value = 4) %>% 
       set("branches_k_color", value = brewer.pal(3, "Dark2"), k = 3)
@@
     png(here("Plots", "Dend", "metal-branches.png"), height = 900, width = 1600)
-    plot(d3, axes = FALSE) %>% 
-      par(cex = 5) %>% 
+    plot(d3, axes = FALSE) 
+      par(cex = 5) 
       title(xlab = "", ylab = "", main = "Metal")
@@
     png(here("Plots", "Dend", "salsa-branches.png"), height = 900, width = 1600)
-    plot(d4, axes = FALSE) %>% 
-      par(cex = 5) %>% 
-      title(xlab = "", ylab = "", main = "Metal")
-
+    plot(d4, axes = FALSE)  
+      par(cex = 5) 
+      title(xlab = "", ylab = "", main = "Salsa")
 ```

### 2023-08-05 response.tex
Updates from Overleaf

\documentclass[a4paper,12pt]{extarticle}
\usepackage[utf8]{inputenc}
\usepackage{geometry}
    \geometry{a4paper}
\title{Response to Memo}

\begin{document}
\maketitle
\section{Response to Editor's Letter}
The editor noted that the manuscript received a mixed response from the reviewers, with R1 being more positive and R2 and R3 more critical. The more critical reviewers were missing a substantive takeaway for the sociology of taste beyond the proposed methods. The editor's main recommendation was to ``to connect your findings more directly to Poetics (among other) papers that focus on `intra-genre' variation\ldots and culturally dissonant or `discrepant tastes' in music ---ideas often generated through discourse-based or ethnographic approaches that seem to be largely validated by your approach and findings.'' I decided to follow this last route. The last version of the paper trudged through multiple macro genres and their micro-variations in a somewhat listless way. For this version of the paper, I decided to focus on two macrogenres---Metal and Salsa---for which I could find some pointers in the scholarly literature regarding microgenre variation and then show how the link clustering approach can uncover some of the predicted variations in survey data. I think this more focused approach works better and is more effective in showcasing the validity of the proposed approach. I hope the reviewers agree.

\section{Response to R1}
This reviewer found the previous version of the manuscript to be ``incredibly exciting and smart'' and admired the ``relational thinking'' at the basis of the proposed approach. The reviewer also appreciated the broader implications of the argument and approach for social science data analysis more generally.

\subsection{Suggestions I took up}
\begin{itemize}
    \item R1 Suggested I acknowledge precursors of the proposed approach, such as Goldberg's Relational Class Analysis (RCA). I added a relevant discussion of this and other precursors in section 3.1.  
    \item R1 sagaciously pointed to the formal similarity between splitting a macrogenre into microgenre variation and the principle of ``equifinality'' and multiple ``causal recipes'' from Qualitative Comparative Analysis. I address this issue in footnote 3.  
    \item R1 also smartly suggested that I clarify the distinction between the micro-variations uncovered by the link-clustering approach and the more qualitative ones people may make using folk (or even official) classifications. I now address these issues in the concluding section. 
\end{itemize}

\subsection{Suggestions I didn't take up}
\begin{itemize}
    \item R1 suggested that I may perhaps expand on the more ``polemical'' strands of the previous version of the paper, comparing traditional methods against those that exploit the relationality inherent in most data. Since I have excised most of this discussion in this version of the paper, and since going in this direction would have taken the paper too far afield, I decided not to go in this direction. I retained some hints that most methods are affected by the microgenre critique and that adopting the techniques proposed in this paper can help across the board. 
\end{itemize}

\section{Response to R2}
R2 characterized the paper as offering ``an innovative approach to analyzing existing survey datasets on cultural tastes,'' noting that the strength of the paper lied primarily in its ``methodological contribution,'' but that ``the theoretical context and implications of this contribution could be better specified.''

\subsection{Suggestions I took up}
\begin{itemize}
    \item R2 noted that the introduction ended abruptly and that led the reader to lack context as to what the substance and main implications of the analysis that was to follow. To address this issue, I have revised the introduction to provide more context as to the substance of the approach and added a transition paragraph into the methods that provides a synoptic summary of what is to follow. 
    \item R2 suggests that I ``better motivate'' the microgenre concept. I have done this in two ways. First, the current version of the introduction develops the idea in more detail and reviews previous work that points to the concept in more substantive contexts. Second, the idea is also developed in more detail when reviewing previous work focused on the two genre case studies (sections 5.1 and 5.2), which also deploy or hint at the concept in a more substantive context. 
    \item R2 wondered how the microgenres induced from the link-clustering approach and whether the ``micro'' label even fits (e.g., why not meso), which are similar to the wonderings R1 had. As noted, I now address the issues of correspondence (maybe) and scale (relative) in the discussion section.
    \item R2 encouraged me to spell out the implications of the analysis, which they found ``rather narrow'' in the last version, particularly concerning ``suggested directions forward for key debates.'' I think that the macrogenre case studies do that effectively, and I have revised the discussion to reflect that.  
\end{itemize}

\subsection{Suggestions I didn't take up}
\begin{itemize}
    \item R2 complained about the ``lengthy'' methodological setup and suggested that I do more to outline the contribution ``up front'' as a way to obviate the need for a toy example. I tried versions of this, but it didn't work for me. I also like the toy example and think it is necessary for people without a technical background to get behind the black box of what the link-clustering is doing. So I kept it (although I removed the discussion of other methods, as noted so this section is less lengthy).  
\end{itemize}

\section{Response to R3}
R3 thought that the previous version of the paper did a ``fine job of completing what it sets out to do'' but didn't think that the paper made much of a theoretical or empirical contribution, thinking it read more like an introductory methods piece, suitable for pedagogy in a methods class. R3, like R2, was missing a more substantive takeaway that would address ``ongoing debates.'' The reviewer also complained about silly language.

I couldn't do much about the silly language (sorry!). Still, as noted, I rewrote the methods section focusing on two macrogenres selected because either debate existed in the literature or previous work suggested the existence of microgenre variations. I think the presented results address these debates head-on and show how the proposed method can shed light on them and move the discussion forward, so hopefully I did a bit to address this part of the reviewer's critique. 
\end{document}

### 2023-08-05 blah.tex
Updates from Overleaf

        Measures to values: \\
    \begin{itemize}
        \item[--] Education.- Ordinal variable: (1) Less than high school, (2) High school, (3) Associate's Degree, (4) Some college, (5) Bachelor's degree, (6) MA degree, (7) Doctoral or Professional degree.
        \item[--] Parent's College.- Binary variable: At least one parent obtained a college degree (1).
        \item[--] Age.- Ordinal variable: (1) 18--19, (2) 20--25, (3) 25--29, (4) 30--34, (5) 35--39, (6), 40--44, (7), 45--49, (8), 50--54, (9) 55--59, (10), 60--64, (11) 65--69, (12) 70--74, (13) 75--79, (14) 80+.
    \end{itemize}

### 2023-08-05 title-page.tex
Updates from Overleaf

\documentclass[a4paper,12pt]{extarticle}
\usepackage[utf8]{inputenc}
\usepackage{blindtext}
\usepackage{geometry}
    \geometry{a4paper}

\title{From Macrogenres to Microgenres via Relationality\footnote{Reserved for acknowledgements.}}

\author{Omar Lizardo \\ \small Department of Sociology \\ \textit{\small University of California, Los Angeles}\thanks{375 Portola Plaza, 265 Haines Hall, Los Angeles California, 90095.} \\ \small olizardo@soc.ucla.edu}

\begin{document}
\maketitle

\end{document}

### 2023-08-05 bio.tex

\documentclass[a4paper,12pt]{extarticle}
\usepackage[utf8]{inputenc}
\usepackage{geometry}
    \geometry{a4paper}
\title{Author's Biography}

\begin{document}
\maketitle
Omar Lizardo (He/Him) is the LeRoy Neiman Term Chair Professor in the Department of Sociology at the University of California, Los Angeles. He studies Culture, Cognition, Networks, Consumption, Institutions, Organization, and Social Theory. His work has appeared in such journals as \textit{American Sociological Review}, \textit{Social Forces}, \textit{Sociological Forum}, \textit{Sociological Theory}, \textit{Theory \& Society}, \textit{Journal for the Theory of Social Behaviour}, \textit{Poetics}, and \textit{Social Networks}. He is the co-editor of the \textit{Handbook of Classical Sociological Theory} published by Springer and a co-author of the book \textit{Measuring Culture} published by Columbia University Press. He serves on the editorial board of \textit{Social Forces}, \textit{Journal for the Theory of Social Behaviour}, \textit{Theory \& Society}, and \textit{Poetics}. He is also a member of the Board of Reviewing Editors for the journal \textit{Science}, an Associate Editor for \textit{Discover Data}, one of the current lead editors of \textit{Sociological Theory}, and a former chair of the American Sociological Association's Section on the Sociology of Culture. His recent publications have focused on the decline of cultural participation in Southern Europe in the wake of the Eurozone crisis, methods for analyzing relational similarities in two-mode networks, and theorizing analytical approaches to the study of cultural phenomena.
\end{document}

### 2023-08-05 highlights.tex

\documentclass[a4paper,12pt]{extarticle}
\usepackage[utf8]{inputenc}
\usepackage{geometry}
    \geometry{a4paper}
\title{Highlights}

\begin{document}
\maketitle
\begin{itemize}
    \item Recent work has begun to use relational approaches to study taste
    \item However, this work relies on vague genre labels
    \item These labels hide macrogenres, overstating boundaries
    \item I propose a link-clustering approach
    \item The proposed approach uncovers valid microgenres
\end{itemize}
\end{document}

Recent work in the sociology of taste has begun to grapple with the relational properties of traditional survey-based data using techniques inspired by network analysis. Despite productive results from this endeavor, critics rightly question the face and ecological validity of the vague macrogenre labels included in standard arts participation surveys (e.g., Classical, Rock, Rap), which feed into these novel methods. In this paper, I propose a link-clustering approach for discovering focused microgenres from standard survey-based information on cultural tastes, exploiting the underlying relational patterns realized by the indirect connectivity structure of genres (via people) in a two-mode network. The link-clustering approach partially answers two of the challenges of macrogenre critics: The fact that actual genres are overlapping and not crisply bounded and the fact that there is hidden heterogeneity within the broad labels we usually focus on. The results reveal an intuitive partition of traditional macrogenres into focused microgenres, capable of separating audiences along relevant sociodemographic markers, such as education, gender and ethnoracial identities, and age/generation.

### 2023-08-05 main.tex

@@
 \usepackage{geometry}
+\usepackage{tablefootnote}
     \geometry{a4paper}
@@
 
-\title{Discovering Focused Microgenre Communities}
+\title{From Macrogenres to Microgenres via Relationality}
 
@@
 \subsubsection*{Abstract} 
-Recent work in the sociology of taste has begun to grapple directly with the relational properties of traditional survey-based data using techniques inspired by network analysis.
-Despite the generally salutary results from this endeavor, critics rightly question the face and ecological validity of the vague macrogenre labels included in standard arts participation surveys (e.g., Classical, Rock, Rap).
-To deal with this issue, in this paper, I propose a link-clustering approach for discovering focused microgenres from standard survey-based information on cultural tastes, one that exploits the underlying relational patterns realized by the indirect connectivity structure of genres (via people) in a two-mode network.
+Recent work in the sociology of taste has begun to grapple with the relational properties of traditional survey-based data using techniques inspired by network analysis.
+Despite productive results from this endeavor, critics rightly question the face and ecological validity of the vague macrogenre labels included in standard arts participation surveys (e.g., Classical, Rock, Rap), which feed into these novel methods.
+In this paper, I propose a link-clustering approach for discovering focused microgenres from standard survey-based information on cultural tastes, exploiting the underlying relational patterns realized by the indirect connectivity structure of genres (via people) in a two-mode network.
 The link-clustering approach partially answers two of the challenges of macrogenre critics: The fact that actual genres are overlapping and not crisply bounded and the fact that there is hidden heterogeneity within the broad labels we usually focus on.
-To demonstrate the validity of the approach, I contrast the application of the usual techniques to the same data, conceived in the usual ``macro" way, and after discovering hidden microgenres.
-The results reveal an intuitive partition of traditional macrogenres into focused microgenres, capable of separating audiences along relevant sociodemographic markers, such as education, ethnoracial identity, subjective class identification, and age/generation.
+The results reveal an intuitive partition of traditional macrogenres into focused microgenres, capable of separating audiences along relevant sociodemographic markers, such as education, gender and ethnoracial identities, and age/generation.
 \newpage
@@
 Recent work in the sociology of taste has blurred the distinction, foundational for much early work, between ``relational'' network data (codifying the relationships between people) and survey data (codifying the relationship between people and ``variables'').
-The basic idea is that all data, whether collected purposefully as ``network'' data collected as part of a social survey, is \textit{relational} data.
+The basic idea is that all data, whether collected purposefully as ``network'' data collected or gathered as part of a traditional social survey, is \textit{relational} data.
 The main difference is the types of entities that are related \citep{borgatti_everett97}.
-Any data source that can be stored in matrix form has ``modes'' (how many types of entities are related) and ``ways'' (the number of entities linked by a relation, usually two at a time).
+Any data source that can be stored in matrix form has ``modes'' (the types of linked entities) and ``ways'' (the number of entities linked by a relation, usually two at a time).
 The standard network data set is ``one mode'' (we usually look at one type of entity at a time, like people, organizations, schools, countries, and the like) and two ``ways'' (people-by-people or organization-by-organization pairs).
@@
 Accordingly, a spate of recent work has begun the job of theoretical translation, enriching the first-generation of work in the sociology of taste with network-flavored concepts.
-Accordingly, \citet{pachucki2010cultural} extend Ronald Burt's theory of structural holes for understanding how people can bridge gaps not just in one-mode person-to-person networks but in two-mode person-to-culture networks.
-Following this lead, \citet{lizardo14} provides a metric based on Burt's conception of network efficiency that is meant to characterize the slippery concept of ``omnivorousness" concerning genres and cultural forms people engage in.
+For instance, \citet{pachucki2010cultural} extend Ronald Burt's theory of structural holes for understanding how people can bridge gaps not just in one-mode person-to-person networks but in two-mode person-to-culture networks.
+Following this lead, \citet{lizardo14} provides a metric for such holes in cultural structure based on Burt's conception of network efficiency that is meant to characterize the slippery concept of ``omnivorousness" concerning genres and cultural forms people engage in.
 This approach goes beyond just summing or counting people's cultural engagements to consider the audience overlap between the genres themselves.
@@
 A similar approach, based on ideas of positional equivalence in networks, can be extended beyond the study of beliefs and social attitudes to identify respondents who share cultural schemas \citep{goldberg2011mapping}.
-\citet{lizardo18} adapts techniques first developed for the study of economic complexity in two-mode networks of geographic sites and products/technologies for the characterization of genres (e.g., popular versus niche) and audience (e.g., omnivore versus ``univore'') characteristics in survey data on cultural tastes.
+\citet{lizardo18} adapts techniques first developed for the study of economic complexity in two-mode networks of geographic sites and products/technologies \citep{hidalgo2009building} for characterizing genres (e.g., popular versus niche) and audiences (e.g., omnivore versus ``univore'') in survey data on cultural tastes.
 
@@
 
-Thus, for DiMaggio, genres are dual entities precisely in Breiger's sense defined above.
+Thus, for DiMaggio, genres are dual entities precisely in Breiger's (1974) sense defined above.
 Genre categories are composed of the audiences that engage them (are subsets of the larger set of people).
@@
 
-Like much network theorizing, this conceptualization is elegant but gets messy in the application.
+Like much network theorizing, this conceptualization is elegant but gets messy in application.
 As \citet[149]{lena2015relational} has noted, ``[n]o ordering principle is as fundamental to culture as genre'' yet, none is also as vexed.
-Lena raises one issue: Sociologists have relational intuitions about genres but tend to default to musicological definitions for convenience.
+Lena raises one fundamental issue: Sociologists have relational intuitions about genres but tend to default to musicological definitions for convenience.
 Thus, when it comes to considering which genres to include in a survey on cultural tastes, the tendency is to pick off-the-shelf from the menu of genre categories.
@@
 For convenience’s sake, survey data must settle on a ``middle'' level of categorization so as not to tax respondents' patience (or knowledge).
-Thus, the standard ``lists'' of cultural genres, such as ``Pop Art,'' ``Romantic Comedy," or ``Blues.'' However, as recent work points out, people, venues, fandoms, scenes, subcultures, communities, organizations, critics, gatekeepers, and even states and other powerful institutions, make sociologically relevant distinctions within macrogenres categories \citep{hesmondhalgh2005subcultures, Holt2007, Van_Poecke2018, Hield2014-xe}.
+Thus, the standard ``lists'' of cultural genres, such as ``Pop Art,'' ``Romantic Comedy," or ``Blues.'' However, as recent work points out, people, venues, fandoms, scenes, subcultures, communities, organizations, critics, gatekeepers, and even states and other powerful institutions, make sociologically relevant distinctions \textit{within} macrogenres categories \citep{hesmondhalgh2005subcultures, Holt2007, Van_Poecke2018, Hield2014-xe}.
 Genres may also develop and accumulate variations as they ``travel'' across production, dissemination, and consumption sites in their historical trajectory \citep{Lena2012}.
@@
 
-For instance, within the Sheffield ``musicworld,'' the broad genre category of ``Folk''---one usually included in the typical survey questionnaire like the one used in this paper---can refer to at least three existing microgenres: A ``traditionalist'' one---see \citep{Lena2012}---composed mainly of late nineteenth and early twentieth English ballads documenting working-class and mining-town life, a ``scene'' genre centered on 1960s political protest and pop songs (a la Dylan) or more contemporary ``avant-garde'' genre featuring reflexive, sometimes parodic takes on the previous two, and centered on blurring performer-audience boundaries.
+For instance, within the Sheffield ``musicworld,'' the broad genre category of ``Folk''---one usually included in the typical survey questionnaire like the one used in this paper---can refer to at least three existing microgenres: A ``traditionalist'' one---see \citep{Lena2012}---composed mainly of late nineteenth and early twentieth English ballads documenting working-class and mining-town life, a ``scene'' genre centered on 1960s political protest and pop songs (a la Bob Dylan) or more contemporary ``avant-garde'' genre featuring reflexive, sometimes parodic takes on the previous two, and centered on blurring performer-audience boundaries.
 As Hield and Crossley \citeyearpar[197]{Hield2014-xe} note, ``[t]hese and other such distinctions are not registered in\ldots surveys.''
@@
 
-But what happens when all the data we have (as with long-standing surveys such as the Survey for Public Participation in the Arts or the General Social Survey) is at the macrogenre label?
+But what happens when the data at our disposal (as with long-standing surveys such as the Survey for Public Participation in the Arts or the General Social Survey) is at the macrogenre label?
 Both overlapping boundary and microgenre heterogeneity critics of traditional genre labels would say to ignore these data and collect new data that does not rely on misleading macrogenre labels.
 I propose another solution: {\em Exploit the inherent relationality embedded in survey data responses} \citep{goldberg2011mapping, boutyline2017belief, lizardo18}.
-
 More specifically, my point will be that by exploiting the inherent relationality already contained in the usual survey data (when treated as two-mode network data), old data can reveal insights that pertain to the very features sociological critics of the macrogenre label concept say are missing.
-In particular, it is possible to use embedded sets of relations between people and genres to discover the heterogeneous microgenre communities critics say are hidden by macrogenre labels (thus, my point is that these are hidden but not necessarily absent).
-This approach is thus ideal for making new use of old data.
+In particular, it is possible to use embedded sets of relations between people and genres to discover the heterogeneous microgenre communities critics say are hidden by macrogenre labels.
+This approach is thus ideal for making new use of old data while, at the same time, sidestepping some, but not all, the limitations of the microgenre critique.
 
@@
 In this sense, I followed a path already trailed by others.
-For instance, Goldberg's \citeyearpar{goldberg2011mapping} {\em Relational Class Analysis} (RCA) ``classifies the people'' (in the terms developed below when reviewing standard data-analytic approaches in the sociology of taste) included a survey by partitioning a person-by-person matrix built from higher order similarities (sums of differences of differences) between each pair of person's corresponding response vector coding their stances (e.g., like, dislike, neutral) toward a set of cultural objects (e.g., genres, attitude items).
-
-Boutyline's 
-\citeyearpar{boutyline2017improving} {\em Correlational Class Analysis} (CCA) also classifies the people but this time by using the absolute value of the correlation distance between response vectors to build the person-by-person similarity matrix.
+For instance, Goldberg's \citeyearpar{goldberg2011mapping} {\em Relational Class Analysis} (RCA) ``classifies the people''  included a survey by partitioning a person-by-person matrix built from higher order similarities (sums of differences-of-differences) between each pair of person's corresponding response vector coding their stances (e.g., like, dislike, neutral) toward a set of cultural objects (e.g., genres, attitude items).
+Boutyline's \citeyearpar{boutyline2017improving} {\em Correlational Class Analysis} (CCA) also classifies the people but this time by using the absolute value of the correlation distance between response vectors to build the person-by-person similarity matrix.
 Boutyline and Vaisey's {\em Belief Network Analysis} (BNA) classifies the objects people connect to (in their case, beliefs, but could also be genres) by creating a weighted object network, where the weight of the tie between two objects (attitude toward government spending and attitude toward immigration) is given by the magnitude of their correlation coefficient in the survey.
@@
 As we will see, I propose a complementary and synergistic approach with these previous efforts.
-More to the point, the relational identification of microgenres should be able to improve the applicability of techniques like RCA, CCA, and BNA (and related techniques) because, just like standard statistical approaches (like Factor Analysis, Principal Component Analysis, Latent Class Analysis and so forth), and even techniques (like Multiple Correspondence Analysis that are sometimes opposed to the traditional statistical ones, these newfangled relational techniques are also dragged down by the macrogenre curse.
+More to the point, the relational identification of microgenres should be able to improve the applicability of techniques like RCA, CCA, and BNA (and related techniques) because, just like standard statistical approaches (like Factor Analysis, Principal Component Analysis, Latent Class Analysis and so forth), and even techniques like Multiple Correspondence Analysis sometimes opposed to the traditional statistical ones, these newfangled relational techniques are also dragged down by the macrogenre curse.
 Thus, RCA and CCA are bound to compute relationality and correlation distances within people but have to rely on vague macrogenre labels.
@@
 All quantitative techniques researchers use in the sociology of taste must work with the (broad) genre categories included in the survey.
-As such, they are powerless to deal with these (reasonable) objections.
+As such, they are powerless to deal with the (reasonable) objections brought up by the microgenre dissenters.
 
@@
 
-\section{Analytic Appproach}
+In the remainder of the paper, I introduce the link-clustering approach to eliciting microgenres using the relational information embedded in the joint choices (and avoidance) of macrogenres available in traditional survey data.
+I first introduce the motivation behind the method using a simple ``toy example'' and then move to the more substantive ground in two ``case studies,'' concerning two genres for which substantiated proposals exist in the literature regarding micro-variations.
+I show that the proposed approach extracts novel insights from survey data that help address, shed light on, and adjudicate these debates at a population level while providing novel leads to future work.
+
+\section{Analytic Approach}
 \subsection{Data to be Used in the Study}
@@
 As noted at the outset, this requires that we stop looking at the usual survey data that forms the bulk of empirical material in the quantitative study of taste as ``survey data'' (e.g., data collected on the characteristics of individuals in the form of ``variables'').
-This presumption is baked into traditional techniques (like Factor Analysis or Latent Class Analysis) that fit statistical models to such data.
-It is also embedded in ``relational'' techniques like Multiple Correspondence Analysis which, while not steeped in the preoccupations of standard statistical inference (although it could be), divert our attention to the indirect relations between macrogenres (or between people), usually conceptualized as distances in a social space.
+As noted, this assumption is baked into traditional techniques (like Factor Analysis or Latent Class Analysis) that fit statistical models to such data.
+But it is also embedded in ``relational'' techniques like Multiple Correspondence Analysis which, while not steeped in the preoccupations of standard statistical inference (although they could be), divert our attention to the indirect relations between macrogenres (or between people), usually conceptualized as distances in a social space \citep{flemmen_etal18}.
 This kind of indirect relationality is fine and dandy.
@@
 \begin{figure}[t!]
+    \captionsetup[subfigure]{font=footnotesize,labelfont=footnotesize}
      \centering
@@
 The similarity of one person-to-genre edge to another, when both edges point to the same genre \citep{ahn_etal10}, should be proportional to the overlap between the ``cultural ego networks'' of the two people at the tail end of the edges.
-As \citet{lizardo14} defines it, for any respondent $i$, in a survey on cultural taste, the cultural ego network is simply the set of genres $\{G_1, G_2,\dots G_k\}$ chosen by the person.
+As \citet{lizardo14} defines it, for any respondent $i$, in a survey on cultural taste, the cultural ego network is simply the set of genres $\{G_1, G_2,\dots G_k\}$ chosen by the person, where $k$ is the total number of genres chosen (``omnivorousness by volume'').
 
@@
 In Figure~\ref{fig:link-toy1}, these two links are highlighted in yellow by the ``strung out'' edgelist and are shown in red in the corresponding bipartite subgraph shown in Figure~\ref{fig:link-toy2}.
-The similarity ($S$) between the two links is then given by:
+The usual Jaccard distance then gives the similarity ($S$) between the two links:
 
@@
 Where $n_+(P_1)$ is the cultural ego network of Person 1 and $n_+(P_3)$ is the cultural ego network of Person 3.
-The formula says that the similarity between two person-to-genre links sharing a genre, in this case, the similarity between the $P_1-G_2$ edge and the $P_3-G_2$ edge, is given by the intersection of Person 1's and Person 3's cultural ego network divided by their union (also known as Jaccard's coefficient).
-When the cultural ego networks of two people are the same $S=1$, when they are completely disjoint, sharing no genres, meaning the intersection is the empty set,  $S = 0$.
+The formula says that the similarity between two person-to-genre links sharing a genre, in this case, the similarity between the $P_1-G_2$ edge and the $P_3-G_2$ edge, is given by the intersection of Person 1's and Person 3's cultural ego network divided by their union.
+When the cultural ego networks of two people are the same $S=1$ when they are completely disjoint $S = 0$.
 All other cases of person-to-genre edges sharing the same genre return a number between zero and one ($0 > S < 1$).\footnote{Note that the only substantive similarities we care about are between person-to-genre edges that share the same genre but have different people attached to them at the other end.
-All other person-to-genre edges featuring people connected to different genres are set to zero.} In the toy example case, $P_1$ and $P_3$ consume two genres out of the four possible ones they could consume in common, resulting in an edge similarity score of $\frac{2}{4} = 0.50$.
+All other person-to-genre edges similarities featuring people connected to different genres are set to zero.} In the toy example case, $P_1$ and $P_3$ consume two genres out of the four possible ones they could consume in common, resulting in an edge similarity score of $\frac{2}{4} = 0.50$.
 
 \begin{figure}
+    \captionsetup[subfigure]{font=footnotesize,labelfont=footnotesize}
     \centering
-     \begin{subfigure}[b]{0.6\textwidth}
+     \begin{subfigure}[b]{0.4\textwidth}
         \includegraphics[width=1.0\textwidth]{Toy/toy-sim.png}
@@
     \end{subfigure}
-     \begin{subfigure}[b]{0.6\textwidth}
+     \begin{subfigure}[b]{0.4\textwidth}
         \includegraphics[width=1.0\textwidth]{Toy/toy-dis.png}
@@
 Note that moving from the top down, the dendrogram splits person-to-genre links according to the macrogenre label.
-That is macrogenre information is preserved in the clustering and can be recovered by splitting the dendrogram at a height where the number of clusters is equal to the original number of macrogenres (in this toy case, four).
+Macrogenre information is preserved in the clustering and can be recovered by splitting the dendrogram at a height where the number of clusters equals the original number of macrogenres (in this toy case, four).
 Moving from the bottom up, the hierarchical clustering of the dissimilarity matrix yields {\em link communities} \citep{ahn_etal10}, in which both people nodes, but, most crucially, genres nodes are assigned to different clumps.
-In the limiting case, each person-to-genre link is assigned to a cluster, namely, the dendrogram's bottom-most ``leaves.'' The more interesting thing is that as we move up to a point below macrogenres clusters and above the leaves, we see a partition of {\em varieties} of macrogenres.
+In the limiting case, each person-to-genre link is assigned to a single cluster, namely, the dendrogram's bottom-most ``leaves.''
+
+The more interesting thing is that as we move up to a point below macrogenres clusters and above the leaves, we see a partition of {\em varieties} of macrogenres.
 For instance, macrogenre $G4$ is split into two focused microgenre varieties.
-The first is attached to persons $P2$ and $P4$, and the second is attached to persons $P3$ and $P5$, respectively.
+The first is attached to people $P2$ and $P4$, and the second is attached to people $P3$ and $P5$, respectively.
 The idea is that the macrogenre nodes (e.g., ``Classical'') assigned to different clumps represent micro-variations of the macrogenre label that differ primarily relationally or structurally; different ``types'' of ``Classical'' are different because their audiences make distinct choices {\em with respect} to the other genres in the survey.
@@
         \centering
-        \includegraphics[width=1.0\textwidth]{Plots/Dend/all-branches-macro.png}
+        \includegraphics[width=1.0\textwidth]{Plots/Dend/macro.png}
         \caption{c = 8, k = 20}
@@
         \centering
-        \includegraphics[width=1.0\textwidth]{Plots/Dend/all-branches-macro-labels.png}
+        \includegraphics[width=1.0\textwidth]{Plots/Dend/macro-lab.png}
         \caption{c = 8, k = 20}
@@
     \end{subfigure} 
-     \begin{subfigure}[b]{0.32\textwidth}
+     \begin{subfigure}[b]{0.5\textwidth}
         \centering
-        \includegraphics[width=1.0\textwidth]{Plots/Dend/classic-rock-branches.png}
-        \caption{c = 3, k = 12}
-        \label{fig:dend-micro-classic-rock}
+        \includegraphics[width=1.0\textwidth]{Plots/Dend/metal-branches.png}
+        \caption{k = 3}
+        \label{fig:dend-micro-metal}
     \end{subfigure}
-     \begin{subfigure}[b]{0.32\textwidth}
+     \begin{subfigure}[b]{0.5\textwidth}
         \centering
-        \includegraphics[width=1.0\textwidth]{Plots/Dend/blues-branches.png}
-        \caption{c = 3, k = 5}
-        \label{fig:dend-micro-blues}
-    \end{subfigure}
-     \begin{subfigure}[b]{0.32\textwidth}
-        \centering
-        \includegraphics[width=1.0\textwidth]{Plots/Dend/opera-branches.png}
-        \caption{c = 3, k = 2}
-        \label{fig:dend-micro-opera}
+        \includegraphics[width=1.0\textwidth]{Plots/Dend/salsa-branches.png}
+        \caption{k = 3}
+        \label{fig:dend-micro-salsa}
     \end{subfigure}
@@
 Recall that the data features 2,263 people choosing up to 20 macrogenre labels.
-When strung out as an edgelist, this results in 9,216 person-to-genre connections in the data, the resulting $9216 \times 9,216$ matrix, containing Jaccard similarities among person-to-genre links sharing a node in either of the two modes, is then the input to an agglomerative hierarchical clustering algorithm using Ward's \citep{ward63} method.
+When strung out as an edgelist, this results in 9,216 person-to-genre connections in the data, the resulting $9216 \times 9,216$ matrix, containing Jaccard similarities among person-to-genre links sharing a node in either of the two modes, is then the input to an agglomerative hierarchical clustering algorithm using Ward's \citeyearpar{ward63} method.
+
 The hierarchical clustering process proceeds as follows.
 Initially, each person-to-genre link is assigned to a singleton cluster.
-Then, in the second time step, the pairs of links with the largest Jaccard similarities are put in the same clump.
+Then, in the second time step, the pairs of links with the largest Jaccard similarities (smallest distances) are put in the same clump.
 This continues at each time step, where pairs of links with the largest similarity are chosen, and their respective communities are merged.
@@
 From left to right, these are Classic Rock/Oldies, Pop/Top 40, Country, Classical, Easy Listening, Blues/R\&B, Contemporary Rock, Rap/Hip Hop, Jazz, Gospel, Dance/Club, Indie Alternative, Latin, Broadway/Musicals, Heavy Metal/Hard Rock, Reggae, Big Band, Folk, Bluegrass, and Opera.
-As shown in Figures~\ref{fig:dend-micro-classic-rock}-\ref{fig:dend-micro-opera}, microgenre communities for specific genres are produced by cutting the link clustering dendrogram at a lower level; in the examples provided ($C = 3$).
 
-Data scientists worry constantly about choosing a cut value when performing cluster analysis.
+\subsubsection{Where to cut?}
+Data scientists lose sleep over choosing a cut value when performing cluster analysis.
 One advantage of the link clustering approach is that we always know what we are doing because microgenres are strictly nested within the original macrogenres.
-Choosing a smaller cut value produces finer-grained microgenres (perhaps at the expense of analytic tractability and interoperability), and selecting a higher value returns us to broader genre communities closer to the original macrogenre labels we began with (with the limiting case as shown in Figure~\ref{fig:dend-macro} being the original macro genre labels themselves).
+Choosing a smaller cut value produces finer-grained microgenres (perhaps at the expense of analytic tractability and interpretability), and selecting a higher value returns us to broader genre communities closer to the original macrogenre labels we began with (with the limiting case as shown in Figure~\ref{fig:dend-macro} being the original macro genre labels themselves).
 At any cut value $C$, the more popular macrogenres produce more microgenre communities, while the less popular ones produce a smaller number.
 
-For instance, as shown in Figure~\ref{fig:dend-micro-classic-rock}, at $c = 3$, the macrogenre ``Classic Rock'' (the leftmost set of branches in the dendrogram in Figure~\ref{fig:dend-macro}) is split (at the point at which the branches intersect the red dashed cut line) into $k_{(CR)} = 12$ distinct micro-variations, while, as Figure~\ref{fig:dend-micro-opera} shows, the macrogenre ``Opera" (the rightmost set of branches in the dendrogram in Figure~\ref{fig:dend-macro}) is split into only $k_{(Op)} = 2$  microgenre communities.
-Figure~\ref{fig:dend-micro-blues} shows that ``Blues/R\&B'' falls somewhere in between, with $k_{(BRB)} = 5$  microgenre communities uncovered.
-Each cut point in the dendrogram will have a microgenre size distribution $N$ associated with it.
-Lower cut points return a microgenre size distribution dominated by many microgenres with tiny ($N_{mg} < 10$) or trivial $N_{mg} = 2$ audiences.
 Another approach, and the one I will be using in the case studies that follow, is to pick a macrogenre label (a branch in the larger dendrogram), decide \textit{ex ante} how many microgenres it makes sense to analyze, and then cut that branch of the dendrogram at a value that returns the desired number of microgenres.
-
-Note, that although I have been using the labels ``macro'' and ``micro'' as if they referred to substantive or objective partitions, they are best interpreted as {\em relative} to a given classification level.
-Thus, microgenres are ``micro'' relative to the usual (perhaps ``basic'' in Rosch's \citeyearpar{Rosch1978-ue} sense) categorization level of vague macrogenre labels populating most arts participation surveys.
-At any given classification level, further microgenres will be nested within any given micro-partition.
-In this way, microgenre communities should reflect a substantively valid way in which people partition the cultural world, whereby there is always the possibility of making finer-grained distinctions within fine-grained distinctions (e.g., ``old school rap," ``1980s old school rap," ``early 1980s old school rap," and the like).
+That is, fix $k$ and choose a $C$ value that satisfies it.
+For instance, Figures~\ref{fig:dend-micro-metal} and~\ref{fig:dend-micro-salsa} show the ``Metal'' and ``Salsa'' branches of Figure~\ref{fig:dend-macro} cut at a height that returns three microgenres for each macrogenre label.
+I chose these two macrogenres as examples because they will be the basis of the following genre case studies.
 
 \section{Two Genre Case Studies}
-We have shown that we can perform a link clustering and that this clustering returns a nice set of microgenres nested within the usual macrogenres in the survey.
+We have shown that we can perform a link clustering and that this clustering returns a nice set of microgenres nested within the usual macrogenres in the survey (see Figures~\ref{fig:dend-micro-metal} and~\ref{fig:dend-micro-salsa}).
 But does this exercise result in any substantive gains?
@@
 I choose to present two ``case studies'' of macrogenre labels and the resulting microgenre variations returned by the link clustering procedure.
-My criteria were as follows: I selected two macrogenre labels for which I could find some substantiated claim in the scholarly literature regarding possible microgenre variation.
-Naturally, general claims about microgenre variation apply to all macrogenre labels.
+
+My selection criteria were as follows: I picked two macrogenre labels for which I could find some substantiated claim in the scholarly literature regarding possible microgenre variation.
+Naturally, general claims about microgenre variation apply to almost all macrogenre labels.
 Therefore, the ``substantiated in the scholarly literature" serves as a way to narrow the field.
-I also intended to identify macrogenre labels for which some sort of debate or uncertainty existed in the scholarly literature regarding their overall status and their variations.
-I settled on Heavy Metal and Latin/Spanish Music/Salsa using this criterion.
-As we will see, Metal definitely fits this bill, as a lively debate already exists regarding its status as non-elite or an elite cultural form \citep{tampubolon2008revisiting}.
-Latin/Spanish/Salsa represents a more ``minor'' case study, but one that has also been documented to exhibit the sort of microgenre variation we seek \citep{bakk2013estimating}.
+My other criterion is for debate or uncertainty in the scholarly literature regarding the existence or overall status of the presumed microgenre variations.
+I settled on Heavy Metal and Latin/Spanish Music/Salsa using these criteria.
+As we will see, Metal definitely fits both bills, as a lively debate already exists regarding its status as non-elite or an elite cultural form \citep{tampubolon2008revisiting}.
+Latin/Spanish/Salsa represents a more ``minor'' case study, but one that has also been documented to exhibit the sort of microgenre variation we seek \citep{Bachmayer2014-pk}.
 As such, Salsa also showcases the usefulness of the link clustering approach for resolving key issues in the literature and extracting new insights from existing data.
@@
 Since then, it has been the subject of scholarly debate regarding its possibly changing status in the cultural stratification order \citep{tampubolon2008revisiting, goldberg2011mapping, lizardo_skiles15}.
-Heavy Metal stood out in Bryson's study for several reasons.
+Heavy Metal stood out in Bryson's study for two reasons.
 First, it was the most disliked genre in the 1993 General Social Survey culture module data---one of the most heavily analyzed data sources in the sociology of taste---hence the ``Anything But'' in the title of Bryson's eponymous piece.
@@
 Lizardo and Skiles \citeyearpar[][6, table 2]{lizardo_skiles16} used the same data source as in this paper (data from 2012) and found that, nineteen years later, Metal was still the most disliked of the macrogenre labels in a representative sample of Americans.
-Not only that, but when asked who the typical fan of metal looked like, Americans agreed with the stereotype: Low education, ``lower'' and working-class white men \citep[][7, table 3]{lizardo_skiles16}.
+Not only that, but when asked what the typical fan of metal looked like, Americans agreed with the stereotype: Low education, ``lower'' and working-class white men \citep[][7, table 3]{lizardo_skiles16}.
 
@@
 Tampubolon shows that including those ``don't know'' responses significantly changes things.
-Concerning Metal, it indicates that it is strongly disliked among low-education people more than would have been surmised in Bryson's original study, so it is not just a top-down symbolic exclusion story.
+Concerning Metal, it indicates that it is strongly disliked among low-education people, more than would have been surmised in Bryson's original study (because low-education people are more likely to say ``don't know'' to genre questions and are thus more likely to be dropped from the sample when these answers are also excluded), so it is not just a top-down symbolic exclusion story.
 For Tampubolon, this makes Metal ``quite exceptional'' since it is disliked across the board and even more by low-education people.
@@
 
-Tampubolon's argument regarding Metal dovetail with those preferred by Lizardo and Skiles \citeyearpar{lizardo_skiles15}, using the same data source as in this paper.
-Yes, while Metal was still the most disliked genre in 2012, \textit{compared} to 1993, it was one of the macrogenre labels (Rap and Hip Hop being the other) that experienced the steepest \textit{declines} in being disliked in the intervening two decades, especially among younger audiences.
+Goldberg \citeyearpar{goldberg2011mapping}, using the Relational Class Analysis (RCA) technique, found further evidence of the ambiguous status of Metal using the same GSS 1933 data source.
+In Goldberg's analysis, whether education was positively, negatively, or not correlated with a preference for Metal depended on the Relational Class that the respondent fell into, leading Goldberg to conclude that ``\ldots [M]etal seems to simultaneously function as  a  signal  of  high  status according  to  the Contempo-Trad logic and of low status according to the Hi-Low logic'' \citeyearpar[][1421]{goldberg2011mapping}.
+
+Tampubolon's and Goldberg's argument regarding the ambiguous status of the Metal macrogenre dovetail with the results reported by Lizardo and Skiles \citeyearpar{lizardo_skiles15}, using the same data source as in this paper.
+Yes, while Metal was still the most disliked genre in 2012, \textit{compared} to 1993, it was one of the macrogenre labels (Rap and Hip Hop being the other) that experienced the steepest \textit{declines} in being disliked in the intervening two decades, especially among members of younger cohorts.
 This led Lizardo and Skiles \citeyearpar[][18]{lizardo_skiles15} to conclude that ``The fact that young, highly educated Americans are now about as equally unlikely to dislike\ldots Heavy Metal as their same-age non-college educated peers constitutes a dramatic reversal of the pattern noted by Bryson\ldots [Metal] has experienced an improvement in standing among the college educated across almost all levels of age.'' This strongly suggests that enjoying some types of Metal music may be an ``emerging form'' of cultural capital \cite{prieur2013emerging} among certain segments of the young elite.
@@
 \subsubsection{Metal Microgenre Analysis}
-So, will the real heavy metal please stand up?
+So, will the real Heavy Metal please stand up?
 Is Metal a form of emerging cultural capital with potential appeal to young middle-class people or a genre heavily favored by white men with low education?
@@
 
-Given prior work, a strong expectation is that, at the very least, we should observe a microgenre partition separating the ``prototypical'' Metal (appealing to low-education white men) and perhaps a less-prototypical one, appealing to younger audiences with high-level cultural capital with other micro-variations, perhaps tracking generational distinction among members of the metal subculture \citep{lizardo_skiles15}.
+Given prior work, a strong expectation is that, at the very least, we should observe a microgenre partition separating the ``prototypical'' Metal (appealing to low-education white men) and perhaps a less-prototypical one, appealing to younger audiences with high-level cultural capital.
+Other micro-variations may also show up, perhaps tracking generational distinction among members of the metal subculture \citep{koch2020evolutionary}.
 
-\begin{figure}[ht!]
+\begin{figure}[t!]
+    \captionsetup[subfigure]{font=footnotesize}
+    \caption{Coefficient estimates from Linear Probability Models predicting macrogenre and microgenre choices for Metal and Salsa using socio-demographic predictors.}
+    \label{tab:reg}
     \centering    
@@
         %\includegraphics[width=1.0\textwidth]{}
-        \caption{}
-        \label{tab:reg-metal}
     \end{subfigure} \\
@@
         \includegraphics[trim={0 10cm 7cm 0},clip, width=1.0\textwidth]{Tabs/reg-tab-salsa.png}
-        \caption{}
-        \label{tab:reg-latin}
     \end{subfigure}
@@
 
-To address these questions, I partitioned the Heavy-Metal branch of the dendrogram at a height yielding three microgenre variations.
-To examine the issue of audience segmentation, I specify a linear probability regression model with five outcomes: First, a binary variable indicating that a person chose (liked and listened to) the standard macrogenre label (Heavy Metal), and then four models with the microgenre variations as the outcome (Heavy Metal one through four).
-The results are shown in Table~\ref{tab:reg-metal}.
-The main predictors are the respondent's education, an indicator variable for whether at least one of the respondent's parents has a college degree, the respondent's age, racial identification (in five categories with ``white'' as the reference), and gender identification (in two categories with ``man'' as the reference).
+To address these questions, I partitioned the Heavy-Metal branch of the dendrogram at a height yielding three microgenre variations (see Figure~\ref{fig:dend-micro-metal}).
+To examine the issue of audience segmentation, I specify a series of linear probability\footnote{Logit models return substantively identical results, so I stick with LPMs due to ease of interpretation and computation.} regression models with five outcomes: First, a binary variable indicating that a person chose (liked and listened to) the standard macrogenre label (Heavy Metal), and then three models with the microgenre variations as the outcome.
+
+The results are shown in Table~\ref{tab:reg}.\footnote{As an anonymous reader smartly pointed out, another way of interpreting the results of the link-clustering procedure is splitting the outcome variable into multiple versions, the correlates of which then provide evidence of multiple, but substantively distinct ``causal recipes'' to similar outcomes.
+This equifinality principle is a key interpretative and analytic precept in the Qualitative Comparative Analysis tradition, one which has systematic linkages to two-mode network analysis cases by variable data \citep{breiger2014comparative}.} The main predictors are the respondent's education, an indicator variable for whether at least one of the respondent's parents has a college degree, the respondent's age, racial identification (in five categories with ``white'' as the reference), and gender identification (in two categories with ``man'' as the reference).\footnote{Measures to values:
+    \begin{itemize}
+        \item[--] Education.- Ordinal variable: (1) Less than high school, (2) High school, (3) Associate's Degree, (4) Some college, (5) Bachelor's degree, (6) MA degree, (7) Doctoral or Professional degree.
+        \item[--] Age.- Ordinal variable: (1) 18--19, (2) 20--25, (3) 25--29, (4) 30--34, (5) 35--39, (6), 40--44, (7), 45--49, (8), 50--54, (9) 55--59, (10), 60--64, (11) 65--69, (12) 70--74, (13) 75--79, (14) 80+.
+    \end{itemize}}
 Because the age effect is specified using a squared polynomial, it can be hard to interpret its substantive significance.
@@
 Not so fast.
-The results differ when looking at the predictors of the microgenre variation choices.
+The results differ when looking at the predictors of microgenre choices.
 Indeed, the predictors of choosing the first microgenre variation, shown in the second column of the table, are consistent with Tampubolon's story.
-For this microgenre, there is a flat education gradient ($p = 0.54$), and importantly, it is more likely to be consumed by people whose parents have a college degree ($p < 0.05$), indicating a link to cultural capital in the home environment.
+For this microgenre, there is a flat education gradient ($p = 0.54$), and importantly, it is more likely to be consumed by people whose parents have a college degree ($p < 0.05$), indicating a link to cultural capital in the home environment \citep{bourdieu84}.
 This microgenre is tilted towards younger audiences, as only the linear negative age term is statistically significant (see Figure~\ref{fig:age-metal}) and is also neutral with respect to race and gender ($p > 0.05$).
@@
 
-Note that the other two microgenre variations, whose respective coefficient estimates are shown in the third and fourth columns of the table, conform most closely to the audience segmentation we would expect from the version of Metal.
+Note that the other two microgenre variations, whose respective coefficient estimates are shown in the third and fourth columns of the table, conform more closely to the audience segmentation we would expect from the version of Metal.
 These two microgenres mainly appeal to white men of relatively low education.
@@
 This means that the two microgenre variations that most closely conform to the usual audience expectations represent partitions \textit{within} the ``univore'' consumption profile, indicative of distinctive versions of Metal with an appeal to different generational niches \citep{koch2020evolutionary}.
+The link-clustering approach can tell the difference between these Metal variations, separated by a generational gap (see Figure~\ref{fig:age-metal}).
 
@@
 
-Bachmayer et al.
-elicited a list of performers by asking experts to freely name performers and bands and then classify the music typical of the named acts into an ordinal rank based on their judgments of aesthetic quality (``superior,'', ``middlebrow,'' ``inferior'').
+To examine microgenre variation within Salsa, Bachmayer et al.
+elicited a list of artists by asking experts to freely name performers and bands and then classify the music typical of the named acts into an ordinal rank based on their judgments of aesthetic quality (``superior,'', ``middlebrow,'' ``inferior'').
 They then selected the eight artists who were mentioned by at least three of the four expert informants and who displayed a high degree of concordance across experts in terms of their aesthetic rank.
 The eight compositions the experts judged to be typical of each artist's output were selected for guided interviews with forty first-generation Latinx immigrants in the Netherlands and Switzerland (there were no relevant cross-country differences).
-The most highly regarded expert pieces belonged to the sub-genre ``classic salsa,''---essentially early salsa performers that set the standard in the 1960s, 1970s, and 1980s---the middlebrow pieces were mainly variants of ``romantic salsa.'' The less aesthetically worthy pieces generally belonged to more recent styles of ``pop salsa styles.'' Note that this establishes a strict alignment between microgenre aesthetic standing and the historical sequencing of microgenre emergence within the salsa musicworld.
+The most highly regarded expert pieces belonged to the sub-genre ``classic salsa,''---essentially early salsa performers that set the standard in the 1960s, 1970s, and 1980s---the middlebrow pieces were mainly variants of ``romantic salsa.'' The less aesthetically worthy pieces generally belonged to more recent styles of ``pop salsa styles.'' Note that this establishes a strict alignment between microgenre aesthetic standing and the historical sequencing of microgenre emergence within the salsa musical field.
 We should thus expect this to be reflected in the generational location of each microgenre audience.
@@
 High status respondents emphasized compositional and thematic complexity over ``fun'' aspects like rhythm and ``danceability,'' elements crucial in working-class Latinx immigrants' explanations for why they gravitated towards more romantic and pop styles (finding classic salsa sleepy and boring).
-Importantly, ``expert consumers'' (people who worked in the musical field in some capacity) demonstrated the same aestheticized appreciation for classic salsa and denigration of popular styles regardless of their class background.
+Importantly, ``expert consumers'' (people who worked in the musical field in some capacity) demonstrated the same aestheticized appreciation for classic salsa and rejection of popular styles regardless of their class background.
 \citep[][62]{Bachmayer2014-pk} conclude that ``[t]aste in salsa music shows a strong internal, hierarchical order between `artistic' versus `popular' styles that \ldots structures the taste patterns of different social classes.''
@@
 \subsubsection{Salsa Microgenre Analysis}
-Table~\ref{tab:reg-latin} shows the result of a regression analysis analogous to that I specified for the Metal microgenres.
+Table~\ref{tab:reg} shows the result of a series of regression analysis analogous to those I specified for the three Metal microgenres, but this time using binary variables indexing choices of the three Salsa microgenres as outcomes (see Figure~\ref{fig:dend-micro-salsa}).
 The first column shows a model predicting choosing the ``Latin/Spanish/Salsa" macrogenre label using the usual socio-demographic covariates.
@@
 
-The microgenre analysis tells a different story.
-Looking at the third column of the table, predicting choice for the second of the induced microgenres, we find that, indeed, there is a micro-variation that is statistically more likely to be preferred by people of high education whose parents are also more likely to be highly educated ($p < 0.05$).
+Like Metal, the microgenre analysis tells a different story.
+Looking at the third column of the table, predicting choice for the second of the induced microgenres, we find that, indeed, there is a Salsa microgenre statistically more likely to be preferred by people of high education whose parents are also more likely to be highly educated ($p < 0.05$).
 Moreover, the age effect on the choice of this microgenre is \textit{reversed} compared to baseline expectations from the macrogenre regression.
 This microgenre is more likely to be preferred by older respondents (see Figure~\ref{fig:age-salsa}).
-In this way, this microgenre contrasts strongly with the first one extracted by the link clustering procedure, which is overwhelmingly more likely to be preferred by younger respondents.
+In this way, this microgenre contrasts strongly with the first one extracted by the link clustering procedure, which is overwhelmingly more likely to be preferred by younger respondents, and also with the third one, which has a relatively flat age gradient.
+
 These results point to two conclusions: First, there is hierarchical differentiation among microgenres extracted from the ``Latin/Spanish/Salsa'' macrogenre, with one microgenre standing out by its exclusive appeal to high-cultural-capital respondents.
 Second, this hierarchical differentiation is keyed to age, consistent with the idea that the most prestigious Salsa microgenre is also the ``oldest'' and most traditional \citep{Bachmayer2014-pk}.
+The other two Salsa microgenres are neutral concerning education ($p > 0.05$) but differ from the high-cultural capital variant regarding generational location.
+The link-clustering procedure is sensitive to these distinctions, thus allowing us to differentiate between these micro-variations.
 
-\section{Discussion}
+\section{Discussion and Conclusion}
 Let us take stock.
-We began by discussing the network or ``relational'' revolution in the quantitative study of taste in sociology \citep{pachucki2010cultural}.
+We began by discussing the network or ``relational'' revolution in the quantitative study of taste in sociology \citep{pachucki2010cultural, vlegels2017music, lizardo14}.
 We noted that many good things have come from considering survey data on taste using a relational lens, including a deeper specification of core concepts in the literature and even discovering new phenomena and empirical patterns.
 However, we also noted that survey data are as good as the labels chosen to collect the data.
-A resurgent line of critics question whether the labels that appear in our most venerable survey-based studies are true ``genres'' in the sociological (or even stylistic) sense \citep{lena2015relational, vlegels2015music}.
+
+A resurgent line of critics questions whether the labels that appear in our most venerable survey-based studies are true ``genres'' in the sociological (or even stylistic) sense \citep{lena2015relational, vlegels2015music}.
 The labels are broad, likely to be interpreted by people in heterogeneous ways, and thus hide as much as they reveal.
@@
 I proposed to do this using recent developments in the discovery of \textit{overlapping communities} in networks \citep{ahn_etal10}, which partially answers two of the challenges of macrogenre critics: The fact that actual genres are overlapping and not crisply bounded, and the fact that there is hidden heterogeneity within the broad labels we usually focus on.
-Our analysis contrasted the application of the usual techniques to the same data, conceived in the usual ``macro" way, and \textit{after} upping the relationality and discovering the microgenres hidden within.
-Focusing on microgenres reveals variations and patterns of cultural choice (as well as audience segmentation) that we would not have noticed using the standard approach (in this, the critics are right).
-Still, we could do this without dropping the label or querying people about hundreds of micro-styles (most of which they'd be unfamiliar with).
-Instead, we exploited the venerable principle, etched into classical approaches to defining genres in network terms \citep{dimaggio1987classification}, noting that if genres are defined by the people who choose them, then they are also defined by the other choices that people make when they choose them; the country that combines with one version of Classical may not be the same country that combines with a version of the Blues (and neither is the same as the country that refuses to combine with any other style).
+As revealed by the two macrogenre ``case studies,'' focusing on microgenres reveals variations and patterns of cultural choice (as well as audience segmentation) that we would not have noticed using the standard approach (in this, the critics are right).
+Moreover, these variations capture, at a large-scale level, intuitions and suspicions people have harbored in previous work regarding those particular macrogenres levels while revealing novel insights.
+For instance, we can be pretty sure that there is indeed a version of Metal that is copacetic with the tastes of certain high-cultural capital youth cutting across gender and racial boundaries \citep{tampubolon2008revisiting}, even if most versions of Metal continue to exist within its traditional socio-demographic of less-educated white men \citep{bryson96}.
+In the same way, we can detect a clear status partition in the field Salsa music consumption, with an older elite crowd separated by a generational divide from a younger audience set, very likely keyed the distinction between the aesthetically consecrated ``classics'' and more recent popular fare \citep{Bachmayer2014-pk}.
+More importantly, for the themes we began with, we could discern these patterns of micro-variation of this \textit{without} dropping the label or querying people about hundreds of micro-styles or performers (most of which they'd be unfamiliar with).
 
-The approach here is general and can be applied to studying other genre complexes beyond musical taste (allowing for economic data collection) and to studying other processes beyond taste.
+Instead, we exploited the venerable principle, etched into classical approaches to defining genres in network terms \citep{dimaggio1987classification}, noting that if genres are defined by the people who choose them, then they are also defined by the other choices that people make when they choose them; the country people combine with one version of Classical may not be the same country that combines with a version of the Blues (and neither is the same as the country that refuses to combine with any other style), nor is that Classical that combines with Country the same as others.
+Accordingly, the approach proposed here is ripe to be applied to all ``old'' data sources and cultural participation, potentially extracting and revealing many unexploited insights.
+
+Note that although I have been using the labels ``macro'' and ``micro'' as if they referred to substantive or objective partitions, they are best interpreted as {\em relative} to a given classification level.
+Thus, microgenres are ``micro'' relative to the usual (perhaps ``basic'' in Rosch's \citeyearpar{Rosch1978-ue} sense) categorization level of vague macrogenre labels populating most arts participation surveys.
+At any given classification level, further microgenres will be nested within any given micro-partition.
+In this way, microgenre communities are bound to reflect substantively valid ways people partition and understand the cultural world, whereby there is always the possibility of making finer-grained distinctions within fine-grained distinctions.
+
+Note, however, that the distinctions uncovered by the link-clustering approach based on the way audiences combine genres or not, may or may not necessarily correspond to micro-\textit{musiciological} distinctions (e.g., ``old school rap," ``1980s old school rap," ``early 1980s old school rap," and the like).\footnote{I thank an anonymous reader for making this observation.} These are, instead, micro-distinctions within genres \textit{sociologically} defined \citep{lena2015relational}.
+Now, it could be the case---as strongly hinted in the case of Salsa---that these micro-boundaries do coincide, although whether they do so should be the subject of future work taking a mixed-methods strategy.
+
+Nevertheless, the approach proposed here is general.
+It can be applied to studying other genre complexes beyond musical taste (allowing for economic data collection) and to studying other processes beyond taste.
 This includes belief, opinion, and attitude data.
 Essentially allows us to move from ``vague'' responses to more focused responses by exploiting the hidden patterns in the inter-response network formed when people respond to other items.
-Overall, we also learned a general lesson concerning our usual people or item classification techniques: To the extent that these are applied to items that themselves are ``vaguely'' defined, they will also yield even vaguer (and perhaps less than useful) macro-classifications of those items (like ``popular'' and ``high status'').
-The same may be said for such macro-classifications of opinions such as ``liberal'' and ``conservative,'' which, while being the primary way we interpret how people split themselves into groups by the beliefs they choose to hold, is decreasingly apt today if they ever were.
+The same lesson learned in studying genres in the sociology of taste applies to the study of opinion and belief data more generally \citep{boutyline2017belief}.
+To the extent that these are applied to items that themselves are ``vaguely'' defined, they will also yield even vaguer (and perhaps less than useful) meta-classifications of those beliefs and attitudes (like ``liberal'' and ``conservative'').
+These are the primary ways we interpret how people split themselves into groups by the beliefs they choose to hold, but are decreasingly apt today if they ever were.
 

### 2024-01-06 qmd/04_microgenre-analysis.qmd
Most recent plots and analyses

@@
 ```
-`
+
+```{r Microgenre Regression Models (Supp.)}
+    spec <- c("educ", "parcoll", "poly(age.n, 2)", 
+              "blk", "his", "asn", "gender")
+    labs <- c("Intercept", "Education", "Parents College",
+                            "Age", "Age-Squared", 
+                            "Race ID: Black", "Race ID: Hispanic",
+                            "Race ID: Asian", "Gender ID: Woman")
+
+    res.folk <- genre.reg.mods("Folk", k = 4, xvars = spec)
+    res.indie <- genre.reg.mods("Indie_Alt", k = 4, xvars = spec)
+
+    tab_model(res.folk$mods, 
+              digits = 3, show.ci = FALSE, 
+              auto.label = FALSE, transform = NULL,
+              pred.labels = labs,
+              file = here("Tabs", "reg-tab-folk.html"))
+    #webshot(here("Tabs", "reg-tab-folk.html"), here("Tabs", "reg-tab-folk.png"))
+
+    tab_model(res.indie$mods, 
+              digits = 3, show.ci = FALSE, 
+              auto.label = FALSE, transform = NULL,
+              pred.labels = labs,
+              file = here("Tabs", "reg-tab-indie.html"))
+    #webshot(here("Tabs", "reg-tab-indie.html"), here("Tabs", "reg-tab-indie.png"))
+
+```
+
+```{r Microgenre Regression Plots (Age/Supp.)}
+    age.preds <- pred.probs(x = "age.n", res.folk$mods)
+    p <- plot.preds(d = age.preds, 
+                    xb = c(3, 7, 11),
+                    xlabs = c("Young", "Middle Aged", "Old"),
+                    ym = -0.02,
+                    yl = .1, 
+                    xm = 2, 
+                    xl = 12)
+    save_plot(filename = here("Plots", "Micro", "micro-by-age-folk.png"), 
+              fig = p,
+              height = 25, width = 20)
+
+    age.preds <- pred.probs(x = "age.n", res.indie$mods)
+    p <- plot.preds(d = age.preds, 
+                    xb = c(3, 7, 11),
+                    xlabs = c("Young", "Middle Aged", "Old"),
+                    ym = -0.05,
+                    yl = .25, 
+                    xm = 2, 
+                    xl = 12)
+    save_plot(filename = here("Plots", "Micro", "micro-by-age-indie.png"), 
+              fig = p,
+              height = 25, width = 20)
+```

### 2024-01-06 main.tex
Updates from Overleaf

@@
 In this paper, I propose a link-clustering approach for discovering focused microgenres from standard survey-based information on cultural tastes, exploiting the underlying relational patterns realized by the indirect connectivity structure of genres (via people) in a two-mode network.
-The link-clustering approach partially answers two of the challenges of macrogenre critics: The fact that actual genres are overlapping and not crisply bounded and the fact that there is hidden heterogeneity within the broad labels we usually focus on.
-The results reveal an intuitive partition of traditional macrogenres into focused microgenres, capable of separating audiences along relevant sociodemographic markers, such as education, gender and ethnoracial identities, and age/generation.
+The link-clustering approach partially answers two of the challenges of macrogenre critics: The fact that actual genres are overlapping and not crisply bounded and that there is hidden heterogeneity within the broad labels we usually focus on.
+To showcase the fruitfulness of the proposed approach, I engage in two ``case studies'' featuring the vague macro genres of ``Heavy Metal'' and ``Latin/Salsa'' music and show the focused microgenres produced by the link clustering procedure are segmented in ways that help resolve puzzles that have emerged in previous work.
 \newpage
@@
 Recent work in the sociology of taste has blurred the distinction, foundational for much early work, between ``relational'' network data (codifying the relationships between people) and survey data (codifying the relationship between people and ``variables'').
-The basic idea is that all data, whether collected purposefully as ``network'' data collected or gathered as part of a traditional social survey, is \textit{relational} data.
-The main difference is the types of entities that are related \citep{borgatti_everett97}.
-Any data source that can be stored in matrix form has ``modes'' (the types of linked entities) and ``ways'' (the number of entities linked by a relation, usually two at a time).
-The standard network data set is ``one mode'' (we usually look at one type of entity at a time, like people, organizations, schools, countries, and the like) and two ``ways'' (people-by-people or organization-by-organization pairs).
+The basic idea is that all data, whether collected purposefully as ``network'' data collected or as part of a traditional social survey, is \textit{relational} data.
+The main difference is the types of entities related \citep{borgatti_everett97}.
+Any data source that can be stored in matrix form has ``modes'' (the types of linked entities) and ``ways'' (the number of entities connected by a relation, usually two at a time).
+The standard network data set is ``one mode'' (we typically look at one type of entity at a time, like people, organizations, schools, countries, and the like) and two ``ways'' (people-by-people or organization-by-organization pairs).
 In the same way, the usual person-by-variables survey data has two modes and two ways.
 The relations are not people-by-people but people-by-variables.
-People are connected to the survey items they answer by relations of affinity, disagreement, choice, or even negatively (by not answering).
+People are connected to the survey items they answer by ties of affinity, disagreement, choice, or even negatively (by not responding).
 Following, \citet{breiger74}, it is possible to recover person-by-person (one mode, two ways) matrices from the usual person-by-variables data matrices.
@@
 
-When transplanted to the sociology of taste, for which survey data has been the workhorse source of insights and empirical generalizations \citep{peterson_kern96, bryson96, vaneijck01,savage_gayo11}, this blurring of the boundaries between the two main sources of relational data in the social sciences can be revelatory.
+When transplanted to the sociology of taste, for which survey data has been the workhorse source of insights and empirical generalizations \citep{peterson_kern96, bryson96, vaneijck01,savage_gayo11}, this blurring of the boundaries between the two primary sources of relational data in the social sciences can be revelatory.
 This goes beyond the fact, to be exploited below, that once we treat survey data as network data, then the entire methodological panoply developed by social network analysts (and increasingly ``network scientists'' working across many disciplines) for the last fifty or so years becomes part of the analytic toolbox.
-In addition, the entire \textit{conceptual} arsenal of social network theory \citep{borgatti11} also becomes available.
-As \citet[244]{borgatti_everett97} note, once we convert ``2-mode data sets into 1-mode matrices{\dots}we can then apply the techniques (if not the theories) of network analysis.''
+In addition, the entire \textit{conceptual} arsenal of social network theory also becomes available \citep[244]{borgatti_everett97}.
 
@@
 Following this lead, \citet{lizardo14} provides a metric for such holes in cultural structure based on Burt's conception of network efficiency that is meant to characterize the slippery concept of ``omnivorousness" concerning genres and cultural forms people engage in.
-This approach goes beyond just summing or counting people's cultural engagements to consider the audience overlap between the genres themselves.
+This approach goes beyond summing or counting people's cultural engagements to consider the audience overlap between the genres.
 Thus, the true omnivore is a person who consumes genres with low audience overlap.
-Other work in this same vein extends ideas related to positional equivalence in networks \citet{breiger1976social} to uncover ``blocks'' of respondents that tend to dislike the same set of genres that others like \citep{okada2017structure}.
-A similar approach, based on ideas of positional equivalence in networks, can be extended beyond the study of beliefs and social attitudes to identify respondents who share cultural schemas \citep{goldberg2011mapping}.
-\citet{lizardo18} adapts techniques first developed for the study of economic complexity in two-mode networks of geographic sites and products/technologies \citep{hidalgo2009building} for characterizing genres (e.g., popular versus niche) and audiences (e.g., omnivore versus ``univore'') in survey data on cultural tastes.
+Other work in this same vein extends ideas related to positional equivalence in networks \citep[see][]{breiger1976social} to uncover ``blocks'' of respondents that tend to dislike the same set of genres that others like \citep{okada2017structure}.
+A similar approach, based on positional equivalence in networks, can be extended beyond the study of beliefs and social attitudes to identify respondents who share cultural schemas \citep{goldberg2011mapping}.
+More recently, \citet{lizardo18} adapts techniques first developed for the study of economic complexity in two-mode networks of geographic sites and products/technologies \citep{hidalgo2009building} for characterizing genres (e.g., popular versus niche) and audiences (e.g., omnivore versus ``univore'') in survey data on cultural tastes.
 
@@
 
-Thus, for DiMaggio, genres are dual entities precisely in Breiger's (1974) sense defined above.
+Thus, for DiMaggio, genres are dual entities precisely in Breiger's (1974) sense noted earlier.
 Genre categories are composed of the audiences that engage them (are subsets of the larger set of people).
-People, on the other hand, are related to one another (e.g., via relations of similarity, opposition, or non-overlap) by the genres they choose, and genres related to one another via overlaps (intersections) in the sets of people who choose them \citet{lizardo18}.
+People, on the other hand, are related to one another (e.g., via relations of similarity, opposition, or non-overlap) by the genres they choose, and genres related to one another via overlaps (intersections) in the sets of people who choose them.
 
 Like much network theorizing, this conceptualization is elegant but gets messy in application.
-As \citet[149]{lena2015relational} has noted, ``[n]o ordering principle is as fundamental to culture as genre'' yet, none is also as vexed.
-Lena raises one fundamental issue: Sociologists have relational intuitions about genres but tend to default to musicological definitions for convenience.
-Thus, when it comes to considering which genres to include in a survey on cultural tastes, the tendency is to pick off-the-shelf from the menu of genre categories.
+As \citet[149]{lena2015relational} has noted, ``[n]o ordering principle is as fundamental to culture as genre'' yet none is also as vexed.
+Lena raises one fundamental issue: Sociologists have relational intuitions about genres but tend to default to substantive musicological definitions for convenience.
+Thus, when considering which genres to include in a survey on cultural tastes, the tendency is to pick off-the-shelf from the menu of institutionalized---usually at the level of the culture industry or field of cultural production---genre categories.
 The problem with these folk genre classifications is that they miss the fuzzy, overlapping ways real-world genres are organized.
@@
 Genres may also develop and accumulate variations as they ``travel'' across production, dissemination, and consumption sites in their historical trajectory \citep{Lena2012}.
-These ``microgenres'' are embedded within larger macrogenres in complex ways that the standard survey approach misses.
 
-For instance, within the Sheffield ``musicworld,'' the broad genre category of ``Folk''---one usually included in the typical survey questionnaire like the one used in this paper---can refer to at least three existing microgenres: A ``traditionalist'' one---see \citep{Lena2012}---composed mainly of late nineteenth and early twentieth English ballads documenting working-class and mining-town life, a ``scene'' genre centered on 1960s political protest and pop songs (a la Bob Dylan) or more contemporary ``avant-garde'' genre featuring reflexive, sometimes parodic takes on the previous two, and centered on blurring performer-audience boundaries.
+For instance, in a study of rap songs that charted in the Top 100 R\&B Billboard charts from 1979-1995, Lena \citeyearpar[299]{lena2004meaning}, used a ``combination of lyrical, vocal, and musical attributes, in combination with the record label and geographic location of the producers'' to code for thirteen distinct ``rap'' microgenres, including ``booty rap, crossover rap, don rap, dirty south rap, east coast gangsta rap, g funk, jazz rap, new jack swing, parody rap, pimp rap, race rap, rock rap, and west coast gangsta rap.'' These microgenres are embedded within larger macrogenres like ``rap and Hip Hop'' in complex ways that the standard survey approach misses.
+
+In the same way, within the Sheffield ``musicworld,'' the broad genre category of ``Folk''---one usually included in the typical survey questionnaire like the one used in this paper---can refer to at least three existing microgenres: A ``traditionalist'' one---see \citep{Lena2012}---composed mainly of late nineteenth and early twentieth English ballads documenting working-class and mining-town life, a ``scene'' genre centered on 1960s political protest and pop songs (\`{a} la Bob Dylan) or more contemporary ``avant-garde'' genre featuring reflexive, sometimes parodic take on the previous two, and centered on blurring performer-audience boundaries.
 As Hield and Crossley \citeyearpar[197]{Hield2014-xe} note, ``[t]hese and other such distinctions are not registered in\ldots surveys.''
@@
 \section{What to do about the problem of genre}
-One solution to the problem posed by vague macrogenre labels, suggested by \citet{vlegels2015music, vlegels2017music} concerning musical genres, is to ``change the mode'' and ``drop the label'' by asking respondents not just for their levels of engagement or liking of broad macrogenre labels but for performers within those labels.
-This work shows that once these ``microgenre'' distinctions based on performers are made, some core empirical generalizations in the sociology of taste (e.g., highly educated people like classical music) are controverted or at least heavily qualified.
+One solution to the problem posed by vague macrogenre labels, suggested by \citet{vlegels2015music, vlegels2017music} concerning musical genres, is to ``change the mode'' and ``drop the label'' by asking respondents not just for their levels of engagement or liking of broad macrogenre labels but for performers within those labels \citep{nault2021social}.
+This work shows that once these ``microgenre'' distinctions based on performers are made, some core empirical generalizations in the sociology of taste (e.g., highly educated people like classical music) are contradicted or at least heavily qualified.
 This \textit{microgenre heterogeneity} critique thus asserts that the standard genre labels studied by social scientists hide as much as they reveal because microgenre communities can be internally diverse and even contain mutually opposed groups in the social space \citep{flemmen_etal18}.
@@
 So, it is unclear what to do (and how to interpret) the usual data collected by sociologists who study taste using surveys.
+As Jarness \citeyearpar{jarness2015} notes, ``researchers (have had to) deploy crude measures based on wide genre categories, such as pop/rock, classical and country and western in the mapping of musical tastes.
+In this way, they have tended to obscure that sociologically significant taste distinctions exist within these somewhat arbitrary genre categories.''
 
@@
 I propose another solution: {\em Exploit the inherent relationality embedded in survey data responses} \citep{goldberg2011mapping, boutyline2017belief, lizardo18}.
-More specifically, my point will be that by exploiting the inherent relationality already contained in the usual survey data (when treated as two-mode network data), old data can reveal insights that pertain to the very features sociological critics of the macrogenre label concept say are missing.
+More specifically, my point will be that by exploiting the intrinsic relationality already contained in the usual survey data (when treated as two-mode network data), old data can reveal insights that pertain to the very features sociological critics of the macrogenre label concept say are missing.
 In particular, it is possible to use embedded sets of relations between people and genres to discover the heterogeneous microgenre communities critics say are hidden by macrogenre labels.
-This approach is thus ideal for making new use of old data while, at the same time, sidestepping some, but not all, the limitations of the microgenre critique.
+This approach is thus ideal for making new use of old data while sidestepping some, but not all, of the limitations of the microgenre critique.
 
@@
 As we will see, I propose a complementary and synergistic approach with these previous efforts.
-More to the point, the relational identification of microgenres should be able to improve the applicability of techniques like RCA, CCA, and BNA (and related techniques) because, just like standard statistical approaches (like Factor Analysis, Principal Component Analysis, Latent Class Analysis and so forth), and even techniques like Multiple Correspondence Analysis sometimes opposed to the traditional statistical ones, these newfangled relational techniques are also dragged down by the macrogenre curse.
-Thus, RCA and CCA are bound to compute relationality and correlation distances within people but have to rely on vague macrogenre labels.
+More to the point, the relational identification of microgenres can improve the applicability of techniques like RCA, CCA, and BNA (and related techniques) because, just like standard statistical approaches (like Factor Analysis, Principal Component Analysis, Latent Class Analysis, and so forth), and even techniques like Multiple Correspondence Analysis sometimes opposed to the traditional statistical ones, these newfangled relational techniques are also dragged down by the macrogenre curse.
+Thus, RCA and CCA are bound to compute relationality and correlation distances within people but rely on vague macrogenre labels.
 
@@
 But what if what one group means by ``Heavy Metal" differs from what another group means by the same vague label?
-Are we certain that certain {\em all} types of classical music are ``opposed'' to or divergent from engagement with Country or Hip Hop?
-Some versions of Indie/Alt Rock are considered today as ``highbrow'' as Classical music (used to be) \citep{Van_Poecke2018}; or there may exist types of Country music that appeal to highly educated audiences and, thus, to people who might also listen to musicals?
-All quantitative techniques researchers use in the sociology of taste must work with the (broad) genre categories included in the survey.
+Are we sure that certain {\em all} types of classical music are ``opposed'' to or divergent from engagement with Country or Hip Hop?
+Some versions of Indie/Alt Rock are today considered ``highbrow'' as Classical music (used to be) \citep{Van_Poecke2018}.
+Do high-cultural capital respondents inherently shun every variant of Country?
+As \citet{lembo2017three} shows, there are microgenres of Country music---in that case, featuring a traditionalist appreciation for the ``hard'' ``Honky Tonk'' sound developed in 1920s Texas---that appeal to highly educated audiences and, thus, to people who are also likely also listen to Musical Theater compositions, Jazz, and Opera.
+Even though the most likely answers to the preceding rhetorical suggestions fall on the side of significant microgenre variation, quantitative techniques researchers use in the sociology of taste must work with the (broad) genre categories included in the survey.
 As such, they are powerless to deal with the (reasonable) objections brought up by the microgenre dissenters.
 
-Importantly, this implies that the clumping of vague macrogenre labels into even vaguer meta-macrogenres (discourses, styles, logics, schemas) like ``highbrow'' ``Popular," or ``Folk," could be a spurious by-product of the vague labeling (as microgenres critics have long suspected).
+Importantly, this implies that the clumping of vague macrogenre labels into even more ambiguous meta-macro genres (discourses, styles, logics, schemas) like ``highbrow'' ``Popular," or ``Folk" could be a spurious by-product of the vague labeling (as microgenres critics have long suspected).
 This matters because such macrogenre clumping does much conceptual (and technical) work in our data reduction, interpretation, and substantive theorizing efforts.
-The result is that it is likely that people are classified as following the same cultural logic of genre valuation and evaluation when they, in fact, follow distinct logics.
-In fact, a key implication of the approach to be described below is that regardless of the particular technique used, sociologists of taste are likely to underestimate population heterogeneity in the logics of classification and evaluation people use to navigate the cultural space \citep{lahire2008individual}.
+The result is that it is likely that people are classified as following the same cultural logic of genre valuation and evaluation when they follow distinct logics.
+A key implication of the approach to be described below is that regardless of the particular technique used, sociologists of taste are likely to underestimate population heterogeneity in the logics of classification and evaluation people use to navigate the cultural space \citep{lahire2008individual}.
 This heterogeneity has to be {\em revealed} before constructing belief or attitude networks, classifying people into schematic classes, embedding genres into a dimensional space, or putting people into latent classes.
@@
 In the remainder of the paper, I introduce the link-clustering approach to eliciting microgenres using the relational information embedded in the joint choices (and avoidance) of macrogenres available in traditional survey data.
-I first introduce the motivation behind the method using a simple ``toy example'' and then move to the more substantive ground in two ``case studies,'' concerning two genres for which substantiated proposals exist in the literature regarding micro-variations.
+I first introduce the motivation behind the method using a simple ``toy example'' and then move to more substantive ground in two ``case studies'' concerning two genres for which substantiated proposals regarding micro-variations exist in the literature.
 I show that the proposed approach extracts novel insights from survey data that help address, shed light on, and adjudicate these debates at a population level while providing novel leads to future work.
@@
 
-Like GSS 1993, SSI 2012 included items assessing respondents’ likes and dislikes (as well as a middle category of ``mixed feelings'') for 20 categories of musical style: classical/ symphony and chamber, opera/operetta, jazz, Broadway musicals/show tunes, mood/easy listening, big band/swing, classic rock/oldies, country, bluegrass, folk, hymns/gospel, Latin/Spanish/salsa, rap/hip hop, blues/R\&B, reggae, top 40/pop music, contemporary rock, indie/alternative rock, dance/club/electronic, and hard rock/heavy metal.
-In addition to providing a taste judgment for each item, respondents were also asked if they regularly listened to each macrogenre.
-The following analyses are based on a data frame in which people are coded as engaging the macrogenre if they report both liking and listening to it.
-The two-mode network we will be working with is thus of dimensions and has $2263$ people and $20$ genres.
-This defines an affiliation matrix $A_{PG}$ of the same dimensions, with entries equal to 1 if person $P$ likes \textit{and} listens to macrogenre label $G$ and zero otherwise.
+Like GSS 1993, SSI 2012 included items assessing respondents’ likes and dislikes (as well as a middle category of ``mixed feelings'') for 20 categories of musical style: Classical/Symphony and Chamber, Opera/Operetta, Jazz, Broadway Musicals/Show Tunes, Mood/Easy Listening, Big Band/Swing, Classic Rock/Oldies, Country, Bluegrass, Folk, Hymns/Gospel, Latin/Spanish/Salsa, Rap/Hip Hop, Blues/R\&B, Reggae, Rop 40/Pop, Contemporary Rock, Indie/Alternative Rock, Dance/Club/Electronic, and Hard Rock/Heavy metal.
+In addition to providing a taste judgment for each item, respondents were also asked if they regularly listened to each.
+The two-mode network we will be working with is thus of dimensions $2263$ (people) $\times$ $20$ (genres).
+This defines an affiliation matrix $\mathbf{A}$ of the same row and column dimensions, with entries ($a_{ij}$) equal to 1 if person $i$ likes \textit{and} listens to macrogenre label $j$ and zero otherwise.
 
@@
 I address the microgenre issue using a technique for overlapping community detection called \textit{link clustering} \citep{ahn_etal10}.
-The basic idea is simple and illustrated in the toy example in Figure~\ref{fig:link-toy1}.
+The basic idea is simple and illustrated in the toy example in Figure~\ref{fig:link-toy1}.\footnote{Code to replicate all of the analyses reported in this paper and software implementing the link clustering procedure, can be found at \nolinkurl{https://github.com/olizardo/Discovering-Focused-Microgenre-Communities}}.
 Breaking with approaches that attempt to cluster people and genres by focusing on the people or the genres, we take the person-to-genre {\em link} as the unit of analysis and focus our classification energies on those.
@@
 The similarity of one person-to-genre edge to another, when both edges point to the same genre \citep{ahn_etal10}, should be proportional to the overlap between the ``cultural ego networks'' of the two people at the tail end of the edges.
-As \citet{lizardo14} defines it, for any respondent $i$, in a survey on cultural taste, the cultural ego network is simply the set of genres $\{G_1, G_2,\dots G_k\}$ chosen by the person, where $k$ is the total number of genres chosen (``omnivorousness by volume'').
+As \citet{lizardo14} defines it, for any respondent $i$, in a survey on cultural taste, the cultural ego network is simply the set of genres $\{G_1, G_2,\dots G_k\}$ chosen by the person, where $k$ is the total number of genres selected (``omnivorousness by volume'').
 
@@
 The formula says that the similarity between two person-to-genre links sharing a genre, in this case, the similarity between the $P_1-G_2$ edge and the $P_3-G_2$ edge, is given by the intersection of Person 1's and Person 3's cultural ego network divided by their union.
-When the cultural ego networks of two people are the same $S=1$ when they are completely disjoint $S = 0$.
-All other cases of person-to-genre edges sharing the same genre return a number between zero and one ($0 > S < 1$).\footnote{Note that the only substantive similarities we care about are between person-to-genre edges that share the same genre but have different people attached to them at the other end.
+When the cultural ego networks of two people are the same $S=1$ when they are entirely disjoint $S = 0$, all other cases of person-to-genre edges sharing the same genre return a number between zero and one ($0 > S < 1$).\footnote{Note that the only substantive similarities we care about are between person-to-genre edges that share the same genre but have different people attached to them at the other end.
 All other person-to-genre edges similarities featuring people connected to different genres are set to zero.} In the toy example case, $P_1$ and $P_3$ consume two genres out of the four possible ones they could consume in common, resulting in an edge similarity score of $\frac{2}{4} = 0.50$.
@@
 Note two features of the similarity matrix.
-First, by definition, two person-to-genre links that go from different genres to the same person are maximally similar (as the overlap is 1.0).
-This means that only links that go from different people to the same genre exhibit overlap variation, and this is driven (``reflectively'' \citep{lizardo18}) by the overlap between the neighborhoods of the other mode (people).
+First, by definition, two person-to-genre links from different genres to the same person are maximally similar (as the overlap is 1.0).
+This means that only links that go from other people to the same genre exhibit overlap variation, and this is driven (``reflectively'' \citep{lizardo18}) by the overlap between the neighborhoods of the other mode (people).
 Next, we transform the similarity matrix into a {\em dissimilarity} matrix by subtracting one from each entry (shown in  Figure~\ref{tab:toy-dis}).
@@
 For instance, macrogenre $G4$ is split into two focused microgenre varieties.
-The first is attached to people $P2$ and $P4$, and the second is attached to people $P3$ and $P5$, respectively.
+The first is attached to people $P2$ and $P4$, and the second is connected to people $P3$ and $P5$, respectively.
 The idea is that the macrogenre nodes (e.g., ``Classical'') assigned to different clumps represent micro-variations of the macrogenre label that differ primarily relationally or structurally; different ``types'' of ``Classical'' are different because their audiences make distinct choices {\em with respect} to the other genres in the survey.
@@
 
-The resulting partition has two interesting (and desirable) properties.
+The resulting partition has two attractive (and desirable) properties.
 First, the number of genre communities that \textit{people} belong to is deterministic, and it is given by the number of macrogenre labels they initially chose.
@@
 Recall that the data features 2,263 people choosing up to 20 macrogenre labels.
-When strung out as an edgelist, this results in 9,216 person-to-genre connections in the data, the resulting $9216 \times 9,216$ matrix, containing Jaccard similarities among person-to-genre links sharing a node in either of the two modes, is then the input to an agglomerative hierarchical clustering algorithm using Ward's \citeyearpar{ward63} method.
+When strung out as an edgelist, this results in 9,216 person-to-genre connections in the data.
+The resulting $9216 \times 9,216$ matrix, containing Jaccard similarities among person-to-genre links sharing a node in either of the two modes, is then the input to an agglomerative hierarchical clustering algorithm using Ward's \citeyearpar{ward63} method.
 
@@
 As Figure~\ref{fig:dend-macro-labels} shows, the agglomerative link clustering procedure roughly arranges the macrogenre levels by their original popularity (number of person-to-genre links).
-From left to right, these are Classic Rock/Oldies, Pop/Top 40, Country, Classical, Easy Listening, Blues/R\&B, Contemporary Rock, Rap/Hip Hop, Jazz, Gospel, Dance/Club, Indie Alternative, Latin, Broadway/Musicals, Heavy Metal/Hard Rock, Reggae, Big Band, Folk, Bluegrass, and Opera.
+From left to right, these are Classic Rock/Oldies, Pop/Top 40, Country, Classical, Easy Listening, Contemporary Rock, Blues/R\&B, Rap/Hip Hop, Jazz, /EDM, Dance/Club/EDM Gospel, Indie Alternative, Broadway/Musicals, Heavy Metal/Hard Rock, Latin/Spanish/Salsa, Reggae, Big Band, Folk, Bluegrass, and Opera.
 
@@
 
-Another approach, and the one I will be using in the case studies that follow, is to pick a macrogenre label (a branch in the larger dendrogram), decide \textit{ex ante} how many microgenres it makes sense to analyze, and then cut that branch of the dendrogram at a value that returns the desired number of microgenres.
+Another approach, and the one I will be using in the case studies that follow, is to pick a macrogenre label (a branch in the larger dendrogram), decide \textit{ex-ante} how many microgenres it makes sense to analyze, and then cut that branch of the dendrogram at a value that returns the desired number of microgenres.
 That is, fix $k$ and choose a $C$ value that satisfies it.
@@
 There are many ways we can proceed.
-I choose to present two ``case studies'' of macrogenre labels and the resulting microgenre variations returned by the link clustering procedure.
+I present two ``case studies'' of macrogenre labels and the resulting microgenre variations returned by the link clustering procedure.
 
@@
 My other criterion is for debate or uncertainty in the scholarly literature regarding the existence or overall status of the presumed microgenre variations.
-I settled on Heavy Metal and Latin/Spanish Music/Salsa using these criteria.
-As we will see, Metal definitely fits both bills, as a lively debate already exists regarding its status as non-elite or an elite cultural form \citep{tampubolon2008revisiting}.
+Using these criteria, I settled on Heavy Metal and Latin/Spanish Music/Salsa.
+As we will see, Metal fits both bills, as a lively debate already exists regarding its status as non-elite or an elite cultural form \citep{tampubolon2008revisiting}.
 Latin/Spanish/Salsa represents a more ``minor'' case study, but one that has also been documented to exhibit the sort of microgenre variation we seek \citep{Bachmayer2014-pk}.
-As such, Salsa also showcases the usefulness of the link clustering approach for resolving key issues in the literature and extracting new insights from existing data.
+As such, Salsa also showcases the usefulness of the link clustering approach for resolving critical issues in the literature and extracting new insights from existing data.
 
@@
 First, it was the most disliked genre in the 1993 General Social Survey culture module data---one of the most heavily analyzed data sources in the sociology of taste---hence the ``Anything But'' in the title of Bryson's eponymous piece.
-Second, it was the prototypical genre that was relatively more favored by working-class audiences but absolutely hated by individuals with high education.
+Second, it was the genre most favored by working-class audiences but hated by individuals with high education.
 Thus, it served as the linchpin of Bryson's symbolic exclusion argument; omnivores were omnivorous up to a point, except when it came to those genres most favored by those with low education.
 
-Regardless, the picture we got of Metal concerning audience segmentation was clear: It was a genre that primarily appealed to working-class, low-education white men and was rejected by pretty much everyone else.
+Regardless, the picture we got of Metal concerning audience segmentation was clear: It was a genre that primarily appealed to working-class, low-education white men and was rejected by everyone else.
 Lizardo and Skiles \citeyearpar[][6, table 2]{lizardo_skiles16} used the same data source as in this paper (data from 2012) and found that, nineteen years later, Metal was still the most disliked of the macrogenre labels in a representative sample of Americans.
-Not only that, but when asked what the typical fan of metal looked like, Americans agreed with the stereotype: Low education, ``lower'' and working-class white men \citep[][7, table 3]{lizardo_skiles16}.
+Not only that but when asked what the typical fan of metal looked like, Americans agreed with the stereotype: Low education, ``lower'' and working-class white men \citep[][7, table 3]{lizardo_skiles16}.
 
 Yet, cracks began to appear in this picture as soon as it was hung.
-First, Tampubolon \citeyearpar{tampubolon2008revisiting} re-analyzed the Bryson data using a different methodological approach (latent-class analysis), making different inclusion decisions regarding the ``don't know'' responses.
+First, Tampubolon \citeyearpar{tampubolon2008revisiting} re-analyzed the Bryson data using a different methodological approach (latent-class analysis), making other inclusion decisions regarding the ``don't know'' responses.
 Tampubolon shows that including those ``don't know'' responses significantly changes things.
-Concerning Metal, it indicates that it is strongly disliked among low-education people, more than would have been surmised in Bryson's original study (because low-education people are more likely to say ``don't know'' to genre questions and are thus more likely to be dropped from the sample when these answers are also excluded), so it is not just a top-down symbolic exclusion story.
-For Tampubolon, this makes Metal ``quite exceptional'' since it is disliked across the board and even more by low-education people.
+Concerning Metal, it indicates that it is intensely disliked among low-education people, more than would have been surmised in Bryson's original study (because low-education people are more likely to say ``don't know'' to genre questions and are thus more likely to be dropped from the sample when these answers are also excluded), so it is not just a top-down symbolic exclusion story.
+For Tampubolon, this makes Metal ``quite exceptional'' since it is disliked across the board and even more by people with low education.
 
-Tampubolon's work indicates that just because Metal's audience is composed of low-education people does not mean that the rest of the less-educated population loves it; they hate it passionately.
-Tampubolon's analysis of ``Like'' responses also shows that Metal, rather than being exclusively preferred by a univorous group of ``Metalheads'' (who only prefer metal and dislike everything else), also makes it into the taste profile of one of two omnivorous groups uncovered in his analysis.
+Tampubolon's work indicates that because Metal's audience is composed of people with low education, it does not mean that the rest of the less-educated population loves it; they hate it passionately.
+Tampubolon's analysis of ``Like'' responses also shows that Metal, rather than being exclusively preferred by a univorous group of ``Metalheads'' (who only like metal and dislike everything else), also makes it into the taste profile of one of two omnivorous groups uncovered in his analysis.
 Thus, Metal ends up straddling omnivores and univores.
@@
 Yes, while Metal was still the most disliked genre in 2012, \textit{compared} to 1993, it was one of the macrogenre labels (Rap and Hip Hop being the other) that experienced the steepest \textit{declines} in being disliked in the intervening two decades, especially among members of younger cohorts.
-This led Lizardo and Skiles \citeyearpar[][18]{lizardo_skiles15} to conclude that ``The fact that young, highly educated Americans are now about as equally unlikely to dislike\ldots Heavy Metal as their same-age non-college educated peers constitutes a dramatic reversal of the pattern noted by Bryson\ldots [Metal] has experienced an improvement in standing among the college educated across almost all levels of age.'' This strongly suggests that enjoying some types of Metal music may be an ``emerging form'' of cultural capital \cite{prieur2013emerging} among certain segments of the young elite.
+This led Lizardo and Skiles \citeyearpar[][18]{lizardo_skiles15} to conclude that ``The fact that young, highly educated Americans are now about as equally unlikely to dislike\ldots Heavy Metal as their same-age non-college-educated peers constitutes a dramatic reversal of the pattern noted by Bryson\ldots [Metal] has experienced an improvement in standing among the college-educated across almost all levels of age.'' This strongly suggests that enjoying some types of Metal music may be an ``emerging form'' of cultural capital---as defined by \citet{prieur2013emerging}---among specific segments of the young elite.
 
@@
 Given prior work, a strong expectation is that, at the very least, we should observe a microgenre partition separating the ``prototypical'' Metal (appealing to low-education white men) and perhaps a less-prototypical one, appealing to younger audiences with high-level cultural capital.
-Other micro-variations may also show up, perhaps tracking generational distinction among members of the metal subculture \citep{koch2020evolutionary}.
+Other micro-variations may also show up, possibly tracking generational distinction among members of the metal subculture \citep{koch2020evolutionary}.
 
@@
 To address these questions, I partitioned the Heavy-Metal branch of the dendrogram at a height yielding three microgenre variations (see Figure~\ref{fig:dend-micro-metal}).
-To examine the issue of audience segmentation, I specify a series of linear probability\footnote{Logit models return substantively identical results, so I stick with LPMs due to ease of interpretation and computation.} regression models with five outcomes: First, a binary variable indicating that a person chose (liked and listened to) the standard macrogenre label (Heavy Metal), and then three models with the microgenre variations as the outcome.
+To examine the issue of audience segmentation, I specify a series of linear probability\footnote{Logit models return substantively identical results, so I stick with LPMs due to ease of interpretation and computation.} regression models with four outcomes: First, a binary variable indicating that a person chose (liked and listened to) the standard macrogenre label (Heavy Metal), and then three models with the microgenre variations as the outcome.
 
 The results are shown in Table~\ref{tab:reg}.\footnote{As an anonymous reader smartly pointed out, another way of interpreting the results of the link-clustering procedure is splitting the outcome variable into multiple versions, the correlates of which then provide evidence of multiple, but substantively distinct ``causal recipes'' to similar outcomes.
-This equifinality principle is a key interpretative and analytic precept in the Qualitative Comparative Analysis tradition, one which has systematic linkages to two-mode network analysis cases by variable data \citep{breiger2014comparative}.} The main predictors are the respondent's education, an indicator variable for whether at least one of the respondent's parents has a college degree, the respondent's age, racial identification (in five categories with ``white'' as the reference), and gender identification (in two categories with ``man'' as the reference).\footnote{Measures to values:
+This equifinality principle is a crucial interpretative and analytic precept in the Qualitative Comparative Analysis (QCA) tradition, one which has systematic linkages to two-mode network analysis cases by variable data \citep{breiger2014comparative}.} The main predictors are the respondent's education, an indicator variable for whether at least one of the respondent's parents has a college degree, the respondent's age, racial identification (in five categories with ``white'' as the reference), and gender identification (in two categories with ``man'' as the reference).\footnote{Measures to values:
     \begin{itemize}
-        \item[--] Education.- Ordinal variable: (1) Less than high school, (2) High school, (3) Associate's Degree, (4) Some college, (5) Bachelor's degree, (6) MA degree, (7) Doctoral or Professional degree.
+        \item[--] Education.- Ordinal variable: (1) Less than high school, (2) High school, (3) Associate's Degree, (4) Some college, (5) Bachelor's degree, (6) M.A.
+degree, (7) Doctoral or Professional degree.
         \item[--] Age.- Ordinal variable: (1) 18--19, (2) 20--25, (3) 25--29, (4) 30--34, (5) 35--39, (6), 40--44, (7), 45--49, (8), 50--54, (9) 55--59, (10), 60--64, (11) 65--69, (12) 70--74, (13) 75--79, (14) 80+.
@@
 Not so fast.
-The results differ when looking at the predictors of microgenre choices.
+The results differ when looking at the predictors of other microgenre choices.
 Indeed, the predictors of choosing the first microgenre variation, shown in the second column of the table, are consistent with Tampubolon's story.
 For this microgenre, there is a flat education gradient ($p = 0.54$), and importantly, it is more likely to be consumed by people whose parents have a college degree ($p < 0.05$), indicating a link to cultural capital in the home environment \citep{bourdieu84}.
-This microgenre is tilted towards younger audiences, as only the linear negative age term is statistically significant (see Figure~\ref{fig:age-metal}) and is also neutral with respect to race and gender ($p > 0.05$).
+This microgenre is tilted towards younger audiences, as only the linear negative age term is statistically significant (see Figure~\ref{fig:age-metal}) and is also neutral concerning race and gender ($p > 0.05$).
 Given that this microgenre version of Metal appeals mainly to young middle-class respondents and does not repel women or non-white audiences, it starkly contrasts what we would have concluded from observing the macrogenre label effects.
@@
 These two microgenres mainly appeal to white men of relatively low education.
-The main difference between these two microgenres is generational location, with the second microgenre appealing mainly to young adults and middle-aged men and the third variant attracting a younger crowd (see Figure~\ref{fig:age-metal}).
+The main difference between these two microgenres is generational location, with the second microgenre primarily appealing to young adults and middle-aged men and the third variant attracting a younger crowd (see Figure~\ref{fig:age-metal}).
 This means that the two microgenre variations that most closely conform to the usual audience expectations represent partitions \textit{within} the ``univore'' consumption profile, indicative of distinctive versions of Metal with an appeal to different generational niches \citep{koch2020evolutionary}.
@@
 The Salsa music genre has not had as storied a career in the sociology of taste as Metal.
-In fact, it has been under-researched and, for the most part, ignored.
+It has been under-researched and, for the most part, ignored.
 I include it in the following analysis due to a shining exception to this pattern, represented by a qualitative study by \citet{Bachmayer2014-pk}, which strongly suggests internal microgenre differentiation within this broad macrogenre label relevant to the reception and consumption side.
-These differentiations are keyed to hierarchical distinctions across Salsa microgenres based on social status and the concomitant internalization of class-based aesthetic dispositions \citep{lizardo2012reconceptualizing}.
+This differentiation is keyed to hierarchical distinctions across Salsa microgenres based on social status and the concomitant internalization of class-based aesthetic dispositions \citep{lizardo2012reconceptualizing}.
 
@@
 elicited a list of artists by asking experts to freely name performers and bands and then classify the music typical of the named acts into an ordinal rank based on their judgments of aesthetic quality (``superior,'', ``middlebrow,'' ``inferior'').
-They then selected the eight artists who were mentioned by at least three of the four expert informants and who displayed a high degree of concordance across experts in terms of their aesthetic rank.
-The eight compositions the experts judged to be typical of each artist's output were selected for guided interviews with forty first-generation Latinx immigrants in the Netherlands and Switzerland (there were no relevant cross-country differences).
-The most highly regarded expert pieces belonged to the sub-genre ``classic salsa,''---essentially early salsa performers that set the standard in the 1960s, 1970s, and 1980s---the middlebrow pieces were mainly variants of ``romantic salsa.'' The less aesthetically worthy pieces generally belonged to more recent styles of ``pop salsa styles.'' Note that this establishes a strict alignment between microgenre aesthetic standing and the historical sequencing of microgenre emergence within the salsa musical field.
+They then selected the eight artists mentioned by at least three of the four expert informants who displayed a high degree of concordance across experts in terms of their aesthetic rank.
+Eight compositions experts judged typical of each artist's output were used in guided interviews with forty first-generation Latinx immigrants in the Netherlands and Switzerland (there were no relevant cross-country differences).
+The most highly regarded expert pieces belonged to the sub-genre ``Classic Salsa''---essentially early salsa performers that set the standard in the 1960s, 1970s, and 1980s---the middlebrow pieces were mainly variants of ``romantic salsa.'' The less aesthetically worthy pieces generally belonged to more recent, radio-friendly styles of ``pop salsa.'' Note that this establishes a strict alignment between microgenre aesthetic standing and the historical sequencing of microgenre emergence within the salsa musical field.
 We should thus expect this to be reflected in the generational location of each microgenre audience.
@@
 More educated respondents gravitated towards classic salsa and explicitly denigrated audiences that went for more popular styles---enacting a version of Ien Ang's \citeyearpar{ang2000dallas} ``ideology of mass culture'' in this field.
-High status respondents emphasized compositional and thematic complexity over ``fun'' aspects like rhythm and ``danceability,'' elements crucial in working-class Latinx immigrants' explanations for why they gravitated towards more romantic and pop styles (finding classic salsa sleepy and boring).
-Importantly, ``expert consumers'' (people who worked in the musical field in some capacity) demonstrated the same aestheticized appreciation for classic salsa and rejection of popular styles regardless of their class background.
+High-status respondents emphasized compositional and thematic complexity over ``fun'' aspects like rhythm and ``danceability,'' elements crucial in working-class Latinx immigrants' explanations for why they gravitated towards more romantic and pop styles (finding classic salsa sleepy and boring).
+Importantly, ``expert consumers'' (people who worked in the musical field in some capacity) demonstrated the same aestheticized appreciation for classic salsa and rejection of popular styles regardless of class background.
 \citep[][62]{Bachmayer2014-pk} conclude that ``[t]aste in salsa music shows a strong internal, hierarchical order between `artistic' versus `popular' styles that \ldots structures the taste patterns of different social classes.''
@@
 \subsubsection{Salsa Microgenre Analysis}
-Table~\ref{tab:reg} shows the result of a series of regression analysis analogous to those I specified for the three Metal microgenres, but this time using binary variables indexing choices of the three Salsa microgenres as outcomes (see Figure~\ref{fig:dend-micro-salsa}).
+Table~\ref{tab:reg} shows the result of a series of regression analyses analogous to those I specified for the three Metal microgenres, but this time using binary variables indexing choices of the three Salsa microgenres as outcomes (see Figure~\ref{fig:dend-micro-salsa}).
 The first column shows a model predicting choosing the ``Latin/Spanish/Salsa" macrogenre label using the usual socio-demographic covariates.
-The next three columns show the predictors of choosing each microgenre variation extracted from cutting the macrogenre label branch of the dendrogram at the required height.
+The following three columns show the predictors of choosing each microgenre variation extracted from cutting the macrogenre label branch of the dendrogram at the required height.
 Looking at the first column, we would have concluded that choosing Salsa is not predicted by either respondent's ($p = 0.26$) or parent's ($p = 0.17$) education, suggesting that taste for this genre is orthogonal to cultural capital and status.
@@
 Like Metal, the microgenre analysis tells a different story.
-Looking at the third column of the table, predicting choice for the second of the induced microgenres, we find that, indeed, there is a Salsa microgenre statistically more likely to be preferred by people of high education whose parents are also more likely to be highly educated ($p < 0.05$).
+Looking at the third column of the table, predicting choice for the second of the induced microgenres, we find that, indeed, there is a Salsa microgenre statistically more likely to be preferred by highly educated people whose parents are also more likely to be highly educated ($p < 0.05$).
 Moreover, the age effect on the choice of this microgenre is \textit{reversed} compared to baseline expectations from the macrogenre regression.
 This microgenre is more likely to be preferred by older respondents (see Figure~\ref{fig:age-salsa}).
-In this way, this microgenre contrasts strongly with the first one extracted by the link clustering procedure, which is overwhelmingly more likely to be preferred by younger respondents, and also with the third one, which has a relatively flat age gradient.
+This microgenre contrasts strongly with the first one extracted by the link clustering procedure, which is overwhelmingly more likely to be preferred by younger respondents, and the third one, which has a relatively flat age gradient.
 
@@
 
-A resurgent line of critics questions whether the labels that appear in our most venerable survey-based studies are true ``genres'' in the sociological (or even stylistic) sense \citep{lena2015relational, vlegels2015music}.
+A resurgent line of critics question whether the labels that appear in our most venerable survey-based studies are true ``genres'' in the sociological (or even stylistic) sense \citep{lena2015relational, vlegels2015music}.
 The labels are broad, likely to be interpreted by people in heterogeneous ways, and thus hide as much as they reveal.
 I noted recent attempts to drop the idea of vague macrogenre labels and either study actual sociological genres on the ground (thus partially abandoning studies of audience segmentation or at least radically reconfigure them) or ``dropping the label'' \citep{sonnett2016ambivalence} by querying people about more focused objects of taste (e.g., performers within genres).
-These are all important and good developments, but we also noted that they may throw away a good thing.
+These are all essential and good developments, but we also noted that they may throw away a good thing.
 Upping the relationality by exploiting hidden patterns in the same old vague macrogenre data collected before can reveal focused microgenres.
@@
 I proposed to do this using recent developments in the discovery of \textit{overlapping communities} in networks \citep{ahn_etal10}, which partially answers two of the challenges of macrogenre critics: The fact that actual genres are overlapping and not crisply bounded, and the fact that there is hidden heterogeneity within the broad labels we usually focus on.
-As revealed by the two macrogenre ``case studies,'' focusing on microgenres reveals variations and patterns of cultural choice (as well as audience segmentation) that we would not have noticed using the standard approach (in this, the critics are right).
+As revealed by the two macrogenre ``case studies,'' focusing on microgenres shows variations and patterns of cultural choice (as well as audience segmentation) that we would not have noticed using the standard approach (in this, the critics are correct).
 Moreover, these variations capture, at a large-scale level, intuitions and suspicions people have harbored in previous work regarding those particular macrogenres levels while revealing novel insights.
-For instance, we can be pretty sure that there is indeed a version of Metal that is copacetic with the tastes of certain high-cultural capital youth cutting across gender and racial boundaries \citep{tampubolon2008revisiting}, even if most versions of Metal continue to exist within its traditional socio-demographic of less-educated white men \citep{bryson96}.
-In the same way, we can detect a clear status partition in the field Salsa music consumption, with an older elite crowd separated by a generational divide from a younger audience set, very likely keyed the distinction between the aesthetically consecrated ``classics'' and more recent popular fare \citep{Bachmayer2014-pk}.
-More importantly, for the themes we began with, we could discern these patterns of micro-variation of this \textit{without} dropping the label or querying people about hundreds of micro-styles or performers (most of which they'd be unfamiliar with).
+For instance, we can be pretty sure that there is indeed a version of Metal that is copacetic with the tastes of certain high-cultural capital youth cutting across gender and racial boundaries \citep{tampubolon2008revisiting}, even if most versions of Metal continue to exist within its traditional socio-demographic niche of less-educated white men \citep{bryson96}.
+In the same way, we can detect a clear status partition in the field of Salsa music consumption, with an older elite crowd separated by a generational divide from a younger audience set, very likely keyed the distinction between the aesthetically consecrated ``classics'' and more recent popular fare \citep{Bachmayer2014-pk}.
+More importantly, for the themes we began with, we could discern these patterns of micro-variation of this \textit{without} dropping the label or querying people about hundreds of micro-styles or performers (most of which they would be unfamiliar with).
 
-Instead, we exploited the venerable principle, etched into classical approaches to defining genres in network terms \citep{dimaggio1987classification}, noting that if genres are defined by the people who choose them, then they are also defined by the other choices that people make when they choose them; the country people combine with one version of Classical may not be the same country that combines with a version of the Blues (and neither is the same as the country that refuses to combine with any other style), nor is that Classical that combines with Country the same as others.
+Instead, we exploited the venerable principle, etched into classical approaches to defining genres in network terms \citep{dimaggio1987classification}, noting that if genres are defined by the people who choose them, then they are also defined by the other choices that people make when they choose them; the \textit{Country} people combine with one version of \textit{Classical} may not be the same \textit{Country} that combines with a version of the \textit{Blues} (and neither is the same as the \textit{Country} that refuses to combine with any other style).
+Reciprocally, neither is the \textit{Classical} that combines with \textit{Country} the same as others.
 Accordingly, the approach proposed here is ripe to be applied to all ``old'' data sources and cultural participation, potentially extracting and revealing many unexploited insights.
@@
 Nevertheless, the approach proposed here is general.
-It can be applied to studying other genre complexes beyond musical taste (allowing for economic data collection) and to studying other processes beyond taste.
+It can be applied to studying other genre complexes beyond musical taste (allowing for economic data collection) and other processes beyond taste.
 This includes belief, opinion, and attitude data.
-Essentially allows us to move from ``vague'' responses to more focused responses by exploiting the hidden patterns in the inter-response network formed when people respond to other items.
+Essentially, it enables us to move from ``vague'' responses to more focused responses by exploiting the hidden patterns in the inter-response network formed when people respond to other items.
 The same lesson learned in studying genres in the sociology of taste applies to the study of opinion and belief data more generally \citep{boutyline2017belief}.
-To the extent that these are applied to items that themselves are ``vaguely'' defined, they will also yield even vaguer (and perhaps less than useful) meta-classifications of those beliefs and attitudes (like ``liberal'' and ``conservative'').
-These are the primary ways we interpret how people split themselves into groups by the beliefs they choose to hold, but are decreasingly apt today if they ever were.
+To the extent that these are applied to items that are ``vaguely'' defined, they will yield even vaguer (and perhaps less than helpful) meta-classifications of those beliefs and attitudes (like ``liberal'' and ``conservative'').
+These are the primary ways we interpret how people split themselves into groups by the beliefs they choose to hold, but they are decreasingly apt today if they ever were.
 

### 2024-01-06 qmd/02_toy-ex.qmd
updated toy ex

@@
         column_spec(1, bold = TRUE) %>% 
-        save_kable(here("Toy", "toy-sim.png"))
-    #webshot(here("Toy", "toy-sim.html"), here("Toy", "toy-sim.png"))
+        save_kable(here("Toy", "toy-sim.html"))
+    webshot(here("Toy", "toy-sim.html"), here("Toy", "toy-sim.png"))
 
@@
         column_spec(1, bold = TRUE) %>% 
-        save_kable(here("Toy", "toy-dis.png"))
-    #webshot(here("Toy", "toy-dis.html"), here("Toy", "toy-dis.png"))
+        save_kable(here("Toy", "toy-dis.html"))
+    webshot(here("Toy", "toy-dis.html"), here("Toy", "toy-dis.png"))
 ```
@@
     hc.res$labels <- e.names
-    p <- fviz_dend(hc.res, k = 4, k_colors = "uchicago", show_labels = TRUE, cex = 1.5, lwd = 2) 
+    p <- fviz_dend(hc.res, k = 4, k_colors = "uchicago", 
+                   show_labels = TRUE, cex = 1.5, lwd = 2) 
     p <- p + geom_hline(yintercept = 0.75, 
@@
                         color = "red", 
-                        size = 1.2)
+                        linewidth = 1.2)
     p <- p + labs(y = "", title = "") 

### 2024-01-06 main.tex

@@
 \usepackage{geometry}
+\usepackage{url}
 \usepackage{tablefootnote}
@@
 I address the microgenre issue using a technique for overlapping community detection called \textit{link clustering} \citep{ahn_etal10}.
-The basic idea is simple and illustrated in the toy example in Figure~\ref{fig:link-toy1}.\footnote{Code to replicate all of the analyses reported in this paper and software implementing the link clustering procedure, can be found at \nolinkurl{https://github.com/olizardo/Discovering-Focused-Microgenre-Communities}}.
+The basic idea is simple and illustrated in the toy example in Figure~\ref{fig:link-toy1}.\footnote{Code to replicate all of the analyses reported in this paper and software implementing the link clustering procedure, can be found at \url{https://github.com/olizardo/Discovering-Focused-Microgenre-Communities}}.
 Breaking with approaches that attempt to cluster people and genres by focusing on the people or the genres, we take the person-to-genre {\em link} as the unit of analysis and focus our classification energies on those.
@@
 
+% Answer: [trim={left bottom right top},clip]
 \begin{figure}
@@
      \begin{subfigure}[b]{0.4\textwidth}
-        \includegraphics[width=1.0\textwidth]{Toy/toy-sim.png}
+        \includegraphics[width=1.0\textwidth, trim={0 12cm 12cm 0},clip]{Toy/toy-sim.png}
         \caption{Edge similarity matrix from toy example.}
@@
      \begin{subfigure}[b]{0.4\textwidth}
-        \includegraphics[width=1.0\textwidth]{Toy/toy-dis.png}
+        \includegraphics[width=1.0\textwidth, trim={0 12cm 12cm 0},clip]{Toy/toy-dis.png}
         \caption{Edge distance matrix from toy example.}
@@
 Recall that the data features 2,263 people choosing up to 20 macrogenre labels.
-When strung out as an edgelist, this results in 9,216 person-to-genre connections in the data.
+Out of the maximum possible number of connections that could exist in this network ($2263 \times 20 = 45260$), we observe $9216$ person-to-genre links (for a density of $9216 \div 45260 = 0.20$).
+When strung out as an edge list, this results in 9,216 person-to-genre connections in the data.
 The resulting $9216 \times 9,216$ matrix, containing Jaccard similarities among person-to-genre links sharing a node in either of the two modes, is then the input to an agglomerative hierarchical clustering algorithm using Ward's \citeyearpar{ward63} method.
@@
 My other criterion is for debate or uncertainty in the scholarly literature regarding the existence or overall status of the presumed microgenre variations.
-Using these criteria, I settled on Heavy Metal and Latin/Spanish Music/Salsa.
+Using these criteria, I settled on Heavy Metal and Latin/Spanish/Salsa.
 As we will see, Metal fits both bills, as a lively debate already exists regarding its status as non-elite or an elite cultural form \citep{tampubolon2008revisiting}.
@@
 Tampubolon shows that including those ``don't know'' responses significantly changes things.
-Concerning Metal, it indicates that it is intensely disliked among low-education people, more than would have been surmised in Bryson's original study (because low-education people are more likely to say ``don't know'' to genre questions and are thus more likely to be dropped from the sample when these answers are also excluded), so it is not just a top-down symbolic exclusion story.
+Concerning Metal, the new analysis indicated it was intensely disliked among low-education people, more than would have been surmised in Bryson's original study (because low-education people are more likely to say ``don't know'' to genre questions and are thus more likely to be dropped from the sample when these answers are also excluded), so it is not just a top-down symbolic exclusion story.
 For Tampubolon, this makes Metal ``quite exceptional'' since it is disliked across the board and even more by people with low education.
 
-Tampubolon's work indicates that because Metal's audience is composed of people with low education, it does not mean that the rest of the less-educated population loves it; they hate it passionately.
+Tampubolon's work indicates that observing Metal's audience being composed of people with low education does not mean that the rest of the (non-Metalhead) less-educated population loves it; they hate it passionately.
 Tampubolon's analysis of ``Like'' responses also shows that Metal, rather than being exclusively preferred by a univorous group of ``Metalheads'' (who only like metal and dislike everything else), also makes it into the taste profile of one of two omnivorous groups uncovered in his analysis.
@@
 
-Instead, we exploited the venerable principle, etched into classical approaches to defining genres in network terms \citep{dimaggio1987classification}, noting that if genres are defined by the people who choose them, then they are also defined by the other choices that people make when they choose them; the \textit{Country} people combine with one version of \textit{Classical} may not be the same \textit{Country} that combines with a version of the \textit{Blues} (and neither is the same as the \textit{Country} that refuses to combine with any other style).
+Instead, we exploited the venerable principle, etched into classical approaches to defining genres in network terms \citep{dimaggio1987classification}, noting that if genres are defined by the people who choose them, then they are also defined by the other choices that people make when they choose them; the \textit{Country} people combine with one version of \textit{Classical} may not be the same \textit{Country} that combines with a version of the \textit{Indie or Alternative Rock}, and neither is the same as the \textit{Country} that refuses to combine with any other style \citep{lembo2017three}.
 Reciprocally, neither is the \textit{Classical} that combines with \textit{Country} the same as others.

### 2024-01-07 title-page.tex
Updated title page

@@
 
-\title{From Macrogenres to Microgenres via Relationality\footnote{Reserved for acknowledgements.}}
+\title{From Macrogenres to Microgenres via Relationality\footnote{Previous versions of this paper were presented at the University of Notre Dame Sociology Department Culture Workshop, the University of Arizona School of Sociology Brown Bag Series, the Duke University Department of Sociology Jensen Lecture Series, and as a keynote address at the Understanding Everyday Participation Project Closing Conference in Manchester, UK, where I received incisive feedback and questions from various audience members, most of which was incorporated into the first completed draft of the paper.
+Particular thanks go to Vaughn Schmutz and three \textit{Poetics} anonymous readers whose comments, suggestions, and challenges greatly improved the initial submission.}}
 

### 2024-01-07 main-elsevier.tex
Final submission

--- 2024-01-06 main.tex
@@
-\documentclass[a4paper,12pt]{extarticle}
+\documentclass[a4paper,12pt]{article}
 \usepackage[utf8]{inputenc}
@@
      \begin{subfigure}[b]{0.6\textwidth}
-        \includegraphics[width=1.0\textwidth]{Toy/link-clust-toy1.png}
+        \includegraphics[width=1.0\textwidth]{link-clust-toy1.png}
         \caption{Two person-genre edges sharing the same genre.}
@@
      \begin{subfigure}[b]{0.3\textwidth}
-        \includegraphics[width=1.0\textwidth]{Toy/link-clust-toy2.png}
+        \includegraphics[width=1.0\textwidth]{link-clust-toy2.png}
         \caption{Similarity between person-genre edges depends on the other genres people are linked to.}
@@
      \begin{subfigure}[b]{0.4\textwidth}
-        \includegraphics[width=1.0\textwidth, trim={0 12cm 12cm 0},clip]{Toy/toy-sim.png}
+        \includegraphics[width=1.0\textwidth, trim={0 12cm 12cm 0},clip]{toy-sim.png}
         \caption{Edge similarity matrix from toy example.}
@@
      \begin{subfigure}[b]{0.4\textwidth}
-        \includegraphics[width=1.0\textwidth, trim={0 12cm 12cm 0},clip]{Toy/toy-dis.png}
+        \includegraphics[width=1.0\textwidth, trim={0 12cm 12cm 0},clip]{toy-dis.png}
         \caption{Edge distance matrix from toy example.}
@@
      \begin{subfigure}[b]{0.6\textwidth}
-        \includegraphics[width=1.0\textwidth]{Toy/link-clust-toy.png}
+        \includegraphics[width=1.0\textwidth]{link-clust-toy.png}
         \caption{Dendrogram from Ward clustering of toy example edge distance matrix cut at four clusters.}
@@
         \centering
-        \includegraphics[width=1.0\textwidth]{Plots/Dend/macro.png}
+        \includegraphics[width=1.0\textwidth]{macro.png}
         \caption{c = 8, k = 20}
@@
         \centering
-        \includegraphics[width=1.0\textwidth]{Plots/Dend/macro-lab.png}
+        \includegraphics[width=1.0\textwidth]{macro-lab.png}
         \caption{c = 8, k = 20}
@@
         \centering
-        \includegraphics[width=1.0\textwidth]{Plots/Dend/metal-branches.png}
+        \includegraphics[width=1.0\textwidth]{metal-branches.png}
         \caption{k = 3}
@@
         \centering
-        \includegraphics[width=1.0\textwidth]{Plots/Dend/salsa-branches.png}
+        \includegraphics[width=1.0\textwidth]{salsa-branches.png}
         \caption{k = 3}
@@
     \end{subfigure}
-    \caption{}
+    \caption{Dendrograms from link clustering procedure on real data.}
     \label{fig:dend}
@@
      \begin{subfigure}[b]{0.9\textwidth}
-        \includegraphics[trim={0 10cm 7cm 0},clip, width=1.0\textwidth]{Tabs/reg-tab-metal.png}
+        \includegraphics[trim={0 10cm 7cm 0},clip, width=1.0\textwidth]{reg-tab-metal.png}
         % trim={<left> <lower> <right> <upper>}
@@
      \begin{subfigure}[b]{0.9\textwidth}
-        \includegraphics[trim={0 10cm 7cm 0},clip, width=1.0\textwidth]{Tabs/reg-tab-salsa.png}
+        \includegraphics[trim={0 10cm 7cm 0},clip, width=1.0\textwidth]{reg-tab-salsa.png}
     \end{subfigure}
@@
         \centering    
-        \includegraphics[width=1.0\textwidth]{Plots/Micro/micro-by-age-metal.png}
+        \includegraphics[width=1.0\textwidth]{micro-by-age-metal.png}
         \caption{}
@@
         \centering    
-        \includegraphics[width=1.0\textwidth]{Plots/Micro/micro-by-age-salsa.png}
+        \includegraphics[width=1.0\textwidth]{micro-by-age-salsa.png}
         \caption{}
@@
     \end{subfigure}
+    \caption{Age effects on Metal and Salsa microgenres.}
 \end{figure}

### 2024-01-07 title-page.tex
Final submission

--- 2023-08-05 title-page.tex
@@
 
-\title{From Macrogenres to Microgenres via Relationality\footnote{Reserved for acknowledgements.}}
+\title{From Macrogenres to Microgenres Via Relationality\footnote{Previous versions of this paper were presented at the University of Notre Dame Sociology Department Culture Workshop, the University of Arizona School of Sociology Brown Bag Series, the Duke University Department of Sociology Jensen Lecture Series, and as a keynote address at the Understanding Everyday Participation Project Closing Conference in Manchester, UK, where I received incisive feedback and questions from various audience members, most of which was incorporated into the first completed draft of the paper.
+Particular thanks go to Vaughn Schmutz and three \textit{Poetics} anonymous readers whose comments, suggestions, and challenges greatly improved the initial submission.}}
 
